### 2019-09-04 NewMonti24.tex
corrections up to page 7

%\documentclass[pra,showpacs,twocolumn]{revtex4}

\documentclass[preprint,showpacs,pra]{revtex4-1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multirow}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2953}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%TCIDATA{LastRevised=Thursday, March 07, 2019 14:11:39}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\input{tcilatex}
\begin{document}

\title{Ionization of molecules by multicharged bared ions by using the \
stoichiometric model }
\author{author}
\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
\author{author}
\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
\affiliation{Fac. de Ciencias Exactas y Naturales, Universidad de Buenos Aires}
\date{\today }

\begin{abstract}
\end{abstract}

\pacs{79.20.Rf, 68.49.Bc, 34.20.Cf,34.50.-s,34.35.+a}
\maketitle

\section{INTRODUCTION}

The damage caused by the impact of multi-charged heavy projectile has 
become a field of interest because of the use in ion-beam cancer therapy.
The effectiveness of the radiation depends on the choice of the ions. 
In particular, theoretical and experimental studies with different 
projectiles concluded that charged carbon ions could be the most suitable 
ion to use. This result opens a new challenge for the theoretical point 
of view since multi-charged atoms at not-so-high-velocities depart from 
the first Born approximation, which is the most popular theory used in 
this field. The first Born approximation, as any perturbative direct 
calculation, warrants the $Z^{2}$ laws, where $Z$ is the projectile 
charge. However the damage concentrated in the vicinities of the Bragg 
peak correspond to energies of hundreds of KeV/amu, that is in the 
intermediate energy region. Precisely in this region,  the Born 
approximation starts to fail. Another problem arises from the theoretical 
point of view; we are dealing with complex molecules. This article deals 
precisely with theses two items. First, we perform more appropriate 
calculations on the primary damage mechanism, i.e., atomic ionization by 
multi-charged ions, which can replace the Born results. Second, 
we use and inspect the stoichiometric model, which reduces a molecule 
to a sum of atomic processes quantities weighted by the numbers of such 
atom in the molecule.

Since we have to deal with multi-charged ions, we resort to the 
Continuum Distorted Wave-Eikonal Initial State (CDW for short) which 
includes higher perturbative corrections. We start from the premise 
that the ionization process is the mechanism that deposits the most 
significant primary energy. This process produces an electron-energy 
spectrum that needs to be integrated. Also, these ejected electrons 
become a new source of local damage, which requires to be investigated 
because these quantities are used in Monte Carlo simulations. With 
this end in mind, we calculate not only the ionization cross-sections 
but also energy and mean angular values of the emitted electrons.

To deal with the molecules, we resort to the simplest stoichiometric 
model (SSM): we assume that the molecule is composed of isolated 
independent atoms. In all cases, the total cross-section is simply 
the sum of the cross-section of each atom.

With these two tools in mind, i.e., CDW instead of Born approximation 
and the SSM, we calculate ionization cross-section of different 
molecules (see Table~\ref{tab:families}) by the impact of antiprotons,
H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$,\ and O$^{8+}$. In particular, 
in Section 3, we are interested in DNA molecules such as Adenine, 
Timine, Cytosine, Guanine, Uracil, and DNA backbone.

The results are processed to test the Toburen scaling rule, which 
states that the ratio of the ionization cross-section divided by 
the number valence electrons (outer electrons) plotted in terms of
the projectile velocity can be arranged in a narrow universal band.
We have also applied this rule to several hydrocarbons and piramide 
molecules. We will prove that the width of the resulting universal 
band can be significantly reduced if we redefine the effective valence 
electrons as in Section 3.2.

It is well known that the residual electrons from the ionization 
process cause biological damage. To inspect this mechanism, in 
Section 3.3 and 3.4, we have calculated the mean electron energy 
an angular values. To our surprise, we found a substantial dependence 
of the charged projectile, which is unexpected in the first 
Born approximation.

To deal with projectiles of hefty charges, we resort to the CDW. 
However, the stoichiometric model used seems to be very simplistic 
since it considers each atom as neutral, which is not correct. 
In Section 3.5, we used the molecular electronic structure code 
{\sc gamess}~\cite{gamess} to calculate the excess or defect of 
electron density one each atom. With this knowledge, we modify the 
simple stoichiometric model to account for the departure from 
neutrality. We find that, for the DNA molecules, this modification 
does not introduce a substantial change.

\section{THEORY: IONIZATION OF ATOMS}

In our study, we will consider six atoms $\alpha=$ H, C, N, O, P, and S. 
Most of the organic molecules are composed of these atoms. Some 
particular molecules also include halogen atoms such as fluor and 
bromine; ionization cross-sections of these elements have been 
previously published~\cite{miraglia2008,miraglia2009}.

Total ionization cross-sections of these atoms were calculated using 
the CDW. The initial bound and final continuum radial wave functions 
were obtained by using the{\sc radialf} code developed by Salvat and 
co-workers, using a Hartree-Fock potential obtained from the 
Depurated Inversion Model~\cite{mendez2016,mendez2018}. 
We used a few thousand pivot points to solve the Schr\"{o}dinger 
equation, depending on the number of oscillations of the continuum 
state. The radial integration was performed using the 
cubic spline technique. The number of angular momenta considered 
varied from 8, at very low ejected-electron energies, up to 30, 
for the highest energies considered. The same number of azimuth 
angles were required to obtain the four-fold differential 
cross-section. The calculation performed does not display prior-post 
discrepancies at all. Each atomic total cross-section in Eq (1) was 
calculated using 35 to 100 momentum transfer values, 28 fixed 
electron angles, and around 45 electron energies depending on the 
projectile impact energy. See further details of the calculation 
in Ref.~\cite{montanari2017}. Simultaneously, we will be reporting 
state to state ionization cross sections for these cases in 
Ref.~\cite{miraglia2019}, which will be very useful to estimate 
molecule fragmentation.

In Figure 1, we report our results of total ionization of the six 
essential elements by the impact of six different projectiles, i.e., 
antiprotons, H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$. 
To reduce the resulting 36 magnitudes into a single consistent 
figure, we use the fact that in the first Born approximation, 
the ionization cross-section scales with the square of the projectile 
charge, i.e., $Z^{2}$. The values of the impact energies considered 
range between 0.1 to 10 MeV/amu, i.e., where the CDW is supposed 
to hold. In fact, for the highest projectile charges the minimum 
impact energy where the CDW is expected to be valid could be 
higher than 100 KeV. From some MeV/amu on, the first the Born 
approximation provides quite reliable results and using a much 
simpler formalism; we check it. We use the same color to indicate 
the projectile charge in all figures of this work: dashed-red, 
solid-red, blue, magenta, olive and orange for antiprotons, 
H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$, respectively. 
Notably, there is no complete tabulation of ionization of atoms by 
the impact of multiple-charged ions. We hope that the ones presented 
in this article will be helpful.

\section{IONIZATION OF MOLECULES}

\subsection{The stoichiometric model}

Lets us consider a molecule $M$ composed by $n_{\alpha}$ atoms of the
element $\alpha$, the SSM describes the total ionization cross section 
of the molecule $\sigma_{M}$ as a simple sum of ionization cross 
sections of the isolated atoms $\sigma_{\alpha}$, i.e.,
\begin{equation}
 \sigma_{M}=\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}\,.  
 \label{10}
\end{equation}
We divided sixteen molecular targets of our interest in 3 families. 
The classification we defined is given in Table~\ref{tab:families}.

\begin{table}
\begin{tabular}{|p{0.06\textwidth}|p{0.525\textwidth}|}
\hline
 CH  & CH$_4$, C$_2$H$_2$, C$_2$H$_4$, C$_2$H$_6$, and C$_6$H$_6$ \\
\hline
 CHN & C$_5$H$_5$N, C$_4$H$_4$N$_2$, C$_2$H$_7$N, and CH$_5$N \\
\hline
 \multirow{4}{*}{DNA} & adenine (C$_5$H$_5$N$_5$), timine (C$_5$H$_6$N$_2$O$_2$), \\
     & cytosine (C$_4$H$_5$N$_2$O), guanine (C$_5$H$_5$N$_5$O), \\
     & uracil (C$_4$H$_4$N$_2$O$_2$), DNA backbone (C$_5$H$_{10}$O$_5$P), \\
     & dry DNA (C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$)\\
\hline
\end{tabular}
\caption{Sixteen molecular targets of our interest classified in 3 
\label{tab:families}
families.}
\end{table}

In Figure 2, we report the total ionization cross sections by the 
impact of multicharged ions for the four fundamental DNA components: 
adenine, timine, cytosine, and guanine. Our reports for uracil and 
DNA backbone containing P are given in Figure 3. For adenine, the 
agreement with the three experiments available in our range of validity 
is quite good. For uracil, we have a puzzling situation: our results 
show good agreement with the experiments by proton impact of Itoh 
{\it et al.}~\cite{itoh2013}, but for the same target our theory fails 
by a factor of two for the impact of C$^{4+}$ and O$^{6+}$ ions. 
Nonetheless, it should be stated that our theoretical results coincide 
with the ones by Champion, Rivarola and 
collaborators~\cite{champion2012,agnihotri2012}, which may indicate a 
possible misstep of the experiments.

\subsection{Scaling rule}

The first attempt to develop a comprehensive but straightforward 
phenomenological model for electron ejection from large molecules was 
posed by Toburen and collaborators~\cite{toburen1975,toburen1976}. 
The authors found it convenient to scale the experimental ionization 
cross section in terms of the number of outer or weakly bound valence 
electrons (total number of electrons minus the inner-shell ones). 
We introduce the cross section per weakly bound electron or ionization 
cross section per valence electron, $\sigma_{e}$, as
\begin{equation}
\sigma_{e}=\frac{\sigma_{M}}{N_{M}}=\frac{\sum\limits_{\alpha}
n_{\alpha}\sigma_{\alpha}}{\sum\limits_{\alpha}n_{\alpha}v_{\alpha}}
=\sigma_{e}(v)\,, 
\label{27} 
\end{equation}
where
\begin{equation}
v_{\alpha}=\left\{ 
\begin{array}{ll}
4, & \text{for C,} \\ 
5, & \text{for N and P,} \\ 
6, & \text{for O and S,}
\end{array}\right.
\label{eq:nelec} 
\end{equation}
and $v_{H}=1$. The Toburen rule can be stated by saying that 
$\sigma_{e}$ is a \textit{universal} parameter independent on the 
molecule, which depends solely on the impact velocity. 
In Ref.~\cite{toburen1976}, it was found experimentally that for proton 
impact on some simple molecules, $\sigma_{e}$ results
\begin{equation}
\begin{array}{cccc}
E\text{(MeV)}               & 0.25 & 1.00 & 2.00 \\ 
\sigma_{e} (10^{-16}cm^{2}) & 0.39 & 0.17 & 0.11
\end{array}
\label{30}
\end{equation}
with an estimated error of about 20\%. A similar ratio was found in 
Ref.~\cite{itoh2013} for proton impact on uracil and adenine. 
Figure 5a shows $\sigma_{e}$ calculated with the CDW as a function of 
the impact velocity for different projectile charges computed with the 
SSM for the sixteen molecular targets displayed in 
Table~\ref{tab:families}. The universality with $Z$ is the one provided 
by Born approximation, i.e., $\sigma _{e}(Z)=Z^{2}\sigma_{e}(Z=1)$, 
and it holds for large impact velocities, as shown Figure 5a.
Obviously, for lower impact velocities the distorted wave CDW breaks 
this behavior discarding the rule $Z^{2}$. Although the Toburen rule 
holds for high energies, its performance is still not satisfactory: 
the universal band is quite broad. The departure of our theoretical 
results from the Toburen rule can be easily explained by the fact that 
our atomic cross sections $\sigma_{\alpha}$ behave differently for 
each atom in terms of the projectile charges. By inspecting Figure 1, 
one can easily see that the rule $\sigma_{\alpha}/v_{\alpha}\sim
\sigma_{e}$ is not well satisfied by the CDW. A much better general 
atomic rule is given by
\begin{equation}
\sigma_{e}^{\text{CDW}}=\frac{\sum\limits_{\alpha}
n_{\alpha}\sigma_{\alpha}^{\text{CDW}}}{\sum\limits_{\alpha}n_{\alpha}
v_{\alpha}^{\text{CDW}}},
\label{32} 
\end{equation}
where 
\begin{equation}
v_{\alpha }^{\text{CDW}} \sim\left\{ 
\begin{array}{ll}
4,\ \ \  & \text{for C, N, and O,} \\ 
4.5,\ \  & \text{for P and S}
\end{array}
\right. 
\label{35}
\end{equation}
and, obviously, $v_{H}^{\text{CDW}}=1$. The cross sections 
$\sigma_{e}^{\text{CDW}}$ 
are plotted in Figure 5b. A much better sharp band is observed, 
especially at high energy, where the theory is expected to work. It 
will be interesting for experiments to tune up this theoretical 
prediction.

\subsection{Emitted electron energies}

In a given biological medium, direct ion ionization accounts for just 
a fraction of the overall damage. Secondary electrons, as well as 
recoil target ions, also contribute substantially to the total damage. 
We can consider the single differential cross section of the shell 
$nl$ of the atom $\alpha$, $d\sigma _{\alpha nl}/dE$, to be a function 
of the ejected electron energy $E$ as a simple distribution 
function~\cite{surdutovic2018}. Then, we can define the mean value 
$\overline{E}_{\alpha}$ as in Ref.~\cite{abril2015},
\begin{eqnarray}
\overline{E}_{\alpha} &=&\frac{\langle E_{\alpha}\rangle}{\langle
1\rangle}=\frac{1}{\sigma_{\alpha}}\sum\limits_{nl}\int dE\,E
\frac{d\sigma_{\alpha,nl}}{dE}\,,  
\label{40} \\
\langle 1\rangle &=&\sigma_{\alpha}=\sum\limits_{nl}\int dE\,
\frac{d\sigma_{\alpha,nl}}{dE}\,,  
\label{50}
\end{eqnarray}
where $\Sigma_{nl}$ takes into account the sum of the different 
sub-shell contributions of the element $\alpha$.

Figure 5 shows $\overline{E}_{i}$ for six elements from 
Table~\ref{tab:families}. The range of impact velocities was shorten up 
to $v=10$ because of a numerical limitation in the spherical harmonics 
expansion. In our theoretical treatment, we expand our final continuum 
wave function as per usual,
\begin{equation}
\psi_{\overrightarrow{k}}^{-}(\overrightarrow{r})=\sum_{l=0}^{l_{\max
}}\sum_{m=-l}^{l}R_{kl}^{-}(r)Y_{l}^{m}(\widehat{r})Y_{l}^{m^{\ast }}
(\widehat{k})\,.
\label{60}
\end{equation}
We are confident with our calculations up to $l_{\max}\sim 30$. 
As the impact velocity $v$ increases, so do $\langle E_{\alpha}\rangle$
and $l_{\max}$, which results in the inclusion of very oscillatory 
functions in the integrand. Furthermore, the integrand of
$\langle E_{\alpha}\rangle$ includes the kinetic energy $E$
(see Eq.~(\ref{40}), which cancels the small energy region and 
reinforces the large values, making the result more sensible to large
angular momenta. Regardless, for $v>10,$ the first Born approximation 
holds.

In Figure 5, we estimate $\overline{E}_{\alpha}$ in the 0.5--2 a.u.
velocity range, or equivalently from 15 to 50 eV, for all the targets.
Our results agree with the experimental findings~\cite{surdutovic2018}. 
The dependence with the projectile charge $Z$ is surprisingly sensible,
which can duplicate the proton results. This effect can be attributed 
to the depletion caused by the multicharged ions to the yields of low 
energy electrons. In the high electron energy regime, the CDW falls on 
the simple first Born approximation, surviving the simple $Z^{2}$ law.
Then, the ratio in Eq.~(\ref{40}) cancels out and 
$\overline{E}_{\alpha}$ becomes a universal value independent on $Z$.

Extending the simple stoichiometric model for the mean electron energy
calculation, it results
\begin{equation}
\overline{E}_{M}=\frac{\sum\limits_{\alpha}n_{\alpha}
\overline{E_{\alpha}}}{\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}}.
\label{70}
\end{equation}
For impact of H$^{+}$ and He$^{2+~}$ on water at 1 MeV/amu we obtain of 
$\overline{E}_{H_{2}O}=$43.7 \ and 45eV, while the experiments on liquid
water Pimblott and LaVerne [] found \ 51.5 and 52.2 eV, respectively. 
Just to stress the importance of the projectile charge, for O$^{8+}$ on 
water at the same impact energy 1 MeV/amu we, obtain 
$\overline{E}_{H_{2}O}=54.7$ eV, i.e. 25\% larger than proton impact. 
We recall here that there should not be any difference if the 
calculation is carried in first Born approximation. We will came back
on this issue

\subsection{Emitted electron angles}

As mentioned before, secondary electrons contribute to the total damage. It
is important not only the ejection energy but also the angle of emission. In
similar fashion, we can consider the magnitude $d\sigma _{\alpha
,nl}/d\Omega $ \ -i.e. the single differential cross section in terms of the
ejected electron solid angle $\Omega $ -\ as a distribution function, and
define the mean angle $\overline{\theta }_{\alpha }$ as

\begin{equation}
\overline{\theta }_{\alpha }=\frac{\langle \theta _{\alpha }\rangle }{%
\langle 1\rangle }=\frac{1}{\sigma _{\alpha }}\sum\limits_{nl}\int d\Omega
\ \theta \ \frac{d\sigma _{\alpha ,nl}}{d\Omega }
\end{equation}%
Figure 6 shows $\overline{\theta }_{\alpha }$ for our six elements of
interest. Again here we observe an important dependence dependence of $%
\overline{\theta }_{\alpha }\ $with $Z.$ It is the common view 
\cite{Rudd1992} that the angular dispersion of emitted electrons are nearly
isotropic due to the fact that angular anisotropy of sub-50-eV yield is not
significant. A typical used value of ejection angle is about $\overline{%
\theta }_{\alpha }\sim $70 degrees \cite{surdutovic2018} and this quite
correct in the range of validity of the first Born approximation for any
target. But when a distorted wave approximation is used as observed in
Figure 6, $\overline{\theta }_{\alpha }$ decreases substantially with $Z$ in
the intermediate energy region. For example for C$^{6+}$ impact the Bragg
peak occurs at 0.3 MeV/amu where \ $\overline{\theta }_{\alpha }$ calculated
in CDW is about the half of the one calculated with the First Born
approximation. \ This correction should close the damage to the forward
direction.

The only responsible of this correction is the\ capture to the continuum
effect: the larger the charge $Z$ the smaller $\overline{\theta }$ will be,
of course at intermediate energies, not at high impact energies where the
Born approximation rules. One illustrative observation is the behavior of
antiprotons: the projectile in this case repels the electrons \ making the
distribution almost symmetric. Note the opposite effect of proton and
antiprotons, they run one oppose to the other one, as compared with the
first Born approximation.

\subsection{A modified stoichiometric model}

One can correctly argue that\ the SSM considers an assembly of isolated
neutral atoms which is definitively unrealistic. A first improvement is to
consider that the atoms are not neutral and within the molecule they have
more or less electrons given by a \ charge $q_{\alpha }$. One parameter that
measures $q_{\alpha }$ is the Mulliken charge. This is not the only one,
there is a large variety of charges such as the net or natural atomic charge 
\cite{lee2003}, the lowin charge, etc.

Consider\ that the total amount of electrons $Q_{\alpha }\ $on element $%
\alpha $ are equally distributed on all the atoms $\alpha ,$ therefore each
element $\alpha \ $\ will have a an additional charge: $q_{\alpha
}=Q_{\alpha }/n_{\alpha }$. positive or negative depending on the relative
electronegative value respect to the other ones~\cite{rappe1991}. Instead
of the integer number of elements $n_{\alpha }$ of the atom $\alpha$, it
could be argued that we have now an continuous number of atoms given by 
\begin{equation}
n_{\alpha }^{\prime }=n_{\alpha }-\frac{q_{\alpha }}{v_{\alpha }^{CDW}}
\label{100}
\end{equation}%
In the case of neutral atoms $q_{\alpha }=0,$ we obviously recover $%
n_{\alpha }^{\prime }=n_{\alpha }$ as before$.$

To inspect the effect of the $q_{\alpha }$ we have run GAMES with the 
6-31G basis set, including polarization functions for all the atoms. 
The calculations were carried out implementing the B3LYP 
functional~\cite{Becke1993,Stephens1994}. In Table~(\ref{110}) we display
$q_{\alpha }$ of the different DNA basis and in the last column we rewrite
the new stoichiometric expression. 
\begin{equation}
\begin{array}{|l|l|l|l|l|l|}
\hline
\text{Element}\,\,\,  & \mathrm{H} & \mathrm{C} & \mathrm{N} & \mathrm{O} & \text{New stoichiometry} \\ \hline
\mathrm{Adenine}  & +0.32 & -0.55 & +0.23 &       & \mathrm{C}_{4.92}\mathrm{H}_{5.14}\mathrm{N}_{4.77} \\ \hline
\mathrm{Thymine}  & +0.20 & -0.54 & +0.19 & -0.52 & \mathrm{C}_{4.95}\mathrm{H}_{6.13}\mathrm{N}_{1.95}\mathrm{O}_{2.13} \\ \hline
\mathrm{Cytosine} & +0.28 & -0.56 & +0.21 & -0.53 & \mathrm{C}_{3.93}\mathrm{H}_{5.14}\mathrm{N}_{2.79}\mathrm{O}_{1.13} \\ \hline
\mathrm{Guanine}  & +0.46 & -0.58 & +0.20 & -0.36 & \mathrm{C}_{4.89}\mathrm{H}_{5.15}\mathrm{N}_{4.80}\mathrm{O}_{1.09} \\ \hline
\end{array}
\label{110}
\end{equation}

All the previous formula holds with the simple replacement of integer value $%
n_{\alpha }$ by the continuous values\ $n_{\alpha }^{\prime }$ to produce a
new ionization cross section $\sigma ^{\prime }$

In Figure 7, we displays the relative difference of ionization cross
sections 
\begin{equation}
e=\frac{\sigma ^{\prime }-\sigma }{\sigma }\times 100  \label{120}
\end{equation}%
for the four DNA basis. The difference is \ just very few percents.
Indicating that the SSM is a quite robust model to treat the type of
molecule we are dealing with, and of course within the range error that one
can expect from the SSM.

We now return to the calculation of the mean electron energy of H$^{+}$ and
He$^{2+~}$ in water\ \ $\overline{E}_{H_{2}O}$. If we consider that \ the
residual charge of \ each hydrogen in water is $q_{H}=$+0.35 \ \cite%
{rappe1991}\ which implies that on Oxygen we have \ a residual charge of $%
q_{O}=$-0.7, we could re-write the formula of water using (\ref{120}) as H$%
_{1.3}$O$_{1.17}$ considering $n_{O}^{CDW}\simeq 4$ and $n_{H}^{CDW}\simeq
1. $ Recalculating mean electron energy by impact of \ H$^{+}$ and He$^{2+~}$
on water at 1 MeV/amu we obtain: $\overline{E}_{H_{2}O}=$46.2 \ and 47.6 eV
which compared a little better with the experiments: 51.5 and 52.2 eV \cite%
{pimblott2007}, respectively. i.e. within 10\% of the experiments which is
not bad accounting for the simplicity of our method.

Another parameter that we can calculate in our model is the fraction of
energy carried by the electron $f$ defined as%
\begin{equation}
f=\frac{\sum\limits_{\alpha }n_{\alpha }\sigma _{\alpha }\overline{%
E_{\alpha }}}{\sum\limits_{\alpha }n_{\alpha }(\sigma _{\alpha }\overline{%
E_{\alpha }}+\sum\limits_{nl}\sigma _{\alpha nl}E_{\alpha nl})}  \label{90}
\end{equation}%
Using our shell-to-shell ionization cross sections $\sigma _{\alpha nl}\ $%
\cite{miraglia2019}\ and atomic binding energies of the atom$\ \alpha ,$ $%
E_{\alpha nl}\ $\cite{clementi}, we obtain $f=$0$.70\ $and $\ 0.71$ for \ H$%
^{+}$ and He$^{2+~}$ on water at 1 MeV/amu,. which differ from the
experiments \ $f=0.81$ and $0.80$, \ respectively.

This difference with the experiment could be attributed to the difference of
binding energy between the molecular water 12.65 eV and the atomic component
H (13.6 eV) and O (17.19 eV), which is an issue beyond our independent atom
approximation and so our model cannot not accounted for. We could estimate
this contribution resorting, once more to the stoichiometric, model, we can
arriesgar a upper-limit difference per molecule of water\ as

\begin{equation}
\delta E=(13.6-12.65)1.17+(17.19-12.65)1.3=7\ \text{eV}  \label{80}
\end{equation}%
Most of this energy should be transfer to the kinetics energy of the emitted
electron. Thus we can \ add 7 eV to the previous values to give $\overline{E}%
_{H_{2}O}=$53.2 \ and 54.6 eV for \ H$^{+}$ and He$^{2+~}$ on water at 1
MeV/amu, respectively, much near to the experiments: 51.5 and 52.2 eV. If we
add $\delta E$ to the numerator of Eq.(\ref{90}) we obtain\ $f=0.81$ and $%
0.80$ in perfect agreement with the experiments (see Table 1 of Ref.(\cite%
{pimblott2007})

\section{CONCLUSIONS}

We have calculated ionization cross sections by impact of antiprotons, H$^{+}
$, He$^{2+}$, Be$^{4+}$, C$^{6+}$,\ and O$^{8+}$ with molecule involved in
biological basis containing H, C, N, O, P and S with the CDW method. \ The
importance of the influence of $Z\ $was observed in the mean energy $%
\overline{E}_{\alpha }\ $and angle $\overline{\theta }_{\alpha }.$ For a
given target $\alpha ,$ as $Z$ increases $\overline{E}_{\alpha }$ increases
but $\overline{\theta }_{\alpha }$ decreases \ At high impact energy, say
larger than 1 MeV/amu these values tend to the ones of the Born
approximation which embodies the simple Z$^{2}$ law. Sixteen molecules were
investigated using the simple stoichiometric model. Results for the six DNA
basis were presented and compared with the sparse available experiments \ We
explore the rule of Toburen which scales all the molecular ionization cross
section when divided by the number of weakly bound valence electrons $\nu
_{\alpha }$ given by Eq.(\ref{27})$.$ We have found the rule scales much
better when normalizing our theoretical ionization cross sections to the
number\ $\upsilon _{\alpha }^{\prime }$ given by Eq.(\ref{35}). And finally
we attempt to improve the stoichiometric model by the use of the Mulliken
charge to redefine a new stoichiometric model containing continuum rather
than integer proportions. NO substantial correction was found indicating
that the SSM works quite well.

Our aims is this article is to provide the tools to estimate any inelastic
parameter parameter -such as the emission angle, the emitted mean energy and
cross section- by the impact of any multicharged \ on any molecule
containing H, C, N, O, P and S, with the help of the stoichimetrical model.
Our goal was quite \textbf{pretencioso}, considering the simplicity of our
proposal. However we think our results could be used to estimate the
ionization magnitude with an acceptable level of uncertailties

\bigskip

\section{References}

\begin{thebibliography}{99}

\bibitem{gamess}
M. W. Schmidt, K. K. Baldridge, J. A. Boatz, S. T. Elbert, M. S. Gordon, 
J. H. Jensen, S. Koseki, N. Matsunaga, K. A. Nguyen, S. J. Su, T. L. Windus, 
M. Dupuis, J. A. Montgomery 
J. Comput. Chem. 14, 1347-1363 (1993)

\bibitem{miraglia2008} 
J. E. Miraglia and M. S. Gravielle. Ionization of the
He, Ne, Ar, Kr, and Xe isoelectronic series by proton impact. Phys Rev A 
\textbf{78}, 052705 (2008)

\bibitem{miraglia2009} 
J. E. Miraglia, Ionization of He, Ne, Ar, Kr, and Xe
by proton impact: Single differential distributions. Phys Rev A \textbf{79},
022708 (2009).

\bibitem{mendez2016} 
A.M.P. Mendez, D.M. Mitnik, and J.E. Miraglia.
Depurated inversion method for orbital-specific exchange potentials. 
Int. J. Quantum Chem. 24 ,116 (2016).

\bibitem{mendez2018} 
A.M.P. Mendez, D.M. Mitnik, and J.E. Miraglia. Local Effective 
Hartree--Fock Potentials Obtained by the Depurated Inversion Method,
76. (2018).

\bibitem{montanari2017} 
Ionization probabilities of Ne, Ar, Kr, and Xe by
proton impact for different initial states and impact energies. Nucl. Instr.
Meth. Phys. Res. B 407 (2017) 236-243.

\bibitem{miraglia2019} 
J. E. Miraglia. Shell-to-shell ionization cross
sections of antiprotons, H$^{+}$, \ He$^{2+},$ Be$^{4+},$ C$^{6+}$ and O$%
^{8+}$ on H, C, N, O, P, and S atoms To be published Archive 2019.

\bibitem{itoh2013} 
A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D.
Rivarola,~Cross sections for ionization of uracil by MeV-energy-proton
impact,\ Physical Review A 88, 052711 (2013)

\bibitem{} in energy and angles~,

\bibitem{champion2012} 
C Champion, M E Galassi, O Foj\'{o}n, H Lekadir, J Hanssen, R D Rivarola,
P F Weck, A N Agnihotri, S Nandi, and L C Tribedi. Ionization of RNA-uracil
by highly charged carbon ions. J. Phys.: Conf. Ser. 373, 012004 (2012).

\bibitem{agnihotri2012}
A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A.
Kumar, M. E. Galassi, R. D. Rivarola, O. Foj\'{o}n, C. Champion, J. Hanssen,
H. Lekadir, P. F. Weck, and L. C. Tribedi. Ionization of uracil in
collisions with highly charged carbon and oxygen ions of energy 100 keV to
78 MeV.\ \ Phys Rev A 85, 032711 (2012).

\bibitem{toburen1975} 
W. E. Wilson and L. H. Toburen. Electron emission from
proton ---hydrocarbon-molecule collisions at 0.3---2.0 MeV. PHYSICAL REVIEW
A\ 11 1303 (1975).

\bibitem{toburen1976} 
D. J. Lynch, L. H. Toburen, and W. E. Wilson. Electron
emission from methane, ammonia, monomethylamine, and dimethylamine by 0.25
to 2.0 MeV protons. J. Chem. Phys. 64, 2616 (1976).

\bibitem{surdutovic2018} 
Multiscale approach to the physics of radiation
damage with ions. E. Surdutovich and A. V. Solov'yov, arXiv:1312.0897v,
(2013)

\bibitem{abril2015} 
P. de Vera1, I. Abril, R. Garcia-Molina and
A.V.Solov'yov,\ Ionization of biomolecular targets by ion impact: input data
for radiobiological applications. Journal of Physics: Conference Series 438
(2013) 012015

\bibitem{lee2003} 
Jung-Goo Lee, Ho Young Jeong, and Hosull Lee, Charges of
Large Molecules Using Reassociation of Fragments. Bull. Korean Chem. Soc.24\
2003, 369 .

\bibitem{rappe1991} 
A. K. Rappe, A. K.and W. A. Goddard III,. J. Phys. Chem. 
\textbf{95 (}1991) 3358.

\bibitem{Becke1993}
A. D. Becke, 
J. Chem. Phys. 98, 5648-5652 (1993)

\bibitem{Stephens1994}
P. J. Stephens, F. J. Devlin, C. F. Chabalowski, M. J. Frisch,
J. Phys. Chem. 98, 11623-11627 (1994)

\bibitem{pimblott2007} 
S.M. Pimblott and J. A. LaVerne, Radiation
Physics and Chemistry 76, 1244-1247 (2007)

\bibitem{Rudd1992} 
M. E. Rudd, Y.-K. Kim,, D. H. Madison and T. J. Gay.
Electron production in proton collisions with atoms and molecules: energy
distributions. Rev. Mod. Phys. \textbf{64}, 44-490 (1992).

\end{thebibliography}

\end{document}

### 2019-09-05 NewMonti24.tex
checked up to section 3.4

@@
 
-\documentclass[preprint,showpacs,pra]{revtex4-1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[preprint,12pt]{article}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{amssymb}
@@
 \usepackage{multirow}
+
+\usepackage{authblk}
 
@@
 
-\input{tcilatex}
+%\input{tcilatex}
 \begin{document}
 
-\title{Ionization of molecules by multicharged bared ions by using the \
-stoichiometric model }
+\title{Ionization of molecules by multicharged bared ions by using the
+stoichiometric model}
 \author{author}
-\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
+\affil{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
 Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
-\author{author}
-\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
-Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
-\affiliation{Fac. de Ciencias Exactas y Naturales, Universidad de Buenos Aires}
+%\author{author}
+%\affil{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
+%Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
+%\affil{Fac. de Ciencias Exactas y Naturales, Universidad de Buenos Aires}
 \date{\today }
+
+\maketitle
 
@@
 
-\pacs{79.20.Rf, 68.49.Bc, 34.20.Cf,34.50.-s,34.35.+a}
-\maketitle
+%\pacs{79.20.Rf, 68.49.Bc, 34.20.Cf,34.50.-s,34.35.+a}
 
-\section{INTRODUCTION}
+\section{Introduction}
 
-The damage caused by the impact of multi-charged heavy projectile has 
-become a field of interest because of the use in ion-beam cancer therapy.
-The effectiveness of the radiation depends on the choice of the ions. 
-In particular, theoretical and experimental studies with different 
-projectiles concluded that charged carbon ions could be the most suitable 
-ion to use. This result opens a new challenge for the theoretical point 
-of view since multi-charged atoms at not-so-high-velocities depart from 
-the first Born approximation, which is the most popular theory used in 
-this field. The first Born approximation, as any perturbative direct 
-calculation, warrants the $Z^{2}$ laws, where $Z$ is the projectile 
-charge. However the damage concentrated in the vicinities of the Bragg 
-peak correspond to energies of hundreds of KeV/amu, that is in the 
-intermediate energy region. Precisely in this region,  the Born 
-approximation starts to fail. Another problem arises from the theoretical 
-point of view; we are dealing with complex molecules. This article deals 
-precisely with theses two items. First, we perform more appropriate 
-calculations on the primary damage mechanism, i.e., atomic ionization by 
-multi-charged ions, which can replace the Born results. Second, 
-we use and inspect the stoichiometric model, which reduces a molecule 
-to a sum of atomic processes quantities weighted by the numbers of such 
-atom in the molecule.
+The damage caused by the impact of multicharged heavy projectile has 
+become a field of interest because of its implementation in ion-beam 
+cancer therapy. The effectiveness of the radiation depends on the 
+choice of the ions. In particular, theoretical and experimental studies 
+with different projectiles have concluded that charged carbon ions 
+could be the most suitable ions to use. The study of such systems 
+represent a challenge from the theoretical point of view. The most 
+widely used method to compute ionization of multicharged atoms is the 
+first Born approximation. 
+This perturbative method warrants the $Z^{2}$ laws, where $Z$ is the 
+projectile charge. However, the damage concentrated in the vicinities 
+of the Bragg peak correspond to energies of hundreds of KeV/amu. 
+Precisely in this region, often refered to as the intermediate energy 
+region, the Born approximation starts to fail. Another theoretical 
+issue arises from the targets themselves; we are dealing with complex 
+molecules. This article deals precisely with these two aspects. 
+First, we perform more appropriate calculations on the primary damage 
+mechanism, i.e., atomic ionization by multicharged ions, which can 
+replace the Born results. Second, we inspect and use an stoichiometric 
+model, which reduces a molecule to a sum of atomic processes quantities 
+weighted by the numbers of such atom in the molecule.
 
-Since we have to deal with multi-charged ions, we resort to the 
-Continuum Distorted Wave-Eikonal Initial State (CDW for short) which 
-includes higher perturbative corrections. We start from the premise 
-that the ionization process is the mechanism that deposits the most 
-significant primary energy. This process produces an electron-energy 
-spectrum that needs to be integrated. Also, these ejected electrons 
-become a new source of local damage, which requires to be investigated 
-because these quantities are used in Monte Carlo simulations. With 
-this end in mind, we calculate not only the ionization cross-sections 
-but also energy and mean angular values of the emitted electrons.
+To overcome the first perturbative approximation limitations and 
+since the projectiles are multicharged ions, we resort to the 
+Continuum Distorted Wave-Eikonal Initial State (CDW), which includes 
+higher perturbative corrections. We start from the premise that the 
+ionization process is the mechanism that deposits the most significant 
+amount of primary energy. This process produces an electron-energy 
+spectrum that needs to be integrated. Moreover, the ejected electrons 
+become a new source of local damage. These secondary electrons are 
+included in Monte Carlo simulations and hence their behavior must be
+investigated. With this end in mind, we calculate not only the 
+ionization cross-sections but also energy and mean angular distributions 
+of the emitted electrons.
 
-To deal with the molecules, we resort to the simplest stoichiometric 
-model (SSM): we assume that the molecule is composed of isolated 
-independent atoms. In all cases, the total cross-section is simply 
-the sum of the cross-section of each atom.
+The molecular structure complexity of the target is dealt with by 
+implementing the simplest stoichiometric model (SSM); we assume that 
+the molecule is composed of isolated independent atoms. In all cases, 
+the total cross-section is simply the sum of the cross-section of each 
+atom.
 
-With these two tools in mind, i.e., CDW instead of Born approximation 
-and the SSM, we calculate ionization cross-section of different 
+Then, by implementing the SSM and the CDW --instead of the first Born 
+approximation--, we calculate ionization cross-section of several 
 molecules (see Table~\ref{tab:families}) by the impact of antiprotons,
-H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$,\ and O$^{8+}$. In particular, 
-in Section 3, we are interested in DNA molecules such as Adenine, 
-Timine, Cytosine, Guanine, Uracil, and DNA backbone.
+H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$,\ and O$^{8+}$. Furthermore, 
+in Section 3, we investigate different DNA and RNA molecules
+such as adenine, timine, cytosine, guanine, uracil, and also DNA 
+backbone.
 
 The results are processed to test the Toburen scaling rule, which 
-states that the ratio of the ionization cross-section divided by 
-the number valence electrons (outer electrons) plotted in terms of
-the projectile velocity can be arranged in a narrow universal band.
-We have also applied this rule to several hydrocarbons and piramide 
-molecules. We will prove that the width of the resulting universal 
-band can be significantly reduced if we redefine the effective valence 
-electrons as in Section 3.2.
+states that the ratio between the ionization cross-section and the 
+number of valence electrons (outer electrons) in terms of the 
+projectile velocity can be arranged in a narrow universal band. 
+We have also applied this rule to several hydrocarbons and nucleobases. 
+In Section 3.2, we will prove that the width of the resulting universal 
+band can be significantly reduced if we redefine the effective number 
+of valence electrons.
 
 It is well known that the residual electrons from the ionization 
-process cause biological damage. To inspect this mechanism, in 
-Section 3.3 and 3.4, we have calculated the mean electron energy 
-an angular values. To our surprise, we found a substantial dependence 
-of the charged projectile, which is unexpected in the first 
-Born approximation.
+process cause significant biological damage. To inspect this mechanism, 
+in Section 3.3 and 3.4, we calculated the mean electron energy an 
+angular distributions. Surprisingly, we found a substantial dependence 
+of the charged projectile, which is unexpected in the first Born 
+approximation.
 
-To deal with projectiles of hefty charges, we resort to the CDW. 
-However, the stoichiometric model used seems to be very simplistic 
-since it considers each atom as neutral, which is not correct. 
-In Section 3.5, we used the molecular electronic structure code 
+The hefty charge projectiles are dealt with the CDW. However, the 
+stoichiometric model used seems to be very simplistic. The approximation
+considers each atom as neutral, which is not correct. In Section 3.5, 
+we used the molecular electronic structure code 
 {\sc gamess}~\cite{gamess} to calculate the excess or defect of 
-electron density one each atom. With this knowledge, we modify the 
-simple stoichiometric model to account for the departure from 
-neutrality. We find that, for the DNA molecules, this modification 
-does not introduce a substantial change.
+electron density one each atom. Then, the simple stoichiometric model is
+modified to account for the departure from neutrality of the atoms. 
+We find that for the DNA molecules this modification does not introduce 
+a substantial change.
 
-\section{THEORY: IONIZATION OF ATOMS}
+\section{Theory: Ionization of Atoms}
 
@@
 
-Total ionization cross-sections of these atoms were calculated using 
+The total ionization cross-sections of these atoms were calculated using 
 the CDW. The initial bound and final continuum radial wave functions 
-were obtained by using the{\sc radialf} code developed by Salvat and 
-co-workers, using a Hartree-Fock potential obtained from the 
-Depurated Inversion Model~\cite{mendez2016,mendez2018}. 
+were obtained by using the {\sc radialf} code, developed by Salvat and 
+co-workers, and a Hartree-Fock potential obtained from the Depurated 
+Inversion Model~\cite{mendez2016,mendez2018}. 
 We used a few thousand pivot points to solve the Schr\"{o}dinger 
@@
 cross-section. The calculation performed does not display prior-post 
-discrepancies at all. Each atomic total cross-section in Eq (1) was 
-calculated using 35 to 100 momentum transfer values, 28 fixed 
-electron angles, and around 45 electron energies depending on the 
-projectile impact energy. See further details of the calculation 
-in Ref.~\cite{montanari2017}. Simultaneously, we will be reporting 
-state to state ionization cross sections for these cases in 
-Ref.~\cite{miraglia2019}, which will be very useful to estimate 
+discrepancies at all. Each atomic total cross-section in 
+Eq.~(\ref{eq:sumion}) was calculated using 35 to 100 momentum transfer 
+values, 28 fixed electron angles, and around 45 electron energies 
+depending on the projectile impact energy. Further details of the 
+calculation are given in Ref.~\cite{montanari2017}. Simultaneously, we 
+will be reporting state to state ionization cross sections for these 
+cases in Ref.~\cite{miraglia2019}, which will be very useful to estimate 
 molecule fragmentation.
 
-In Figure 1, we report our results of total ionization of the six 
-essential elements by the impact of six different projectiles, i.e., 
+In Figure 1, we report our total ionization results for the six 
+essential elements by the impact of six different projectiles: 
 antiprotons, H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$. 
 To reduce the resulting 36 magnitudes into a single consistent 
-figure, we use the fact that in the first Born approximation, 
+figure, we considered the fact that in the first Born approximation
 the ionization cross-section scales with the square of the projectile 
-charge, i.e., $Z^{2}$. The values of the impact energies considered 
-range between 0.1 to 10 MeV/amu, i.e., where the CDW is supposed 
+charge, $Z^{2}$. The values of the impact energies considered 
+range between 0.1 to 10 MeV/amu, where the CDW is supposed 
 to hold. In fact, for the highest projectile charges the minimum 
 impact energy where the CDW is expected to be valid could be 
-higher than 100 KeV. From some MeV/amu on, the first the Born 
-approximation provides quite reliable results and using a much 
-simpler formalism; we check it. We use the same color to indicate 
-the projectile charge in all figures of this work: dashed-red, 
+higher than 100 KeV. Moreover, we corroborated that the first Born 
+approximation provides quite reliable results only for energies higher 
+than a couple of MeV/amu. We use the same color to indicate the 
+projectile charge throughout the figures of this work: dashed-red, 
 solid-red, blue, magenta, olive and orange for antiprotons, 
@@
 Notably, there is no complete tabulation of ionization of atoms by 
-the impact of multiple-charged ions. We hope that the ones presented 
-in this article will be helpful.
+the impact of multicharged ions. We hope that the ones presented 
+in this article will be of help for future works.
 
-\section{IONIZATION OF MOLECULES}
+\section{Ionization of Molecules}
 
@@
 of the molecule $\sigma_{M}$ as a simple sum of ionization cross 
-sections of the isolated atoms $\sigma_{\alpha}$, i.e.,
+sections of the isolated atoms $\sigma_{\alpha}$, 
 \begin{equation}
  \sigma_{M}=\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}\,.  
- \label{10}
+ \label{eq:sumion}
 \end{equation}
 We divided sixteen molecular targets of our interest in 3 families. 
-The classification we defined is given in Table~\ref{tab:families}.
-
+The classification defined is given in Table~\ref{tab:families}.
 \begin{table}
-\begin{tabular}{|p{0.06\textwidth}|p{0.525\textwidth}|}
+\begin{center}
+\begin{tabular}{|p{0.06\textwidth}|p{0.55\textwidth}|}
 \hline
@@
 \hline
- \multirow{4}{*}{DNA} & adenine (C$_5$H$_5$N$_5$), timine (C$_5$H$_6$N$_2$O$_2$), \\
+ \multirow{4}{*}{DNA} & adenine (C$_5$H$_5$N$_5$), 
+                        timine (C$_5$H$_6$N$_2$O$_2$), \\
      & cytosine (C$_4$H$_5$N$_2$O), guanine (C$_5$H$_5$N$_5$O), \\
-     & uracil (C$_4$H$_4$N$_2$O$_2$), DNA backbone (C$_5$H$_{10}$O$_5$P), \\
+     & uracil (C$_4$H$_4$N$_2$O$_2$), \\
+     & DNA backbone (C$_5$H$_{10}$O$_5$P), \\
      & dry DNA (C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$)\\
@@
 families.}
+\end{center}
 \end{table}
@@
 DNA backbone containing P are given in Figure 3. For adenine, the 
-agreement with the three experiments available in our range of validity 
+agreement with the experimental data available in our range of validity 
 is quite good. For uracil, we have a puzzling situation: our results 
@@
 phenomenological model for electron ejection from large molecules was 
-posed by Toburen and collaborators~\cite{toburen1975,toburen1976}. 
+proposed by Toburen {\it et al.}~\cite{toburen1975,toburen1976}. 
 The authors found it convenient to scale the experimental ionization 
@@
 \sigma_{e}=\frac{\sigma_{M}}{N_{M}}=\frac{\sum\limits_{\alpha}
-n_{\alpha}\sigma_{\alpha}}{\sum\limits_{\alpha}n_{\alpha}v_{\alpha}}
+n_{\alpha}\sigma_{\alpha}}{\sum\limits_{\alpha}n_{\alpha}\nu_{\alpha}}
 =\sigma_{e}(v)\,, 
@@
 \begin{equation}
-v_{\alpha}=\left\{ 
+\nu_{\alpha}=\left\{ 
 \begin{array}{ll}
@@
 \end{equation}
-and $v_{H}=1$. The Toburen rule can be stated by saying that 
+and $\nu_{H}=1$. The Toburen rule can be stated by saying that 
 $\sigma_{e}$ is a \textit{universal} parameter independent on the 
@@
 Ref.~\cite{itoh2013} for proton impact on uracil and adenine. 
-Figure 5a shows $\sigma_{e}$ calculated with the CDW as a function of 
+Figure 4a shows $\sigma_{e}$ calculated with the CDW as a function of 
 the impact velocity for different projectile charges computed with the 
@@
 by Born approximation, i.e., $\sigma _{e}(Z)=Z^{2}\sigma_{e}(Z=1)$, 
-and it holds for large impact velocities, as shown Figure 5a.
-Obviously, for lower impact velocities the distorted wave CDW breaks 
-this behavior discarding the rule $Z^{2}$. Although the Toburen rule 
-holds for high energies, its performance is still not satisfactory: 
-the universal band is quite broad. The departure of our theoretical 
+and it holds for large impact velocities, as shown Figure 4a.
+Of course, for lower impact velocities, the CDW breaks the behavior of 
+the $Z^{2}$ rule. Although the Toburen rule holds for high energies, 
+its performance is still not satisfactory: the universal band is quite 
+broad. The departure of our theoretical 
 results from the Toburen rule can be easily explained by the fact that 
@@
 n_{\alpha}\sigma_{\alpha}^{\text{CDW}}}{\sum\limits_{\alpha}n_{\alpha}
-v_{\alpha}^{\text{CDW}}},
+\nu_{\alpha}^{\text{CDW}}},
 \label{32} 
@@
 \begin{equation}
-v_{\alpha }^{\text{CDW}} \sim\left\{ 
+\nu_{\alpha }^{\text{CDW}} \sim\left\{ 
 \begin{array}{ll}
@@
 \end{equation}
-and, obviously, $v_{H}^{\text{CDW}}=1$. The cross sections 
+and, obviously, $\nu_{H}^{\text{CDW}}=1$. The cross sections 
 $\sigma_{e}^{\text{CDW}}$ 
-are plotted in Figure 5b. A much better sharp band is observed, 
+are plotted in Figure 4b. A much better sharp band is observed, 
 especially at high energy, where the theory is expected to work. It 
-will be interesting for experiments to tune up this theoretical 
+will be interesting for experiments to cross-check this theoretical 
 prediction.
@@
 
-In a given biological medium, direct ion ionization accounts for just 
-a fraction of the overall damage. Secondary electrons, as well as 
-recoil target ions, also contribute substantially to the total damage. 
+In a given biological medium, direct ionization by ion impact accounts 
+for just a fraction of the overall damage. Secondary electrons, as well 
+as recoil target ions, also contribute substantially to the total damage. 
 We can consider the single differential cross section of the shell 
@@
 Table~\ref{tab:families}. The range of impact velocities was shorten up 
-to $v=10$ because of a numerical limitation in the spherical harmonics 
+to $v=10$ a.u. due to numerical limitations in the spherical harmonics 
 expansion. In our theoretical treatment, we expand our final continuum 
@@
 $\langle E_{\alpha}\rangle$ includes the kinetic energy $E$
-(see Eq.~(\ref{40}), which cancels the small energy region and 
+(see Eq.~(\ref{40})), which cancels the small energy region and 
 reinforces the large values, making the result more sensible to large
-angular momenta. Regardless, for $v>10,$ the first Born approximation 
-holds.
+angular momenta. Regardless, for $v>10$ a.u., the first Born 
+approximation holds.
 
@@
 Our results agree with the experimental findings~\cite{surdutovic2018}. 
-The dependence with the projectile charge $Z$ is surprisingly sensible,
-which can duplicate the proton results. This effect can be attributed 
-to the depletion caused by the multicharged ions to the yields of low 
-energy electrons. In the high electron energy regime, the CDW falls on 
-the simple first Born approximation, surviving the simple $Z^{2}$ law.
-Then, the ratio in Eq.~(\ref{40}) cancels out and 
-$\overline{E}_{\alpha}$ becomes a universal value independent on $Z$.
+The dependence of the mean energy value with the projectile charge $Z$ 
+is surprisingly sensible, which can duplicate the proton results. 
+This effect can be attributed to the depletion caused by the 
+multicharged ions to the yields of low energy electrons. In the high 
+electron energy regime, the CDW falls on the simple first Born 
+approximation, surviving the $Z^{2}$ law. Then, the ratio in 
+Eq.~(\ref{40}) cancels out and $\overline{E}_{\alpha}$ becomes a 
+universal value independent on $Z$.
 
@@
 \end{equation}
-For impact of H$^{+}$ and He$^{2+~}$ on water at 1 MeV/amu we obtain of 
-$\overline{E}_{H_{2}O}=$43.7 \ and 45eV, while the experiments on liquid
-water Pimblott and LaVerne [] found \ 51.5 and 52.2 eV, respectively. 
-Just to stress the importance of the projectile charge, for O$^{8+}$ on 
-water at the same impact energy 1 MeV/amu we, obtain 
-$\overline{E}_{H_{2}O}=54.7$ eV, i.e. 25\% larger than proton impact. 
-We recall here that there should not be any difference if the 
-calculation is carried in first Born approximation. We will came back
-on this issue
+For impact of H$^{+}$ and He$^{2+~}$ on water at 1 MeV/amu, we obtain 
+$\overline{E}_{H_{2}O}=43.7$ and 45 eV, while the experimental values 
+on liquid water by Pimblott and LaVerne [xxx] were found to be 51.5 and 
+52.2 eV, respectively. Just to stress the importance of the projectile 
+charge, for O$^{8+}$ on water, at the same impact energy 1 MeV/amu, 
+we obtained $\overline{E}_{H_{2}O}=54.7$ eV, which is 25\% larger than 
+proton impact result. It is worth noting that there should not be any 
+difference if the calculations were carried in first Born approximation. 
+We will came back on this issue later.
 
@@
 
-As mentioned before, secondary electrons contribute to the total damage. It
-is important not only the ejection energy but also the angle of emission. In
-similar fashion, we can consider the magnitude $d\sigma _{\alpha
-,nl}/d\Omega $ \ -i.e. the single differential cross section in terms of the
-ejected electron solid angle $\Omega $ -\ as a distribution function, and
-define the mean angle $\overline{\theta }_{\alpha }$ as
+As mentioned before, secondary electrons contribute to the total damage. 
+Then, it is important not only the ejection energy but also the angle 
+of emission. Once again, we can consider the single differential cross 
+section in terms of the ejected electron solid angle $\Omega$, 
+$d\sigma_{\alpha,nl}/d\Omega$, to be expressed as a distribution 
+function, and define the mean angle $\overline{\theta}_{\alpha}$ as
+\begin{equation}
+\overline{\theta}_{\alpha}=\frac{\langle\theta_{\alpha}\rangle}
+{\langle 1\rangle}=\frac{1}{\sigma_{\alpha}}\sum\limits_{nl}
+\int d\Omega\,\theta\,\frac{d\sigma_{\alpha,nl}}{d\Omega}
+\end{equation}
+Figure 6 shows $\overline{\theta}_{\alpha}$ for our six elements of 
+interest. A new important dependence of $\overline{\theta}_{\alpha}$ 
+with $Z$ is observed. It is the common view~\cite{Rudd1992} that the 
+angular dispersion of emitted electrons are nearly isotropic due to the
+fact that angular anisotropy of sub-50-eV yield is not significant. 
+A typical value of ejection angle used in the literature is 
+$\overline{\theta}_{\alpha}\sim 70$ degrees~\cite{surdutovic2018}, and 
+it is quite correct in the range of validity of the first Born 
+approximation for any target. But when a distorted wave approximation 
+is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
+in the intermediate energy region, as observed in Figure 6. 
+For example, for C$^{6+}$ impact, the Bragg peak occurs at 0.3 MeV/amu, 
+where $\overline{\theta}_{\alpha}$ computed with the CDW method is 
+about half of the value obtained with the first Born approximation. 
+This correction should close the damage to the forward direction.
 
-\begin{equation}
-\overline{\theta }_{\alpha }=\frac{\langle \theta _{\alpha }\rangle }{%
-\langle 1\rangle }=\frac{1}{\sigma _{\alpha }}\sum\limits_{nl}\int d\Omega
-\ \theta \ \frac{d\sigma _{\alpha ,nl}}{d\Omega }
-\end{equation}%
-Figure 6 shows $\overline{\theta }_{\alpha }$ for our six elements of
-interest. Again here we observe an important dependence dependence of $%
-\overline{\theta }_{\alpha }\ $with $Z.$ It is the common view 
-\cite{Rudd1992} that the angular dispersion of emitted electrons are nearly
-isotropic due to the fact that angular anisotropy of sub-50-eV yield is not
-significant. A typical used value of ejection angle is about $\overline{%
-\theta }_{\alpha }\sim $70 degrees \cite{surdutovic2018} and this quite
-correct in the range of validity of the first Born approximation for any
-target. But when a distorted wave approximation is used as observed in
-Figure 6, $\overline{\theta }_{\alpha }$ decreases substantially with $Z$ in
-the intermediate energy region. For example for C$^{6+}$ impact the Bragg
-peak occurs at 0.3 MeV/amu where \ $\overline{\theta }_{\alpha }$ calculated
-in CDW is about the half of the one calculated with the First Born
-approximation. \ This correction should close the damage to the forward
-direction.
-
-The only responsible of this correction is the\ capture to the continuum
-effect: the larger the charge $Z$ the smaller $\overline{\theta }$ will be,
-of course at intermediate energies, not at high impact energies where the
-Born approximation rules. One illustrative observation is the behavior of
-antiprotons: the projectile in this case repels the electrons \ making the
-distribution almost symmetric. Note the opposite effect of proton and
-antiprotons, they run one oppose to the other one, as compared with the
-first Born approximation.
+The only responsible of this correction is the capture to the continuum
+effect: the larger the charge $Z$ the smaller $\overline{\theta}$ will 
+be, of course at intermediate energies, not at high impact energies, 
+where the Born approximation rules. One illustrative observation is the 
+behavior of antiprotons: the projectile in this case repels the 
+electrons making the distribution almost symmetric. Note the opposite 
+effect of proton and antiprotons, they run one opposite to the other, 
+as compared with the first Born approximation.
 
@@
 \hline
-\text{Element}\,\,\,  & \mathrm{H} & \mathrm{C} & \mathrm{N} & \mathrm{O} & \text{New stoichiometry} \\ \hline
-\mathrm{Adenine}  & +0.32 & -0.55 & +0.23 &       & \mathrm{C}_{4.92}\mathrm{H}_{5.14}\mathrm{N}_{4.77} \\ \hline
-\mathrm{Thymine}  & +0.20 & -0.54 & +0.19 & -0.52 & \mathrm{C}_{4.95}\mathrm{H}_{6.13}\mathrm{N}_{1.95}\mathrm{O}_{2.13} \\ \hline
-\mathrm{Cytosine} & +0.28 & -0.56 & +0.21 & -0.53 & \mathrm{C}_{3.93}\mathrm{H}_{5.14}\mathrm{N}_{2.79}\mathrm{O}_{1.13} \\ \hline
-\mathrm{Guanine}  & +0.46 & -0.58 & +0.20 & -0.36 & \mathrm{C}_{4.89}\mathrm{H}_{5.15}\mathrm{N}_{4.80}\mathrm{O}_{1.09} \\ \hline
+\text{Element}\,\,\, & \mathrm{H} & \mathrm{C} & \mathrm{N} & \mathrm{O} & 
+\text{New stoichiometry} \\ 
+\hline
+\mathrm{Adenine}  & +0.32 & -0.55 & +0.23 &       & 
+\mathrm{C}_{4.92}\mathrm{H}_{5.14}\mathrm{N}_{4.77} \\ 
+\hline
+\mathrm{Thymine}  & +0.20 & -0.54 & +0.19 & -0.52 & 
+\mathrm{C}_{4.95}\mathrm{H}_{6.13}\mathrm{N}_{1.95}\mathrm{O}_{2.13} \\ 
+\hline
+\mathrm{Cytosine} & +0.28 & -0.56 & +0.21 & -0.53 & 
+\mathrm{C}_{3.93}\mathrm{H}_{5.14}\mathrm{N}_{2.79}\mathrm{O}_{1.13} \\ 
+\hline
+\mathrm{Guanine}  & +0.46 & -0.58 & +0.20 & -0.36 & 
+\mathrm{C}_{4.89}\mathrm{H}_{5.15}\mathrm{N}_{4.80}\mathrm{O}_{1.09} \\ 
+\hline
 \end{array}

### 2019-09-05 NewMonti24.tex
energy levels added

@@
 \end{equation}
-and $\nu_{H}=1$. The Toburen rule can be stated by saying that 
+and $\nu_{\text{H}}=1$. The Toburen rule can be stated by saying that 
 $\sigma_{e}$ is a \textit{universal} parameter independent on the 
@@
 \end{equation}
-and, obviously, $\nu_{H}^{\text{CDW}}=1$. The cross sections 
-$\sigma_{e}^{\text{CDW}}$ 
-are plotted in Figure 4b. A much better sharp band is observed, 
-especially at high energy, where the theory is expected to work. It 
-will be interesting for experiments to cross-check this theoretical 
-prediction.
+and, obviously, $\nu_{\text{H}}^{\text{CDW}}=1$. The cross sections 
+$\sigma_{e}^{\text{CDW}}$ are plotted in Figure~4b. A much better sharp 
+band is observed, especially at high energy, where the theory is 
+expected to work. It will be interesting for experiments to cross-check 
+this theoretical prediction.
 
@@
 
-Figure 5 shows $\overline{E}_{i}$ for six elements from 
+Figure 5 shows $\overline{E}_{\alpha}$ for six elements from 
 Table~\ref{tab:families}. The range of impact velocities was shorten up 
@@
 For impact of H$^{+}$ and He$^{2+~}$ on water at 1 MeV/amu, we obtain 
-$\overline{E}_{H_{2}O}=43.7$ and 45 eV, while the experimental values 
+$\overline{E}_{\text{H}_{2}\text{O}}=43.7$ and 45 eV, while the 
+experimental values 
 on liquid water by Pimblott and LaVerne [xxx] were found to be 51.5 and 
@@
 charge, for O$^{8+}$ on water, at the same impact energy 1 MeV/amu, 
-we obtained $\overline{E}_{H_{2}O}=54.7$ eV, which is 25\% larger than 
+we obtained $\overline{E}_{\text{H}_{2}\text{O}}=54.7$ eV, which is 25\% 
+larger than 
 proton impact result. It is worth noting that there should not be any 

### 2019-09-06 NewMonti24.tex
Table 2 modified

@@
 \usepackage{multirow}
+\usepackage{gensymb}
+\usepackage{float}
 
@@
 
-The damage caused by the impact of multicharged heavy projectile has 
-become a field of interest because of its implementation in ion-beam 
+The damage caused by the impact of multicharged heavy projectiles has 
+become a field of interest due to its recent implementation in ion-beam 
 cancer therapy. The effectiveness of the radiation depends on the 
@@
 model, which reduces a molecule to a sum of atomic processes quantities 
-weighted by the numbers of such atom in the molecule.
+weighted by the number of such atom in the molecule.
 
-To overcome the first perturbative approximation limitations and 
+To overcome the first perturbative approximation limitations, and 
 since the projectiles are multicharged ions, we resort to the 
@@
 in Section 3, we investigate different DNA and RNA molecules
-such as adenine, timine, cytosine, guanine, uracil, and also DNA 
+such as adenine, cytosine, guanine, thymine, uracil, and also DNA 
 backbone.
@@
 process cause significant biological damage. To inspect this mechanism, 
-in Section 3.3 and 3.4, we calculated the mean electron energy an 
+in Section 3.3 and 3.4, we calculated the mean electron energy and
 angular distributions. Surprisingly, we found a substantial dependence 
@@
 \end{equation}
-We divided sixteen molecular targets of our interest in 3 families. 
+We divided sixteen molecular targets of our interest in three families. 
 The classification defined is given in Table~\ref{tab:families}.
@@
 \begin{center}
-\begin{tabular}{|p{0.06\textwidth}|p{0.55\textwidth}|}
+\begin{tabular}{|p{0.06\textwidth}|p{0.65\textwidth}|}
 \hline
@@
  \multirow{4}{*}{DNA} & adenine (C$_5$H$_5$N$_5$), 
-                        timine (C$_5$H$_6$N$_2$O$_2$), \\
-     & cytosine (C$_4$H$_5$N$_2$O), guanine (C$_5$H$_5$N$_5$O), \\
-     & uracil (C$_4$H$_4$N$_2$O$_2$), \\
-     & DNA backbone (C$_5$H$_{10}$O$_5$P), \\
+                        cytosine (C$_4$H$_5$N$_2$O), \\
+     & guanine (C$_5$H$_5$N$_5$O), thymine (C$_5$H$_6$N$_2$O$_2$), \\
+     & uracil (C$_4$H$_4$N$_2$O$_2$), DNA backbone (C$_5$H$_{10}$O$_5$P), \\
      & dry DNA (C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$)\\
@@
 \end{tabular}
-\caption{Sixteen molecular targets of our interest classified in 3 
+\caption{Sixteen molecular targets of our interest classified in three 
+families.}
 \label{tab:families}
-families.}
 \end{center}
@@
 impact of multicharged ions for the four fundamental DNA components: 
-adenine, timine, cytosine, and guanine. Our reports for uracil and 
+adenine, cytosine, guanine and thymine. Our reports for uracil and 
 DNA backbone containing P are given in Figure 3. For adenine, the 
@@
 Nonetheless, it should be stated that our theoretical results coincide 
-with the ones by Champion, Rivarola and 
+with calculations by Champion, Rivarola and 
 collaborators~\cite{champion2012,agnihotri2012}, which may indicate a 
@@
 As mentioned before, secondary electrons contribute to the total damage. 
-Then, it is important not only the ejection energy but also the angle 
+Then, not only is the ejection energy important but also the angle 
 of emission. Once again, we can consider the single differential cross 
 section in terms of the ejected electron solid angle $\Omega$, 
-$d\sigma_{\alpha,nl}/d\Omega$, to be expressed as a distribution 
-function, and define the mean angle $\overline{\theta}_{\alpha}$ as
+$d\sigma_{\alpha,nl}/d\Omega$, to be expressed as a distribution function, 
+and the mean angle $\overline{\theta}_{\alpha}$ can be defined as
 \begin{equation}
@@
 interest. A new important dependence of $\overline{\theta}_{\alpha}$ 
-with $Z$ is observed. It is the common view~\cite{Rudd1992} that the 
-angular dispersion of emitted electrons are nearly isotropic due to the
-fact that angular anisotropy of sub-50-eV yield is not significant. 
-A typical value of ejection angle used in the literature is 
-$\overline{\theta}_{\alpha}\sim 70$ degrees~\cite{surdutovic2018}, and 
+with $Z$ is observed. It is a general belief~\cite{Rudd1992} that the 
+angular dispersion of emitted electrons are nearly isotropic. This effect 
+is caused by the insignificant angular anisotropy of sub-50-eV yield. 
+A typical value for the ejection angle considered in the literature is 
+$\overline{\theta}_{\alpha}\sim 70\degree$~\cite{surdutovic2018}, and 
 it is quite correct in the range of validity of the first Born 
-approximation for any target. But when a distorted wave approximation 
+approximation for any target. But, when a distorted wave approximation 
 is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
@@
 For example, for C$^{6+}$ impact, the Bragg peak occurs at 0.3 MeV/amu, 
-where $\overline{\theta}_{\alpha}$ computed with the CDW method is 
+where $\overline{\theta}_{\alpha}$, computed with the CDW method, is 
 about half of the value obtained with the first Born approximation. 
@@
 
-The only responsible of this correction is the capture to the continuum
-effect: the larger the charge $Z$ the smaller $\overline{\theta}$ will 
-be, of course at intermediate energies, not at high impact energies, 
-where the Born approximation rules. One illustrative observation is the 
-behavior of antiprotons: the projectile in this case repels the 
-electrons making the distribution almost symmetric. Note the opposite 
-effect of proton and antiprotons, they run one opposite to the other, 
-as compared with the first Born approximation.
+We can attribute this correction to the capture to the continuum effect;
+the larger the charge $Z$, the smaller $\overline{\theta}$ will be. Of 
+course, this effect only holds at intermediate energies and not at high 
+impact energies, where the Born approximation rules. One illustrative 
+observation is the behavior of antiprotons: the projectile in this case 
+repels the electrons, making the distribution almost symmetric. 
+Note the opposite effect of proton and antiprotons; they run one 
+opposite to the other, as compared with the first Born approximation.
 
@@
 
-One can correctly argue that\ the SSM considers an assembly of isolated
-neutral atoms which is definitively unrealistic. A first improvement is to
-consider that the atoms are not neutral and within the molecule they have
-more or less electrons given by a \ charge $q_{\alpha }$. One parameter that
-measures $q_{\alpha }$ is the Mulliken charge. This is not the only one,
-there is a large variety of charges such as the net or natural atomic charge 
-\cite{lee2003}, the lowin charge, etc.
+The SSM considers the molecule to be assembled by isolated neutral atoms, 
+which is definitively unrealistic. A first improvement can be suggested 
+by assuming that the atoms are not neutral and that they have an uneven
+distribution of electrons within the molecule; this distribution can be
+given by an effective charge $q_{\alpha}$. A possible value for 
+$q_{\alpha}$ is given by the Mulliken charge. However, there are a wide
+variety of charge distributions, such as the net or natural atomic
+charge~\cite{lee2003}, the L\"owdin charge, etc.
 
-Consider\ that the total amount of electrons $Q_{\alpha }\ $on element $%
-\alpha $ are equally distributed on all the atoms $\alpha ,$ therefore each
-element $\alpha \ $\ will have a an additional charge: $q_{\alpha
-}=Q_{\alpha }/n_{\alpha }$. positive or negative depending on the relative
-electronegative value respect to the other ones~\cite{rappe1991}. Instead
-of the integer number of elements $n_{\alpha }$ of the atom $\alpha$, it
-could be argued that we have now an continuous number of atoms given by 
+Consider that the total amount of electrons $Q_{\alpha }$ on the element
+$\alpha$ are equally distributed on all the $\alpha$ atoms. Therefore, 
+each element $\alpha$ will have an additional charge: 
+$q_{\alpha}=Q_{\alpha}/n_{\alpha}$, which can be positive or negative.
+This value will depend on the relative electronegativity value with 
+respect to the other atoms~\cite{rappe1991}. Now, instead of an
+integer number of elements $n_{\alpha}$ of the atom $\alpha$, we have a 
+fractional number of atoms given by 
 \begin{equation}
-n_{\alpha }^{\prime }=n_{\alpha }-\frac{q_{\alpha }}{v_{\alpha }^{CDW}}
-\label{100}
+n_{\alpha }^{\prime }=n_{\alpha }-
+\frac{q_{\alpha }}{\nu_{\alpha }^{\text{CDW}}}
+\label{eq:newstoi}
 \end{equation}%
-In the case of neutral atoms $q_{\alpha }=0,$ we obviously recover $%
-n_{\alpha }^{\prime }=n_{\alpha }$ as before$.$
+In the case of neutral atoms, $q_{\alpha}=0$ and we recover 
+$n_{\alpha}^{\prime}=n_{\alpha}$, as it should be.
 
-To inspect the effect of the $q_{\alpha }$ we have run GAMES with the 
-6-31G basis set, including polarization functions for all the atoms. 
-The calculations were carried out implementing the B3LYP 
-functional~\cite{Becke1993,Stephens1994}. In Table~(\ref{110}) we display
-$q_{\alpha }$ of the different DNA basis and in the last column we rewrite
-the new stoichiometric expression. 
-\begin{equation}
-\begin{array}{|l|l|l|l|l|l|}
+To inspect the effect of $q_{\alpha}$, we computed the molecular
+structure of several nucleobases with the {\sc gamess} code. We 
+used the 6-31G(d,p) basis set, which includes polarization 
+functions for all the atoms. The calculations were carried out 
+implementing the B3LYP functional~\cite{Becke1993,Stephens1994} to 
+account for the correlation and exchange effects. 
+In Table~\ref{tab:newstoi}, we display the charge $q_{\alpha}$ of four 
+DNA molecules. The last column shows the new stoichiometric formula
+found by implementing Eq.~(\ref{eq:newstoi}).
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{|p{0.12\textwidth}|p{0.07\textwidth}|p{0.07\textwidth}|p{
+0.07\textwidth}|p{0.07\textwidth}|p{0.25\textwidth}|}
 \hline
-\text{Element}\,\,\, & \mathrm{H} & \mathrm{C} & \mathrm{N} & \mathrm{O} & 
-\text{New stoichiometry} \\ 
+Element & C & H & N & O & New stoichiometry \\
 \hline
-\mathrm{Adenine}  & +0.32 & -0.55 & +0.23 &       & 
-\mathrm{C}_{4.92}\mathrm{H}_{5.14}\mathrm{N}_{4.77} \\ 
+Adenine & +0.32 & +0.23 & --0.55 &       & C$_{4.92}$H$_{4.77}$N$_{5.14}$ \\ 
 \hline
-\mathrm{Thymine}  & +0.20 & -0.54 & +0.19 & -0.52 & 
-\mathrm{C}_{4.95}\mathrm{H}_{6.13}\mathrm{N}_{1.95}\mathrm{O}_{2.13} \\ 
+Cytosine & +0.28 & +0.21 & --0.56 & --0.53 & C$_{3.93}$H$_{2.79}$N$_{5.14}$O$_{1.13}$ \\ 
 \hline
-\mathrm{Cytosine} & +0.28 & -0.56 & +0.21 & -0.53 & 
-\mathrm{C}_{3.93}\mathrm{H}_{5.14}\mathrm{N}_{2.79}\mathrm{O}_{1.13} \\ 
+Guanine & +0.46 & +0.20 & --0.58 & --0.36 & C$_{4.89}$H$_{4.80}$N$_{5.15}$O$_{1.09}$ \\ 
 \hline
-\mathrm{Guanine}  & +0.46 & -0.58 & +0.20 & -0.36 & 
-\mathrm{C}_{4.89}\mathrm{H}_{5.15}\mathrm{N}_{4.80}\mathrm{O}_{1.09} \\ 
+Thymine & +0.20 & +0.19 & --0.54 & --0.52 & C$_{4.95}$H$_{1.95}$N$_{6.13}$O$_{2.13}$ \\ 
 \hline
-\end{array}
-\label{110}
-\end{equation}
+\end{tabular}
+\caption{Effective charge $q_{\alpha}$ and new stoichiometric formula 
+defined by Eq.~(\ref{eq:newstoi}) for four DNA molecules.}
+\label{tab:newstoi}
+\end{center}
+\end{table}
 
-All the previous formula holds with the simple replacement of integer value $%
-n_{\alpha }$ by the continuous values\ $n_{\alpha }^{\prime }$ to produce a
-new ionization cross section $\sigma ^{\prime }$
+The previous formula can be rewritten by replacing the integer value 
+$n_{\alpha}$ by the fractional values $n_{\alpha}^{\prime}$. This 
+analog formulations are now implemented to compute the new ionization 
+cross sections, $\sigma^{\prime}$.
 
-In Figure 7, we displays the relative difference of ionization cross
+In Figure 7, we display the relative difference of ionization cross 
 sections 
 \begin{equation}
-e=\frac{\sigma ^{\prime }-\sigma }{\sigma }\times 100  \label{120}
-\end{equation}%
-for the four DNA basis. The difference is \ just very few percents.
-Indicating that the SSM is a quite robust model to treat the type of
-molecule we are dealing with, and of course within the range error that one
-can expect from the SSM.
+e=\frac{\sigma^{\prime}-\sigma}{\sigma}\times 100
+\label{120}
+\end{equation}
+for the four DNA basis. The difference obtained is of just very few 
+percents, which indicates that the SSM is a quite robust model to treat 
+the type of molecule we are dealing with, and of course within the 
+range error that one can expect from the SSM.
 

### 2019-09-06 NewMonti24.tex
added binding energy spectra and corrections

@@
 each atom in terms of the projectile charges. By inspecting Figure 1, 
-one can easily see that the rule $\sigma_{\alpha}/v_{\alpha}\sim
+one can easily see that the rule $\sigma_{\alpha}/\nu_{\alpha}\sim
 \sigma_{e}$ is not well satisfied by the CDW. A much better general 
@@
 \right. 
-\label{35}
+\label{eq:scalingCDW}
 \end{equation}
@@
 
-In Figure 7, we display the relative difference of ionization cross 
+In Figure 8, we display the relative difference of ionization cross 
 sections 
@@
 \end{equation}
-for the four DNA basis. The difference obtained is of just very few 
+for the four DNA bases. The difference obtained is of just very few 
 percents, which indicates that the SSM is a quite robust model to treat 
@@
 
-We now return to the calculation of the mean electron energy of H$^{+}$ and
-He$^{2+~}$ in water\ \ $\overline{E}_{H_{2}O}$. If we consider that \ the
-residual charge of \ each hydrogen in water is $q_{H}=$+0.35 \ \cite%
-{rappe1991}\ which implies that on Oxygen we have \ a residual charge of $%
-q_{O}=$-0.7, we could re-write the formula of water using (\ref{120}) as H$%
-_{1.3}$O$_{1.17}$ considering $n_{O}^{CDW}\simeq 4$ and $n_{H}^{CDW}\simeq
-1. $ Recalculating mean electron energy by impact of \ H$^{+}$ and He$^{2+~}$
-on water at 1 MeV/amu we obtain: $\overline{E}_{H_{2}O}=$46.2 \ and 47.6 eV
-which compared a little better with the experiments: 51.5 and 52.2 eV \cite%
-{pimblott2007}, respectively. i.e. within 10\% of the experiments which is
-not bad accounting for the simplicity of our method.
+Our molecular binding energies of the outer electrons for adenine, 
+cytosine, guanine and thymine are shown in Figure~7. On the left side 
+of the figure, we show the atomic Hartree--Fock energies of the 
+constituent elements, which can give an idea of how the molecular levels 
+distribute. A dashed line around -0.8 a.u. is drawn to separate in two 
+the band levels of the outer electrons. The electrons in the molecular 
+targets corresponding to the $2s$ of N and C in the atomic case are 
+placed in a secondary gap. The lower levels of the secondary gap 
+correspond to the oxygen. The number of electrons in the valence 
+shell for all O would seem to be equal to 4, as previously setted by the 
+scaling rule Eq.~(\ref{eq:scalingCDW}). The N case is not as straightfoward;
+the electrons that would correspond to the $2s$ are located just below
+the line. The $\nu_{\alpha }^{\text{CDW}}$ value given for N would 
+suggest that a significant amount of electron density from the secondary gap 
+is shared with the valence band.
 
-Another parameter that we can calculate in our model is the fraction of
-energy carried by the electron $f$ defined as%
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.95\textwidth]{energylevels/DNA.eps}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We now return to the calculation of the mean electron energy of H$^{+}$ 
+and He$^{2+}$ in water, $\overline{E}_{\text{H}_2\text{O}}$. If we 
+consider that the residual charge of each hydrogen in water is 
+$q_{\text{H}}=+0.35$~\cite{rappe1991}, which implies that on oxygen we have a 
+residual charge of $q_{\text{O}}=-0.7$, we could re-write the formula of water 
+using Eq.~(\ref{120}) as H$_{1.3}$O$_{1.17}$ by considering 
+$n_{\text{O}}^{\text{CDW}}\simeq 4$ and 
+$n_{\text{H}}^{\text{CDW}}\simeq 1$. Recalculating mean electron energy 
+by impact of H$^{+}$ and He$^{2+}$ on water at 1 MeV/amu, we obtain
+$\overline{E}_{\text{H}_2\text{O}}=46.2$ and 47.6 eV. Our results 
+are 10\% apart from the experimental values: 51.5 and 
+52.2~eV~\cite{pimblott2007}, respectively, which is not bad considering 
+the simplicity of our model.
+
+Another parameter that can computed within our model is the fraction of
+energy carried by the electron $f$, which is defined as
 \begin{equation}
-f=\frac{\sum\limits_{\alpha }n_{\alpha }\sigma _{\alpha }\overline{%
-E_{\alpha }}}{\sum\limits_{\alpha }n_{\alpha }(\sigma _{\alpha }\overline{%
-E_{\alpha }}+\sum\limits_{nl}\sigma _{\alpha nl}E_{\alpha nl})}  \label{90}
-\end{equation}%
-Using our shell-to-shell ionization cross sections $\sigma _{\alpha nl}\ $%
-\cite{miraglia2019}\ and atomic binding energies of the atom$\ \alpha ,$ $%
-E_{\alpha nl}\ $\cite{clementi}, we obtain $f=$0$.70\ $and $\ 0.71$ for \ H$%
-^{+}$ and He$^{2+~}$ on water at 1 MeV/amu,. which differ from the
-experiments \ $f=0.81$ and $0.80$, \ respectively.
+f=\frac{\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}
+\overline{E_{\alpha}}}{\sum\limits_{\alpha}n_{\alpha}(\sigma_{\alpha}
+\overline{E_{\alpha}}+\sum\limits_{nl}\sigma_{\alpha nl}E_{\alpha nl})}\,.
+\label{90}
+\end{equation}
+Using our shell-to-shell ionization cross sections 
+$\sigma_{\alpha nl}$~\cite{miraglia2019}, and atomic binding energies of 
+the atom $\alpha$, $E_{\alpha nl}$~\cite{clementi}, we obtain 
+$f=0.70$ and $0.71$ on water at 1 MeV/amu for H$^{+}$ and He$^{2+}$, 
+which differ from the respective experimental values $f=0.81$ and $0.80$.
 
-This difference with the experiment could be attributed to the difference of
-binding energy between the molecular water 12.65 eV and the atomic component
-H (13.6 eV) and O (17.19 eV), which is an issue beyond our independent atom
-approximation and so our model cannot not accounted for. We could estimate
-this contribution resorting, once more to the stoichiometric, model, we can
-arriesgar a upper-limit difference per molecule of water\ as
+The difference between our calculations and the experiments could be 
+attributed to the binding energy values of the molecular water~12.65 eV 
+and its atomic components, H (13.6 eV) and O (17.19 eV). This theoretical
+discrepancy goes beyond our independent atom approximation and so it 
+cannot be accounted for by our model. Once again, we could estimate this 
+contribution by resorting to the stoichiometric model. We can make an 
+asses for a maximum difference per molecule of water as
+\begin{equation}
+\delta E=(13.6-12.65)\times1.17+(17.19-12.65)\times1.3=7\,\text{eV}  
+\label{80}
+\end{equation}
+Most of this energy should be transfer to the kinetic energy of the 
+emitted electron. Thus, by adding 7 eV to the previous values, we obtain
+$\overline{E}_{\text{H}_2\text{O}}=53.2$ and 54.6 eV for H$^{+}$ and 
+He$^{2+}$ on water at 1 MeV/amu, respectively, which are much closer to
+the experimental values. If we add $\delta E$ to the numerator of 
+Eq.~(\ref{90}), we obtain $f=0.81$ and $0.80$, in perfect agreement with 
+the experiments (see Table 1 of Ref.~\cite{pimblott2007}).
 
-\begin{equation}
-\delta E=(13.6-12.65)1.17+(17.19-12.65)1.3=7\ \text{eV}  \label{80}
-\end{equation}%
-Most of this energy should be transfer to the kinetics energy of the emitted
-electron. Thus we can \ add 7 eV to the previous values to give $\overline{E}%
-_{H_{2}O}=$53.2 \ and 54.6 eV for \ H$^{+}$ and He$^{2+~}$ on water at 1
-MeV/amu, respectively, much near to the experiments: 51.5 and 52.2 eV. If we
-add $\delta E$ to the numerator of Eq.(\ref{90}) we obtain\ $f=0.81$ and $%
-0.80$ in perfect agreement with the experiments (see Table 1 of Ref.(\cite%
-{pimblott2007})
+\section{Conclusions}
 
-\section{CONCLUSIONS}
+We calculated ionization cross sections by impact of antiprotons, 
+H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$ for sixteen 
+molecules containing H, C, N, O, P and S with the CDW method. The 
+importance of the influence of $Z$ was observed in the mean energy 
+$\overline{E}_{\alpha}$ and angle $\overline{\theta}_{\alpha}$. 
+For a given target $\alpha$, as $Z$ increases, $\overline{E}_{\alpha}$ 
+increases, but $\overline{\theta}_{\alpha}$ decreases. At high impact 
+energy, say larger than 1 MeV/amu, these values converge to the Born 
+approximation, which embodies the simple $Z^{2}$ law. The sixteen 
+molecules selected were investigated using the simple stoichiometric 
+model. Results for six DNA bases were presented and compared with the 
+sparse available experiments. We explore the rule of Toburen which scales 
+all the molecular ionization cross section when divided by the number of 
+weakly bound valence electrons $\nu_{\alpha}$ given by Eq.~(\ref{27}). 
+We found the rule scales much better when normalizing our theoretical 
+ionization cross sections to the number $\nu_{\alpha}^{\text{CDW}}$ 
+given by Eq.~(\ref{eq:scalingCDW}). Finally, we attempt to improve the 
+stoichiometric model by using the Mulliken charge to define a new model 
+containing fractional rather than integer proportions. No substantial 
+correction was found, which indicates that the SSM works quite well.
+By inspecting the molecular binding energy from quantum mechanical 
+structure calculations, we were able to understand the values defined
+for $\nu_{\alpha}^{\text{CDW}}$.
 
-We have calculated ionization cross sections by impact of antiprotons, H$^{+}
-$, He$^{2+}$, Be$^{4+}$, C$^{6+}$,\ and O$^{8+}$ with molecule involved in
-biological basis containing H, C, N, O, P and S with the CDW method. \ The
-importance of the influence of $Z\ $was observed in the mean energy $%
-\overline{E}_{\alpha }\ $and angle $\overline{\theta }_{\alpha }.$ For a
-given target $\alpha ,$ as $Z$ increases $\overline{E}_{\alpha }$ increases
-but $\overline{\theta }_{\alpha }$ decreases \ At high impact energy, say
-larger than 1 MeV/amu these values tend to the ones of the Born
-approximation which embodies the simple Z$^{2}$ law. Sixteen molecules were
-investigated using the simple stoichiometric model. Results for the six DNA
-basis were presented and compared with the sparse available experiments \ We
-explore the rule of Toburen which scales all the molecular ionization cross
-section when divided by the number of weakly bound valence electrons $\nu
-_{\alpha }$ given by Eq.(\ref{27})$.$ We have found the rule scales much
-better when normalizing our theoretical ionization cross sections to the
-number\ $\upsilon _{\alpha }^{\prime }$ given by Eq.(\ref{35}). And finally
-we attempt to improve the stoichiometric model by the use of the Mulliken
-charge to redefine a new stoichiometric model containing continuum rather
-than integer proportions. NO substantial correction was found indicating
-that the SSM works quite well.
-
-Our aims is this article is to provide the tools to estimate any inelastic
-parameter parameter -such as the emission angle, the emitted mean energy and
-cross section- by the impact of any multicharged \ on any molecule
-containing H, C, N, O, P and S, with the help of the stoichimetrical model.
-Our goal was quite \textbf{pretencioso}, considering the simplicity of our
-proposal. However we think our results could be used to estimate the
-ionization magnitude with an acceptable level of uncertailties
+The main objective of this article is to provide the tools to estimate 
+any inelastic parameter parameter --such as emission angle, emitted mean 
+energy and cross section-- by the impact of any multicharged on any 
+molecule containing H, C, N, O, P and S, with the help of the 
+stoichimetrical model. Our goal was quite ambitious, considering the 
+simplicity of our proposal. However, we think our results could be used 
+to estimate the ionization magnitude with an acceptable level of 
+uncertainty.
 
 \bigskip
-
-\section{References}
 
@@
 
+\bibitem{clementi}
+E. Clementi, C. Roetti,
+At. Data Nucl. Data Tables 14, 177--478 (1974).
+
 \end{thebibliography}

### 2019-09-13 NewMonti25.tex
version25 sent
scaling figure + small arranges in text

--- 2019-09-06 NewMonti24.tex
@@
 \begin{center}
-\begin{tabular}{|p{0.06\textwidth}|p{0.65\textwidth}|}
+\begin{tabular}{|p{0.06\textwidth}|p{0.62\textwidth}|}
 \hline
@@
      & guanine (C$_5$H$_5$N$_5$O), thymine (C$_5$H$_6$N$_2$O$_2$), \\
-     & uracil (C$_4$H$_4$N$_2$O$_2$), DNA backbone (C$_5$H$_{10}$O$_5$P), \\
+     & uracil (C$_4$H$_4$N$_2$O$_2$), tetrahydrofuran (C$_4$H$_8$O), \\
+     & DNA backbone (C$_5$H$_{10}$O$_5$P), \\
      & dry DNA (C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$)\\
@@
 \end{tabular}
-\caption{Sixteen molecular targets of our interest classified in three 
+\caption{Seventeen molecular targets of our interest classified in three 
 families.}
@@
 \end{equation}
-where
+where $\nu_{\alpha}$ is the number of weakly bound electrons of the atom
+$\alpha$, given by
 \begin{equation}
@@
 Ref.~\cite{itoh2013} for proton impact on uracil and adenine.
+
+\begin{figure}[t!]
+\includegraphics[width=\textwidth]{figuras/scaling85.eps}
+\caption{Ionization cross section per weakly bound electron using
+(a) Eq.~(\ref{eq:nelec}) and (b) Eq.~(\ref{eq:scalingCDW}).}
+\label{fig:newscaling}
+\end{figure}
 Figure 4a shows $\sigma_{e}$ calculated with the CDW as a function of 
-the impact velocity for different projectile charges computed with the 
-SSM for the sixteen molecular targets displayed in 
+the impact energy for different projectile charges computed with the 
+SSM for the seventeen molecular targets displayed in 
 Table~\ref{tab:families}. The universality with $Z$ is the one provided 
@@
 \centering
-\includegraphics[width=0.95\textwidth]{energylevels/DNA.eps}
+%\includegraphics[width=0.95\textwidth]{energylevels/DNA.eps}
+\includegraphics[width=0.95\textwidth]{DNA.eps}
 \end{figure}
@@
 We calculated ionization cross sections by impact of antiprotons, 
-H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$ for sixteen 
+H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$ for seventeen 
 molecules containing H, C, N, O, P and S with the CDW method. The 
@@
 energy, say larger than 1 MeV/amu, these values converge to the Born 
-approximation, which embodies the simple $Z^{2}$ law. The sixteen 
+approximation, which embodies the simple $Z^{2}$ law. The seventeen 
 molecules selected were investigated using the simple stoichiometric 

### 2019-09-15 NewMonti25.tex
atomic scaling fig added + fontsize modified

@@
 molecules (see Table~\ref{tab:families}) by the impact of antiprotons,
-H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$,\ and O$^{8+}$. Furthermore, 
+H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$,\ and O$^{+8}$. Furthermore, 
 in Section 3, we investigate different DNA and RNA molecules
@@
 essential elements by the impact of six different projectiles: 
-antiprotons, H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$. 
+antiprotons, H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
 To reduce the resulting 36 magnitudes into a single consistent 
@@
 solid-red, blue, magenta, olive and orange for antiprotons, 
-H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$, respectively. 
+H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$, respectively. 
 Notably, there is no complete tabulation of ionization of atoms by 
@@
 in this article will be of help for future works.
+\begin{figure}
+\includegraphics[width=\textwidth]{figuras/atomicscaling.eps}
+\caption{.}
+\label{eq:atomscaling}
+\end{figure}
 
@@
  \multirow{4}{*}{DNA} & adenine (C$_5$H$_5$N$_5$), 
-                        cytosine (C$_4$H$_5$N$_2$O), \\
+                        cytosine (C$_4$H$_5$N$_3$O), \\
      & guanine (C$_5$H$_5$N$_5$O), thymine (C$_5$H$_6$N$_2$O$_2$), \\
@@
 {\it et al.}~\cite{itoh2013}, but for the same target our theory fails 
-by a factor of two for the impact of C$^{4+}$ and O$^{6+}$ ions. 
+by a factor of two for the impact of C$^{+4}$ and O$^{+6}$ ions. 
 Nonetheless, it should be stated that our theoretical results coincide 
@@
 \begin{figure}[t!]
-\includegraphics[width=\textwidth]{figuras/scaling85.eps}
+\includegraphics[width=\textwidth]{figuras/molscaling85.eps}
 \caption{Ionization cross section per weakly bound electron using
@@
 \end{equation}
-For impact of H$^{+}$ and He$^{2+~}$ on water at 1 MeV/amu, we obtain 
+For impact of H$^{+}$ and He$^{+2}$ on water at 1 MeV/amu, we obtain 
 $\overline{E}_{\text{H}_{2}\text{O}}=43.7$ and 45 eV, while the 
@@
 52.2 eV, respectively. Just to stress the importance of the projectile 
-charge, for O$^{8+}$ on water, at the same impact energy 1 MeV/amu, 
+charge, for O$^{+8}$ on water, at the same impact energy 1 MeV/amu, 
 we obtained $\overline{E}_{\text{H}_{2}\text{O}}=54.7$ eV, which is 25\% 
-larger than 
-proton impact result. It is worth noting that there should not be any 
-difference if the calculations were carried in first Born approximation. 
-We will came back on this issue later.
+larger than proton impact result. It is worth noting that there should 
+not be any difference if the calculations were carried in first Born 
+approximation. We will came back on this issue later.
 
@@
 in the intermediate energy region, as observed in Figure 6. 
-For example, for C$^{6+}$ impact, the Bragg peak occurs at 0.3 MeV/amu, 
+For example, for C$^{+6}$ impact, the Bragg peak occurs at 0.3 MeV/amu, 
 where $\overline{\theta}_{\alpha}$, computed with the CDW method, is 
@@
 \hline
-Adenine & +0.32 & +0.23 & --0.55 &       & C$_{4.92}$H$_{4.77}$N$_{5.14}$ \\ 
+Adenine & +0.32 & +0.23 & --0.55 &       & 
+C$_{4.92}$H$_{4.77}$N$_{5.14}$ \\ 
 \hline
-Cytosine & +0.28 & +0.21 & --0.56 & --0.53 & C$_{3.93}$H$_{2.79}$N$_{5.14}$O$_{1.13}$ \\ 
+Cytosine & +0.28 & +0.21 & --0.56 & --0.53 & 
+C$_{3.93}$H$_{2.79}$N$_{5.14}$O$_{1.13}$ \\ 
 \hline
-Guanine & +0.46 & +0.20 & --0.58 & --0.36 & C$_{4.89}$H$_{4.80}$N$_{5.15}$O$_{1.09}$ \\ 
+Guanine & +0.46 & +0.20 & --0.58 & --0.36 & 
+C$_{4.89}$H$_{4.80}$N$_{5.15}$O$_{1.09}$ \\ 
 \hline
-Thymine & +0.20 & +0.19 & --0.54 & --0.52 & C$_{4.95}$H$_{1.95}$N$_{6.13}$O$_{2.13}$ \\ 
+Thymine & +0.20 & +0.19 & --0.54 & --0.52 & 
+C$_{4.95}$H$_{1.95}$N$_{6.13}$O$_{2.13}$ \\ 
 \hline
@@
 shell for all O would seem to be equal to 4, as previously setted by the 
-scaling rule Eq.~(\ref{eq:scalingCDW}). The N case is not as straightfoward;
-the electrons that would correspond to the $2s$ are located just below
-the line. The $\nu_{\alpha }^{\text{CDW}}$ value given for N would 
-suggest that a significant amount of electron density from the secondary gap 
-is shared with the valence band.
+scaling rule Eq.~(\ref{eq:scalingCDW}). The N case is not as 
+straightfoward; the electrons that would correspond to the $2s$ are 
+located just below the line. The $\nu_{\alpha }^{\text{CDW}}$ value 
+given for N would suggest that a significant amount of electron density 
+from the secondary gap is shared with the valence band.
 
@@
 \centering
-%\includegraphics[width=0.95\textwidth]{energylevels/DNA.eps}
-\includegraphics[width=0.95\textwidth]{DNA.eps}
+\includegraphics[width=\textwidth]{figuras/levelsDNA.eps}
 \end{figure}
@@
 We now return to the calculation of the mean electron energy of H$^{+}$ 
-and He$^{2+}$ in water, $\overline{E}_{\text{H}_2\text{O}}$. If we 
+and He$^{+2}$ in water, $\overline{E}_{\text{H}_2\text{O}}$. If we 
 consider that the residual charge of each hydrogen in water is 
-$q_{\text{H}}=+0.35$~\cite{rappe1991}, which implies that on oxygen we have a 
-residual charge of $q_{\text{O}}=-0.7$, we could re-write the formula of water 
-using Eq.~(\ref{120}) as H$_{1.3}$O$_{1.17}$ by considering 
+$q_{\text{H}}=+0.35$~\cite{rappe1991}, which implies that on oxygen we 
+have a residual charge of $q_{\text{O}}=-0.7$, we could re-write the 
+formula of water using Eq.~(\ref{120}) as H$_{1.3}$O$_{1.17}$ by 
+considering 
 $n_{\text{O}}^{\text{CDW}}\simeq 4$ and 
 $n_{\text{H}}^{\text{CDW}}\simeq 1$. Recalculating mean electron energy 
-by impact of H$^{+}$ and He$^{2+}$ on water at 1 MeV/amu, we obtain
+by impact of H$^{+}$ and He$^{+2}$ on water at 1 MeV/amu, we obtain
 $\overline{E}_{\text{H}_2\text{O}}=46.2$ and 47.6 eV. Our results 
@@
 the atom $\alpha$, $E_{\alpha nl}$~\cite{clementi}, we obtain 
-$f=0.70$ and $0.71$ on water at 1 MeV/amu for H$^{+}$ and He$^{2+}$, 
+$f=0.70$ and $0.71$ on water at 1 MeV/amu for H$^{+}$ and He$^{+2}$, 
 which differ from the respective experimental values $f=0.81$ and $0.80$.
@@
 $\overline{E}_{\text{H}_2\text{O}}=53.2$ and 54.6 eV for H$^{+}$ and 
-He$^{2+}$ on water at 1 MeV/amu, respectively, which are much closer to
+He$^{+2}$ on water at 1 MeV/amu, respectively, which are much closer to
 the experimental values. If we add $\delta E$ to the numerator of 
@@
 We calculated ionization cross sections by impact of antiprotons, 
-H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$ for seventeen 
+H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$ for seventeen 
 molecules containing H, C, N, O, P and S with the CDW method. The 
@@
 J. E. Miraglia and M. S. Gravielle. Ionization of the
-He, Ne, Ar, Kr, and Xe isoelectronic series by proton impact. Phys Rev A 
-\textbf{78}, 052705 (2008)
+He, Ne, Ar, Kr, and Xe isoelectronic series by proton impact. 
+Phys Rev A \textbf{78}, 052705 (2008)
 
@@
 J. E. Miraglia, Ionization of He, Ne, Ar, Kr, and Xe
-by proton impact: Single differential distributions. Phys Rev A \textbf{79},
-022708 (2009).
+by proton impact: Single differential distributions. 
+Phys. Rev. A \textbf{79}, 022708 (2009).
 
@@
 Ionization probabilities of Ne, Ar, Kr, and Xe by
-proton impact for different initial states and impact energies. Nucl. Instr.
-Meth. Phys. Res. B 407 (2017) 236-243.
+proton impact for different initial states and impact energies. 
+Nucl. Instr. Meth. Phys. Res. B 407 (2017) 236-243.
 
@@
 J. E. Miraglia. Shell-to-shell ionization cross
-sections of antiprotons, H$^{+}$, \ He$^{2+},$ Be$^{4+},$ C$^{6+}$ and O$%
-^{8+}$ on H, C, N, O, P, and S atoms To be published Archive 2019.
+sections of antiprotons, H$^{+}$, He$^{+2},$ Be$^{+4},$ C$^{+6}$ and 
+O$^{+8}$ on H, C, N, O, P, and S atoms To be published Archive 2019.
 
@@
 A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D.
-Rivarola,~Cross sections for ionization of uracil by MeV-energy-proton
-impact,\ Physical Review A 88, 052711 (2013)
+Rivarola, Cross sections for ionization of uracil by MeV-energy-proton
+impact, 
+Phys. Rev. A 88, 052711 (2013)
 
@@
 P F Weck, A N Agnihotri, S Nandi, and L C Tribedi. Ionization of RNA-uracil
-by highly charged carbon ions. J. Phys.: Conf. Ser. 373, 012004 (2012).
+by highly charged carbon ions.
+J. Phys.: Conf. Ser. 373, 012004 (2012).
 
@@
 collisions with highly charged carbon and oxygen ions of energy 100 keV to
-78 MeV.\ \ Phys Rev A 85, 032711 (2012).
+78 MeV. 
+Phys. Rev. A 85, 032711 (2012).
 
@@
 W. E. Wilson and L. H. Toburen. Electron emission from
-proton ---hydrocarbon-molecule collisions at 0.3---2.0 MeV. PHYSICAL REVIEW
-A\ 11 1303 (1975).
+proton --hydrocarbon-molecule collisions at 0.3--2.0 MeV. 
+Phys. Rev. A 11, 1303 (1975).
 
@@
 emission from methane, ammonia, monomethylamine, and dimethylamine by 0.25
-to 2.0 MeV protons. J. Chem. Phys. 64, 2616 (1976).
+to 2.0 MeV protons. 
+J. Chem. Phys. 64, 2616 (1976).
 
@@
 Multiscale approach to the physics of radiation
-damage with ions. E. Surdutovich and A. V. Solov'yov, arXiv:1312.0897v,
-(2013)
+damage with ions. E. Surdutovich and A. V. Solov'yov, 
+arXiv:1312.0897v, (2013)
 
@@
 A.V.Solov'yov,\ Ionization of biomolecular targets by ion impact: input data
-for radiobiological applications. Journal of Physics: Conference Series 438
+for radiobiological applications. 
+Journal of Physics: Conference Series 438
 (2013) 012015
@@
 Jung-Goo Lee, Ho Young Jeong, and Hosull Lee, Charges of
-Large Molecules Using Reassociation of Fragments. Bull. Korean Chem. Soc.24\
-2003, 369 .
+Large Molecules Using Reassociation of Fragments. 
+Bull. Korean Chem. Soc.24 2003, 369 .
 
 \bibitem{rappe1991} 
-A. K. Rappe, A. K.and W. A. Goddard III,. J. Phys. Chem. 
-\textbf{95 (}1991) 3358.
+A. K. Rappe, A. K.and W. A. Goddard III,. 
+J. Phys. Chem. \textbf{95 (}1991) 3358.
 
@@
 Electron production in proton collisions with atoms and molecules: energy
-distributions. Rev. Mod. Phys. \textbf{64}, 44-490 (1992).
+distributions. 
+Rev. Mod. Phys. \textbf{64}, 44-490 (1992).
 

### 2019-09-16 NewMonti25.tex
DNA figure in working progress

@@
 in Section 3, we investigate different DNA and RNA molecules
-such as adenine, cytosine, guanine, thymine, uracil, and also DNA 
-backbone.
+such as adenine, cytosine, guanine, thymine, uracil, tetrahydrofuran 
+(THF), pyrimidine and also DNA backbone.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Theory: Ionization of Atoms}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\begin{figure}[H]
+\centering
+%\includegraphics[width=\textwidth]{figuras/atomicscaling.eps}
+\includegraphics[width=0.7\textwidth]{figuras/Fig_finales/Fig1.eps}
+\caption{Scaled total ionization cross section of six atomic targets 
+by impact of six projectiles.}
+\label{eq:atomscaling}
+\end{figure} 
 In Figure 1, we report our total ionization results for the six 
@@
 in this article will be of help for future works.
-\begin{figure}
-\includegraphics[width=\textwidth]{figuras/atomicscaling.eps}
-\caption{.}
-\label{eq:atomscaling}
-\end{figure}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Ionization of Molecules}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{center}
-\begin{tabular}{|p{0.06\textwidth}|p{0.62\textwidth}|}
+\begin{tabular}{|p{0.06\textwidth}|p{0.56\textwidth}|}
 \hline
- CH  & CH$_4$, C$_2$H$_2$, C$_2$H$_4$, C$_2$H$_6$, and C$_6$H$_6$ \\
+ CH  & CH$_4$, C$_2$H$_2$, C$_2$H$_4$, C$_2$H$_6$, C$_6$H$_6$ \\
 \hline
- CHN & C$_5$H$_5$N, C$_4$H$_4$N$_2$, C$_2$H$_7$N, and CH$_5$N \\
+ CHN & C$_5$H$_5$N, C$_4$H$_4$N$_2$, C$_2$H$_7$N, CH$_5$N \\
 \hline
- \multirow{4}{*}{DNA} & adenine (C$_5$H$_5$N$_5$), 
-                        cytosine (C$_4$H$_5$N$_3$O), \\
-     & guanine (C$_5$H$_5$N$_5$O), thymine (C$_5$H$_6$N$_2$O$_2$), \\
-     & uracil (C$_4$H$_4$N$_2$O$_2$), tetrahydrofuran (C$_4$H$_8$O), \\
-     & DNA backbone (C$_5$H$_{10}$O$_5$P), \\
-     & dry DNA (C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$)\\
+ \multirow{5}{*}{DNA} 
+     & C$_5$H$_5$N$_5$ (adenine), C$_4$H$_5$N$_3$O (cytosine), \\
+     & C$_5$H$_5$N$_5$O (guanine), C$_5$H$_6$N$_2$O$_2$ (thymine), \\
+     & C$_4$H$_4$N$_2$O$_2$ (uracil), C$_4$H$_8$O (THF), \\
+     & C$_5$H$_{10}$O$_5$P (DNA backbone), \\
+     & C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$ (dry DNA) \\
 \hline
@@
 In Figure 2, we report the total ionization cross sections by the 
-impact of multicharged ions for the four fundamental DNA components: 
-adenine, cytosine, guanine and thymine. Our reports for uracil and 
-DNA backbone containing P are given in Figure 3. For adenine, the 
-agreement with the experimental data available in our range of validity 
-is quite good. For uracil, we have a puzzling situation: our results 
-show good agreement with the experiments by proton impact of Itoh 
-{\it et al.}~\cite{itoh2013}, but for the same target our theory fails 
-by a factor of two for the impact of C$^{+4}$ and O$^{+6}$ ions. 
+impact of multicharged ions for adenine, cytosine, guanine and thymine. 
+For adenine, the agreement with the experimental data 
+available (circles)~\cite{iriki2011} is quite good in our range of validity. 
+To the best of our knowledge, there are not experimental data on 
+ion--collision ionization for the rest of the molecules. We included 
+electron impact measurements (right--oriented triangles)~\cite{mozejko2003} 
+for incident energies greater than 500keV, were good agreement is found 
+with proton ionization for all the molecules. 
+%In fact, recent models for electron impact in complex biomolecules 
+%have been under progress~\ref{tan2018}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\textwidth]{figuras/Fig_finales/Fig2.eps}
+\caption{Present ionization cross section by impact of six projectiles, 
+and experimental values for proton and electron ionization.}
+\label{eq:crossDNA}
+\end{figure}
+
+Our reports for uracil, DNA backbone, pyrimidine and THF are given in 
+Figure 3. For uracil, we have good agreement with the experimental 
+proton impact measurements by Itoh~{\it et al.}~\cite{itoh2013}. 
+However, for the same target, our theory fails by a factor of two for 
+the experimental ionization values by the impact of C$^{+4}$~(square symbols), 
+O$^{+6}$~(circle symbols) and O$^{+8}$~(triangle--down symbols) 
+ions~\cite{agnihotri2012,agnihotri2013}. 
 Nonetheless, it should be stated that our theoretical results coincide 
@@
 possible misstep of the experiments. 
+For pyrimidine, we show comparison of our results with experimental 
+proton~\cite{wolff2014} and electron~\cite{bug2017} ionization. 
+The electron impact measurements agree with our calculations for energies
+higher than 500keV. Unexpectedly, the proton impact cross sections are
+significantly lower than our findings. 
+The THF molecule results are compared with proton~\cite{wang2016} and 
+electron~\cite{wolf2019,bug2017,fuss2009} impact measurements, showing
+overall good agreement with our theory.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\textwidth]{figuras/Fig_finales/Fig3.eps}
+\caption{Present ionization cross section by impact of six projectiles, 
+and experimental values for proton and electron ionization.}
+\label{eq:crossDNA}
+\end{figure}
 
@@
 
+\bibitem{iriki2011}
+Y. Iriki, Y. Kikuchi, M. Imai, and A. Itoh
+Phys. Rev. A \textbf{84} 052719 (2011).
+
+\bibitem{mozejko2003}
+P. Mozejko and L. Sanche, Radiat Environ. 
+Biophys \textbf{42}, 201 (2003).
+
+\bibitem{tan2018}
+H. Q. Tan, Z. Mi, and A. A. Bettiol, 
+Simple and universal model for electron-impact ionization of complex biomolecules, 
+Phys. Rev. E \text{97}, 032403 (2018)
+
 \bibitem{itoh2013} 
-A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D.
-Rivarola, Cross sections for ionization of uracil by MeV-energy-proton
-impact, 
-Phys. Rev. A 88, 052711 (2013)
+A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D. Rivarola, 
+Cross sections for ionization of uracil by MeV-energy-proton impact, 
+Phys. Rev. A 88, 052711 (2013).
 
@@
 Phys. Rev. A 85, 032711 (2012).
+
+\bibitem{agnihotri2013}
+A N Agnihotri, S Kasthurirangan, S Nandi, A Kumar, C Champion,, H Lekadir, 
+J Hanssen, P FWeck, M E Galassi, R D Rivarola, O Fojon and L C Tribedi, 
+Absolute total ionization cross sections of uracil (C4H4N2O2) in 
+collisions with MeV energy highly charged carbon, oxygen and fluorine ions
+J. Phys. B \textbf{46}, 185201 (2013).
+
+\bibitem{wolff2014}
+W. Wolff, H. Luna, L. Sigaud, A. C. Tavares, and E. C. Montenegro
+Absolute total and partial dissociative cross sections of pyrimidine
+at electron and proton intermediate impact velocities
+J. Chem. Phys. \textbf{140}, 064309 (2014).
+
+\bibitem{bug2017}
+M. U. Bug, W. Y. Baek, H. Rabus, C. Villagrasa, S. Meylan, A. B. Rosenfeld,
+An electron-impact cross section data set (10 eV--1 keV) of DNA
+constituents based on consistent experimental data: A requisite for 
+Monte Carlo simulations,
+Rad. Phys. Chem. \textbf{130} 459--479 (2017).
+
+\bibitem{wang2016}
+M. Wang, B. Rudek, D. Bennett, P. de Vera, M. Bug, T. Buhr, W. Y. Baek, 
+G. Hilgers, H. Rabus, 
+Cross sections for ionization of tetrahydrofuran by protons at energies 
+between 300 and 3000 keV
+Phys. Rev. A \textbf{93}, 052711 (2016).
+
+\bibitem{wolf2019}
+W. Wolff, B. Rudek, L. A. da Silva, G. Hilgers, E. C. Montenegro, 
+M. G. P. Homem,
+Absolute ionization and dissociation cross sections of tetrahydrofuran:
+Fragmentation--ion production mechanisms
+J. Chem. Phys. \textbf{151}, 064304 (2019).
+
+\bibitem{fuss2009}
+M. Fuss, A. Muñoz, J. C. Oller, F. Blanco, D. Almeida, P. Limão-Vieira, 
+T. P. D. Do, M. J. Brunger, G. García,
+Electron-scattering cross sections for collisions with tetrahydrofuran 
+from 50 to 5000 eV
+Phys. Rev. A \textbf{80}, 052709 (2009).
 

### 2019-09-18 NewMonti25.tex
added experiments on DNA mols
changed colors

@@
 
-\begin{figure}[H]
-\centering
-%\includegraphics[width=\textwidth]{figuras/atomicscaling.eps}
-\includegraphics[width=0.7\textwidth]{figuras/Fig_finales/Fig1.eps}
-\caption{Scaled total ionization cross section of six atomic targets 
-by impact of six projectiles.}
-\label{eq:atomscaling}
-\end{figure} 
-In Figure 1, we report our total ionization results for the six 
-essential elements by the impact of six different projectiles: 
+In Fig.~\ref{fig:atomscaling}, we report our total ionization results 
+for the six essential elements by the impact of six different projectiles: 
 antiprotons, H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
@@
 H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$, respectively. 
+The charge state of the projectiles are also given in the figures.
 Notably, there is no complete tabulation of ionization of atoms by 
@@
 
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig1.eps}
+\caption{Scaled total ionization cross section of six atomic targets 
+by impact of multicharged projectiles.}
+\label{fig:atomscaling}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{The stoichiometric model}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The classification defined is given in Table~\ref{tab:families}.
-\begin{table}
+
+\begin{table}[H]
 \begin{center}
-\begin{tabular}{|p{0.06\textwidth}|p{0.56\textwidth}|}
+\begin{tabular}{|p{0.06\textwidth}|p{0.75\textwidth}|}
 \hline
- CH  & CH$_4$, C$_2$H$_2$, C$_2$H$_4$, C$_2$H$_6$, C$_6$H$_6$ \\
+ CH  & CH$_4$ (methane), C$_2$H$_2$ (acetylene), \\
+     & C$_2$H$_4$ (ethene), C$_2$H$_6$ (ethane), C$_6$H$_6$ (benzene) \\
 \hline
- CHN & C$_5$H$_5$N, C$_4$H$_4$N$_2$, C$_2$H$_7$N, CH$_5$N \\
+ CHN & C$_5$H$_5$N (pyridine), C$_4$H$_4$N$_2$ (pyrimidine), \\
+& C$_2$H$_7$N 
+(dimenthylamine), CH$_5$N (monomethylamine) \\
 \hline
- \multirow{5}{*}{DNA} 
+ \multirow{4}{*}{DNA} 
      & C$_5$H$_5$N$_5$ (adenine), C$_4$H$_5$N$_3$O (cytosine), \\
@@
      & C$_4$H$_4$N$_2$O$_2$ (uracil), C$_4$H$_8$O (THF), \\
-     & C$_5$H$_{10}$O$_5$P (DNA backbone), \\
-     & C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$ (dry DNA) \\
+     & C$_5$H$_{10}$O$_5$P (DNA backbone), C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$ (dry DNA) \\
 \hline
 \end{tabular}
-\caption{Seventeen molecular targets of our interest classified in three 
-families.}
+\caption{Molecular targets of our interest classified in three families.}
 \label{tab:families}
@@
 
-In Figure 2, we report the total ionization cross sections by the 
-impact of multicharged ions for adenine, cytosine, guanine and thymine. 
-For adenine, the agreement with the experimental data 
-available (circles)~\cite{iriki2011} is quite good in our range of validity. 
-To the best of our knowledge, there are not experimental data on 
-ion--collision ionization for the rest of the molecules. We included 
-electron impact measurements (right--oriented triangles)~\cite{mozejko2003} 
-for incident energies greater than 500keV, were good agreement is found 
-with proton ionization for all the molecules. 
-%In fact, recent models for electron impact in complex biomolecules 
-%have been under progress~\ref{tan2018}.
+We report the total ionization cross sections by the impact of 
+multicharged ions for adenine, cytosine, guanine and thymine in 
+Fig.~\ref{fig:crossDNA_1}. For adenine, the agreement with the 
+experimental data available (circles)~\cite{iriki2011} is very good 
+in our range of validity. To the best of our knowledge, there are not 
+experimental data on ion--collision ionization for the rest of the 
+molecules. We included electron impact measurements (right--oriented 
+triangles)~\cite{rahman2016} with the corresponding equivelocity 
+conversion for incident energies higher than 500~keV. In this region, 
+the proton and electron cross section should agree. Although the electron 
+impact measurements are above our findings for all the molecular targets, 
+it is worth stating that our results agree very well with other 
+theoretical predictions~\cite{mozejko2003,tan2018}. The symbols used to 
+make reference to the proton and electron experimental data will be kept 
+for subsequent figures.
 
-\begin{figure}[H]
+\begin{figure}[t!]
 \centering
-\includegraphics[width=0.7\textwidth]{figuras/Fig_finales/Fig2.eps}
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
 \caption{Present ionization cross section by impact of six projectiles, 
 and experimental values for proton and electron ionization.}
-\label{eq:crossDNA}
+\label{fig:crossDNA_1}
 \end{figure}
 
-Our reports for uracil, DNA backbone, pyrimidine and THF are given in 
-Figure 3. For uracil, we have good agreement with the experimental 
-proton impact measurements by Itoh~{\it et al.}~\cite{itoh2013}. 
+Our calculations for uracil, DNA backbone, pyrimidine and THF are given in 
+Fig.~\ref{fig:crossDNA_2}. 
+For uracil, we have good agreement with the experimental 
+proton impact measurements (triangle--up) by Itoh~{\it et al.}~\cite{itoh2013}. 
 However, for the same target, our theory fails by a factor of two for 
-the experimental ionization values by the impact of C$^{+4}$~(square symbols), 
-O$^{+6}$~(circle symbols) and O$^{+8}$~(triangle--down symbols) 
+the experimental ionization values by the impact of 
+C$^{+4}$~(squares), O$^{+6}$~(circles) and O$^{+8}$~(triangles--down) 
 ions~\cite{agnihotri2012,agnihotri2013}.
@@
 possible misstep of the experiments. 
-For pyrimidine, we show comparison of our results with experimental 
-proton~\cite{wolff2014} and electron~\cite{bug2017} ionization. 
-The electron impact measurements agree with our calculations for energies
-higher than 500keV. Unexpectedly, the proton impact cross sections are
-significantly lower than our findings. 
-The THF molecule results are compared with proton~\cite{wang2016} and 
-electron~\cite{wolf2019,bug2017,fuss2009} impact measurements, showing
+For pyrimidine, we show comparison of our results with experimental data
+for proton (circles with dash)~\cite{wolff2014} and electron
+(stars)~\cite{bug2017} ionization. The electron impact measurements 
+agree with our calculations for energies higher than 500keV. 
+Unexpectedly, the proton impact cross sections are significantly lower 
+than our findings. 
+The THF molecule results are compared with proton (squares)~\cite{wang2016} 
+and electron~\cite{bug2017,wolf2019,fuss2009} impact measurements, showing
 overall good agreement with our theory.
 
-\begin{figure}[H]
+\begin{figure}[t!]
 \centering
-\includegraphics[width=0.7\textwidth]{figuras/Fig_finales/Fig3.eps}
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig3.eps}
 \caption{Present ionization cross section by impact of six projectiles, 
 and experimental values for proton and electron ionization.}
-\label{eq:crossDNA}
+\label{fig:crossDNA_2}
 \end{figure}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Scaling rule}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Toburen numbers}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The authors found it convenient to scale the experimental ionization 
-cross section in terms of the number of outer or weakly bound valence 
-electrons (total number of electrons minus the inner-shell ones). 
-We introduce the cross section per weakly bound electron or ionization 
-cross section per valence electron, $\sigma_{e}$, as
+cross section in terms of the number of active or weakly--bound valence 
+electrons $n_e$ (i.e. total number of electrons minus the K--shell).
+Following Toburen, we can define the ionization cross section per weakly 
+bound electron, $\sigma_{e}^T$, as
 \begin{equation}
-\sigma_{e}=\frac{\sigma_{M}}{N_{M}}=\frac{\sum\limits_{\alpha}
-n_{\alpha}\sigma_{\alpha}}{\sum\limits_{\alpha}n_{\alpha}\nu_{\alpha}}
-=\sigma_{e}(v)\,, 
+\sigma_{e}^T=\frac{\sigma_{M}}{n_e}=\frac{\sum\limits_{\alpha}
+n_{\alpha}\sigma_{\alpha}}{\sum\limits_{\alpha}n_{\alpha}\nu_{\alpha}^T}
+=\sigma_{e}^T(v)\,, 
 \label{27} 
 \end{equation}
-where $\nu_{\alpha}$ is the number of weakly bound electrons of the atom
-$\alpha$, given by
+where $\nu_{\alpha}^T$ are the Toburen numbers for each $\alpha$ atom 
+is given by
 \begin{equation}
-\nu_{\alpha}=\left\{ 
+\nu_{\alpha}^T=\left\{ 
 \begin{array}{ll}
+1, & \text{for H,} \\
 4, & \text{for C,} \\ 
 5, & \text{for N and P,} \\ 
-6, & \text{for O and S,}
+6, & \text{for O and S}\,.
 \end{array}\right.
@@
 \end{equation} 
-and $\nu_{\text{H}}=1$. The Toburen rule can be stated by saying that 
+The Toburen rule can be stated by saying that 
 $\sigma_{e}$ is a \textit{universal} parameter independent on the 
-molecule, which depends solely on the impact velocity. 
-In Ref.~\cite{toburen1976}, it was found experimentally that for proton 
-impact on some simple molecules, $\sigma_{e}$ results
-\begin{equation}
-\begin{array}{cccc}
-E\text{(MeV)}               & 0.25 & 1.00 & 2.00 \\ 
-\sigma_{e} (10^{-16}cm^{2}) & 0.39 & 0.17 & 0.11
-\end{array}
-\label{30}
-\end{equation}
-with an estimated error of about 20\%. A similar ratio was found in 
-Ref.~\cite{itoh2013} for proton impact on uracil and adenine.
+molecule, which depends solely on the impact velocity, and holds for 
+high impact energies (i.e. 0.25--5 Mev/amu).
+%In Ref.~\cite{toburen1976}, it was found experimentally that for proton 
+%impact on some simple molecules, $\sigma_{e}$ results
+%\begin{equation}
+%\begin{array}{cccc}
+%E\text{(MeV)}               & 0.25 & 1.00 & 2.00 \\ 
+%\sigma_{e} (10^{-16}cm^{2}) & 0.39 & 0.17 & 0.11
+%\end{array}
+%\label{30}
+%\end{equation}
+%with an estimated error of about 20\%. A similar ratio was found in 
+%Ref.~\cite{itoh2013} for proton impact on uracil and adenine. 
+These $\nu_{\alpha}^T$ can be interpreted as the number of active 
+electrons in the collision. Of course, at very high energies also de 
+K--shell electrons will be ionized and these numbers will be different.
+A similar dependence with the number of weakly bound electrons was 
+found in Ref.~\cite{itoh2013} for proton impact on uracil and adenine.
 
 \begin{figure}[t!]
-\includegraphics[width=\textwidth]{figuras/molscaling85.eps}
-\caption{Ionization cross section per weakly bound electron using
-(a) Eq.~(\ref{eq:nelec}) and (b) Eq.~(\ref{eq:scalingCDW}).}
+\centering
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig4.eps}
+\caption{Scaled ionization cross section per weakly bound electron using
+(a)~the Toburen numbers $\nu_{\alpha}^T$, and (b) our proposed numbers
+$\nu_{\alpha}^{\text{CDW}}$.}
 \label{fig:newscaling}
 \end{figure}
-Figure 4a shows $\sigma_{e}$ calculated with the CDW as a function of 
+
+Our CDW results for $\sigma_{e}^T$ are shown in 
+Fig.~\ref{fig:newscaling}a as a function of 
 the impact energy for different projectile charges computed with the 
-SSM for the seventeen molecular targets displayed in 
-Table~\ref{tab:families}. The universality with $Z$ is the one provided 
-by Born approximation, i.e., $\sigma _{e}(Z)=Z^{2}\sigma_{e}(Z=1)$, 
-and it holds for large impact velocities, as shown Figure 4a.
+SSM for the molecular targets from Table~\ref{tab:families}. 
+The universality with $Z$ is the one provided 
+by Born approximation, i.e., $\sigma_{e}^T(Z)=Z^{2}\sigma_{e}^T(Z=1)$, 
+and it holds for large impact velocities, as shown 
+Fig.~\ref{fig:newscaling}a.
 Of course, for lower impact velocities, the CDW breaks the behavior of 
-the $Z^{2}$ rule. Although the Toburen rule holds for high energies, 
+the $Z^{2}$ rule. Although the Toburen scaling holds for high energies, 
 its performance is still not satisfactory: the universal band is quite 
-broad. The departure of our theoretical 
-results from the Toburen rule can be easily explained by the fact that 
-our atomic cross sections $\sigma_{\alpha}$ behave differently for 
-each atom in terms of the projectile charges. By inspecting Figure 1, 
-one can easily see that the rule $\sigma_{\alpha}/\nu_{\alpha}\sim
-\sigma_{e}$ is not well satisfied by the CDW. A much better general 
-atomic rule is given by
+broad.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{New scaling}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The departure of our theoretical 
+results from the Toburen rule can be easily understood %explained by the fact that 
+%our atomic cross sections $\sigma_{\alpha}$ behave differently for 
+%each atom in terms of the projectile charges. By 
+by inspecting Fig.~\ref{fig:atomscaling}. It can be noted that the 
+rule $\sigma_{\alpha}/\nu_{\alpha}^T\sim \sigma_{e}^T$, approximatelly 
+constant, is not well satisfied by the CDW. 
+For example, Fig.~\ref{fig:atomscaling} shows that the cross sections
+for O are actually very similar to the cross sections for C, suggesting 
+4 active electrons in O instead of 6. In the same way, the number of
+active electrons for N, P and S are also different from the 
+$\nu_{\alpha}^T$ of Eq.~(\ref{eq:nelec}).
+
+Based on the CDW results, we propose a new scaling,
 \begin{equation}
-\sigma_{e}^{\text{CDW}}=\frac{\sum\limits_{\alpha}
-n_{\alpha}\sigma_{\alpha}^{\text{CDW}}}{\sum\limits_{\alpha}n_{\alpha}
+\sigma_{e}=\frac{\sigma_M}{\sum\limits_{\alpha}n_{\alpha}
 \nu_{\alpha}^{\text{CDW}}},
@@
 \end{equation}
-where 
+where $\sigma_M$ follows Eq.~(\ref{eq:sumion}), and 
+$\nu_{\alpha}^{\text{CDW}}$ are the new active--electron numbers 
+per atom obtained from the CDW ionization cross sections for 
+different ions in H, C, N, O, P , and S targets. 
+Our proposed active--electron numbers are
 \begin{equation}
@@
 \begin{array}{ll}
-4,\ \ \  & \text{for C, N, and O,} \\ 
-4.5,\ \  & \text{for P and S}
+1, & \text{for H,} \\
+4, & \text{for C, N, and O,} \\ 
+4.5, & \text{for P and S}\,.
 \end{array}
@@
 \end{equation}
-and, obviously, $\nu_{\text{H}}^{\text{CDW}}=1$. The cross sections 
-$\sigma_{e}^{\text{CDW}}$ are plotted in Figure~4b. A much better sharp 
-band is observed, especially at high energy, where the theory is 
-expected to work. It will be interesting for experiments to cross-check 
-this theoretical prediction.
 
+The new scaled cross sections $\sigma_{e}$ are plotted in Figure~4b. 
+A much better sharp band is observed, especially for impact energies 
+$E=(0.5-8)$~MeV/amu for $Z=1$ and $Z=2$, and $E=(2.5-8)$~MeV/amu for 
+$Z>2$. In fact, the experimental data for ionization of adenine, 
+cytosine, thymine, guanine, uracil, pyrimidine and THF by proton impact 
+seems to corroborate the new scaling. We also included the electron impact
+ionization measurements from Figs.~\ref{fig:crossDNA_1} and 
+\ref{fig:crossDNA_2}. It will be interesting to cross--check for 
+experiments with higher projectile charge states.
+
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{|ll|ll|ll|}
+\hline
+ Molecule & $n_e$ &Molecule         & $n_e$ & Molecule             & $n_e$ \\
+\hline
+ H$_2$    & 2  & C$_2$H$_7$N         & 19    & C$_4$H$_5$N$_3$O     & 37    \\
+ H$_2$O   & 6  & C$_4$H$_8$O         & 28    & C$_5$H$_6$N$_2$O$_2$ & 42    \\
+ NH$_3$   & 7  & C$_4$H$_4$N$_2$     & 28    & C$_5$H$_5$N$_5$      & 45    \\
+ CH$_4$   & 8  & C$_6$H$_6$          & 30    & C$_5$H$_5$N$_5$O     & 49    \\
+ CH$_5$N  & 13 & C$_4$H$_4$N$_2$O$_2$& 36    & C$_5$H$_{10}$O$_5$P  & 54.5  \\
+ \hline
+\end{tabular}
+\caption{New scaling numbers for some molecular targets of biological interest.}
+\label{nn}
+\end{center}
+\end{table}
+
+By using Eq.~(\ref{eq:scalingCDW}), the number of active electrons 
+$n_e=\sum_{\alpha} n_{\alpha} \nu_{\alpha}^{\text{CDW}}$ can be redefined. 
+We give new values in Table~\ref{nn} for some molecules of interest.
+These values are very different from the ones proposed by Toburen and used by 
+other authors~\cite{itoh2013}.
+Moreover, an alternative way of showing the scaling can be attained by 
+plotting the ionization cross sections of molecules as a function of the 
+number of active electrons from Table~\ref{nn}. Our findings are displayed 
+in Fig.~\ref{fig:recta} for impact energies 0.5, 1 and 2 MeV. As can be 
+noted, the computed CDW ionization cross sections for all the molecules  
+show a linear dependence with the number of electrons from Table~\ref{nn}. 
+We obtain similar results even for $E=10$~MeV. The comparison with the 
+experimental data available shows very nice agreement, from the smallest 
+molecules, H$_2$, H$_2$O and CH$_4$, up to the most complex ones, like 
+adenine or guanine. In some cases, the experimental data were interpolated.
+Care was taken in such procedure.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.75\textwidth]{figuras/fig_recta.eps}
+\caption{.}
+\label{fig:recta}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Emitted electron energies}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-Figure 5 shows $\overline{E}_{\alpha}$ for six elements from 
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig5.eps}
+\caption{.}
+\label{fig:emittedener}
+\end{figure}
+
+Figure~\ref{fig:emittedener} shows $\overline{E}_{\alpha}$ for six elements from 
 Table~\ref{tab:families}. The range of impact velocities was shorten up 
@@
 
-In Figure 5, we estimate $\overline{E}_{\alpha}$ in the 0.5--2 a.u.
+In Figure~\ref{fig:emittedener} , we estimate $\overline{E}_{\alpha}$ in the 0.5--2 a.u.
 velocity range, or equivalently from 15 to 50 eV, for all the targets.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Emitted electron angles}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{equation}
-Figure 6 shows $\overline{\theta}_{\alpha}$ for our six elements of 
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig6.eps}
+\caption{.}
+\label{fig:emittedang}
+\end{figure}
+
+Figure~\ref{fig:emittedang} shows $\overline{\theta}_{\alpha}$ for our six elements of 
 interest. A new important dependence of $\overline{\theta}_{\alpha}$ 
@@
 is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
-in the intermediate energy region, as observed in Figure 6. 
+in the intermediate energy region, as observed in Figure~\ref{fig:emittedang}. 
 For example, for C$^{+6}$ impact, the Bragg peak occurs at 0.3 MeV/amu, 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{A modified stoichiometric model}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 In Table~\ref{tab:newstoi}, we display the charge $q_{\alpha}$ of four 
-DNA molecules. The last column shows the new stoichiometric formula
-found by implementing Eq.~(\ref{eq:newstoi}).
+DNA molecules.
+
 \begin{table}[H]
@@
 
-The previous formula can be rewritten by replacing the integer value 
-$n_{\alpha}$ by the fractional values $n_{\alpha}^{\prime}$. This 
-analog formulations are now implemented to compute the new ionization 
-cross sections, $\sigma^{\prime}$.
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\textwidth]{figuras/levelsDNA.eps}
+\caption{Molecular binding energies for four DNA molecules.}
+\label{fig:bindener}
+\end{figure}
 
-In Figure 8, we display the relative difference of ionization cross 
-sections 
-\begin{equation}
-e=\frac{\sigma^{\prime}-\sigma}{\sigma}\times 100
-\label{120}
-\end{equation}
-for the four DNA bases. The difference obtained is of just very few 
-percents, which indicates that the SSM is a quite robust model to treat 
-the type of molecule we are dealing with, and of course within the 
-range error that one can expect from the SSM.
-
-Our molecular binding energies of the outer electrons for adenine, 
-cytosine, guanine and thymine are shown in Figure~7. On the left side 
-of the figure, we show the atomic Hartree--Fock energies of the 
-constituent elements, which can give an idea of how the molecular levels 
-distribute. A dashed line around -0.8 a.u. is drawn to separate in two 
-the band levels of the outer electrons. The electrons in the molecular 
+The molecular binding energies of the outer electrons for adenine, 
+cytosine, guanine and thymine are shown in Fig.~\ref{fig:bindener}. 
+On the left side of the figure, we show the atomic Hartree--Fock energies 
+of the constituent elements, which can give an idea of how the molecular 
+levels distribute. A dashed line around $-0.8$~a.u. is drawn to separate 
+in two the band levels of the outer electrons. The electrons in the molecular 
 targets corresponding to the $2s$ of N and C in the atomic case are 
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=\textwidth]{figuras/levelsDNA.eps}
-\end{figure}
+By implementing Eq.~(\ref{eq:newstoi}), it is possible to determine a 
+new stoichiometric formula (last column of Table~\ref{tab:newstoi}). 
+Now, instead of having an integer number of atoms $n_{\alpha}$, we obtain 
+a fractional number $n_{\alpha}^{\prime}$. 
+Molecular cross sections $\sigma^{\prime}$ can be computed considering 
+such values. Relative errors for the ionization cross sections were 
+computed for the DNA bases from Table~\ref{tab:newstoi}. The differences 
+obtained were of just very few percents, which indicates that the modified 
+SSM is a quite robust model to handle these type of molecule within 
+the range error expected for this model.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Ionization of water}
 
-We now return to the calculation of the mean electron energy of H$^{+}$ 
-and He$^{+2}$ in water, $\overline{E}_{\text{H}_2\text{O}}$. If we 
-consider that the residual charge of each hydrogen in water is 
-$q_{\text{H}}=+0.35$~\cite{rappe1991}, which implies that on oxygen we 
-have a residual charge of $q_{\text{O}}=-0.7$, we could re-write the 
-formula of water using Eq.~(\ref{120}) as H$_{1.3}$O$_{1.17}$ by 
-considering 
-$n_{\text{O}}^{\text{CDW}}\simeq 4$ and 
-$n_{\text{H}}^{\text{CDW}}\simeq 1$. Recalculating mean electron energy 
-by impact of H$^{+}$ and He$^{+2}$ on water at 1 MeV/amu, we obtain
+%We now return to the calculation of the mean electron energy of H$^{+}$ 
+%and He$^{+2}$ in water, $\overline{E}_{\text{H}_2\text{O}}$. 
+Considering that the residual charge of each hydrogen in water is 
+$q_{\text{H}}=+0.35$~\cite{rappe1991}, we can imply that the residual charge 
+of oxygen is $q_{\text{O}}=-0.7$. Then, we could re-write the formula 
+of water using Eq.~(\ref{eq:newstoi}) as H$_{1.3}$O$_{1.17}$ (assuming
+$n_{\text{O}}^{\text{CDW}}\simeq 4$ and $n_{\text{H}}^{\text{CDW}}\simeq 1$). 
+Recalculating the mean electron energy by the impact of H$^{+}$ and 
+He$^{+2}$ on water at 1 MeV/amu, we obtain 
 $\overline{E}_{\text{H}_2\text{O}}=46.2$ and 47.6 eV. Our results 
@@
 
-Another parameter that can computed within our model is the fraction of
-energy carried by the electron $f$, which is defined as
+We can be compute the fraction of energy carried by 
+the electron $f$, which is defined as
 \begin{equation}
@@
 Using our shell-to-shell ionization cross sections 
-$\sigma_{\alpha nl}$~\cite{miraglia2019}, and atomic binding energies of 
-the atom $\alpha$, $E_{\alpha nl}$~\cite{clementi}, we obtain 
+$\sigma_{\alpha nl}$~\cite{miraglia2019}, and the atomic binding energies
+$E_{\alpha nl}$~\cite{clementi} of the atom $\alpha$, we obtain 
 $f=0.70$ and $0.71$ on water at 1 MeV/amu for H$^{+}$ and He$^{+2}$, 
@@
 
-The difference between our calculations and the experiments could be 
-attributed to the binding energy values of the molecular water~12.65 eV 
-and its atomic components, H (13.6 eV) and O (17.19 eV). This theoretical
-discrepancy goes beyond our independent atom approximation and so it 
-cannot be accounted for by our model. Once again, we could estimate this 
-contribution by resorting to the stoichiometric model. We can make an 
-asses for a maximum difference per molecule of water as
+The difference between our calculations and the experimental values 
+could be attributed to the binding energy values of the molecular 
+water~12.65 eV with respect to its atomic components, H (13.6 eV) and 
+O (17.19 eV). This theoretical discrepancy goes beyond our independent 
+atom approximation and it cannot be accounted for by our model. Once 
+again, we could estimate this contribution by resorting to the 
+stoichiometric model. We can make an assesment for a maximum difference 
+per molecule of water as 
 \begin{equation}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 $\overline{E}_{\alpha}$ and angle $\overline{\theta}_{\alpha}$. 
-For a given target $\alpha$, as $Z$ increases, $\overline{E}_{\alpha}$ 
-increases, but $\overline{\theta}_{\alpha}$ decreases. At high impact 
-energy, say larger than 1 MeV/amu, these values converge to the Born 
-approximation, which embodies the simple $Z^{2}$ law. The seventeen 
-molecules selected were investigated using the simple stoichiometric 
-model. Results for six DNA bases were presented and compared with the 
-sparse available experiments. We explore the rule of Toburen which scales 
-all the molecular ionization cross section when divided by the number of 
-weakly bound valence electrons $\nu_{\alpha}$ given by Eq.~(\ref{27}). 
+For a given target $\alpha$, as the nuclear charge of the projectile 
+$Z$ increases, so does the mean energy of emittion $\overline{E}_{\alpha}$. 
+Conversely, the mean angle of emission  $\overline{\theta}_{\alpha}$ 
+decreases. At high impact energy, say larger than 1 MeV/amu, these 
+values converge to the Born approximation, which embodies the simple 
+$Z^{2}$ law. The seventeen molecules selected were investigated using 
+the simple stoichiometric model. Results for eigth DNA bases were 
+presented and compared with the sparse available experiments. We explore 
+the rule of Toburen which scales all the molecular ionization cross 
+section when divided by the number of weakly bound valence electrons 
+$\nu_{\alpha}^T$ given by Eq.~(\ref{27}). 
 We found the rule scales much better when normalizing our theoretical 
@@
 containing fractional rather than integer proportions. No substantial 
-correction was found, which indicates that the SSM works quite well.
-By inspecting the molecular binding energy from quantum mechanical 
+correction was found, which indicates that our modified SSM works quite 
+well. By inspecting the molecular binding energy from quantum mechanical 
 structure calculations, we were able to understand the values defined
@@
 
+\bibitem{rahman2016}
+M. A. Rahman and E. Krishnakumar,
+Electron ionization of DNA bases,
+J. Chem. Phys. \textbf{144}, 161102 (2016).
+
 \bibitem{mozejko2003}
-P. Mozejko and L. Sanche, Radiat Environ. 
-Biophys \textbf{42}, 201 (2003).
+P. Mozejko and L. Sanche, 
+Cross section calculations for electron scattering from DNA and RNA bases.
+Radiat Environ. Biophys \textbf{42}, 201 (2003).
 

### 2019-09-18 NewMonti_C.tex
changed colors

--- 2019-09-05 NewMonti24.tex
@@
 \usepackage{graphicx}
-\usepackage{multirow}
+%\usepackage{multirow}
+%\usepackage{gensymb}
+\usepackage{float}
+%\usepackage{authblk}
+%\setcounter{MaxMatrixCols}{10}
 
-\usepackage{authblk}
-
-\setcounter{MaxMatrixCols}{10}
-%TCIDATA{OutputFilter=LATEX.DLL}
-%TCIDATA{Version=5.50.0.2953}
-%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
-%TCIDATA{BibliographyScheme=Manual}
-%TCIDATA{LastRevised=Thursday, March 07, 2019 14:11:39}
-%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
-%TCIDATA{Language=American English}
-
-%\input{tcilatex}
 \begin{document}
@@
 stoichiometric model}
-\author{author}
-\affil{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
-Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
 %\author{author}
-%\affil{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
-%Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
-%\affil{Fac. de Ciencias Exactas y Naturales, Universidad de Buenos Aires}
+%\affiliation{Consejo Nacional de Investigaciones Cient\'{\i}ficas y
+%T\'{e}cnicas - Universidad de Buenos Aires, Instituto de
+%Astronom\'{\i}a y F\'{\i}sica del Espacio, Pabell\'on IAFE, 1428 Buenos Aires, Argentina;}
+
 \date{\today }
@@
 
-\section{Introduction}
+\subsection{Scaling rule}
 
-The damage caused by the impact of multicharged heavy projectile has 
-become a field of interest because of its implementation in ion-beam 
-cancer therapy. The effectiveness of the radiation depends on the 
-choice of the ions. In particular, theoretical and experimental studies 
-with different projectiles have concluded that charged carbon ions 
-could be the most suitable ions to use. The study of such systems 
-represent a challenge from the theoretical point of view. The most 
-widely used method to compute ionization of multicharged atoms is the 
-first Born approximation. 
-This perturbative method warrants the $Z^{2}$ laws, where $Z$ is the 
-projectile charge. However, the damage concentrated in the vicinities 
-of the Bragg peak correspond to energies of hundreds of KeV/amu. 
-Precisely in this region, often refered to as the intermediate energy 
-region, the Born approximation starts to fail. Another theoretical 
-issue arises from the targets themselves; we are dealing with complex 
-molecules. This article deals precisely with these two aspects. 
-First, we perform more appropriate calculations on the primary damage 
-mechanism, i.e., atomic ionization by multicharged ions, which can 
-replace the Born results. Second, we inspect and use an stoichiometric 
-model, which reduces a molecule to a sum of atomic processes quantities 
-weighted by the numbers of such atom in the molecule.
-
-To overcome the first perturbative approximation limitations and 
-since the projectiles are multicharged ions, we resort to the 
-Continuum Distorted Wave-Eikonal Initial State (CDW), which includes 
-higher perturbative corrections. We start from the premise that the 
-ionization process is the mechanism that deposits the most significant 
-amount of primary energy. This process produces an electron-energy 
-spectrum that needs to be integrated. Moreover, the ejected electrons 
-become a new source of local damage. These secondary electrons are 
-included in Monte Carlo simulations and hence their behavior must be
-investigated. With this end in mind, we calculate not only the 
-ionization cross-sections but also energy and mean angular distributions 
-of the emitted electrons.
-
-The molecular structure complexity of the target is dealt with by 
-implementing the simplest stoichiometric model (SSM); we assume that 
-the molecule is composed of isolated independent atoms. In all cases, 
-the total cross-section is simply the sum of the cross-section of each 
-atom.
-
-Then, by implementing the SSM and the CDW --instead of the first Born 
-approximation--, we calculate ionization cross-section of several 
-molecules (see Table~\ref{tab:families}) by the impact of antiprotons,
-H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$,\ and O$^{8+}$. Furthermore, 
-in Section 3, we investigate different DNA and RNA molecules
-such as adenine, timine, cytosine, guanine, uracil, and also DNA 
-backbone.
-
-The results are processed to test the Toburen scaling rule, which 
-states that the ratio between the ionization cross-section and the 
-number of valence electrons (outer electrons) in terms of the 
-projectile velocity can be arranged in a narrow universal band. 
-We have also applied this rule to several hydrocarbons and nucleobases. 
-In Section 3.2, we will prove that the width of the resulting universal 
-band can be significantly reduced if we redefine the effective number 
-of valence electrons.
-
-It is well known that the residual electrons from the ionization 
-process cause significant biological damage. To inspect this mechanism, 
-in Section 3.3 and 3.4, we calculated the mean electron energy an 
-angular distributions. Surprisingly, we found a substantial dependence 
-of the charged projectile, which is unexpected in the first Born 
-approximation.
-
-The hefty charge projectiles are dealt with the CDW. However, the 
-stoichiometric model used seems to be very simplistic. The approximation
-considers each atom as neutral, which is not correct. In Section 3.5, 
-we used the molecular electronic structure code 
-{\sc gamess}~\cite{gamess} to calculate the excess or defect of 
-electron density one each atom. Then, the simple stoichiometric model is
-modified to account for the departure from neutrality of the atoms. 
-We find that for the DNA molecules this modification does not introduce 
-a substantial change.
-
-\section{Theory: Ionization of Atoms}
-
-In our study, we will consider six atoms $\alpha=$ H, C, N, O, P, and S. 
-Most of the organic molecules are composed of these atoms. Some 
-particular molecules also include halogen atoms such as fluor and 
-bromine; ionization cross-sections of these elements have been 
-previously published~\cite{miraglia2008,miraglia2009}.
-
-The total ionization cross-sections of these atoms were calculated using 
-the CDW. The initial bound and final continuum radial wave functions 
-were obtained by using the {\sc radialf} code, developed by Salvat and 
-co-workers, and a Hartree-Fock potential obtained from the Depurated 
-Inversion Model~\cite{mendez2016,mendez2018}. 
-We used a few thousand pivot points to solve the Schr\"{o}dinger 
-equation, depending on the number of oscillations of the continuum 
-state. The radial integration was performed using the 
-cubic spline technique. The number of angular momenta considered 
-varied from 8, at very low ejected-electron energies, up to 30, 
-for the highest energies considered. The same number of azimuth 
-angles were required to obtain the four-fold differential 
-cross-section. The calculation performed does not display prior-post 
-discrepancies at all. Each atomic total cross-section in 
-Eq.~(\ref{eq:sumion}) was calculated using 35 to 100 momentum transfer 
-values, 28 fixed electron angles, and around 45 electron energies 
-depending on the projectile impact energy. Further details of the 
-calculation are given in Ref.~\cite{montanari2017}. Simultaneously, we 
-will be reporting state to state ionization cross sections for these 
-cases in Ref.~\cite{miraglia2019}, which will be very useful to estimate 
-molecule fragmentation.
-
-In Figure 1, we report our total ionization results for the six 
-essential elements by the impact of six different projectiles: 
-antiprotons, H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$. 
-To reduce the resulting 36 magnitudes into a single consistent 
-figure, we considered the fact that in the first Born approximation
-the ionization cross-section scales with the square of the projectile 
-charge, $Z^{2}$. The values of the impact energies considered 
-range between 0.1 to 10 MeV/amu, where the CDW is supposed 
-to hold. In fact, for the highest projectile charges the minimum 
-impact energy where the CDW is expected to be valid could be 
-higher than 100 KeV. Moreover, we corroborated that the first Born 
-approximation provides quite reliable results only for energies higher 
-than a couple of MeV/amu. We use the same color to indicate the 
-projectile charge throughout the figures of this work: dashed-red, 
-solid-red, blue, magenta, olive and orange for antiprotons, 
-H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$, respectively. 
-Notably, there is no complete tabulation of ionization of atoms by 
-the impact of multicharged ions. We hope that the ones presented 
-in this article will be of help for future works.
-
-\section{Ionization of Molecules}
-
-\subsection{The stoichiometric model}
-
-Lets us consider a molecule $M$ composed by $n_{\alpha}$ atoms of the
-element $\alpha$, the SSM describes the total ionization cross section 
-of the molecule $\sigma_{M}$ as a simple sum of ionization cross 
-sections of the isolated atoms $\sigma_{\alpha}$, 
-\begin{equation}
- \sigma_{M}=\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}\,.  
- \label{eq:sumion}
-\end{equation}
-We divided sixteen molecular targets of our interest in 3 families. 
-The classification defined is given in Table~\ref{tab:families}.
-\begin{table}
-\begin{center}
-\begin{tabular}{|p{0.06\textwidth}|p{0.55\textwidth}|}
-\hline
- CH  & CH$_4$, C$_2$H$_2$, C$_2$H$_4$, C$_2$H$_6$, and C$_6$H$_6$ \\
-\hline
- CHN & C$_5$H$_5$N, C$_4$H$_4$N$_2$, C$_2$H$_7$N, and CH$_5$N \\
-\hline
- \multirow{4}{*}{DNA} & adenine (C$_5$H$_5$N$_5$), 
-                        timine (C$_5$H$_6$N$_2$O$_2$), \\
-     & cytosine (C$_4$H$_5$N$_2$O), guanine (C$_5$H$_5$N$_5$O), \\
-     & uracil (C$_4$H$_4$N$_2$O$_2$), \\
-     & DNA backbone (C$_5$H$_{10}$O$_5$P), \\
-     & dry DNA (C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$)\\
-\hline
-\end{tabular}
-\caption{Sixteen molecular targets of our interest classified in 3 
-\label{tab:families}
-families.}
-\end{center}
-\end{table}
-
-In Figure 2, we report the total ionization cross sections by the 
-impact of multicharged ions for the four fundamental DNA components: 
-adenine, timine, cytosine, and guanine. Our reports for uracil and 
-DNA backbone containing P are given in Figure 3. For adenine, the 
-agreement with the experimental data available in our range of validity 
-is quite good. For uracil, we have a puzzling situation: our results 
-show good agreement with the experiments by proton impact of Itoh 
-{\it et al.}~\cite{itoh2013}, but for the same target our theory fails 
-by a factor of two for the impact of C$^{4+}$ and O$^{6+}$ ions. 
-Nonetheless, it should be stated that our theoretical results coincide 
-with the ones by Champion, Rivarola and 
-collaborators~\cite{champion2012,agnihotri2012}, which may indicate a 
-possible misstep of the experiments.
-
-\subsection{Scaling rule}
+\subsubsection{Toburen numbers}
 
@@
 cross section in terms of the number of outer or weakly bound valence
-electrons (total number of electrons minus the inner-shell ones). 
-We introduce the cross section per weakly bound electron or ionization 
-cross section per valence electron, $\sigma_{e}$, as
+electrons \textbf{(i.e. total number of electrons minus the K-shell)}.
+\textbf{Following Toburen we can define the ionization} cross section per weakly bound electron
+%or ionization cross section per valence electron,
+$\sigma_{e}^T$, as
 \begin{equation}
-\sigma_{e}=\frac{\sigma_{M}}{N_{M}}=\frac{\sum\limits_{\alpha}
-n_{\alpha}\sigma_{\alpha}}{\sum\limits_{\alpha}n_{\alpha}\nu_{\alpha}}
+\sigma_{e}^T=\frac{\sigma_{M}}{N_{M}}=\frac{\sum\limits_{\alpha}
+n_{\alpha} \sigma_{\alpha}}{\sum\limits_{\alpha}n_{\alpha}\nu_{\alpha}^T}
 =\sigma_{e}(v)\,,
@@
 \end{equation}
-where
+where \textbf{$\nu_{\alpha}^T$ are the Toburen numbers for each atom:}
 \begin{equation}
-\nu_{\alpha}=\left\{ 
+\nu_{\alpha}^T=\left\{
 \begin{array}{ll}
+1, & \text{H,} \\
 4, & \text{for C,} \\
@@
 \end{equation}
-and $\nu_{\text{H}}=1$. The Toburen rule can be stated by saying that 
+%and $\nu_{\text{H}}=1$.
+The Toburen rule can be stated by saying that
 $\sigma_{e}$ is a \textit{universal} parameter independent on the
-molecule, which depends solely on the impact velocity. 
-In Ref.~\cite{toburen1976}, it was found experimentally that for proton 
-impact on some simple molecules, $\sigma_{e}$ results
-\begin{equation}
-\begin{array}{cccc}
-E\text{(MeV)}               & 0.25 & 1.00 & 2.00 \\ 
-\sigma_{e} (10^{-16}cm^{2}) & 0.39 & 0.17 & 0.11
-\end{array}
-\label{30}
-\end{equation}
-with an estimated error of about 20\%. A similar ratio was found in 
+molecule, which depends solely on the impact velocity\textbf{
+, and holds for high impact energies (i.e. 0.25-5 Mev/amu).}
+%In Ref.~\cite{toburen1976}, it was found experimentally that for proton
+%impact on some simple molecules, $\sigma_{e}$ results
+%\begin{equation}
+%\begin{array}{cccc}
+%E\text{(MeV)}               & 0.25 & 1.00 & 2.00 \\
+%\sigma_{e} (10^{-16}cm^{2}) & 0.39 & 0.17 & 0.11
+%\end{array}
+%\label{30}
+%\end{equation}
+%with an estimated error of about 20\%.
+
+\textbf{
+These $\nu_{\alpha}^T$ can be interpreted as the number of active 
+electrons in the collision. Of course, at very high energies also de 
+K--shell electrons will be ionized and these numbers will be different. }
+
+A similar \textbf{dependence with the number of weakly bound electrons} was found in
 Ref.~\cite{itoh2013} for proton impact on uracil and adenine.
-Figure 4a shows $\sigma_{e}$ calculated with the CDW as a function of 
+
+Figure 4a shows \textbf{our CDW results for} $\sigma_{e}^T$ as a function of
 the impact velocity for different projectile charges computed with the
@@
 Table~\ref{tab:families}. The universality with $Z$ is the one provided
-by Born approximation, i.e., $\sigma _{e}(Z)=Z^{2}\sigma_{e}(Z=1)$, 
+by Born approximation, i.e., $\sigma _{e}^T(Z)=Z^{2}\sigma_{e}^T(Z=1)$,
 and it holds for large impact velocities, as shown Figure 4a.
 Of course, for lower impact velocities, the CDW breaks the behavior of
-the $Z^{2}$ rule. Although the Toburen rule holds for high energies, 
+the $Z^{2}$ rule.
+
+Although the Toburen \textbf{scaling} holds for high energies,
 its performance is still not satisfactory: the universal band is quite
-broad. The departure of our theoretical 
-results from the Toburen rule can be easily explained by the fact that 
-our atomic cross sections $\sigma_{\alpha}$ behave differently for 
-each atom in terms of the projectile charges. By inspecting Figure 1, 
-one can easily see that the rule $\sigma_{\alpha}/v_{\alpha}\sim
-\sigma_{e}$ is not well satisfied by the CDW. A much better general 
-atomic rule is given by
+broad.
+
+\subsubsection{New scaling}
+
+The departure of our theoretical
+results from the Toburen rule can be explained by %the fact that
+%our atomic cross sections $\sigma_{\alpha}$ behave differently for
+%each atom in terms of the projectile charges. By
+\textbf{inspecting Figure 1. It can be noted}
+ that the rule $\sigma_{\alpha}/\nu_{\alpha}^T\sim
+\sigma_{e}^T$ \textbf{approximatelly constant} is not well satisfied by 
+the CDW model.
+\textbf{
+For example, Figure 1 shows that the cross sections for O are actually 
+very similar to the cross sections for C, suggesting 4 active electrons 
+in O instead of 6. In the same way the number of active electrons for
+N, P and S are also different from the $\nu_{alpha}^T$ in Equation 
+(\ref{eq:nelec}). This will be an important change in the scaling for 
+molecular targets. Based on the CDW results we propose a new scaling 
+given by}
+%A much better general atomic rule is given by
 \begin{equation}
@@
 n_{\alpha}\sigma_{\alpha}^{\text{CDW}}}{\sum\limits_{\alpha}n_{\alpha}
-\nu_{\alpha}^{\text{CDW}}},
+\nu_{\alpha}},
 \label{32}
 \end{equation}
-where 
+\textbf{where $\nu_{\alpha}$ are the new numbers of active electrons per 
+atom obtained from the CDW ionization cross sections for different ions 
+in H, C, N, O, P , and S targets. The new values are
 \begin{equation}
-\nu_{\alpha }^{\text{CDW}} \sim\left\{ 
+\nu_{\alpha}=\left\{
 \begin{array}{ll}
-4,\ \ \  & \text{for C, N, and O,} \\ 
-4.5,\ \  & \text{for P and S}
-\end{array}
-\right. 
-\label{35}
+1, & \text{H,} \\
+4, & \text{for C, N, O} \\
+4.5, & \text{for P, S} \\
+\end{array}\right.
+\label{eq:scalingCDW}
 \end{equation}
-and, obviously, $\nu_{\text{H}}^{\text{CDW}}=1$. The cross sections 
+}
+The \textbf{scaled} cross sections
 $\sigma_{e}^{\text{CDW}}$ are plotted in Figure~4b. A much better sharp
-band is observed, especially at high energy, where the theory is 
-expected to work. It will be interesting for experiments to cross-check 
-this theoretical prediction.
+band is observed, especially \textbf{for impact energies $E=(0.5-8)MeV/amu$ 
+for $Z=1$ and $Z=2$; and $E=(2.5-8)MeV/amu$ for $Z>2$.}
+%at high energy, where the theory is expected to work.
+\textbf{
+The experimental data for ionization of adenine, cytosine, thymine, 
+guanine, uracil, pyrimidine and THF by proton impact seems to 
+corroborate the new scaling. It will be interesting to cross-check for 
+experiments with projectile charge states $Z>1$.}
 
-\subsection{Emitted electron energies}
+\textbf{In table \ref{nn} we display the number of active electrons 
+obtained using the present scaling for some molecules of interest. These 
+numbers are very different from those proposed by Toburen \cite{} and 
+used by other authors \cite{Itoh,others}.}
 
-In a given biological medium, direct ionization by ion impact accounts 
-for just a fraction of the overall damage. Secondary electrons, as well 
-as recoil target ions, also contribute substantially to the total damage. 
-We can consider the single differential cross section of the shell 
-$nl$ of the atom $\alpha$, $d\sigma _{\alpha nl}/dE$, to be a function 
-of the ejected electron energy $E$ as a simple distribution 
-function~\cite{surdutovic2018}. Then, we can define the mean value 
-$\overline{E}_{\alpha}$ as in Ref.~\cite{abril2015},
-\begin{eqnarray}
-\overline{E}_{\alpha} &=&\frac{\langle E_{\alpha}\rangle}{\langle
-1\rangle}=\frac{1}{\sigma_{\alpha}}\sum\limits_{nl}\int dE\,E
-\frac{d\sigma_{\alpha,nl}}{dE}\,,  
-\label{40} \\
-\langle 1\rangle &=&\sigma_{\alpha}=\sum\limits_{nl}\int dE\,
-\frac{d\sigma_{\alpha,nl}}{dE}\,,  
-\label{50}
-\end{eqnarray}
-where $\Sigma_{nl}$ takes into account the sum of the different 
-sub-shell contributions of the element $\alpha$.
+\begin{table}
+\begin{center}
+\begin{tabular}{llllll}
+\hline
+ Molecule & number &Molecule         &number & Molecule             &number \\
+ H$_2$    & 2  & C$_2$H$_7$N         & 19    & C$_4$H$_5$N$_3$O     & 37    \\
+ H$_2$O   & 6  & C$_4$H$_8$O         & 28    & C$_5$H$_6$N$_2$O$_2$ & 42    \\
+ NH$_3$   & 7  & C$_4$H$_4$N$_2$     & 28    & C$_5$H$_5$N$_5$      & 45    \\
+ CH$_4$   & 8  & C$_6$H$_6$          & 30    & C$_5$H$_5$N$_5$O     & 49    \\
+ CH$_5$N  & 13 & C$_4$H$_4$N$_2$O$_2$& 36    & C$_5$H$_{10}$O$_5$P  & 54.5  \\
+ \hline
+\end{tabular}
+\caption{New scaling numbers for SOME molecular targets of biological interest.}
+\label{nn}
+\end{center}
+\end{table}
 
-Figure 5 shows $\overline{E}_{\alpha}$ for six elements from 
-Table~\ref{tab:families}. The range of impact velocities was shorten up 
-to $v=10$ a.u. due to numerical limitations in the spherical harmonics 
-expansion. In our theoretical treatment, we expand our final continuum 
-wave function as per usual,
-\begin{equation}
-\psi_{\overrightarrow{k}}^{-}(\overrightarrow{r})=\sum_{l=0}^{l_{\max
-}}\sum_{m=-l}^{l}R_{kl}^{-}(r)Y_{l}^{m}(\widehat{r})Y_{l}^{m^{\ast }}
-(\widehat{k})\,.
-\label{60}
-\end{equation}
-We are confident with our calculations up to $l_{\max}\sim 30$. 
-As the impact velocity $v$ increases, so do $\langle E_{\alpha}\rangle$
-and $l_{\max}$, which results in the inclusion of very oscillatory 
-functions in the integrand. Furthermore, the integrand of
-$\langle E_{\alpha}\rangle$ includes the kinetic energy $E$
-(see Eq.~(\ref{40})), which cancels the small energy region and 
-reinforces the large values, making the result more sensible to large
-angular momenta. Regardless, for $v>10$ a.u., the first Born 
-approximation holds.
+\textbf{An alternative way of showing this scaling is to plot the ionization cross sections of molecules as a function of the number of active electrons given in table \ref{nn}.
+This is displayed in the figure \ref{recta} for impact energies 0.5, 1 and 2 MeV.
+As can be noted the CDW ionization cross sections calculated for different molecules actually show a linear dependence with the number of electrons given in table \ref{nn}.
+We obtain similar straigth lines even for E=10 MeV.
+The comparisson with the experimental data available shows very nice agreement from the smallest molecules H$_2$, H$_2$O and CH$_4$, up to the most complex ones like adenine or guanine}.
 
-In Figure 5, we estimate $\overline{E}_{\alpha}$ in the 0.5--2 a.u.
-velocity range, or equivalently from 15 to 50 eV, for all the targets.
-Our results agree with the experimental findings~\cite{surdutovic2018}. 
-The dependence of the mean energy value with the projectile charge $Z$ 
-is surprisingly sensible, which can duplicate the proton results. 
-This effect can be attributed to the depletion caused by the 
-multicharged ions to the yields of low energy electrons. In the high 
-electron energy regime, the CDW falls on the simple first Born 
-approximation, surviving the $Z^{2}$ law. Then, the ratio in 
-Eq.~(\ref{40}) cancels out and $\overline{E}_{\alpha}$ becomes a 
-universal value independent on $Z$.
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.95\textwidth]{fig_recta.eps}
+\end{figure}
 
-Extending the simple stoichiometric model for the mean electron energy
-calculation, it results
-\begin{equation}
-\overline{E}_{M}=\frac{\sum\limits_{\alpha}n_{\alpha}
-\overline{E_{\alpha}}}{\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}}.
-\label{70}
-\end{equation}
-For impact of H$^{+}$ and He$^{2+~}$ on water at 1 MeV/amu, we obtain 
-$\overline{E}_{\text{H}_{2}\text{O}}=43.7$ and 45 eV, while the 
-experimental values 
-on liquid water by Pimblott and LaVerne [xxx] were found to be 51.5 and 
-52.2 eV, respectively. Just to stress the importance of the projectile 
-charge, for O$^{8+}$ on water, at the same impact energy 1 MeV/amu, 
-we obtained $\overline{E}_{\text{H}_{2}\text{O}}=54.7$ eV, which is 25\% 
-larger than 
-proton impact result. It is worth noting that there should not be any 
-difference if the calculations were carried in first Born approximation. 
-We will came back on this issue later.
-
-\subsection{Emitted electron angles}
-
-As mentioned before, secondary electrons contribute to the total damage. 
-Then, it is important not only the ejection energy but also the angle 
-of emission. Once again, we can consider the single differential cross 
-section in terms of the ejected electron solid angle $\Omega$, 
-$d\sigma_{\alpha,nl}/d\Omega$, to be expressed as a distribution 
-function, and define the mean angle $\overline{\theta}_{\alpha}$ as
-\begin{equation}
-\overline{\theta}_{\alpha}=\frac{\langle\theta_{\alpha}\rangle}
-{\langle 1\rangle}=\frac{1}{\sigma_{\alpha}}\sum\limits_{nl}
-\int d\Omega\,\theta\,\frac{d\sigma_{\alpha,nl}}{d\Omega}
-\end{equation}
-Figure 6 shows $\overline{\theta}_{\alpha}$ for our six elements of 
-interest. A new important dependence of $\overline{\theta}_{\alpha}$ 
-with $Z$ is observed. It is the common view~\cite{Rudd1992} that the 
-angular dispersion of emitted electrons are nearly isotropic due to the
-fact that angular anisotropy of sub-50-eV yield is not significant. 
-A typical value of ejection angle used in the literature is 
-$\overline{\theta}_{\alpha}\sim 70$ degrees~\cite{surdutovic2018}, and 
-it is quite correct in the range of validity of the first Born 
-approximation for any target. But when a distorted wave approximation 
-is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
-in the intermediate energy region, as observed in Figure 6. 
-For example, for C$^{6+}$ impact, the Bragg peak occurs at 0.3 MeV/amu, 
-where $\overline{\theta}_{\alpha}$ computed with the CDW method is 
-about half of the value obtained with the first Born approximation. 
-This correction should close the damage to the forward direction.
-
-The only responsible of this correction is the capture to the continuum
-effect: the larger the charge $Z$ the smaller $\overline{\theta}$ will 
-be, of course at intermediate energies, not at high impact energies, 
-where the Born approximation rules. One illustrative observation is the 
-behavior of antiprotons: the projectile in this case repels the 
-electrons making the distribution almost symmetric. Note the opposite 
-effect of proton and antiprotons, they run one opposite to the other, 
-as compared with the first Born approximation.
-
-\subsection{A modified stoichiometric model}
-
-One can correctly argue that\ the SSM considers an assembly of isolated
-neutral atoms which is definitively unrealistic. A first improvement is to
-consider that the atoms are not neutral and within the molecule they have
-more or less electrons given by a \ charge $q_{\alpha }$. One parameter that
-measures $q_{\alpha }$ is the Mulliken charge. This is not the only one,
-there is a large variety of charges such as the net or natural atomic charge 
-\cite{lee2003}, the lowin charge, etc.
-
-Consider\ that the total amount of electrons $Q_{\alpha }\ $on element $%
-\alpha $ are equally distributed on all the atoms $\alpha ,$ therefore each
-element $\alpha \ $\ will have a an additional charge: $q_{\alpha
-}=Q_{\alpha }/n_{\alpha }$. positive or negative depending on the relative
-electronegative value respect to the other ones~\cite{rappe1991}. Instead
-of the integer number of elements $n_{\alpha }$ of the atom $\alpha$, it
-could be argued that we have now an continuous number of atoms given by 
-\begin{equation}
-n_{\alpha }^{\prime }=n_{\alpha }-\frac{q_{\alpha }}{v_{\alpha }^{CDW}}
-\label{100}
-\end{equation}%
-In the case of neutral atoms $q_{\alpha }=0,$ we obviously recover $%
-n_{\alpha }^{\prime }=n_{\alpha }$ as before$.$
-
-To inspect the effect of the $q_{\alpha }$ we have run GAMES with the 
-6-31G basis set, including polarization functions for all the atoms. 
-The calculations were carried out implementing the B3LYP 
-functional~\cite{Becke1993,Stephens1994}. In Table~(\ref{110}) we display
-$q_{\alpha }$ of the different DNA basis and in the last column we rewrite
-the new stoichiometric expression. 
-\begin{equation}
-\begin{array}{|l|l|l|l|l|l|}
-\hline
-\text{Element}\,\,\, & \mathrm{H} & \mathrm{C} & \mathrm{N} & \mathrm{O} & 
-\text{New stoichiometry} \\ 
-\hline
-\mathrm{Adenine}  & +0.32 & -0.55 & +0.23 &       & 
-\mathrm{C}_{4.92}\mathrm{H}_{5.14}\mathrm{N}_{4.77} \\ 
-\hline
-\mathrm{Thymine}  & +0.20 & -0.54 & +0.19 & -0.52 & 
-\mathrm{C}_{4.95}\mathrm{H}_{6.13}\mathrm{N}_{1.95}\mathrm{O}_{2.13} \\ 
-\hline
-\mathrm{Cytosine} & +0.28 & -0.56 & +0.21 & -0.53 & 
-\mathrm{C}_{3.93}\mathrm{H}_{5.14}\mathrm{N}_{2.79}\mathrm{O}_{1.13} \\ 
-\hline
-\mathrm{Guanine}  & +0.46 & -0.58 & +0.20 & -0.36 & 
-\mathrm{C}_{4.89}\mathrm{H}_{5.15}\mathrm{N}_{4.80}\mathrm{O}_{1.09} \\ 
-\hline
-\end{array}
-\label{110}
-\end{equation}
-
-All the previous formula holds with the simple replacement of integer value $%
-n_{\alpha }$ by the continuous values\ $n_{\alpha }^{\prime }$ to produce a
-new ionization cross section $\sigma ^{\prime }$
-
-In Figure 7, we displays the relative difference of ionization cross
-sections 
-\begin{equation}
-e=\frac{\sigma ^{\prime }-\sigma }{\sigma }\times 100  \label{120}
-\end{equation}%
-for the four DNA basis. The difference is \ just very few percents.
-Indicating that the SSM is a quite robust model to treat the type of
-molecule we are dealing with, and of course within the range error that one
-can expect from the SSM.
-
-We now return to the calculation of the mean electron energy of H$^{+}$ and
-He$^{2+~}$ in water\ \ $\overline{E}_{H_{2}O}$. If we consider that \ the
-residual charge of \ each hydrogen in water is $q_{H}=$+0.35 \ \cite%
-{rappe1991}\ which implies that on Oxygen we have \ a residual charge of $%
-q_{O}=$-0.7, we could re-write the formula of water using (\ref{120}) as H$%
-_{1.3}$O$_{1.17}$ considering $n_{O}^{CDW}\simeq 4$ and $n_{H}^{CDW}\simeq
-1. $ Recalculating mean electron energy by impact of \ H$^{+}$ and He$^{2+~}$
-on water at 1 MeV/amu we obtain: $\overline{E}_{H_{2}O}=$46.2 \ and 47.6 eV
-which compared a little better with the experiments: 51.5 and 52.2 eV \cite%
-{pimblott2007}, respectively. i.e. within 10\% of the experiments which is
-not bad accounting for the simplicity of our method.
-
-Another parameter that we can calculate in our model is the fraction of
-energy carried by the electron $f$ defined as%
-\begin{equation}
-f=\frac{\sum\limits_{\alpha }n_{\alpha }\sigma _{\alpha }\overline{%
-E_{\alpha }}}{\sum\limits_{\alpha }n_{\alpha }(\sigma _{\alpha }\overline{%
-E_{\alpha }}+\sum\limits_{nl}\sigma _{\alpha nl}E_{\alpha nl})}  \label{90}
-\end{equation}%
-Using our shell-to-shell ionization cross sections $\sigma _{\alpha nl}\ $%
-\cite{miraglia2019}\ and atomic binding energies of the atom$\ \alpha ,$ $%
-E_{\alpha nl}\ $\cite{clementi}, we obtain $f=$0$.70\ $and $\ 0.71$ for \ H$%
-^{+}$ and He$^{2+~}$ on water at 1 MeV/amu,. which differ from the
-experiments \ $f=0.81$ and $0.80$, \ respectively.
-
-This difference with the experiment could be attributed to the difference of
-binding energy between the molecular water 12.65 eV and the atomic component
-H (13.6 eV) and O (17.19 eV), which is an issue beyond our independent atom
-approximation and so our model cannot not accounted for. We could estimate
-this contribution resorting, once more to the stoichiometric, model, we can
-arriesgar a upper-limit difference per molecule of water\ as
-
-\begin{equation}
-\delta E=(13.6-12.65)1.17+(17.19-12.65)1.3=7\ \text{eV}  \label{80}
-\end{equation}%
-Most of this energy should be transfer to the kinetics energy of the emitted
-electron. Thus we can \ add 7 eV to the previous values to give $\overline{E}%
-_{H_{2}O}=$53.2 \ and 54.6 eV for \ H$^{+}$ and He$^{2+~}$ on water at 1
-MeV/amu, respectively, much near to the experiments: 51.5 and 52.2 eV. If we
-add $\delta E$ to the numerator of Eq.(\ref{90}) we obtain\ $f=0.81$ and $%
-0.80$ in perfect agreement with the experiments (see Table 1 of Ref.(\cite%
-{pimblott2007})
-
-\section{CONCLUSIONS}
-
-We have calculated ionization cross sections by impact of antiprotons, H$^{+}
-$, He$^{2+}$, Be$^{4+}$, C$^{6+}$,\ and O$^{8+}$ with molecule involved in
-biological basis containing H, C, N, O, P and S with the CDW method. \ The
-importance of the influence of $Z\ $was observed in the mean energy $%
-\overline{E}_{\alpha }\ $and angle $\overline{\theta }_{\alpha }.$ For a
-given target $\alpha ,$ as $Z$ increases $\overline{E}_{\alpha }$ increases
-but $\overline{\theta }_{\alpha }$ decreases \ At high impact energy, say
-larger than 1 MeV/amu these values tend to the ones of the Born
-approximation which embodies the simple Z$^{2}$ law. Sixteen molecules were
-investigated using the simple stoichiometric model. Results for the six DNA
-basis were presented and compared with the sparse available experiments \ We
-explore the rule of Toburen which scales all the molecular ionization cross
-section when divided by the number of weakly bound valence electrons $\nu
-_{\alpha }$ given by Eq.(\ref{27})$.$ We have found the rule scales much
-better when normalizing our theoretical ionization cross sections to the
-number\ $\upsilon _{\alpha }^{\prime }$ given by Eq.(\ref{35}). And finally
-we attempt to improve the stoichiometric model by the use of the Mulliken
-charge to redefine a new stoichiometric model containing continuum rather
-than integer proportions. NO substantial correction was found indicating
-that the SSM works quite well.
-
-Our aims is this article is to provide the tools to estimate any inelastic
-parameter parameter -such as the emission angle, the emitted mean energy and
-cross section- by the impact of any multicharged \ on any molecule
-containing H, C, N, O, P and S, with the help of the stoichimetrical model.
-Our goal was quite \textbf{pretencioso}, considering the simplicity of our
-proposal. However we think our results could be used to estimate the
-ionization magnitude with an acceptable level of uncertailties
+\end{document}
 
 \bigskip
-
-\section{References}
 

### 2019-09-19 NewMonti25.tex
symbols changed in origin figures

@@
 \usepackage{float}
-
 \usepackage{authblk}
+\usepackage{MnSymbol}
 
@@
 Fig.~\ref{fig:crossDNA_1}. For adenine, the agreement with the 
-experimental data available (circles)~\cite{iriki2011} is very good 
+experimental data available~\cite{iriki2011} is very good 
 in our range of validity. To the best of our knowledge, there are not 
 experimental data on ion--collision ionization for the rest of the 
-molecules. We included electron impact measurements (right--oriented 
-triangles)~\cite{rahman2016} with the corresponding equivelocity 
+molecules. We included electron impact measurements~\cite{rahman2016} 
+with the corresponding equivelocity 
 conversion for incident energies higher than 500~keV. In this region, 
@@
 it is worth stating that our results agree very well with other 
-theoretical predictions~\cite{mozejko2003,tan2018}. The symbols used to 
-make reference to the proton and electron experimental data will be kept 
-for subsequent figures.
+theoretical predictions~\cite{mozejko2003,tan2018}. 
+%The symbols used to make reference to the proton and electron experimental data will be kept for subsequent figures.
 
@@
 \includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
-\caption{Present ionization cross section by impact of six projectiles, 
-and experimental values for proton and electron ionization.}
+\caption{Scaled ionization cross section by impact of multicharged ions. 
+Experiments: 
+$\circ$~\cite{iriki2011} for proton impact and $\square$~\cite{rahman2016} 
+for electron impact with equivelocity conversion.}
 \label{fig:crossDNA_1}
@@
 For uracil, we have good agreement with the experimental 
-proton impact measurements (triangle--up) by Itoh~{\it et al.}~\cite{itoh2013}. 
+proton impact measurements by Itoh~{\it et al.}~\cite{itoh2013}. 
 However, for the same target, our theory fails by a factor of two for 
 the experimental ionization values by the impact of 
-C$^{+4}$~(squares), O$^{+6}$~(circles) and O$^{+8}$~(triangles--down) 
-ions~\cite{agnihotri2012,agnihotri2013}.
+C$^{+4}$, O$^{+6}$ and O$^{+8}$ ions~\cite{agnihotri2012,agnihotri2013}.
 Nonetheless, it should be stated that our theoretical results coincide 
 with calculations by Champion, Rivarola and 
-collaborators~\cite{champion2012,agnihotri2012}, which may indicate a 
+collaborators~\cite{agnihotri2012,champion2012}, which may indicate a 
 possible misstep of the experiments. 
 For pyrimidine, we show comparison of our results with experimental data
-for proton (circles with dash)~\cite{wolff2014} and electron
-(stars)~\cite{bug2017} ionization. The electron impact measurements 
+for proton~\cite{wolff2014} and electron~\cite{bug2017} ionization. 
+The electron impact measurements 
 agree with our calculations for energies higher than 500keV. 
@@
 than our findings. 
-The THF molecule results are compared with proton (squares)~\cite{wang2016} 
+The THF molecule results are compared with proton~\cite{wang2016} 
 and electron~\cite{bug2017,wolf2019,fuss2009} impact measurements, showing
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig3.eps}
-\caption{Present ionization cross section by impact of six projectiles, 
-and experimental values for proton and electron ionization.}
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig3.eps}
+\caption{Scaled ionization cross section by impact of multicharged ions. 
+Experiments: proton impact on $\triangle$ uracil~\cite{itoh2013}, 
+$\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$
+THF~\cite{wang2016}. Impact of $\ominus$ C$^{+4}$, 
+$\boxminus$ C$^{+6}$, O$^{+6}$, F$^{+6}$, and
+$\triangle\mkern-14mu-$ O$^{+8}$, F$^{+8}$ on 
+uracil~\cite{agnihotri2012,agnihotri2013}. 
+Symbols~$\rhd$~\cite{bug2017}, $\lhd$~\cite{wolf2019}, and 
+$\medstar$~\cite{fuss2009} for electron impact with equivelocity conversion.}
 \label{fig:crossDNA_2}
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig4.eps}
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig4.eps}
 \caption{Scaled ionization cross section per weakly bound electron using
 (a)~the Toburen numbers $\nu_{\alpha}^T$, and (b) our proposed numbers
-$\nu_{\alpha}^{\text{CDW}}$.}
+$\nu_{\alpha}^{\text{CDW}}$. Experiments: proton impact on 
+$\circ$ adenine~\cite{iriki2011}, $\triangle$ uracil~\cite{itoh2013}, 
+$\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$ 
+THF~\cite{wang2016}; electron impact on $\rhd$ pyrimidine~\cite{bug2017},
+and $\lhd$, $\medstar$~\cite{wolf2019,fuss2009} THF.}
 \label{fig:newscaling}
@@
 $E=(0.5-8)$~MeV/amu for $Z=1$ and $Z=2$, and $E=(2.5-8)$~MeV/amu for 
-$Z>2$. In fact, the experimental data for ionization of adenine, 
-cytosine, thymine, guanine, uracil, pyrimidine and THF by proton impact 
-seems to corroborate the new scaling. We also included the electron impact
-ionization measurements from Figs.~\ref{fig:crossDNA_1} and 
-\ref{fig:crossDNA_2}. It will be interesting to cross--check for 
-experiments with higher projectile charge states.
+$Z>2$. In fact, the experimental data for ionization of 
+adenine~\cite{iriki2011}, uracil~\cite{itoh2013}, 
+pyrimidine~\cite{wolff2014} and THF~\cite{wang2016} by proton impact 
+seems to corroborate the new scaling. 
+We also included the electron impact ionization measurements with equivelocity 
+conversion on pyrimidine~\cite{bug2017}, and THF~\cite{bug2017,wolf2019,fuss2009}. 
+It will be interesting to cross--check for experiments with higher 
+projectile charge states.
 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figuras/fig_recta.eps}
-\caption{.}
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig_recta.eps}
+\caption{Ionization cross sections by impact of protons at 0.5, 1 and 2 MeV
+in terms of the number of active electrons given by Table~\ref{nn}.
+Experiments: $\circ$~adenine~\cite{iriki2011}, $\triangle$ uracil~\cite{itoh2013}, 
+$\bigtriangledown$ pyrimidine~\cite{wolff2014}, 
+$\blacktriangle$ C2H$_7$N, CH$_5$N, methane and amonia~\cite{lynch1976},
+$\bigstar$ amonia and H$_2$~\cite{rudd1985}, and $\bullet$ water~\cite{luna2007}.}
 \label{fig:recta}
@@
 \includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig5.eps}
-\caption{.}
+\caption{Mean emitted energy distribution for ionization by impact of
+multicharged ions.}
 \label{fig:emittedener}
@@
 multicharged ions to the yields of low energy electrons. In the high 
-electron energy regime, the CDW falls on the simple first Born 
 approximation, surviving the $Z^{2}$ law. Then, the ratio in 
@@
 For impact of H$^{+}$ and He$^{+2}$ on water at 1 MeV/amu, we obtain 
-$\overline{E}_{\text{H}_{2}\text{O}}=43.7$ and 45 eV, while the 
+\mbox{$\overline{E}_{\text{H}_{2}\text{O}}=43.7$} and 45 eV, while the 
 experimental values 
-on liquid water by Pimblott and LaVerne [xxx] were found to be 51.5 and 
-52.2 eV, respectively. Just to stress the importance of the projectile 
-charge, for O$^{+8}$ on water, at the same impact energy 1 MeV/amu, 
-we obtained $\overline{E}_{\text{H}_{2}\text{O}}=54.7$ eV, which is 25\% 
-larger than proton impact result. It is worth noting that there should 
-not be any difference if the calculations were carried in first Born 
-approximation. We will came back on this issue later.
+on liquid water by Pimblott and LaVerne \cite{pimblott2007} were found 
+to be 51.5 and 52.2 eV, respectively. Just to stress the importance of 
+the projectile charge, for O$^{+8}$ on water, at the same impact energy 
+1 MeV/amu, we obtained \mbox{$\overline{E}_{\text{H}_{2}\text{O}}=54.7$} eV, 
+which is 25\% larger than proton impact result. It is worth noting that 
+there should not be any difference if the calculations were carried in 
+first Born approximation. We will came back on this issue later.
 
@@
 \includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig6.eps}
-\caption{.}
+\caption{Mean emitted angle distribution for ionization by impact of
+multicharged ions.}
 \label{fig:emittedang}
@@
 \includegraphics[width=\textwidth]{figuras/levelsDNA.eps}
-\caption{Molecular binding energies for four DNA molecules.}
+\caption{Theoretical molecular binding energies for adenine, cytosine, 
+guanine, thymine and uracil compared to those of atomic constituents.}
 \label{fig:bindener}
@@
 Cross sections for ionization of uracil by MeV-energy-proton impact, 
-Phys. Rev. A 88, 052711 (2013).
+Phys. Rev. A \textbf{88}, 052711 (2013).
 
-\bibitem{} in energy and angles~,
-
-\bibitem{champion2012} 
-C Champion, M E Galassi, O Foj\'{o}n, H Lekadir, J Hanssen, R D Rivarola,
-P F Weck, A N Agnihotri, S Nandi, and L C Tribedi. Ionization of RNA-uracil
-by highly charged carbon ions.
-J. Phys.: Conf. Ser. 373, 012004 (2012).
+%\bibitem{} in energy and angles~,
 
@@
 Kumar, M. E. Galassi, R. D. Rivarola, O. Foj\'{o}n, C. Champion, J. Hanssen,
-H. Lekadir, P. F. Weck, and L. C. Tribedi. Ionization of uracil in
-collisions with highly charged carbon and oxygen ions of energy 100 keV to
-78 MeV. 
-Phys. Rev. A 85, 032711 (2012).
+H. Lekadir, P. F. Weck, and L. C. Tribedi. 
+Ionization of uracil in collisions with highly charged carbon and oxygen 
+ions of energy 100 keV to 78 MeV. 
+Phys. Rev. A \text{85}, 032711 (2012).
 
@@
 J Hanssen, P FWeck, M E Galassi, R D Rivarola, O Fojon and L C Tribedi, 
-Absolute total ionization cross sections of uracil (C4H4N2O2) in 
+Absolute total ionization cross sections of uracil (C$_4$H$_4$N$_2$O$_2$) in 
 collisions with MeV energy highly charged carbon, oxygen and fluorine ions
 J. Phys. B \textbf{46}, 185201 (2013).
+
+\bibitem{champion2012} 
+C Champion, M E Galassi, O Foj\'{o}n, H Lekadir, J Hanssen, R D Rivarola,
+P F Weck, A N Agnihotri, S Nandi, and L C Tribedi. 
+Ionization of RNA-uracil by highly charged carbon ions.
+J. Phys.: Conf. Ser. \textbf{373}, 012004 (2012).
 
@@
 Phys. Rev. A \textbf{80}, 052709 (2009).
+
+\bibitem{lynch1976}
+D. J. Lynch, L. H. Toburen, and W. E. Wilson,
+Electron emission from methane, ammonia, monomethylamine, and
+dimethylamine by 0.25 to 2.0 MeV protons
+J. Chem. Phys. \textbf{64}, 2616 (1976).
+
+\bibitem{rudd1985}
+M.E. Rudd, Y.-K. Kim, D.H. Madison, J.W. Gallagher,
+Electron production in proton collisions: total cross sections,
+Review of Modern Physics, \textbf{57}, 965--994 (1985).
+
+\bibitem{luna2007}
+H. Luna, A. L. F. de Barros, J. A. Wyer, S. W. J. Scully, J. Lecointre, 
+P. M. Y. Garcia, G. M. Sigaud, A. C. F. Santos, V. Senthil, M. B. Shah, 
+C. J. Latimer, and E. C. Montenegro,
+Water-molecule dissociation by proton and hydrogen impact,
+Phys. Rev. A \textbf{75} 042711 (2007).
 

### 2019-09-20 NewMonti25.tex
added angle data + mol bind ener analysis

@@
 
-\title{Ionization of molecules by multicharged bared ions by using the
-stoichiometric model}
+\title{Ionization of biological molecules by multicharged ions by using 
+the stoichiometric model}
 \author{author}
@@
 
-The damage caused by the impact of multicharged heavy projectiles has 
-become a field of interest due to its recent implementation in ion-beam 
-cancer therapy. The effectiveness of the radiation depends on the 
-choice of the ions. In particular, theoretical and experimental studies 
-with different projectiles have concluded that charged carbon ions 
-could be the most suitable ions to use. The study of such systems 
-represent a challenge from the theoretical point of view. The most 
-widely used method to compute ionization of multicharged atoms is the 
-first Born approximation. 
-This perturbative method warrants the $Z^{2}$ laws, where $Z$ is the 
-projectile charge. However, the damage concentrated in the vicinities 
-of the Bragg peak correspond to energies of hundreds of KeV/amu. 
-Precisely in this region, often refered to as the intermediate energy 
+The damage caused by the impact of multicharged heavy projectiles on 
+biological targets has become a field of interest due to its recent 
+implementation in ion--beam cancer therapy. The effectiveness of the 
+radiation depends on the choice of the ions. In particular, theoretical 
+and experimental studies with different projectiles have concluded that 
+charged carbon ions could be the most suitable ions to be used. The 
+study of such systems represent a challenge from the theoretical point 
+of view. The most widely used method to compute ionization of 
+multicharged atoms is the first Born approximation. This perturbative 
+method warrants the $Z^{2}$ laws, where $Z$ is the projectile charge. 
+However, the damage is concentrated in the vicinities of the Bragg peak,
+at energies of hundreds of keV/amu. Precisely in this intermediate 
 region, the Born approximation starts to fail. Another theoretical 
 issue arises from the targets themselves; we are dealing with complex 
-molecules. This article deals precisely with these two aspects. 
+molecules, which are a hard task for {\it ab initio} calculations. 
+The objective of this article is to deal with these two aspects. 
 First, we perform more appropriate calculations on the primary damage 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Emitted electron energies}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In a given biological medium, direct ionization by ion impact accounts 
+for just a fraction of the overall damage. Secondary electrons, as well 
+as recoil target ions, also contribute substantially to the total damage. 
+We can consider the single differential cross section of the shell 
+$nl$ of the atom $\alpha$, $d\sigma_{\alpha nl}/dE$, to be a function 
+of the ejected electron energy $E$ as a simple distribution 
+function~\cite{surdutovic2018}. Then, we can define the mean value 
+$\overline{E}_{\alpha}$ as in Ref.~\cite{abril2015},
+\begin{eqnarray}
+\overline{E}_{\alpha} &=&\frac{\langle E_{\alpha}\rangle}{\langle
+1\rangle}=\frac{1}{\sigma_{\alpha}}\sum\limits_{nl}\int dE\,E
+\frac{d\sigma_{\alpha,nl}}{dE}\,,  
+\label{40} \\
+\langle 1\rangle &=&\sigma_{\alpha}=\sum\limits_{nl}\int dE\,
+\frac{d\sigma_{\alpha,nl}}{dE}\,,  
+\label{50}
+\end{eqnarray}
+where $\Sigma_{nl}$ takes into account the sum of the different 
+sub-shell contributions of the element $\alpha$.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig5.eps}
+\caption{Mean emitted energy distribution for ionization by impact of
+multicharged ions. Charge state of projectiles given by arrow.}
+\label{fig:emittedener}
+\end{figure}
+
+Figure~\ref{fig:emittedener} shows $\overline{E}_{\alpha}$ for six elements from 
+Table~\ref{tab:families}. The range of impact velocities was shorten up 
+to $v=10$ a.u. due to numerical limitations in the spherical harmonics 
+expansion. In our theoretical treatment, we expand our final continuum 
+wave function as per usual,
+\begin{equation}
+\psi_{\overrightarrow{k}}^{-}(\overrightarrow{r})=\sum_{l=0}^{l_{\max
+}}\sum_{m=-l}^{l}R_{kl}^{-}(r)Y_{l}^{m}(\widehat{r})Y_{l}^{m^{\ast }}
+(\widehat{k})\,.
+\label{60}
+\end{equation}
+We are confident with our calculations up to $l_{\max}\sim 30$. 
+As the impact velocity $v$ increases, so do $\langle E_{\alpha}\rangle$
+and $l_{\max}$, which results in the inclusion of very oscillatory 
+functions in the integrand. Furthermore, the integrand of
+$\langle E_{\alpha}\rangle$ includes the kinetic energy $E$
+(see Eq.~(\ref{40})), which cancels the small energy region and 
+reinforces the large values, making the result more sensible to large
+angular momenta. Regardless, for $v>10$ a.u., the first Born 
+approximation holds.
+
+In Figure~\ref{fig:emittedener} , we estimate $\overline{E}_{\alpha}$ 
+in the 0.5--2 a.u.
+velocity range, or equivalently from 15 to 50 eV, for all the targets.
+Our results agree with the experimental findings~\cite{surdutovic2018}. 
+The dependence of the mean energy value with the projectile charge $Z$ 
+is surprisingly sensible, which can duplicate the proton results. 
+This effect can be attributed to the depletion caused by the 
+multicharged ions to the yields of low energy electrons. In the high 
+approximation, surviving the $Z^{2}$ law. Then, the ratio in 
+Eq.~(\ref{40}) cancels out and $\overline{E}_{\alpha}$ becomes a 
+universal value independent on $Z$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Emitted electron angles}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+As mentioned before, secondary electrons contribute to the total damage. 
+Then, not only is the ejection energy important but also the angle 
+of emission. Once again, we can consider the single differential cross 
+section in terms of the ejected electron solid angle $\Omega$, 
+$d\sigma_{\alpha,nl}/d\Omega$, to be expressed as a distribution function, 
+and the mean angle $\overline{\theta}_{\alpha}$ can be defined as
+\begin{equation}
+\overline{\theta}_{\alpha}=\frac{\langle\theta_{\alpha}\rangle}
+{\langle 1\rangle}=\frac{1}{\sigma_{\alpha}}\sum\limits_{nl}
+\int d\Omega\,\theta\,\frac{d\sigma_{\alpha,nl}}{d\Omega}
+\end{equation}
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig6.eps}
+\caption{Mean emitted angle distribution for ionization by impact of
+multicharged ions.}
+\label{fig:emittedang}
+\end{figure}
+
+Figure~\ref{fig:emittedang} shows $\overline{\theta}_{\alpha}$ for our six elements of 
+interest. A new important dependence of $\overline{\theta}_{\alpha}$ 
+with $Z$ is observed. It is a general belief~\cite{Rudd1992} that the 
+angular dispersion of emitted electrons are nearly isotropic. This effect 
+is caused by the insignificant angular anisotropy of sub-50-eV yield. 
+A typical value for the ejection angle considered in the literature is 
+$\overline{\theta}_{\alpha}\sim 70\degree$~\cite{surdutovic2018}, and 
+it is quite correct in the range of validity of the first Born 
+approximation for any target. But, when a distorted wave approximation 
+is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
+in the intermediate energy region, as observed in Figure~\ref{fig:emittedang}. 
+For example, for C$^{+6}$ impact, the Bragg peak occurs at 0.3 MeV/amu, 
+where $\overline{\theta}_{\alpha}$, computed with the CDW method, is 
+about half of the value obtained with the first Born approximation. 
+This correction should close the damage to the forward direction.
+
+We can attribute this correction to the capture to the continuum effect;
+the larger the charge $Z$, the smaller $\overline{\theta}$ will be. Of 
+course, this effect only holds at intermediate energies and not at high 
+impact energies, where the Born approximation rules. One illustrative 
+observation is the behavior of antiprotons: the projectile in this case 
+repels the electrons, making the distribution almost symmetric. 
+Note the opposite effect of proton and antiprotons; they run one 
+opposite to the other, as compared with the first Born approximation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Ionization of Molecules}
@@
 \end{equation}
-We divided sixteen molecular targets of our interest in three families. 
+We divided seventeen molecular targets of our interest in three families. 
 The classification defined is given in Table~\ref{tab:families}.
@@
 high impact energies (i.e. 0.25--5 Mev/amu).
-%In Ref.~\cite{toburen1976}, it was found experimentally that for proton 
-%impact on some simple molecules, $\sigma_{e}$ results
-%\begin{equation}
-%\begin{array}{cccc}
-%E\text{(MeV)}               & 0.25 & 1.00 & 2.00 \\ 
-%\sigma_{e} (10^{-16}cm^{2}) & 0.39 & 0.17 & 0.11
-%\end{array}
-%\label{30}
-%\end{equation}
-%with an estimated error of about 20\%. A similar ratio was found in 
-%Ref.~\cite{itoh2013} for proton impact on uracil and adenine. 
 These $\nu_{\alpha}^T$ can be interpreted as the number of active 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Emitted electron energies}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In a given biological medium, direct ionization by ion impact accounts 
-for just a fraction of the overall damage. Secondary electrons, as well 
-as recoil target ions, also contribute substantially to the total damage. 
-We can consider the single differential cross section of the shell 
-$nl$ of the atom $\alpha$, $d\sigma _{\alpha nl}/dE$, to be a function 
-of the ejected electron energy $E$ as a simple distribution 
-function~\cite{surdutovic2018}. Then, we can define the mean value 
-$\overline{E}_{\alpha}$ as in Ref.~\cite{abril2015},
-\begin{eqnarray}
-\overline{E}_{\alpha} &=&\frac{\langle E_{\alpha}\rangle}{\langle
-1\rangle}=\frac{1}{\sigma_{\alpha}}\sum\limits_{nl}\int dE\,E
-\frac{d\sigma_{\alpha,nl}}{dE}\,,  
-\label{40} \\
-\langle 1\rangle &=&\sigma_{\alpha}=\sum\limits_{nl}\int dE\,
-\frac{d\sigma_{\alpha,nl}}{dE}\,,  
-\label{50}
-\end{eqnarray}
-where $\Sigma_{nl}$ takes into account the sum of the different 
-sub-shell contributions of the element $\alpha$.
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig5.eps}
-\caption{Mean emitted energy distribution for ionization by impact of
-multicharged ions.}
-\label{fig:emittedener}
-\end{figure}
-
-Figure~\ref{fig:emittedener} shows $\overline{E}_{\alpha}$ for six elements from 
-Table~\ref{tab:families}. The range of impact velocities was shorten up 
-to $v=10$ a.u. due to numerical limitations in the spherical harmonics 
-expansion. In our theoretical treatment, we expand our final continuum 
-wave function as per usual,
-\begin{equation}
-\psi_{\overrightarrow{k}}^{-}(\overrightarrow{r})=\sum_{l=0}^{l_{\max
-}}\sum_{m=-l}^{l}R_{kl}^{-}(r)Y_{l}^{m}(\widehat{r})Y_{l}^{m^{\ast }}
-(\widehat{k})\,.
-\label{60}
-\end{equation}
-We are confident with our calculations up to $l_{\max}\sim 30$. 
-As the impact velocity $v$ increases, so do $\langle E_{\alpha}\rangle$
-and $l_{\max}$, which results in the inclusion of very oscillatory 
-functions in the integrand. Furthermore, the integrand of
-$\langle E_{\alpha}\rangle$ includes the kinetic energy $E$
-(see Eq.~(\ref{40})), which cancels the small energy region and 
-reinforces the large values, making the result more sensible to large
-angular momenta. Regardless, for $v>10$ a.u., the first Born 
-approximation holds.
-
-In Figure~\ref{fig:emittedener} , we estimate $\overline{E}_{\alpha}$ in the 0.5--2 a.u.
-velocity range, or equivalently from 15 to 50 eV, for all the targets.
-Our results agree with the experimental findings~\cite{surdutovic2018}. 
-The dependence of the mean energy value with the projectile charge $Z$ 
-is surprisingly sensible, which can duplicate the proton results. 
-This effect can be attributed to the depletion caused by the 
-multicharged ions to the yields of low energy electrons. In the high 
-approximation, surviving the $Z^{2}$ law. Then, the ratio in 
-Eq.~(\ref{40}) cancels out and $\overline{E}_{\alpha}$ becomes a 
-universal value independent on $Z$.
-
-Extending the simple stoichiometric model for the mean electron energy
-calculation, it results
-\begin{equation}
-\overline{E}_{M}=\frac{\sum\limits_{\alpha}n_{\alpha}
-\overline{E_{\alpha}}}{\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}}.
-\label{70}
-\end{equation}
-For impact of H$^{+}$ and He$^{+2}$ on water at 1 MeV/amu, we obtain 
-\mbox{$\overline{E}_{\text{H}_{2}\text{O}}=43.7$} and 45 eV, while the 
-experimental values 
-on liquid water by Pimblott and LaVerne \cite{pimblott2007} were found 
-to be 51.5 and 52.2 eV, respectively. Just to stress the importance of 
-the projectile charge, for O$^{+8}$ on water, at the same impact energy 
-1 MeV/amu, we obtained \mbox{$\overline{E}_{\text{H}_{2}\text{O}}=54.7$} eV, 
-which is 25\% larger than proton impact result. It is worth noting that 
-there should not be any difference if the calculations were carried in 
-first Born approximation. We will came back on this issue later.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Emitted electron angles}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-As mentioned before, secondary electrons contribute to the total damage. 
-Then, not only is the ejection energy important but also the angle 
-of emission. Once again, we can consider the single differential cross 
-section in terms of the ejected electron solid angle $\Omega$, 
-$d\sigma_{\alpha,nl}/d\Omega$, to be expressed as a distribution function, 
-and the mean angle $\overline{\theta}_{\alpha}$ can be defined as
-\begin{equation}
-\overline{\theta}_{\alpha}=\frac{\langle\theta_{\alpha}\rangle}
-{\langle 1\rangle}=\frac{1}{\sigma_{\alpha}}\sum\limits_{nl}
-\int d\Omega\,\theta\,\frac{d\sigma_{\alpha,nl}}{d\Omega}
-\end{equation}
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig6.eps}
-\caption{Mean emitted angle distribution for ionization by impact of
-multicharged ions.}
-\label{fig:emittedang}
-\end{figure}
-
-Figure~\ref{fig:emittedang} shows $\overline{\theta}_{\alpha}$ for our six elements of 
-interest. A new important dependence of $\overline{\theta}_{\alpha}$ 
-with $Z$ is observed. It is a general belief~\cite{Rudd1992} that the 
-angular dispersion of emitted electrons are nearly isotropic. This effect 
-is caused by the insignificant angular anisotropy of sub-50-eV yield. 
-A typical value for the ejection angle considered in the literature is 
-$\overline{\theta}_{\alpha}\sim 70\degree$~\cite{surdutovic2018}, and 
-it is quite correct in the range of validity of the first Born 
-approximation for any target. But, when a distorted wave approximation 
-is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
-in the intermediate energy region, as observed in Figure~\ref{fig:emittedang}. 
-For example, for C$^{+6}$ impact, the Bragg peak occurs at 0.3 MeV/amu, 
-where $\overline{\theta}_{\alpha}$, computed with the CDW method, is 
-about half of the value obtained with the first Born approximation. 
-This correction should close the damage to the forward direction.
-
-We can attribute this correction to the capture to the continuum effect;
-the larger the charge $Z$, the smaller $\overline{\theta}$ will be. Of 
-course, this effect only holds at intermediate energies and not at high 
-impact energies, where the Born approximation rules. One illustrative 
-observation is the behavior of antiprotons: the projectile in this case 
-repels the electrons, making the distribution almost symmetric. 
-Note the opposite effect of proton and antiprotons; they run one 
-opposite to the other, as compared with the first Born approximation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{A modified stoichiometric model}
@@
 
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{llllll}
+\hline
+ $E_{\text{av}}$ & Adenine & Cytosine & Guanine & Thymine & Uracil \\
+\hline
+ Molecular & -7.1955 & -6.9058 & -7.4725 & -7.5304 & -7.6224 \\
+ Toburen   & -8.4236 & -8.6743 & -8.7275 & -8.7947 & -9.0022 \\
+ Our work  & -7.9027 & -7.8639 & -7.9420 & -7.8066 & -7.8839 \\
+\hline
+\end{tabular}
+\caption{.}
+\label{tab:gravener}
+\end{center}
+\end{table}
+
 By implementing Eq.~(\ref{eq:newstoi}), it is possible to determine a 
@@
 the range error expected for this model.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Ionization of water}
-
-%We now return to the calculation of the mean electron energy of H$^{+}$ 
-%and He$^{+2}$ in water, $\overline{E}_{\text{H}_2\text{O}}$. 
-Considering that the residual charge of each hydrogen in water is 
-$q_{\text{H}}=+0.35$~\cite{rappe1991}, we can imply that the residual charge 
-of oxygen is $q_{\text{O}}=-0.7$. Then, we could re-write the formula 
-of water using Eq.~(\ref{eq:newstoi}) as H$_{1.3}$O$_{1.17}$ (assuming
-$n_{\text{O}}^{\text{CDW}}\simeq 4$ and $n_{\text{H}}^{\text{CDW}}\simeq 1$). 
-Recalculating the mean electron energy by the impact of H$^{+}$ and 
-He$^{+2}$ on water at 1 MeV/amu, we obtain 
-$\overline{E}_{\text{H}_2\text{O}}=46.2$ and 47.6 eV. Our results 
-are 10\% apart from the experimental values: 51.5 and 
-52.2~eV~\cite{pimblott2007}, respectively, which is not bad considering 
-the simplicity of our model.
-
-We can be compute the fraction of energy carried by 
-the electron $f$, which is defined as
-\begin{equation}
-f=\frac{\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}
-\overline{E_{\alpha}}}{\sum\limits_{\alpha}n_{\alpha}(\sigma_{\alpha}
-\overline{E_{\alpha}}+\sum\limits_{nl}\sigma_{\alpha nl}E_{\alpha nl})}\,.
-\label{90}
-\end{equation}
-Using our shell-to-shell ionization cross sections 
-$\sigma_{\alpha nl}$~\cite{miraglia2019}, and the atomic binding energies
-$E_{\alpha nl}$~\cite{clementi} of the atom $\alpha$, we obtain 
-$f=0.70$ and $0.71$ on water at 1 MeV/amu for H$^{+}$ and He$^{+2}$, 
-which differ from the respective experimental values $f=0.81$ and $0.80$.
-
-The difference between our calculations and the experimental values 
-could be attributed to the binding energy values of the molecular 
-water~12.65 eV with respect to its atomic components, H (13.6 eV) and 
-O (17.19 eV). This theoretical discrepancy goes beyond our independent 
-atom approximation and it cannot be accounted for by our model. Once 
-again, we could estimate this contribution by resorting to the 
-stoichiometric model. We can make an assesment for a maximum difference 
-per molecule of water as 
-\begin{equation}
-\delta E=(13.6-12.65)\times1.17+(17.19-12.65)\times1.3=7\,\text{eV}  
-\label{80}
-\end{equation}
-Most of this energy should be transfer to the kinetic energy of the 
-emitted electron. Thus, by adding 7 eV to the previous values, we obtain
-$\overline{E}_{\text{H}_2\text{O}}=53.2$ and 54.6 eV for H$^{+}$ and 
-He$^{+2}$ on water at 1 MeV/amu, respectively, which are much closer to
-the experimental values. If we add $\delta E$ to the numerator of 
-Eq.~(\ref{90}), we obtain $f=0.81$ and $0.80$, in perfect agreement with 
-the experiments (see Table 1 of Ref.~\cite{pimblott2007}).
 

### 2019-09-21 NewMonti25.tex
new figures included in tex

@@
 \centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig1.eps}
+%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig1.eps}
+\includegraphics[width=\textwidth]{figuras/atomicscaling.eps}
 \caption{Scaled total ionization cross section of six atomic targets 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig5.eps}
+%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig5.eps}
+\includegraphics[width=\textwidth]{figuras/ener_mean.eps}
 \caption{Mean emitted energy distribution for ionization by impact of
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig6.eps}
+%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig6.eps}
+\includegraphics[width=\textwidth]{figuras/ang_mean.eps}
 \caption{Mean emitted angle distribution for ionization by impact of
@@
 theoretical predictions~\cite{mozejko2003,tan2018}.
-%The symbols used to make reference to the proton and electron experimental data will be kept for subsequent figures.
 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
+%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
+\includegraphics[width=\textwidth]{figuras/adn1.eps}
 \caption{Scaled ionization cross section by impact of multicharged ions. 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig3.eps}
+%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig3.eps}
+\includegraphics[width=\textwidth]{figuras/adn2.eps}
 \caption{Scaled ionization cross section by impact of multicharged ions. 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig4.eps}
+%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig4.eps}
+\includegraphics[width=\textwidth]{figuras/molscaling85.eps}
 \caption{Scaled ionization cross section per weakly bound electron using

### 2019-09-23 NewMonti25.tex
claudia's comments included

@@
 %\documentclass[pra,showpacs,twocolumn]{revtex4}
-
-\documentclass[preprint,12pt]{article}
+\documentclass[preprint]{revtex4}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \usepackage{MnSymbol}
+\usepackage{gensymb}
 
-\setcounter{MaxMatrixCols}{10}
-%TCIDATA{OutputFilter=LATEX.DLL}
-%TCIDATA{Version=5.50.0.2953}
-%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
-%TCIDATA{BibliographyScheme=Manual}
-%TCIDATA{LastRevised=Thursday, March 07, 2019 14:11:39}
-%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
-%TCIDATA{Language=American English}
-
-%\input{tcilatex}
 \begin{document}
@@
 the stoichiometric model}
+
 \author{author}
-\affil{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
-Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
+%\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio 
+%(CONICET-UBA).
+%Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
 %\author{author}
@@
 %\affil{Fac. de Ciencias Exactas y Naturales, Universidad de Buenos Aires}
-\date{\today }
 
-\maketitle
+\date{\today}% It is always \today, today,
 
@@
 
+%\keywords{Suggested keywords}
+
+\maketitle
+
+\tableofcontents
 %\pacs{79.20.Rf, 68.49.Bc, 34.20.Cf,34.50.-s,34.35.+a}
@@
 and experimental studies with different projectiles have concluded that 
-charged carbon ions could be the most suitable ions to be used. The 
-study of such systems represent a challenge from the theoretical point 
-of view. The most widely used method to compute ionization of 
-multicharged atoms is the first Born approximation. This perturbative 
-method warrants the $Z^{2}$ laws, where $Z$ is the projectile charge. 
-However, the damage is concentrated in the vicinities of the Bragg peak,
-at energies of hundreds of keV/amu. Precisely in this intermediate 
-region, the Born approximation starts to fail. Another theoretical 
-issue arises from the targets themselves; we are dealing with complex 
-molecules, which are a hard task for {\it ab initio} calculations. 
-The objective of this article is to deal with these two aspects. 
-First, we perform more appropriate calculations on the primary damage 
-mechanism, i.e., atomic ionization by multicharged ions, which can 
-replace the Born results. Second, we inspect and use an stoichiometric 
-model, which reduces a molecule to a sum of atomic processes quantities 
-weighted by the number of such atom in the molecule.
+charged carbon ions could be the most suitable ions to be used. 
+Nonetheless, the study of such systems represents a challenge from the 
+theoretical point of view.
 
-To overcome the first perturbative approximation limitations, and 
-since the projectiles are multicharged ions, we resort to the 
-Continuum Distorted Wave-Eikonal Initial State (CDW), which includes 
-higher perturbative corrections. We start from the premise that the 
-ionization process is the mechanism that deposits the most significant 
-amount of primary energy. This process produces an electron-energy 
-spectrum that needs to be integrated. Moreover, the ejected electrons 
-become a new source of local damage. These secondary electrons are 
-included in Monte Carlo simulations and hence their behavior must be
-investigated. With this end in mind, we calculate not only the 
-ionization cross-sections but also energy and mean angular distributions 
-of the emitted electrons.
+The ionization of biological molecules by multicharged ions constitutes 
+the primary damage mechanism. The most widely used method to predict
+such processes is the first Born approximation. At high energies, this 
+perturbative method warrants the $Z^{2}$ laws, where $Z$ is the 
+projectile charge. However, the damage is concentrated in the 
+vicinities of the Bragg peak --at energies of hundreds of keV/amu--, 
+precisely where the Born approximation starts to fail. 
+Another theoretical issue arises due to the targets themselves; we are 
+dealing with complex molecules, and the description of such targets 
+represents a hard task for {\it ab initio} calculations. The objective 
+of this article is to deal with these two aspects; first, we perform 
+more appropriate calculations on the primary damage mechanism, which can 
+replace the Born results. Second, we inspect and test a stoichiometric 
+model to describe the ionization of molecular targets.
 
-The molecular structure complexity of the target is dealt with by 
-implementing the simplest stoichiometric model (SSM); we assume that 
-the molecule is composed of isolated independent atoms. In all cases, 
-the total cross-section is simply the sum of the cross-section of each 
-atom.
+To overcome the first perturbative approximation limitations, and since 
+the projectiles are multicharged ions, we resort to the Continuum 
+Distorted Wave--Eikonal Initial State (CDW), which includes higher 
+perturbative corrections. We start from the premise that the ionization 
+process is the mechanism that deposits the most significant amount of 
+primary energy. Moreover, it is well known that the residual electrons 
+from the ionization become a source of significant local biological 
+damage. The secondary electrons are included in Monte Carlo simulations, 
+and hence their behavior must be investigated. 
+In Section~\ref{subsec:meanener} and \ref{subsec:meanang}, we calculate
+the mean energy and angular distributions of the ejected electrons. 
+Surprisingly, we found a substantial dependence of the charged 
+projectile, which is unexpected in the first Born approximation. 
+We deal with the molecular structure complexity of the target by 
+implementing the simplest stoichiometric model (SSM): the molecules are 
+assumed to be composed of isolated independent atoms, and the total 
+cross--section by a linear combination of weighted atomic calculations.
 
-Then, by implementing the SSM and the CDW --instead of the first Born 
-approximation--, we calculate ionization cross-section of several 
-molecules (see Table~\ref{tab:families}) by the impact of antiprotons,
-H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$,\ and O$^{+8}$. Furthermore, 
-in Section 3, we investigate different DNA and RNA molecules
-such as adenine, cytosine, guanine, thymine, uracil, tetrahydrofuran 
-(THF), pyrimidine and also DNA backbone.
+By implementing the CDW and the SSM, we calculate ionization 
+cross--section of several molecules of interest (see 
+Table~\ref{tab:families}) by the impact of antiprotons, H$^{+}$, 
+He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
+In Section~3, we show our results for different DNA and RNA molecules, 
+such as adenine, cytosine, guanine, thymine, uracil, tetrahydrofuran~(THF), 
+pyrimidine, and also DNA backbone. In Section~\ref{subsec:scaling}, we
+test the Toburen scaling rule~\cite{toburen1975,toburen1976}, which 
+states that the ratio between the ionization cross--section and the 
+number of weakly bound electrons can be arranged in a narrow universal 
+band in terms of the projectile velocity. We applied this rule to 
+several hydrocarbons and nucleobases and noted that the width of the 
+resulting universal band could be significantly reduced if we redefine 
+the effective number of active electrons in the collision. The new 
+scaling is then tested by comparison with experimental data.
 
-The results are processed to test the Toburen scaling rule, which 
-states that the ratio between the ionization cross-section and the 
-number of valence electrons (outer electrons) in terms of the 
-projectile velocity can be arranged in a narrow universal band. 
-We have also applied this rule to several hydrocarbons and nucleobases. 
-In Section 3.2, we will prove that the width of the resulting universal 
-band can be significantly reduced if we redefine the effective number 
-of valence electrons.
-
-It is well known that the residual electrons from the ionization 
-process cause significant biological damage. To inspect this mechanism, 
-in Section 3.3 and 3.4, we calculated the mean electron energy and
-angular distributions. Surprisingly, we found a substantial dependence 
-of the charged projectile, which is unexpected in the first Born 
-approximation.
-
-The hefty charge projectiles are dealt with the CDW. However, the 
-stoichiometric model used seems to be very simplistic. The approximation
+Although the multicharged projectiles are dealt with the CDW, the 
+stoichiometric model used seems to be very simplistic. The approach
 considers each atom as neutral, which is not correct. In Section 3.5, 
@@
 {\sc gamess}~\cite{gamess} to calculate the excess or defect of 
-electron density one each atom. Then, the simple stoichiometric model is
-modified to account for the departure from neutrality of the atoms. 
-We find that for the DNA molecules this modification does not introduce 
-a substantial change.
+electron density on the atoms composing the molecules. Then, the SSM is 
+modified to account for the departure from the neutrality of the atoms. 
+We find that the modified SSM for the DNA molecules does not introduce 
+substantial changes in the cross sections.
 
@@
 
-In our study, we will consider six atoms $\alpha=$ H, C, N, O, P, and S. 
+In the present study, we consider six atoms, $\alpha=$ H, C, N, O, P, 
+and S, and six projectiles, antiprotons $\bar{p}$, H$^{+}$, He$^{+2}$, 
+Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
 Most of the organic molecules are composed of these atoms. Some 
 particular molecules also include halogen atoms such as fluor and 
-bromine; ionization cross-sections of these elements have been 
+bromine; ionization cross sections of these elements have been 
 previously published~\cite{miraglia2008,miraglia2009}.
 
-The total ionization cross-sections of these atoms were calculated using 
-the CDW. The initial bound and final continuum radial wave functions 
-were obtained by using the {\sc radialf} code, developed by Salvat and 
-co-workers, and a Hartree-Fock potential obtained from the Depurated 
-Inversion Model~\cite{mendez2016,mendez2018}. 
+The total ionization cross sections of these atoms were calculated using 
+the CDW~[xxx]. The initial bound and final continuum radial wave 
+functions were obtained by using the {\sc radialf} code, developed by 
+Salvat and co--workers~\cite{salvat1995}, and a Hartree-Fock potential 
+obtained from the Depurated Inversion Method~\cite{mendez2016,mendez2018}. 
 We used a few thousand pivot points to solve the Schr\"{o}dinger 
 equation, depending on the number of oscillations of the continuum 
-state. The radial integration was performed using the 
-cubic spline technique. The number of angular momenta considered 
-varied from 8, at very low ejected-electron energies, up to 30, 
-for the highest energies considered. The same number of azimuth 
-angles were required to obtain the four-fold differential 
-cross-section. The calculation performed does not display prior-post 
-discrepancies at all. Each atomic total cross-section in 
-Eq.~(\ref{eq:sumion}) was calculated using 35 to 100 momentum transfer 
-values, 28 fixed electron angles, and around 45 electron energies 
-depending on the projectile impact energy. Further details of the 
-calculation are given in Ref.~\cite{montanari2017}. Simultaneously, we 
-will be reporting state to state ionization cross sections for these 
-cases in Ref.~\cite{miraglia2019}, which will be very useful to estimate 
-molecule fragmentation.
+state. The radial integration was performed using the cubic spline 
+technique. The number of angular momenta considered varied from 8, at 
+very low ejected-electron energies, up to 30, for the highest energies 
+considered. The same number of azimuth angles were required to obtain 
+the four-fold differential cross section. The calculation performed does 
+not display prior-post discrepancies at all. Each atomic total cross 
+section was calculated using 35 to 100 momentum transfer values, 28 
+fixed electron angles, and around 45 electron energies depending on the 
+projectile impact energy. In our theoretical treatment, we expand our 
+final continuum wave function as usual,
+\begin{equation}
+\psi_{\overrightarrow{k}}^{-}(\overrightarrow{r})=\sum_{l=0}^{l_{\max
+}}\sum_{m=-l}^{l}R_{kl}^{-}(r)Y_{l}^{m}(\widehat{r})Y_{l}^{m^{\ast }}
+(\widehat{k})\,.
+\label{eq:contwave}
+\end{equation}
+We are confident with our calculations up to $l_{\max}\sim 30$. Further 
+details of the calculation are given in Ref.~\cite{montanari2017}. 
+Simultaneously, we will be reporting state to state ionization cross 
+sections for the 36 ion--target systems considered in the present 
+work~\cite{miraglia2019}. We expect that these results will be useful
+to estimate molecule fragmentation.
 
-In Fig.~\ref{fig:atomscaling}, we report our total ionization results 
-for the six essential elements by the impact of six different projectiles: 
-antiprotons, H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
+\begin{figure*}[t!]
+\centering
+%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig1.eps}
+\includegraphics[width=0.9\textwidth]{figuras/atomicscaling.eps}
+\caption{Reduced CDW total ionization cross section of six atomic 
+targets. The curves are labeled with the charge state corresponding to 
+the six multicharged projectiles.}
+\label{fig:atomscaling}
+\end{figure*}
+
+We report our total CDW ionization cross sections for the six essential 
+elements by the impact of six projectiles in Fig.~\ref{fig:atomscaling}.
 To reduce the resulting 36 magnitudes into a single consistent 
 figure, we considered the fact that in the first Born approximation
-the ionization cross-section scales with the square of the projectile 
+the ionization cross section scales with the square of the projectile 
 charge, $Z^{2}$. The values of the impact energies considered 
@@
 impact energy where the CDW is expected to be valid could be 
-higher than 100 KeV. Moreover, we corroborated that the first Born 
-approximation provides quite reliable results only for energies higher 
-than a couple of MeV/amu. We use the same color to indicate the 
-projectile charge throughout the figures of this work: dashed-red, 
-solid-red, blue, magenta, olive and orange for antiprotons, 
-H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$, respectively. 
-The charge state of the projectiles are also given in the figures.
-Notably, there is no complete tabulation of ionization of atoms by 
-the impact of multicharged ions. We hope that the ones presented 
-in this article will be of help for future works.
-
-\begin{figure}[t!]
-\centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig1.eps}
-\includegraphics[width=\textwidth]{figuras/atomicscaling.eps}
-\caption{Scaled total ionization cross section of six atomic targets 
-by impact of multicharged projectiles.}
-\label{fig:atomscaling}
-\end{figure}
+higher than 100 keV. We also performed similar calculations with the 
+first Born approximation, and we corroborated that it provides quite 
+reliable results only for energies higher than a couple of MeV/amu. 
+We use the same line color to indicate the projectile charge throughout 
+all the figures of this work: dashed--red, solid--red, blue, magenta, 
+olive and orange for antiprotons, H$^{+}$, He$^{+2}$, Be$^{+4}$, 
+C$^{+6}$, and O$^{+8}$, respectively. Notably, there is no complete 
+tabulation of ionization of atoms by the impact of multicharged ions. 
+We hope that the ones presented in this article will be of help for 
+future works.
 
@@
 \subsection{Emitted electron energies}
+\label{subsec:meanener}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 where $\Sigma_{nl}$ takes into account the sum of the different 
-sub-shell contributions of the element $\alpha$.
+sub--shell contributions of the element $\alpha$.
 
-\begin{figure}[t!]
+\begin{figure*}[t!]
 \centering
 %\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig5.eps}
-\includegraphics[width=\textwidth]{figuras/ener_mean.eps}
+\includegraphics[width=0.9\textwidth]{figuras/ener_mean.eps}
 \caption{Mean emitted energy distribution for ionization by impact of
-multicharged ions. Charge state of projectiles given by arrow.}
+multicharged ions, given by Eq.~(\ref{40}). Dashed lines for $\bar{p}$,
+solid lines for ion charges $+1$, $+2$, $+4$, $+6$ and $+8$,
+as indicated.}
 \label{fig:emittedener}
-\end{figure}
+\end{figure*}
 
-Figure~\ref{fig:emittedener} shows $\overline{E}_{\alpha}$ for six elements from 
-Table~\ref{tab:families}. The range of impact velocities was shorten up 
-to $v=10$ a.u. due to numerical limitations in the spherical harmonics 
-expansion. In our theoretical treatment, we expand our final continuum 
-wave function as per usual,
-\begin{equation}
-\psi_{\overrightarrow{k}}^{-}(\overrightarrow{r})=\sum_{l=0}^{l_{\max
-}}\sum_{m=-l}^{l}R_{kl}^{-}(r)Y_{l}^{m}(\widehat{r})Y_{l}^{m^{\ast }}
-(\widehat{k})\,.
-\label{60}
-\end{equation}
-We are confident with our calculations up to $l_{\max}\sim 30$. 
+The mean emitted electron energies $\overline{E}_{\alpha}$ for H, C, N, 
+O, P and S are shown in Fig.~\ref{fig:emittedener}. The range of impact 
+velocities was shortened to $v=10$ a.u. due to numerical limitations 
+in the spherical harmonics expansion of Eq.~(\ref{eq:contwave}). 
 As the impact velocity $v$ increases, so do $\langle E_{\alpha}\rangle$
@@
 
-In Figure~\ref{fig:emittedener} , we estimate $\overline{E}_{\alpha}$ 
-in the 0.5--2 a.u.
-velocity range, or equivalently from 15 to 50 eV, for all the targets.
-Our results agree with the experimental findings~\cite{surdutovic2018}. 
-The dependence of the mean energy value with the projectile charge $Z$ 
-is surprisingly sensible, which can duplicate the proton results. 
-This effect can be attributed to the depletion caused by the 
-multicharged ions to the yields of low energy electrons. In the high 
-approximation, surviving the $Z^{2}$ law. Then, the ratio in 
-Eq.~(\ref{40}) cancels out and $\overline{E}_{\alpha}$ becomes a 
-universal value independent on $Z$.
+In Fig.~\ref{fig:emittedener}, we estimate $\overline{E}_{\alpha}$ of
+the emitted electron in the 0.5--2.7 a.u. energy range, or equivalently 
+from 15 to 70 eV, for all the targets. Our results agree with the 
+experimental findings~\cite{surdutovic2018}. As can be noted in the 
+figure, the mean energy value is surprisingly sensible to the 
+projectile charge $Z$, which can duplicate the proton results in the 
+intermediate region, i.e. 100--400 keV/amu. The effect observed can be 
+attributed to the depletion caused by the multicharged ions to the 
+yields of low energy electrons. This behavior cannot be found in the 
+first Born approximation, where the $Z^2$ law cancels the $Z$ dependence
+in Eq.~(\ref{40}). At high energies, $\overline{E}_{\alpha}$ tends to a 
+universal value for all ions, as can be seen in Fig.~\ref{fig:emittedener}.
 
@@
 \subsection{Emitted electron angles}
+\label{subsec:meanang}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{figure}[t!]
+\begin{figure*}[t!]
 \centering
 %\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig6.eps}
-\includegraphics[width=\textwidth]{figuras/ang_mean.eps}
+\includegraphics[width=0.9\textwidth]{figuras/ang_mean.eps}
 \caption{Mean emitted angle distribution for ionization by impact of
@@
 \label{fig:emittedang}
-\end{figure}
+\end{figure*}
 
-Figure~\ref{fig:emittedang} shows $\overline{\theta}_{\alpha}$ for our six elements of 
-interest. A new important dependence of $\overline{\theta}_{\alpha}$ 
-with $Z$ is observed. It is a general belief~\cite{Rudd1992} that the 
-angular dispersion of emitted electrons are nearly isotropic. This effect 
-is caused by the insignificant angular anisotropy of sub-50-eV yield. 
+The mean emitted electron angles $\overline{\theta}_{\alpha}$ for the 
+six atoms of interest are shown in Fig.~\ref{fig:emittedang}, and an 
+important dependence of $\overline{\theta}_{\alpha}$ with $Z$ is 
+observed. Once again, this effect is not observed in the first Born 
+approximation. It is a general belief~\cite{Rudd1992} that the 
+angular dispersion of emitted electrons are nearly isotropic. This 
+behavior is caused by the insignificant angular anisotropy of 
+sub--50--eV yield. 
 A typical value for the ejection angle considered in the literature is 
@@
 is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
-in the intermediate energy region, as observed in Figure~\ref{fig:emittedang}. 
+in the intermediate energy region, as observed in Fig.~\ref{fig:emittedang}. 
 For example, for C$^{+6}$ impact, the Bragg peak occurs at 0.3 MeV/amu, 
@@
 about half of the value obtained with the first Born approximation. 
-This correction should close the damage to the forward direction.
+This correction closes the damage to the forward direction.
 
-We can attribute this correction to the capture to the continuum effect;
-the larger the charge $Z$, the smaller $\overline{\theta}$ will be. Of 
-course, this effect only holds at intermediate energies and not at high 
-impact energies, where the Born approximation rules. One illustrative 
-observation is the behavior of antiprotons: the projectile in this case 
-repels the electrons, making the distribution almost symmetric. 
+We can attribute this forward direction correction to the capture to 
+the continuum effect; the larger the charge $Z$, the smaller 
+$\overline{\theta}$ will be. Of course, this effect only holds at 
+intermediate energies and not at high impact energies, where the Born 
+approximation rules. One illustrative observation is the behavior of 
+antiprotons: the projectile in this case repels the electrons, being
+$\overline{\theta}_{\alpha}\sim 90\degree$.
 Note the opposite effect of proton and antiprotons; they run one 
-opposite to the other, as compared with the first Born approximation.
+opposite to the other, as compared with the first Born approximation,
+constituting an angular Barkas effect.
 
@@
 Lets us consider a molecule $M$ composed by $n_{\alpha}$ atoms of the
-element $\alpha$, the SSM describes the total ionization cross section 
-of the molecule $\sigma_{M}$ as a simple sum of ionization cross 
-sections of the isolated atoms $\sigma_{\alpha}$, 
+element $\alpha$, the SSM approaches the total ionization cross section 
+of the molecule $\sigma_{M}$ as a sum of ionization cross sections of 
+the isolated atoms $\sigma_{\alpha}$ weighted by $n_{\alpha}$, 
 \begin{equation}
@@
 \end{equation}
-We divided seventeen molecular targets of our interest in three families. 
-The classification defined is given in Table~\ref{tab:families}.
+We classified the molecular targets of our interest in three families: 
+CH, CHN and DNA, as in Table~\ref{tab:families}.
 
@@
 \begin{center}
-\begin{tabular}{|p{0.06\textwidth}|p{0.75\textwidth}|}
+\begin{tabular}{|p{0.06\textwidth}|p{0.6\textwidth}|}
 \hline
- CH  & CH$_4$ (methane), C$_2$H$_2$ (acetylene), \\
-     & C$_2$H$_4$ (ethene), C$_2$H$_6$ (ethane), C$_6$H$_6$ (benzene) \\
+\multirow{2}{*}{CH} 
+      & CH$_4$ (methane), C$_2$H$_2$ (acetylene), C$_2$H$_4$ (ethene), \\
+      & C$_2$H$_6$ (ethane), C$_6$H$_6$ (benzene) \\
 \hline
- CHN & C$_5$H$_5$N (pyridine), C$_4$H$_4$N$_2$ (pyrimidine), \\
-& C$_2$H$_7$N 
-(dimenthylamine), CH$_5$N (monomethylamine) \\
+\multirow{2}{*}{CHN} 
+      & C$_5$H$_5$N (pyridine), C$_4$H$_4$N$_2$ (pyrimidine), \\ 
+      & C$_2$H$_7$N (dimenthylamine), CH$_5$N (monomethylamine) \\
 \hline
@@
       & C$_4$H$_4$N$_2$O$_2$ (uracil), C$_4$H$_8$O (THF), \\
-     & C$_5$H$_{10}$O$_5$P (DNA backbone), C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$ (dry DNA) \\
+      & C$_5$H$_{10}$O$_5$P (DNA backbone), 
+        C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$ 
+(dry DNA) \\
 \hline
 \end{tabular}
-\caption{Molecular targets of our interest classified in three families.}
+\caption{Molecular targets studied in this work, classified in three 
+families.}
 \label{tab:families}
@@
 
-We report the total ionization cross sections by the impact of 
-multicharged ions for adenine, cytosine, guanine and thymine in 
-Fig.~\ref{fig:crossDNA_1}. For adenine, the agreement with the 
-experimental data available~\cite{iriki2011} is very good 
-in our range of validity. To the best of our knowledge, there are not 
-experimental data on ion--collision ionization for the rest of the 
-molecules. We included electron impact measurements~\cite{rahman2016} 
-with the corresponding equivelocity 
-conversion for incident energies higher than 500~keV. In this region, 
-the proton and electron cross section should agree. Although the electron 
-impact measurements are above our findings for all the molecular targets, 
-it is worth stating that our results agree very well with other 
-theoretical predictions~\cite{mozejko2003,tan2018}.
+In Fig.~\ref{fig:crossDNA_1}, we report the total ionization cross 
+sections by the impact of multicharged ions for adenine, cytosine, 
+guanine and thymine. For adenine, the agreement with the experimental 
+data available~\cite{iriki2011} is very good. To the best of our 
+knowledge, there are not experimental data on ion--collision ionization 
+for the rest of the molecules. We included electron impact 
+measurements~\cite{rahman2016} with the corresponding equivelocity 
+conversion for incident energies higher than 300~eV. In this region, 
+the proton and electron cross section should converge. Although the 
+electron impact measurements are above our findings for all the 
+molecular targets, it is worth stating that our results agree very well 
+with other electron impact theoretical 
+predictions~\cite{mozejko2003,tan2018}.
 
-\begin{figure}[t!]
+\begin{figure*}[t!]
 \centering
 %\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
-\includegraphics[width=\textwidth]{figuras/adn1.eps}
-\caption{Scaled ionization cross section by impact of multicharged ions. 
-Experiments: 
-$\circ$~\cite{iriki2011} for proton impact and $\square$~\cite{rahman2016} 
-for electron impact with equivelocity conversion.}
+\includegraphics[width=0.9\textwidth]{figuras/adn1.eps}
+\caption{Reduced CDW ionization cross section by impact of multicharged 
+ions. Experiments: \mbox{\Large$\circ$}~\cite{iriki2011} for proton 
+impact and $\square$~\cite{rahman2016} for electron impact with 
+equivelocity conversion.}
 \label{fig:crossDNA_1}
-\end{figure}
+\end{figure*}
 
-Our calculations for uracil, DNA backbone, pyrimidine and THF are given in 
-Fig.~\ref{fig:crossDNA_2}. 
-For uracil, we have good agreement with the experimental 
-proton impact measurements by Itoh~{\it et al.}~\cite{itoh2013}. 
+Our results for uracil, DNA backbone, pyrimidine and THF are displayed 
+in Fig.~\ref{fig:crossDNA_2}. For uracil, the agreement with the 
+experimental proton impact measurements by 
+Itoh~{\it et al.}~\cite{itoh2013} is good.
 However, for the same target, our theory fails by a factor of two for 
@@
 
-\begin{figure}[t!]
+\begin{figure*}[t!]
 \centering
 %\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig3.eps}
-\includegraphics[width=\textwidth]{figuras/adn2.eps}
-\caption{Scaled ionization cross section by impact of multicharged ions. 
-Experiments: proton impact on $\triangle$ uracil~\cite{itoh2013}, 
+\includegraphics[width=0.9\textwidth]{figuras/adn2.eps}
+\caption{Reduced CDW ionization cross section by impact of multicharged 
+ions. Experiments: proton impact on $\triangle$ uracil~\cite{itoh2013}, 
 $\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$
@@
 Symbols~$\rhd$~\cite{bug2017}, $\lhd$~\cite{wolf2019}, and 
-$\medstar$~\cite{fuss2009} for electron impact with equivelocity conversion.}
+$\medstar$~\cite{fuss2009} for electron impact with equivelocity 
+conversion.}
 \label{fig:crossDNA_2}
-\end{figure}
+\end{figure*}
 
@@
 \subsection{Scaling rule}
+\label{subsec:scaling}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Toburen numbers}
+\subsubsection{Toburen rule}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 phenomenological model for electron ejection from large molecules was 
-proposed by Toburen {\it et al.}~\cite{toburen1975,toburen1976}. 
+proposed by Toburen and coworkers~\cite{toburen1975,toburen1976}. 
 The authors found it convenient to scale the experimental ionization 
-cross section in terms of the number of active or weakly--bound valence 
-electrons $n_e$ (i.e. total number of electrons minus the K--shell).
-Following Toburen, we can define the ionization cross section per weakly 
-bound electron, $\sigma_{e}^T$, as
+cross section in terms of the number of weakly--bound electrons, $n_e$.
+For instance, for C, N, O, P and S, this number is the total number of 
+electrons minus the K--shell. Following Toburen, the scaled ionization 
+cross section per weakly bound electron $\sigma_{e}^T$ is
 \begin{equation}
-\sigma_{e}^T=\frac{\sigma_{M}}{n_e}=\frac{\sum\limits_{\alpha}
-n_{\alpha}\sigma_{\alpha}}{\sum\limits_{\alpha}n_{\alpha}\nu_{\alpha}^T}
-=\sigma_{e}^T(v)\,, 
+\sigma_{e}^T=\frac{\sigma_{M}}{n_e}\,, 
 \label{27} 
 \end{equation}
-where $\nu_{\alpha}^T$ are the Toburen numbers for each $\alpha$ atom 
-is given by
+where $n_e=\sum_{\alpha}n_{\alpha}\nu_{\alpha}^T$, and $\nu_{\alpha}^T$ 
+are the Toburen numbers given by
 \begin{equation}
@@
 molecule, which depends solely on the impact velocity, and holds for 
-high impact energies (i.e. 0.25--5 Mev/amu).
+high impact energies (i.e. 0.25--5 MeV/amu).
 These $\nu_{\alpha}^T$ can be interpreted as the number of active 
@@
 
-\begin{figure}[t!]
+\begin{figure*}[t!]
 \centering
 %\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig4.eps}
-\includegraphics[width=\textwidth]{figuras/molscaling85.eps}
+\includegraphics[width=0.9\textwidth]{figuras/molscaling85.eps}
 \caption{Scaled ionization cross section per weakly bound electron using
@@
 $\nu_{\alpha}^{\text{CDW}}$. Experiments: proton impact on 
-$\circ$ adenine~\cite{iriki2011}, $\triangle$ uracil~\cite{itoh2013}, 
+\mbox{\Large$\circ$} adenine~\cite{iriki2011}, 
+$\triangle$ uracil~\cite{itoh2013}, 
 $\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$ 
@@
 \label{fig:newscaling}
-\end{figure}
+\end{figure*}
 
-Our CDW results for $\sigma_{e}^T$ are shown in 
-Fig.~\ref{fig:newscaling}a as a function of 
-the impact energy for different projectile charges computed with the 
-SSM for the molecular targets from Table~\ref{tab:families}. 
-The universality with $Z$ is the one provided 
-by Born approximation, i.e., $\sigma_{e}^T(Z)=Z^{2}\sigma_{e}^T(Z=1)$, 
-and it holds for large impact velocities, as shown 
+By implementing the SSM, we computed the scaled CDW cross sections 
+$\sigma_{e}^T$ for the molecular targets of Table~\ref{tab:families}.
+Our results are shown in Fig.~\ref{fig:newscaling}a as a function of 
+the impact energy for different projectile charges. Although the 
+Toburen scaling holds for high energies, its performance is still not 
+satisfactory: the universal band is quite broad, as can be noted in 
 Fig.~\ref{fig:newscaling}a.
-Of course, for lower impact velocities, the CDW breaks the behavior of 
-the $Z^{2}$ rule. Although the Toburen scaling holds for high energies, 
-its performance is still not satisfactory: the universal band is quite 
-broad.
 
@@
 The departure of our theoretical 
-results from the Toburen rule can be easily understood %explained by the fact that 
-%our atomic cross sections $\sigma_{\alpha}$ behave differently for 
-%each atom in terms of the projectile charges. By 
+results from the Toburen rule can be easily understood 
 by inspecting Fig.~\ref{fig:atomscaling}. It can be noted that the 
@@
 \begin{equation}
-\sigma_{e}=\frac{\sigma_M}{\sum\limits_{\alpha}n_{\alpha}
-\nu_{\alpha}^{\text{CDW}}},
+\sigma_{e}=\frac{\sigma_M}{n_e'},
 \label{32} 
 \end{equation}
-where $\sigma_M$ follows Eq.~(\ref{eq:sumion}), and 
-$\nu_{\alpha}^{\text{CDW}}$ are the new active--electron numbers 
+where $n_e'=\sum_{\alpha}n_{\alpha}\nu_{\alpha}^{\text{CDW}}$, and 
+$\nu_{\alpha}^{\text{CDW}}$ are the numbers of active electrons
 per atom obtained from the CDW ionization cross sections for 
-different ions in H, C, N, O, P , and S targets. 
-Our proposed active--electron numbers are
+different ions in H, C, N, O, P , and S targets, given as follows,
 \begin{equation}
@@
 
-The new scaled cross sections $\sigma_{e}$ are plotted in Figure~4b. 
+The new scaled cross sections $\sigma_{e}$ are plotted in 
+Fig.~\ref{fig:newscaling}b. 
 A much better sharp band is observed, especially for impact energies 
@@
 adenine~\cite{iriki2011}, uracil~\cite{itoh2013}, 
-pyrimidine~\cite{wolff2014} and THF~\cite{wang2016} by proton impact 
-seems to corroborate the new scaling. 
-We also included the electron impact ionization measurements with equivelocity 
-conversion on pyrimidine~\cite{bug2017}, and THF~\cite{bug2017,wolf2019,fuss2009}. 
+pyrimidine~\cite{wolff2014} and THF~\cite{wang2016} by proton impact in
+Fig.~\ref{fig:newscaling}b seems to corroborate the new scaling. 
+We also included the electron impact ionization measurements with 
+equivelocity conversion on pyrimidine~\cite{bug2017}, and 
+THF~\cite{bug2017,wolf2019,fuss2009}. 
 It will be interesting to cross--check for experiments with higher 
@@
 \hline
- Molecule & $n_e$ &Molecule         & $n_e$ & Molecule             & $n_e$ \\
+ Molecule & $n_e$ &Molecule          & $n_e$ & Molecule             & $n_e$\\
 \hline
@@
 \end{tabular}
-\caption{New scaling numbers for some molecular targets of biological interest.}
+\caption{New scaling numbers for some molecular targets of biological 
+interest.}
 \label{nn}
@@
 
-By using Eq.~(\ref{eq:scalingCDW}), the number of active electrons 
-$n_e=\sum_{\alpha} n_{\alpha} \nu_{\alpha}^{\text{CDW}}$ can be redefined. 
-We give new values in Table~\ref{nn} for some molecules of interest.
-These values are very different from the ones proposed by Toburen and used by 
-other authors~\cite{itoh2013}.
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig_recta.eps}
+\caption{Ionization cross sections by impact of protons at 0.5, 1 and 2 MeV
+in terms of the number of active electrons given by Table~\ref{nn}.
+Experiments: 
+\mbox{\Large$\circ$}~adenine~\cite{iriki2011}, 
+$\triangle$ uracil~\cite{itoh2013}, 
+$\bigtriangledown$ pyrimidine~\cite{wolff2014}, 
+$\blacktriangle$ C2H$_7$N, CH$_5$N, methane and amonia~\cite{lynch1976},
+\mbox{\scriptsize$\bigstar$} amonia and H$_2$~\cite{rudd1985}, and 
+\mbox{\Large$\bullet$} water~\cite{luna2007}.}
+\label{fig:recta}
+\end{figure*}
+
+By using Eq.~(\ref{eq:scalingCDW}), we define new active electron 
+numbers $n_e'$ for some molecular of interest in Table~\ref{nn}. 
+These values are very different from the ones proposed by Toburen and 
+used by other authors~\cite{itoh2013}.
 Moreover, an alternative way of showing the scaling can be attained by 
@@
 molecules, H$_2$, H$_2$O and CH$_4$, up to the most complex ones, like 
-adenine or guanine. In some cases, the experimental data were interpolated.
-Care was taken in such procedure.
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig_recta.eps}
-\caption{Ionization cross sections by impact of protons at 0.5, 1 and 2 MeV
-in terms of the number of active electrons given by Table~\ref{nn}.
-Experiments: $\circ$~adenine~\cite{iriki2011}, $\triangle$ uracil~\cite{itoh2013}, 
-$\bigtriangledown$ pyrimidine~\cite{wolff2014}, 
-$\blacktriangle$ C2H$_7$N, CH$_5$N, methane and amonia~\cite{lynch1976},
-$\bigstar$ amonia and H$_2$~\cite{rudd1985}, and $\bullet$ water~\cite{luna2007}.}
-\label{fig:recta}
-\end{figure}
+adenine. For electron impact data, the experimental data was interpolated
+between close neighboors.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{A modified stoichiometric model}
+\subsection{Molecular structure of targets}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To test the range of validity of the SSM, we performed a full molecular 
+structure calculation of five nucleobases. We employed the {\sc gamess} 
+code and used the 6-31G(d,p) basis set, which includes polarization 
+functions for all the atoms. The calculations were carried out 
+implementing the B3LYP functional~\cite{Becke1993,Stephens1994} to 
+account for the correlation and exchange effects.
+
+The molecular binding energies of the valence electrons for adenine, 
+cytosine, guanine, thymine and uracil are shown in Fig.~\ref{fig:bindener}. 
+We can compute the center of gravity of the molecular energy levels as 
+an average weighted by the electronic occupation number. The results 
+obtained from the full molecular calculation are given in the first row
+of Table~\ref{tab:gravener}. Similarly, we can compute the baricenter
+of the energy levels defined by the Toburen rule and the one given by
+Eq.~(\ref{eq:scalingCDW}), which are also given in 
+Table~\ref{tab:gravener}. The average energy values obtained from the
+Toburen rule are around 20\% of the full molecular ones. Surprisingly, 
+the new scaling rule gives a significant 
+improvement in the average energy values, reducing the relative errors
+to about~7\%. This improvement would seem to indicate that the new 
+scaling is appropiate.
+
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=0.9\textwidth]{figuras/levelsDNA.eps}
+\caption{Theoretical molecular binding energies for adenine, cytosine, 
+guanine, thymine and uracil compared to those of atomic constituents.}
+\label{fig:bindener}
+\end{figure*}
+
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{|c|ccccc|}
+\hline
+ \multirow{2}{*}{$E_{\text{av}}$ (eV)} & A & C & G & T & U \\
+ & C$_5$H$_5$N$_5$ & C$_4$H$_5$N$_3$O & 
+   C$_5$H$_5$N$_5$O & C$_5$H$_6$N$_2$O$_2$ & C$_4$H$_4$N$_2$O$_2$ \\
+\hline
+ Theoretical calc. & $-7.1955$ & $-6.9058$ & $-7.4725$ & $-7.5304$ & $-7.6224$ \\
+ Toburen rule  & $-8.4236$ & $-8.6743$ & $-8.7275$ & $-8.7947$ & $-9.0022$ \\
+ Present work & $-7.9027$ & $-7.8639$ & $-7.9420$ & $-7.8066$ & $-7.8839$ \\
+%                 17%         25%         17%         17%         18%         
+%                 10%         13%         6%          4%          3%
+\hline
+\end{tabular}
+\caption{Center of gravity of the molecular energy levels of five 
+nucleobases.}
+\label{tab:gravener}
+\end{center}
+\end{table}
+
+Furthermore, on the left side of the Fig.~\ref{fig:bindener}, we show 
+the atomic Hartree--Fock energies of the constituent elements, which 
+gives an insight on the distribution of the weakly bound electrons. 
+A dashed line around $-11$~eV is drawn to separate the band in two. 
+We can consider the atomic energy levels above this line as the ones
+corresponding to the weakly bound electrons from Eq.~(\ref{eq:scalingCDW}).
+For example, the $2s$ and $2p$ electrons of carbon are placed above
+the separating line, which corresponds to the 4 electrons given by 
+Eq.~(\ref{eq:scalingCDW}). In the case of O, only the 4 electrons of 
+the $2p$ orbitals are located above the separating line.
+
+The electrons in the molecular 
+targets corresponding to the $2s$ of N and C in the atomic case are 
+placed in a secondary gap. The lower levels of the secondary gap 
+correspond to the oxygen. The number of electrons in the valence 
+shell for all O would seem to be equal to 4, as previously setted by the 
+scaling rule Eq.~(\ref{eq:scalingCDW}). The N case is not as 
+straightfoward; the electrons that would correspond to the $2s$ are 
+located just below the line. The $\nu_{\alpha }^{\text{CDW}}$ value 
+given for N would suggest that a significant amount of electron density 
+from the secondary gap is shared with the valence band.
 
@@
 
-To inspect the effect of $q_{\alpha}$, we computed the molecular
-structure of several nucleobases with the {\sc gamess} code. We 
-used the 6-31G(d,p) basis set, which includes polarization 
-functions for all the atoms. The calculations were carried out 
-implementing the B3LYP functional~\cite{Becke1993,Stephens1994} to 
-account for the correlation and exchange effects. 
 In Table~\ref{tab:newstoi}, we display the charge $q_{\alpha}$ of four 
-DNA molecules.
+DNA molecules, obtained from the full molecular calculation.
 
@@
 \label{tab:newstoi}
-\end{center}
-\end{table}
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=\textwidth]{figuras/levelsDNA.eps}
-\caption{Theoretical molecular binding energies for adenine, cytosine, 
-guanine, thymine and uracil compared to those of atomic constituents.}
-\label{fig:bindener}
-\end{figure}
-
-The molecular binding energies of the outer electrons for adenine, 
-cytosine, guanine and thymine are shown in Fig.~\ref{fig:bindener}. 
-On the left side of the figure, we show the atomic Hartree--Fock energies 
-of the constituent elements, which can give an idea of how the molecular 
-levels distribute. A dashed line around $-0.8$~a.u. is drawn to separate 
-in two the band levels of the outer electrons. The electrons in the molecular 
-targets corresponding to the $2s$ of N and C in the atomic case are 
-placed in a secondary gap. The lower levels of the secondary gap 
-correspond to the oxygen. The number of electrons in the valence 
-shell for all O would seem to be equal to 4, as previously setted by the 
-scaling rule Eq.~(\ref{eq:scalingCDW}). The N case is not as 
-straightfoward; the electrons that would correspond to the $2s$ are 
-located just below the line. The $\nu_{\alpha }^{\text{CDW}}$ value 
-given for N would suggest that a significant amount of electron density 
-from the secondary gap is shared with the valence band.
-
-\begin{table}[H]
-\begin{center}
-\begin{tabular}{llllll}
-\hline
- $E_{\text{av}}$ & Adenine & Cytosine & Guanine & Thymine & Uracil \\
-\hline
- Molecular & -7.1955 & -6.9058 & -7.4725 & -7.5304 & -7.6224 \\
- Toburen   & -8.4236 & -8.6743 & -8.7275 & -8.7947 & -9.0022 \\
- Our work  & -7.9027 & -7.8639 & -7.9420 & -7.8066 & -7.8839 \\
-\hline
-\end{tabular}
-\caption{.}
-\label{tab:gravener}
 \end{center}
@@
 
+\bibitem{salvat1995}
+Salvat, F., Fernández-Varea, J.M., Williamson, W.
+Comput. Phys. Commun. \textbf{90}, 151--168 (1995)
+
 \bibitem{mendez2016} 
@@
 H. Q. Tan, Z. Mi, and A. A. Bettiol, 
-Simple and universal model for electron-impact ionization of complex biomolecules, 
+Simple and universal model for electron-impact ionization of complex 
+biomolecules, 
 Phys. Rev. E \text{97}, 032403 (2018)

### 2019-09-23 NewMonti25.tex
new scale with ne fig

@@
 %\documentclass[pra,showpacs,twocolumn]{revtex4}
-\documentclass[preprint]{revtex4}
+\documentclass[preprint]{revtex4-2}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \usepackage{float}
-\usepackage{authblk}
 \usepackage{MnSymbol}
@@
 \author{author}
-%\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio 
-%(CONICET-UBA).
-%Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
-%\author{author}
-%\affil{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
-%Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
-%\affil{Fac. de Ciencias Exactas y Naturales, Universidad de Buenos Aires}
+\address{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio 
+(CONICET-UBA).
+Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
+\author{author}
+\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
+Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
+\affiliation{Fac. de Ciencias Exactas y Naturales, Universidad de Buenos Aires}
 
@@
 \begin{abstract}
+In this work we investigate the ionization of molecules of biological 
+interest by impact of multicharged ions in the intermediate to high 
+energy range. We performed full non--perturbative distorted--wave 
+calculations (CDW) for thirty six collisional systems, six charged projeciles 
+(antiprotons, H, He, B, C and O) and by six atomic targets H, C, N, O, 
+F and S. These atoms are the constituents of most of the DNA and 
+biological molecules. By considering the stoichiometric composition of 
+the different molecules we approximate the ionization cross sections 
+as linear combination of the atomic ones.  We show that this simple 
+stoichiometric model (SSM) gives reasonable good results for complex 
+molecules. We focused on seventeen molecules including the DNA 
+(adenine, cytosine, guanine, thymine, uracil), DNA backbone, the 
+pyrimidines, tetrahydrofuran (THF), and the C$_n$H$_n$ compounds. The 
+full comparison of 
+the total ionization cross sections for the different ions normalized 
+to the square of the ion charge gives an interesting picture of the
+experimental state of art. The energy and angular distributions of the 
+emitted electrons are also inspected due to its relation with the 
+radiation damage. Our results show that these two parameters are highly 
+dependent on the projectile charge state, which cannot be noted in a
+first order perturbative calculation. We also analyze the extensively 
+used Toburen 
+scaling of the total ionization cross sections of molecules with the 
+number of weakly bound electrons. We tested this scaling for the seventeen 
+different molecules and the six projectiles per each, which allows to 
+have an insight on the limitation of this scaling. Instead, based on 
+the present CDW results for the atoms, we propose a different number 
+of electrons per atom. This CDW--based scaling highly improves the 
+single curve behaviour for all the targets and ions studied here, in the 
+intermediate to high energy region. The new scaling also describes well 
+the available experimental data, including small molecules such as H2, 
+water, methane and ammonia. For completeness, we performed full 
+molecular calculations for the five DNA molecules, and tested a 
+corrected stoichiometric formula based on the actual number of 
+electrons around each molecular center. The difference of these more 
+realistic ionization cross sections and the SSM ones was less than 
+$3\%$, being an indication of the reliability and robustness of the 
+SSM to deal with this type of molecules. Based on the extensive 
+ion-target systems included in the present study, and the results 
+obtained, the possibilities of the SSM and the new scaling are of 
+great impact.
 \end{abstract}
@@
 
-\tableofcontents
+%\tableofcontents
 %\pacs{79.20.Rf, 68.49.Bc, 34.20.Cf,34.50.-s,34.35.+a}
@@
 bromine; ionization cross sections of these elements have been 
-previously published~\cite{miraglia2008,miraglia2009}.
+previously published~\cite{miraglia2008}.
 
 The total ionization cross sections of these atoms were calculated using 
-the CDW~[xxx]. The initial bound and final continuum radial wave 
+the CDW~\cite{miraglia2008,fainstein1988,miraglia2009}. The initial bound and final continuum radial wave 
 functions were obtained by using the {\sc radialf} code, developed by 
@@
 sections for the 36 ion--target systems considered in the present 
-work~\cite{miraglia2019}. We expect that these results will be useful
-to estimate molecule fragmentation.
+work~\cite{miraglia2019}. A great numerical effort was paid to obtain 
+the present results, and we expect that they will be useful to estimate 
+molecule fragmentation.
 
@@
 \centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig1.eps}
-\includegraphics[width=0.9\textwidth]{figuras/atomicscaling.eps}
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig1.eps}
+%\includegraphics[width=0.9\textwidth]{figuras/atomicscaling.eps}
 \caption{Reduced CDW total ionization cross section of six atomic 
@@
 \centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig5.eps}
-\includegraphics[width=0.9\textwidth]{figuras/ener_mean.eps}
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig5.eps}
+%\includegraphics[width=0.9\textwidth]{figuras/ener_mean.eps}
 \caption{Mean emitted energy distribution for ionization by impact of
@@
 \centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig6.eps}
-\includegraphics[width=0.9\textwidth]{figuras/ang_mean.eps}
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig6.eps}
+%\includegraphics[width=0.9\textwidth]{figuras/ang_mean.eps}
 \caption{Mean emitted angle distribution for ionization by impact of
@@
 \centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
-\includegraphics[width=0.9\textwidth]{figuras/adn1.eps}
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
+%\includegraphics[width=0.9\textwidth]{figuras/adn1.eps}
 \caption{Reduced CDW ionization cross section by impact of multicharged 
@@
 \centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig3.eps}
-\includegraphics[width=0.9\textwidth]{figuras/adn2.eps}
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig3.eps}
+%\includegraphics[width=0.9\textwidth]{figuras/adn2.eps}
 \caption{Reduced CDW ionization cross section by impact of multicharged 
@@
 \centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig4.eps}
-\includegraphics[width=0.9\textwidth]{figuras/molscaling85.eps}
+\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig4.eps}
+%\includegraphics[width=0.9\textwidth]{figuras/molscaling85.eps}
 \caption{Scaled ionization cross section per weakly bound electron using
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig_recta.eps}
+%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig_recta.eps}
+\includegraphics[width=0.75\textwidth]{figuras/scale_ne.eps}
 \caption{Ionization cross sections by impact of protons at 0.5, 1 and 2 MeV
@@
 
+Finishing the present work we noted an accepted manuscript by 
+Luedde~{\it et al.} \cite{luedde2019} who also noted a similar scaling 
+at least for C, N, and O and reinforces the present finding.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 cytosine, guanine, thymine and uracil are shown in Fig.~\ref{fig:bindener}. 
-We can compute the center of gravity of the molecular energy levels as 
+We can compute the center of gravity of these molecular energy levels as 
 an average weighted by the electronic occupation number. The results 
@@
 of Table~\ref{tab:gravener}. Similarly, we can compute the baricenter
-of the energy levels defined by the Toburen rule and the one given by
+of the energy levels defined by the Toburen rule and the new rule, given by
 Eq.~(\ref{eq:scalingCDW}), which are also given in 
@@
 Eq.~(\ref{eq:scalingCDW}). In the case of O, only the 4 electrons of 
-the $2p$ orbitals are located above the separating line.
+the $2p$ orbitals are located above the separating line, which 
+corresponds to the number of weakly bound electron given by 
+our new scaling. 
+The N case is not as straightfoward; the $\nu_{\alpha }^{\text{CDW}}$ 
+value given for N would suggest that some $2s$ electrons corresponding 
+to the molecular squeme are also weakly bonded, leading to 4 electrons.
 
-The electrons in the molecular 
-targets corresponding to the $2s$ of N and C in the atomic case are 
-placed in a secondary gap. The lower levels of the secondary gap 
-correspond to the oxygen. The number of electrons in the valence 
-shell for all O would seem to be equal to 4, as previously setted by the 
-scaling rule Eq.~(\ref{eq:scalingCDW}). The N case is not as 
-straightfoward; the electrons that would correspond to the $2s$ are 
-located just below the line. The $\nu_{\alpha }^{\text{CDW}}$ value 
-given for N would suggest that a significant amount of electron density 
-from the secondary gap is shared with the valence band.
+\subsubsection{A modified stoichiometric model}
 
@@
 $n_{\alpha}^{\prime}=n_{\alpha}$, as it should be. 
-
-In Table~\ref{tab:newstoi}, we display the charge $q_{\alpha}$ of four 
-DNA molecules, obtained from the full molecular calculation.
+In Table~\ref{tab:newstoi}, we display the average effective charge 
+per atom $q_{\alpha}$ of C, H, N and O, for five DNA molecules. 
+The charges were obtained from the full molecular calculation described 
+above.
 
@@
 Thymine & +0.20 & +0.19 & --0.54 & --0.52 & 
-C$_{4.95}$H$_{1.95}$N$_{6.13}$O$_{2.13}$ \\ 
+C$_{4.95}$H$_{1.81}$N$_{6.13}$O$_{2.13}$ \\ 
+\hline
+Uracil & +0.31 & +0.22 & --0.59 & --0.47 & 
+C$_{3.92}$H$_{1.78}$N$_{4.15}$O$_{2.12}$ \\ 
 \hline
 \end{tabular}
-\caption{Effective charge $q_{\alpha}$ and new stoichiometric formula 
-defined by Eq.~(\ref{eq:newstoi}) for four DNA molecules.}
+\caption{Average effective Mulliken charge per atom $q_{\alpha}$, and 
+new stoichiometric formula defined by Eq.~(\ref{eq:newstoi}) for five 
+DNA molecules.}
 \label{tab:newstoi}
@@
 Now, instead of having an integer number of atoms $n_{\alpha}$, we obtain 
-a fractional number $n_{\alpha}^{\prime}$. 
-Molecular cross sections $\sigma^{\prime}$ can be computed considering 
+a fractional number $n_{\alpha}^{\prime}$. New molecular cross sections 
+$\sigma^{\prime}_{M}=\sum_{\alpha}n_{\alpha}'\sigma_{\alpha}$ can be 
+computed considering 
 such values. Relative errors for the ionization cross sections were 
 computed for the DNA bases from Table~\ref{tab:newstoi}. The differences 
-obtained were of just very few percents, which indicates that the modified 
-SSM is a quite robust model to handle these type of molecule within 
+obtained were less than 3\%, which indicates that the modified 
+SSM is a quite robust model to handle these type of molecules within 
 the range error expected for this model.
@@
 
-We calculated ionization cross sections by impact of antiprotons, 
-H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$ for seventeen 
-molecules containing H, C, N, O, P and S with the CDW method. The 
-importance of the influence of $Z$ was observed in the mean energy 
-$\overline{E}_{\alpha}$ and angle $\overline{\theta}_{\alpha}$. 
-For a given target $\alpha$, as the nuclear charge of the projectile 
-$Z$ increases, so does the mean energy of emittion $\overline{E}_{\alpha}$. 
-Conversely, the mean angle of emission  $\overline{\theta}_{\alpha}$ 
-decreases. At high impact energy, say larger than 1 MeV/amu, these 
-values converge to the Born approximation, which embodies the simple 
-$Z^{2}$ law. The seventeen molecules selected were investigated using 
-the simple stoichiometric model. Results for eigth DNA bases were 
-presented and compared with the sparse available experiments. We explore 
-the rule of Toburen which scales all the molecular ionization cross 
-section when divided by the number of weakly bound valence electrons 
-$\nu_{\alpha}^T$ given by Eq.~(\ref{27}). 
-We found the rule scales much better when normalizing our theoretical 
-ionization cross sections to the number $\nu_{\alpha}^{\text{CDW}}$ 
-given by Eq.~(\ref{eq:scalingCDW}). Finally, we attempt to improve the 
-stoichiometric model by using the Mulliken charge to define a new model 
-containing fractional rather than integer proportions. No substantial 
-correction was found, which indicates that our modified SSM works quite 
-well. By inspecting the molecular binding energy from quantum mechanical 
-structure calculations, we were able to understand the values defined
-for $\nu_{\alpha}^{\text{CDW}}$.
+In this work we have encouraged the calculation of ionization cross 
+sections of seventeen biological molecules containing H, C, N, O, P and 
+S by impact of antiprotons, H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, 
+and O$^{8+}$. 
+To that end we have employed the full CDW method including... and a 
+simple stoichiometric model. 
+The mean energy and angle of the emitted electrons, of importance in 
+post-collisional radiation damage,  has also been calculated, showing 
+a clear dependence with the ion charge $Z$. For a given target as $Z$ 
+increases, $\overline{E}_{\alpha}$
+increases, but $\overline{\theta}_{\alpha}$ decreases. At impact
+energies larger than 1 MeV/amu, these values converge to the Born
+approximation, which embodies the simple $Z^{2}$ law.
 
-The main objective of this article is to provide the tools to estimate 
+Total ionization cross sections for adenine, cytocine, thymine, gaunine, 
+uracil, DNA backbone, pyrimidine and THF are presented and compared 
+with the the scarse available experiments. We explore the rule of 
+Toburen which scales
+all the molecular ionization cross section normalizing with certain 
+number of
+weakly bound or valence electrons. We found that ionization cross 
+sections scales much better when normalizing with the number of active 
+electrons in the collision obtained from the CDW results for atoms. 
+This new scaling was tested with very good results for the six 
+projectiles and seventeen molecules studied here. The comparison with 
+the experimental data reinforce this results. Moreover, we also test 
+the scaling by including experimental data of ionization of H$_2$, 
+water, methane and ammonia by proton impact showing good agreement at
+intermediate to high energies.
+Finally, we performed full molecular calculations for the DNA basis. 
+By inspecting the molecular binding energy from quantum mechanical
+structure calculations, we were able to understand the number of 
+electrons proposed in our new CDW-based scaling. We attempt to improve 
+the stoichiometric model by using the Mulliken charge to get fractional
+rather than integer proportions. It is interesting to remark that no 
+substantial
+correction was found, which indicates that the SSM works quite well.
+
+The main objective of this article was to provide the tools to estimate 
 any inelastic parameter parameter --such as emission angle, emitted mean
-energy and cross section-- by the impact of any multicharged on any 
-molecule containing H, C, N, O, P and S, with the help of the 
+energy and cross section-- by the impact of any multicharged projectiles 
+on any molecule containing H, C, N, O, P and S, with the help of the
 stoichimetrical model. Our goal was quite ambitious, considering the
-simplicity of our proposal. However, we think our results could be used 
-to estimate the ionization magnitude with an acceptable level of 
-uncertainty.
+simplicity of our proposal. However, the present results show the 
+validity of the simple stoichiometric model to estimate the ionization 
+magnitude with an acceptable level of uncertainty.
 
@@
 \begin{thebibliography}{99}
+
+\bibitem{toburen1975} 
+W. E. Wilson and L. H. Toburen. Electron emission from
+proton --hydrocarbon-molecule collisions at 0.3--2.0 MeV. 
+Phys. Rev. A 11, 1303 (1975).
+
+\bibitem{toburen1976} 
+D. J. Lynch, L. H. Toburen, and W. E. Wilson. Electron
+emission from methane, ammonia, monomethylamine, and dimethylamine by 0.25
+to 2.0 MeV protons. 
+J. Chem. Phys. 64, 2616 (1976).
 
@@
 Phys. Rev. A \textbf{79}, 022708 (2009).
+
+\bibitem{fainstein1988}
+Fainstein P.D., Ponce V. H. and Rivarola R. D. 
+J. Phys. B: At. Mol. Opt. Phys. \textbf{21} 287 (1988).
 
@@
 O$^{+8}$ on H, C, N, O, P, and S atoms To be published Archive 2019.
+
+\bibitem{surdutovic2018} 
+Multiscale approach to the physics of radiation
+damage with ions. E. Surdutovich and A. V. Solov'yov, 
+arXiv:1312.0897v, (2013)
+
+\bibitem{abril2015} 
+P. de Vera1, I. Abril, R. Garcia-Molina and
+A.V.Solov'yov,\ Ionization of biomolecular targets by ion impact: input data
+for radiobiological applications. 
+Journal of Physics: Conference Series 438
+(2013) 012015
+
+\bibitem{Rudd1992} 
+M. E. Rudd, Y.-K. Kim,, D. H. Madison and T. J. Gay.
+Electron production in proton collisions with atoms and molecules: energy
+distributions. 
+Rev. Mod. Phys. \textbf{64}, 44-490 (1992).
 
@@
 
-\bibitem{toburen1975} 
-W. E. Wilson and L. H. Toburen. Electron emission from
-proton --hydrocarbon-molecule collisions at 0.3--2.0 MeV. 
-Phys. Rev. A 11, 1303 (1975).
+\bibitem{luedde2019}
+H J Luedde et al 2019 
+J. Phys. B: At. Mol. Opt. Phys. in press https://doi.org/10.1088/1361-6455/ab3a63
 
-\bibitem{toburen1976} 
-D. J. Lynch, L. H. Toburen, and W. E. Wilson. Electron
-emission from methane, ammonia, monomethylamine, and dimethylamine by 0.25
-to 2.0 MeV protons. 
-J. Chem. Phys. 64, 2616 (1976).
+\bibitem{Becke1993}
+A. D. Becke, 
+J. Chem. Phys. 98, 5648-5652 (1993)
 
-\bibitem{surdutovic2018} 
-Multiscale approach to the physics of radiation
-damage with ions. E. Surdutovich and A. V. Solov'yov, 
-arXiv:1312.0897v, (2013)
-
-\bibitem{abril2015} 
-P. de Vera1, I. Abril, R. Garcia-Molina and
-A.V.Solov'yov,\ Ionization of biomolecular targets by ion impact: input data
-for radiobiological applications. 
-Journal of Physics: Conference Series 438
-(2013) 012015
+\bibitem{Stephens1994}
+P. J. Stephens, F. J. Devlin, C. F. Chabalowski, M. J. Frisch,
+J. Phys. Chem. 98, 11623-11627 (1994)
 
@@
 
-\bibitem{Becke1993}
-A. D. Becke, 
-J. Chem. Phys. 98, 5648-5652 (1993)
+%\bibitem{pimblott2007} 
+%S.M. Pimblott and J. A. LaVerne, Radiation
+%Physics and Chemistry 76, 1244-1247 (2007)
 
-\bibitem{Stephens1994}
-P. J. Stephens, F. J. Devlin, C. F. Chabalowski, M. J. Frisch,
-J. Phys. Chem. 98, 11623-11627 (1994)
-
-\bibitem{pimblott2007} 
-S.M. Pimblott and J. A. LaVerne, Radiation
-Physics and Chemistry 76, 1244-1247 (2007)
-
-\bibitem{Rudd1992} 
-M. E. Rudd, Y.-K. Kim,, D. H. Madison and T. J. Gay.
-Electron production in proton collisions with atoms and molecules: energy
-distributions. 
-Rev. Mod. Phys. \textbf{64}, 44-490 (1992).
-
-\bibitem{clementi}
-E. Clementi, C. Roetti,
-At. Data Nucl. Data Tables 14, 177--478 (1974).
+%\bibitem{clementi}
+%E. Clementi, C. Roetti,
+%At. Data Nucl. Data Tables 14, 177--478 (1974).
 

### 2019-09-26 NewMonti25.tex
checked with grammarly and new figs

--- 2019-09-23 NewMonti25.tex
@@
 %\documentclass[pra,showpacs,twocolumn]{revtex4}
-\documentclass[preprint]{revtex4}
+\documentclass[preprint,showpacs]{revtex4}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\author{author}
-%\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio 
-%(CONICET-UBA).
-%Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
+\author{A. M. P. Mendez, C. C. Montanari, J. E. Miraglia}
 %\author{author}
-%\affil{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
-%Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
-%\affil{Fac. de Ciencias Exactas y Naturales, Universidad de Buenos Aires}
+%\author{author}
+\address{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio 
+(CONICET--UBA), \\ Buenos Aires, Argentina.}
 
 \date{\today}% It is always \today, today,
+\pacs{34.50Gb, 34.80Gs, 34.80Dp}
 
 \begin{abstract}
+In the present work, we investigate the ionization of molecules of 
+biological interest by the impact of multicharged ions in the 
+intermediate to high energy range. We performed full non--perturbative 
+distorted--wave calculations (CDW) for thirty--six collisional systems. 
+Six atomic targets compose these systems: H, C, N, O, F and S --which 
+are the constituents of most of the DNA and biological molecules-- and 
+six charged projectiles (antiprotons, H, He, B, C, and O). On account 
+of the radiation damage caused by secondary electrons, we also inspect 
+the energy and angular distributions of the emitted electrons from the 
+atomic targets. We examine seventeen molecules: DNA and RNA bases, 
+DNA backbone, pyrimidines, tetrahydrofuran (THF), and several 
+C$_n$H$_n$ compounds. We show that the simple stoichiometric model 
+(SSM), which approximates the molecular ionization cross sections as a 
+linear combination of the atomic ones, gives reasonably good results 
+for complex molecules. We also inspect the extensively used Toburen 
+scaling of the total ionization cross sections of molecules with the 
+number of weakly bound electrons. Based on the present atomic CDW 
+results, we propose new active electron numbers. The CDW--based scaling 
+improves significantly the single curve behavior for all the targets 
+and ions studied here, from the intermediate to the high energy region. 
+Furthermore, the new scaling describes well the available experimental 
+data for proton impact, including small molecules such as H$_2$, water, 
+methane, and ammonia. For completeness, we perform full molecular 
+calculations for five nucleobases and test a modified stoichiometric 
+formula based on the Mulliken charge of the composite atoms. The 
+difference introduced by the new stoichiometric formula is less than 
+$3\%$, which indicates the reliability and robustness of the SSM to 
+deal with this type of molecules. The results of the extensive 
+ion--target examination included in the present study allow us to 
+assert that the SSM and the CDW--based scaling will be useful tools in 
+this area.
 \end{abstract}
@@
 the projectiles are multicharged ions, we resort to the Continuum 
-Distorted Wave--Eikonal Initial State (CDW), which includes higher 
-perturbative corrections. We start from the premise that the ionization 
+Distorted Wave--Eikonal Initial State 
+(CDW)~\cite{fainstein1988,miraglia2008,miraglia2009}, which includes higher 
+perturbative corrections. Details on the CDW calculation are given in 
+Section~\ref{sec:atoms}.
+We start from the premise that the ionization 
 process is the mechanism that deposits the most significant amount of 
-primary energy. Moreover, it is well known that the residual electrons 
-from the ionization become a source of significant local biological 
-damage. The secondary electrons are included in Monte Carlo simulations, 
-and hence their behavior must be investigated. 
+primary energy. Moreover, the residual electrons from the ionization 
+are known to be a source of significant local biological damage. 
+The secondary electrons are included in Monte Carlo simulations, 
+and hence their behavior requires further investigation.
 In Section~\ref{subsec:meanener} and \ref{subsec:meanang}, we calculate
 the mean energy and angular distributions of the ejected electrons. 
-Surprisingly, we found a substantial dependence of the charged 
-projectile, which is unexpected in the first Born approximation. 
-We deal with the molecular structure complexity of the target by 
+Surprisingly, we found a substantial dependence on the projectile charge, 
+which is unexpected in the first Born approximation.
+
+In Section~\ref{subsec:stoichiometric}, we deal with the molecular 
+structure complexity of the targets by 
 implementing the simplest stoichiometric model (SSM): the molecules are 
 assumed to be composed of isolated independent atoms, and the total 
-cross--section by a linear combination of weighted atomic calculations.
-
+cross section by a linear combination of stoichiometric weighted atomic 
+calculations.
 By implementing the CDW and the SSM, we calculate ionization 
-cross--section of several molecules of interest (see 
-Table~\ref{tab:families}) by the impact of antiprotons, H$^{+}$, 
-He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
-In Section~3, we show our results for different DNA and RNA molecules, 
-such as adenine, cytosine, guanine, thymine, uracil, tetrahydrofuran~(THF), 
-pyrimidine, and also DNA backbone. In Section~\ref{subsec:scaling}, we
+cross section of several molecules of biological interest, including 
+DNA and RNA molecules, such as adenine, cytosine, guanine, thymine, uracil, 
+tetrahydrofuran~(THF), pyrimidine, and DNA backbone, by the impact 
+of antiprotons, H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
+In Section~\ref{subsec:scaling}, we
 test the Toburen scaling rule~\cite{toburen1975,toburen1976}, which 
-states that the ratio between the ionization cross--section and the 
+states that the ratio between the ionization cross section and the 
 number of weakly bound electrons can be arranged in a narrow universal 
@@
 several hydrocarbons and nucleobases and noted that the width of the 
-resulting universal band could be significantly reduced if we redefine 
-the effective number of active electrons in the collision. The new 
-scaling is then tested by comparison with experimental data.
+resulting universal band could be significantly reduced if we consider 
+the number of active electrons in the collision based on the 
+CDW results for the different atoms. The new scaling was then tested 
+theoretically and by comparison with experimental data available.
 
-Although the multicharged projectiles are dealt with the CDW, the 
-stoichiometric model used seems to be very simplistic. The approach
-considers each atom as neutral, which is not correct. In Section 3.5, 
+The approach SSM considers the atoms in the molecule as neutral, 
+which is not correct. In Section~\ref{subsec:molcalculations}, 
 we used the molecular electronic structure code 
 {\sc gamess}~\cite{gamess} to calculate the excess or defect of 
-electron density on the atoms composing the molecules. Then, the SSM is 
-modified to account for the departure from the neutrality of the atoms. 
+electron density on the atoms composing the molecules. Then, we modified 
+the SSM to account for the departure from the neutrality of the atoms. 
 We find that the modified SSM for the DNA molecules does not introduce 
@@
 \section{Theory: Ionization of Atoms}
+\label{sec:atoms}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 bromine; ionization cross sections of these elements have been 
-previously published~\cite{miraglia2008,miraglia2009}.
+previously published~\cite{miraglia2008}.
 
 The total ionization cross sections of these atoms were calculated using 
-the CDW~[xxx]. The initial bound and final continuum radial wave 
+the CDW. The initial bound and final continuum radial wave 
 functions were obtained by using the {\sc radialf} code, developed by 
-Salvat and co--workers~\cite{salvat1995}, and a Hartree-Fock potential 
+Salvat and co--workers~\cite{salvat1995}, and a Hartree--Fock potential 
 obtained from the Depurated Inversion Method~\cite{mendez2016,mendez2018}. 
@@
 state. The radial integration was performed using the cubic spline 
-technique. The number of angular momenta considered varied from 8, at 
-very low ejected-electron energies, up to 30, for the highest energies 
-considered. The same number of azimuth angles were required to obtain 
-the four-fold differential cross section. The calculation performed does 
-not display prior-post discrepancies at all. Each atomic total cross 
-section was calculated using 35 to 100 momentum transfer values, 28 
-fixed electron angles, and around 45 electron energies depending on the 
-projectile impact energy. In our theoretical treatment, we expand our 
-final continuum wave function as usual,
+technique. We expand our final continuum wave function as usual,
 \begin{equation}
@@
 \end{equation}
-We are confident with our calculations up to $l_{\max}\sim 30$. Further 
-details of the calculation are given in Ref.~\cite{montanari2017}. 
-Simultaneously, we will be reporting state to state ionization cross 
-sections for the 36 ion--target systems considered in the present 
-work~\cite{miraglia2019}. We expect that these results will be useful
-to estimate molecule fragmentation.
+The number of angular momenta considered varied from 8, at 
+very low ejected--electron energies, up to $l_{\max}\sim 30$, 
+for the highest energies 
+considered. The same number of azimuth angles were required to obtain 
+the four--fold differential cross section. The calculation performed does 
+not display prior--post discrepancies at all. Each atomic total cross 
+section was calculated using 35 to 100 momentum transfer values, 28 
+fixed electron angles, and around 45 electron energies depending on the 
+projectile impact energy. 
+Further details of the calculation are given in Ref.~\cite{montanari2017}.
 
@@
 %\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig1.eps}
-\includegraphics[width=0.9\textwidth]{figuras/atomicscaling.eps}
+\includegraphics[width=0.8\textwidth]{figuras/atomicscaling.eps}
 \caption{Reduced CDW total ionization cross section of six atomic 
@@
 
-We report our total CDW ionization cross sections for the six essential 
-elements by the impact of six projectiles in Fig.~\ref{fig:atomscaling}.
+We display our total CDW ionization cross sections for the six essential 
+elements by the impact of the six projectiles in Fig.~\ref{fig:atomscaling}.
 To reduce the resulting 36 magnitudes into a single consistent 
@@
 the ionization cross section scales with the square of the projectile 
-charge, $Z^{2}$. The values of the impact energies considered 
+charge, $Z^{2}$. The impact energies considered 
 range between 0.1 to 10 MeV/amu, where the CDW is supposed 
@@
 future works.
+
+Simultaneously, we will be reporting state to state ionization cross 
+sections for the 36 ion--target systems considered in the present 
+work~\cite{miraglia2019}. A great numerical effort was paid to obtain 
+these results, and we expect that they will be useful to estimate 
+molecule fragmentation.
 
@@
 %\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig5.eps}
-\includegraphics[width=0.9\textwidth]{figuras/ener_mean.eps}
-\caption{Mean emitted energy distribution for ionization by impact of
-multicharged ions, given by Eq.~(\ref{40}). Dashed lines for $\bar{p}$,
+\includegraphics[width=0.8\textwidth]{figuras/ener_mean.eps}
+\caption{Mean emitted energy distribution for ionization by the impact 
+of multicharged ions, given by Eq.~(\ref{40}). Dashed lines for $\bar{p}$,
 solid lines for ion charges $+1$, $+2$, $+4$, $+6$ and $+8$,
@@
 experimental findings~\cite{surdutovic2018}. As can be noted in the 
-figure, the mean energy value is surprisingly sensible to the 
+figure, the mean energy value is surprisingly sensitive to the 
 projectile charge $Z$, which can duplicate the proton results in the 
-intermediate region, i.e. 100--400 keV/amu. The effect observed can be 
+intermediate region, i.e., 100--400 keV/amu. The effect observed can be 
 attributed to the depletion caused by the multicharged ions to the 
@@
 As mentioned before, secondary electrons contribute to the total damage. 
-Then, not only is the ejection energy important but also the angle 
+Then, not only the ejection energy is essential but also the angle 
 of emission. Once again, we can consider the single differential cross 
@@
 %\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig6.eps}
-\includegraphics[width=0.9\textwidth]{figuras/ang_mean.eps}
+\includegraphics[width=0.8\textwidth]{figuras/ang_mean.eps}
 \caption{Mean emitted angle distribution for ionization by impact of
@@
 The mean emitted electron angles $\overline{\theta}_{\alpha}$ for the 
-six atoms of interest are shown in Fig.~\ref{fig:emittedang}, and an 
-important dependence of $\overline{\theta}_{\alpha}$ with $Z$ is 
-observed. Once again, this effect is not observed in the first Born 
-approximation. It is a general belief~\cite{Rudd1992} that the 
-angular dispersion of emitted electrons are nearly isotropic. This 
+six atoms and six ions of interest are shown in Fig.~\ref{fig:emittedang}.
+An significant dependence of $\overline{\theta}_{\alpha}$ with $Z$ is 
+noticed for all the cases. Once again, this effect could not be 
+observed in the first Born approximation (dotted line).
+
+It is a general belief~\cite{Rudd1992} that the 
+angular dispersion of emitted electrons is nearly isotropic. This 
 behavior is caused by the insignificant angular anisotropy of 
@@
 it is quite correct in the range of validity of the first Born 
-approximation for any target. But, when a distorted wave approximation 
+approximation for any target. However, when a distorted wave approximation 
 is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
-in the intermediate energy region, as observed in Fig.~\ref{fig:emittedang}. 
-For example, for C$^{+6}$ impact, the Bragg peak occurs at 0.3 MeV/amu, 
-where $\overline{\theta}_{\alpha}$, computed with the CDW method, is 
-about half of the value obtained with the first Born approximation. 
-This correction closes the damage to the forward direction.
+in the intermediate energy region. This effect is evident in 
+Fig.~\ref{fig:emittedang};
+for example, at 0.3 MeV/amu --where the Bragg peak for C$^{+6}$ impact 
+occurs-- the CDW $\overline{\theta}_{\alpha}$ is half of the first Born 
+value. This correction closes the damage to the forward direction.
+We can attribute this forward direction correction to the capture to 
+the continuum effect; the higher the charge $Z$, the smaller 
+$\overline{\theta}$ will be. Of course, this effect only holds at 
+intermediate energies and not at high impact energies.
 
-We can attribute this forward direction correction to the capture to 
-the continuum effect; the larger the charge $Z$, the smaller 
-$\overline{\theta}$ will be. Of course, this effect only holds at 
-intermediate energies and not at high impact energies, where the Born 
-approximation rules. One illustrative observation is the behavior of 
-antiprotons: the projectile in this case repels the electrons, being
-$\overline{\theta}_{\alpha}\sim 90\degree$.
-Note the opposite effect of proton and antiprotons; they run one 
-opposite to the other, as compared with the first Born approximation,
-constituting an angular Barkas effect.
+Furthermore, Fig.~\ref{fig:emittedang} provides an illustrative 
+description of the behavior of antiprotons: the projectile repels the 
+electrons, being $\overline{\theta}_{\alpha}\sim 90\degree$. Note the 
+opposite effect of proton and antiprotons respect to the first Born 
+approximation; this phenomenon constitutes an angular Barkas effect.
 
@@
 \section{Ionization of Molecules}
+\label{sec:molecules}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{The stoichiometric model}
+\label{subsec:stoichiometric}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We classified the molecular targets of our interest in three families: 
-CH, CHN and DNA, as in Table~\ref{tab:families}.
+CH, CHN, and DNA, as in Table~\ref{tab:families}.
 
@@
 sections by the impact of multicharged ions for adenine, cytosine, 
-guanine and thymine. For adenine, the agreement with the experimental 
-data available~\cite{iriki2011} is very good. To the best of our 
-knowledge, there are not experimental data on ion--collision ionization 
-for the rest of the molecules. We included electron impact 
-measurements~\cite{rahman2016} with the corresponding equivelocity 
-conversion for incident energies higher than 300~eV. In this region, 
-the proton and electron cross section should converge. Although the 
-electron impact measurements are above our findings for all the 
-molecular targets, it is worth stating that our results agree very well 
-with other electron impact theoretical 
+guanine, and thymine, by combining the SSM and CDW results in 
+Eq.~\ref{eq:sumion}. For adenine, the agreement with the experimental 
+data available for proton impact~\cite{iriki2011} is excellent. To the 
+best of our knowledge, there are no experimental data on ion--collision 
+ionization for the rest of the molecules. We have also included in this 
+figure electron impact measurements~\cite{rahman2016} with the 
+corresponding equivelocity conversion for electron incident energies 
+higher than 300~eV. In this region, the proton and electron cross 
+section should converge. Although the electron impact measurements are 
+above our findings for all the molecular targets, it is worth stating 
+that our results agree very well with other electron impact theoretical 
 predictions~\cite{mozejko2003,tan2018}.
@@
 %\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
-\includegraphics[width=0.9\textwidth]{figuras/adn1.eps}
-\caption{Reduced CDW ionization cross section by impact of multicharged 
-ions. Experiments: \mbox{\Large$\circ$}~\cite{iriki2011} for proton 
-impact and $\square$~\cite{rahman2016} for electron impact with 
-equivelocity conversion.}
+\includegraphics[width=0.8\textwidth]{figuras/adn1.eps}
+\caption{Reduced CDW ionization cross section by the impact of 
+multicharged ions. Experiments: \mbox{\Large$\circ$}~\cite{iriki2011} 
+for proton impact and $\square$~\cite{rahman2016} for electron impact 
+with equivelocity conversion.}
 \label{fig:crossDNA_1}
@@
 
-Our results for uracil, DNA backbone, pyrimidine and THF are displayed 
+Our results for uracil, DNA backbone, pyrimidine, and THF are displayed 
 in Fig.~\ref{fig:crossDNA_2}. For uracil, the agreement with the 
@@
 Itoh~{\it et al.}~\cite{itoh2013} is good.
-However, for the same target, our theory fails by a factor of two for 
-the experimental ionization values by the impact of 
-C$^{+4}$, O$^{+6}$ and O$^{+8}$ ions~\cite{agnihotri2012,agnihotri2013}.
+However, for the same target, our theory is a factor of two above 
+the experimental ionization measurements by Tribedi and 
+collaborators~\cite{agnihotri2012,agnihotri2013} by the impact of 
+multicharged ions.
 Nonetheless, it should be stated that our theoretical results coincide 
-with calculations by Champion, Rivarola and 
+with calculations by Champion, Rivarola, and 
 collaborators~\cite{agnihotri2012,champion2012}, which may indicate a 
 possible misstep of the experiments.
-For pyrimidine, we show comparison of our results with experimental data
-for proton~\cite{wolff2014} and electron~\cite{bug2017} ionization. 
+
+For pyrimidine, we show a comparison of our results with experimental 
+data for proton impact by Wolff~\cite{wolff2014} and also for electron
+impact ionization~\cite{bug2017} at high energies. 
 The electron impact measurements 
@@
 than our findings. 
-The THF molecule results are compared with proton~\cite{wang2016} 
-and electron~\cite{bug2017,wolf2019,fuss2009} impact measurements, showing
-overall good agreement with our theory.
+Much more experiments are available for ionization of THF molecule by 
+proton~\cite{wang2016} and by electron~\cite{bug2017,wolf2019,fuss2009} 
+impact. Our SSM with CDW results show overall good agreement with these
+data.
 
@@
 %\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig3.eps}
-\includegraphics[width=0.9\textwidth]{figuras/adn2.eps}
-\caption{Reduced CDW ionization cross section by impact of multicharged 
-ions. Experiments: proton impact on $\triangle$ uracil~\cite{itoh2013}, 
+\includegraphics[width=0.8\textwidth]{figuras/adn2.eps}
+\caption{Reduced CDW ionization cross section by the impact of 
+multicharged ions. Experiments: proton impact on 
+$\triangle$ uracil~\cite{itoh2013}, 
 $\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scaling rule}
+\subsection{Scaling rules}
 \label{subsec:scaling}
@@
 cross section in terms of the number of weakly--bound electrons, $n_e$.
-For instance, for C, N, O, P and S, this number is the total number of 
+For instance, for C, N, O, P, and S, this number is the total number of 
 electrons minus the K--shell. Following Toburen, the scaled ionization 
@@
 molecule, which depends solely on the impact velocity, and holds for 
-high impact energies (i.e. 0.25--5 MeV/amu).
+high impact energies (i.e., 0.25--5 MeV/amu).
 These $\nu_{\alpha}^T$ can be interpreted as the number of active 
-electrons in the collision. Of course, at very high energies also de 
-K--shell electrons will be ionized and these numbers will be different.
+electrons in the collision. At very high energies, the K--shell 
+electrons will also be ionized, and these numbers will be different.
 A similar dependence with the number of weakly bound electrons was 
@@
 %\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig4.eps}
-\includegraphics[width=0.9\textwidth]{figuras/molscaling85.eps}
+\includegraphics[width=0.8\textwidth]{figuras/molscaling85.eps}
 \caption{Scaled ionization cross section per weakly bound electron using
@@
 
-By implementing the SSM, we computed the scaled CDW cross sections 
+Following the Toburen scaling, we computed the scaled CDW cross sections 
 $\sigma_{e}^T$ for the molecular targets of Table~\ref{tab:families}.
@@
 satisfactory: the universal band is quite broad, as can be noted in 
-Fig.~\ref{fig:newscaling}a.
+this figure.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{New scaling}
+\subsubsection{CDW--based scaling}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 by inspecting Fig.~\ref{fig:atomscaling}. It can be noted that the 
-rule $\sigma_{\alpha}/\nu_{\alpha}^T\sim \sigma_{e}^T$, approximatelly 
+rule $\sigma_{\alpha}/\nu_{\alpha}^T\sim \sigma_{e}^T$, approximately 
 constant, is not well satisfied by the CDW. 
 For example, Fig.~\ref{fig:atomscaling} shows that the cross sections
-for O are actually very similar to the cross sections for C, suggesting 
+for O are very similar to the cross sections for C, suggesting 
 4 active electrons in O instead of 6. In the same way, the number of
-active electrons for N, P and S are also different from the 
-$\nu_{\alpha}^T$ of Eq.~(\ref{eq:nelec}).
+active electrons for N, P, and S obtained with the CDW are also 
+different from the $\nu_{\alpha}^T$ of Eq.~(\ref{eq:nelec}).
 
@@
 per atom obtained from the CDW ionization cross sections for 
-different ions in H, C, N, O, P , and S targets, given as follows,
+different ions in H, C, N, O, P, and S targets, given as follows,
 \begin{equation}
@@
 $E=(0.5-8)$~MeV/amu for $Z=1$ and $Z=2$, and $E=(2.5-8)$~MeV/amu for 
-$Z>2$. In fact, the experimental data for ionization of 
+$Z>2$. The experimental data for ionization of 
 adenine~\cite{iriki2011}, uracil~\cite{itoh2013}, 
-pyrimidine~\cite{wolff2014} and THF~\cite{wang2016} by proton impact in
+pyrimidine~\cite{wolff2014}, and THF~\cite{wang2016} by proton impact in
 Fig.~\ref{fig:newscaling}b seems to corroborate the new scaling. 
 We also included the electron impact ionization measurements with 
-equivelocity conversion on pyrimidine~\cite{bug2017}, and 
+equivelocity conversion on pyrimidine~\cite{bug2017} and 
 THF~\cite{bug2017,wolf2019,fuss2009}. 
-It will be interesting to cross--check for experiments with higher 
-projectile charge states.
+It will be interesting to cross--check with future experiments, mainly 
+for higher projectile charge states.
 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig_recta.eps}
-\caption{Ionization cross sections by impact of protons at 0.5, 1 and 2 MeV
-in terms of the number of active electrons given by Table~\ref{nn}.
+%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig_recta.eps}
+\includegraphics[width=0.8\textwidth]{figuras/scale_ne.eps}
+\caption{Ionization cross sections by the impact of protons at 0.5, 1,
+and 2 MeV in terms of the number of active electrons given by Table~\ref{nn}.
 Experiments: 
@@
 $\bigtriangledown$ pyrimidine~\cite{wolff2014}, 
-$\blacktriangle$ C2H$_7$N, CH$_5$N, methane and amonia~\cite{lynch1976},
-\mbox{\scriptsize$\bigstar$} amonia and H$_2$~\cite{rudd1985}, and 
+$\blacktriangle$ C2H$_7$N, CH$_5$N, methane and ammonia~\cite{lynch1976},
+\mbox{\scriptsize$\bigstar$} ammonia and H$_2$~\cite{rudd1985}, and 
 \mbox{\Large$\bullet$} water~\cite{luna2007}.}
@@
 By using Eq.~(\ref{eq:scalingCDW}), we define new active electron 
-numbers $n_e'$ for some molecular of interest in Table~\ref{nn}. 
-These values are very different from the ones proposed by Toburen and 
-used by other authors~\cite{itoh2013}.
-Moreover, an alternative way of showing the scaling can be attained by 
-plotting the ionization cross sections of molecules as a function of the 
-number of active electrons from Table~\ref{nn}. Our findings are displayed 
-in Fig.~\ref{fig:recta} for impact energies 0.5, 1 and 2 MeV. As can be 
-noted, the computed CDW ionization cross sections for all the molecules  
-show a linear dependence with the number of electrons from Table~\ref{nn}. 
-We obtain similar results even for $E=10$~MeV. The comparison with the 
-experimental data available shows very nice agreement, from the smallest 
-molecules, H$_2$, H$_2$O and CH$_4$, up to the most complex ones, like 
-adenine. For electron impact data, the experimental data was interpolated
-between close neighboors.
+numbers $n_e'$ for some molecules of interest in Table~\ref{nn}. These 
+values are very different from the ones proposed by Toburen and used by 
+other authors~\cite{itoh2013}. Moreover, an alternative way of showing 
+the scaling can be attained by plotting the ionization cross sections 
+of molecules as a function of the number of active electrons from 
+Table~\ref{nn}. Our findings are displayed in Fig.~\ref{fig:recta} for 
+impact energies 0.5, 1, and 2 MeV. As can be noted, the computed CDW 
+ionization cross sections for all the molecules show a linear 
+dependence with the number of electrons from Table~\ref{nn}. We obtain 
+similar results even for $E=10$~MeV. The comparison with the 
+experimental data available shows overall good agreement, for the 
+smallest molecules, H$_2$, H$_2$O, and CH$_4$, up to the most complex 
+ones, like adenine. For electron impact data, the experimental data was 
+interpolated between close neighboors.
+
+While finishing the present work, we noted an accepted manuscript by 
+Luedde~{\it et al.} \cite{luedde2019} on total ionization of biological
+molecules by proton impact, using an independent--atom--model pixel counting
+method. The authors also raised a scaling with $\nu_{\alpha}=4$ 
+for C, N, and O, but $\nu_{\alpha}=6$ for P. The agreement with this 
+independent method for proton impact reinforces our multicharged--ion findings.
 
@@
 \subsection{Molecular structure of targets}
+\label{subsec:molcalculations}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The molecular binding energies of the valence electrons for adenine, 
-cytosine, guanine, thymine and uracil are shown in Fig.~\ref{fig:bindener}. 
-We can compute the center of gravity of the molecular energy levels as 
+cytosine, guanine, thymine, and uracil are shown in Fig.~\ref{fig:bindener}. 
+We can compute the center of gravity of these molecular energy levels as 
 an average weighted by the electronic occupation number. The results 
 obtained from the full molecular calculation are given in the first row
-of Table~\ref{tab:gravener}. Similarly, we can compute the baricenter
-of the energy levels defined by the Toburen rule and the one given by
-Eq.~(\ref{eq:scalingCDW}), which are also given in 
-Table~\ref{tab:gravener}. The average energy values obtained from the
-Toburen rule are around 20\% of the full molecular ones. Surprisingly, 
-the new scaling rule gives a significant 
+of Table~\ref{tab:gravener}. Similarly, we can compute the barycenter
+of the energy levels defined by the Toburen and the CDW--based rules, 
+which are also given in Table~\ref{tab:gravener}. The average energy 
+values obtained from the Toburen rule are around 20\% of the full 
+molecular ones. Surprisingly, the new scaling rule gives a significant 
 improvement in the average energy values, reducing the relative errors
-to about~7\%. This improvement would seem to indicate that the new 
-scaling is appropiate.
+to about~7\%. This improvement would indicate that the new 
+scaling is appropriate.
 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{figuras/levelsDNA.eps}
+\includegraphics[width=0.8\textwidth]{figuras/levelsDNA.eps}
 \caption{Theoretical molecular binding energies for adenine, cytosine, 
-guanine, thymine and uracil compared to those of atomic constituents.}
+guanine, thymine, and uracil compared to those of atomic constituents.}
 \label{fig:bindener}
@@
 
-Furthermore, on the left side of the Fig.~\ref{fig:bindener}, we show 
+Furthermore, on the left side of Fig.~\ref{fig:bindener}, we show 
 the atomic Hartree--Fock energies of the constituent elements, which 
-gives an insight on the distribution of the weakly bound electrons. 
+gives an insight into the distribution of the weakly bound electrons. 
 A dashed line around $-11$~eV is drawn to separate the band in two. 
@@
 Eq.~(\ref{eq:scalingCDW}). In the case of O, only the 4 electrons of 
-the $2p$ orbitals are located above the separating line.
+the $2p$ orbitals are located above the separating line, which 
+corresponds to the number of weakly bound electron given by 
+our new scaling. 
+The N case is not as straightforward; the $\nu_{N=4}^{\text{CDW}}$ 
+would suggest the $2s$ electrons partially contribute to the molecular 
+scheme.
 
-The electrons in the molecular 
-targets corresponding to the $2s$ of N and C in the atomic case are 
-placed in a secondary gap. The lower levels of the secondary gap 
-correspond to the oxygen. The number of electrons in the valence 
-shell for all O would seem to be equal to 4, as previously setted by the 
-scaling rule Eq.~(\ref{eq:scalingCDW}). The N case is not as 
-straightfoward; the electrons that would correspond to the $2s$ are 
-located just below the line. The $\nu_{\alpha }^{\text{CDW}}$ value 
-given for N would suggest that a significant amount of electron density 
-from the secondary gap is shared with the valence band.
+\subsubsection{A modified stoichiometric model}
 
@@
 by assuming that the atoms are not neutral and that they have an uneven
-distribution of electrons within the molecule; this distribution can be
-given by an effective charge $q_{\alpha}$. A possible value for 
-$q_{\alpha}$ is given by the Mulliken charge. However, there are a wide
-variety of charge distributions, such as the net or natural atomic
-charge~\cite{lee2003}, the L\"owdin charge, etc.
+distribution of electrons within the molecule, which can be expressed as 
+an effective charge $q_{\alpha}$ per atom. The Mulliken charge gives a 
+possible value for $q_{\alpha}$; however, there are a wide variety of 
+charge distributions~\cite{lee2003}.
 
-Consider that the total amount of electrons $Q_{\alpha }$ on the element
-$\alpha$ are equally distributed on all the $\alpha$ atoms. Therefore, 
-each element $\alpha$ will have an additional charge: 
+To take this effect into account, we can consider that the total amount 
+of electrons $Q_{\alpha }$ on the element
+$\alpha$ is equally distributed on all the $\alpha$ atoms. Therefore, 
+each element $\alpha$ will have an additional charge, 
 $q_{\alpha}=Q_{\alpha}/n_{\alpha}$, which can be positive or negative.
-This value will depend on the relative electronegativity value with 
-respect to the other atoms~\cite{rappe1991}. Now, instead of an
-integer number of elements $n_{\alpha}$ of the atom $\alpha$, we have a 
-fractional number of atoms given by 
+This amount will depend on the relative electronegativity respect to 
+the other atoms~\cite{rappe1991}. 
+Following this idea, we can define a new number of atoms per molecule
+$n_{\alpha }^{\prime }$, given by
 \begin{equation}
@@
 \end{equation}%
-In the case of neutral atoms, $q_{\alpha}=0$ and we recover 
+In the case of neutral atoms, $q_{\alpha}=0$ and 
 $n_{\alpha}^{\prime}=n_{\alpha}$, as it should be. 
-
-In Table~\ref{tab:newstoi}, we display the charge $q_{\alpha}$ of four 
-DNA molecules, obtained from the full molecular calculation.
+In Table~\ref{tab:newstoi}, we display the average effective charge 
+per atom $q_{\alpha}$ of C, H, N, and O, for five DNA molecules,
+obtained from the full molecular calculation described 
+above.
 
@@
 
-We calculated ionization cross sections by impact of antiprotons, 
-H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$ for seventeen 
-molecules containing H, C, N, O, P and S with the CDW method. The 
-importance of the influence of $Z$ was observed in the mean energy 
-$\overline{E}_{\alpha}$ and angle $\overline{\theta}_{\alpha}$. 
-For a given target $\alpha$, as the nuclear charge of the projectile 
-$Z$ increases, so does the mean energy of emittion $\overline{E}_{\alpha}$. 
-Conversely, the mean angle of emission  $\overline{\theta}_{\alpha}$ 
-decreases. At high impact energy, say larger than 1 MeV/amu, these 
-values converge to the Born approximation, which embodies the simple 
-$Z^{2}$ law. The seventeen molecules selected were investigated using 
-the simple stoichiometric model. Results for eigth DNA bases were 
-presented and compared with the sparse available experiments. We explore 
-the rule of Toburen which scales all the molecular ionization cross 
-section when divided by the number of weakly bound valence electrons 
-$\nu_{\alpha}^T$ given by Eq.~(\ref{27}). 
-We found the rule scales much better when normalizing our theoretical 
-ionization cross sections to the number $\nu_{\alpha}^{\text{CDW}}$ 
-given by Eq.~(\ref{eq:scalingCDW}). Finally, we attempt to improve the 
-stoichiometric model by using the Mulliken charge to define a new model 
-containing fractional rather than integer proportions. No substantial 
-correction was found, which indicates that our modified SSM works quite 
-well. By inspecting the molecular binding energy from quantum mechanical 
-structure calculations, we were able to understand the values defined
-for $\nu_{\alpha}^{\text{CDW}}$.
+In this work, we have encouraged the calculation of ionization cross 
+sections of seventeen biological molecules containing H, C, N, O, P, and 
+S by the impact of antiprotons, H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, 
+and O$^{8+}$. To that end, we have employed the full CDW method and the 
+simple stoichiometric model. 
+The mean energy and angle of the emitted electrons, of importance in 
+post--collisional radiation damage,  has also been calculated, showing 
+a clear dependence with the ion charge $Z$. For a given target as $Z$ 
+increases, $\overline{E}_{\alpha}$
+increases, but $\overline{\theta}_{\alpha}$ decreases, showing a clear 
+tendency to the forward direction. At impact
+energies greater than 2 MeV/amu, these values converge to the Born
+approximation, which embodies the simple $Z^{2}$ law.
 
-The main objective of this article is to provide the tools to estimate 
-any inelastic parameter parameter --such as emission angle, emitted mean 
-energy and cross section-- by the impact of any multicharged on any 
-molecule containing H, C, N, O, P and S, with the help of the 
-stoichimetrical model. Our goal was quite ambitious, considering the 
-simplicity of our proposal. However, we think our results could be used 
-to estimate the ionization magnitude with an acceptable level of 
-uncertainty.
+Total ionization cross sections for adenine, cytosine, thymine, guanine, 
+uracil, DNA backbone, pyrimidine, and THF are presented and compared 
+with the scarcely available experiments. We explore the rule of 
+Toburen, which scales all the molecular ionization cross section 
+normalizing with a certain number of weakly bound or valence electrons. 
+We found that the ionization cross 
+sections scales much better when normalizing with the number of active 
+electrons in the collision obtained from the CDW results for atoms. 
+This new scaling was tested with good results for the six 
+projectiles and seventeen molecules studied here. The comparison with 
+the experimental data reinforce these results. Furthermore, we also tested
+the scaling by including experimental data of ionization of H$_2$, 
+water, methane, and ammonia by proton impact showing good agreement at
+intermediate to high energies.
+
+Finally, we performed full molecular calculations for the DNA basis. 
+By inspecting the molecular binding energy from quantum mechanical
+structure calculations, we were able to understand the number of 
+electrons proposed in our new CDW-based scaling. We attempt to improve 
+the stoichiometric model by using the Mulliken charge to get fractional
+rather than integer proportions. We found no substantial correction,
+which indicates that the SSM works quite well.
+
+In conclusion, the present results reinforce the 
+reliability of the SSM to deal with complex molecules in the intermediate
+to high energy range. Moreover, the simple stoichiometric model and the 
+CDW cross sections in Ref.~\cite{miraglia2019} opens the possibility to 
+describe a wide range of molecules containing H, C, N, O, P, and S, by 
+the impact of multicharged ions.
+
+% The main objective of this article was to provide the tools to estimate 
+% any inelastic parameter parameter --such as emission angle, emitted mean
+% energy and cross section-- by the impact of any multicharged projectiles 
+% on any molecule containing H, C, N, O, P and S, with the help of the
+% stoichimetrical model. Our goal was quite ambitious, considering the
+% simplicity of our proposal. However, the present results show the 
+% validity of the simple stoichiometric model to estimate the ionization 
+% magnitude with an acceptable level of uncertainty.
 
@@
 
-\bibitem{gamess}
-M. W. Schmidt, K. K. Baldridge, J. A. Boatz, S. T. Elbert, M. S. Gordon, 
-J. H. Jensen, S. Koseki, N. Matsunaga, K. A. Nguyen, S. J. Su, T. L. Windus, 
-M. Dupuis, J. A. Montgomery 
-J. Comput. Chem. 14, 1347-1363 (1993)
+\bibitem{fainstein1988}
+Fainstein P.D., Ponce V. H. and Rivarola R. D. 
+J. Phys. B: At. Mol. Opt. Phys. \textbf{21} 287 (1988).
 
@@
 
+\bibitem{toburen1975} 
+W. E. Wilson and L. H. Toburen. Electron emission from
+proton --hydrocarbon-molecule collisions at 0.3--2.0 MeV. 
+Phys. Rev. A \textbf{11}, 1303 (1975).
+
+\bibitem{toburen1976} 
+D. J. Lynch, L. H. Toburen, and W. E. Wilson. Electron
+emission from methane, ammonia, monomethylamine, and dimethylamine by 0.25
+to 2.0 MeV protons. 
+J. Chem. Phys. \textbf{64}, 2616 (1976).
+
+\bibitem{gamess}
+M. W. Schmidt, K. K. Baldridge, J. A. Boatz, S. T. Elbert, M. S. Gordon, 
+J. H. Jensen, S. Koseki, N. Matsunaga, K. A. Nguyen, S. J. Su, T. L. Windus, 
+M. Dupuis, J. A. Montgomery 
+J. Comput. Chem. \textbf{14}, 1347-1363 (1993)
+
 \bibitem{salvat1995}
-Salvat, F., Fernández-Varea, J.M., Williamson, W.
+Salvat, F., Fern\'andez-Varea, J.M., Williamson, W.
 Comput. Phys. Commun. \textbf{90}, 151--168 (1995)
@@
 Depurated inversion method for orbital-specific exchange potentials. 
-Int. J. Quantum Chem. 24 ,116 (2016).
+Int. J. Quantum Chem. \textbf{24} ,116 (2016).
 
 \bibitem{mendez2018} 
-A.M.P. Mendez, D.M. Mitnik, and J.E. Miraglia. Local Effective 
-Hartree--Fock Potentials Obtained by the Depurated Inversion Method,
-76. (2018).
+A.M.P. Mendez, D.M. Mitnik, and J.E. Miraglia. 
+Local Effective Hartree--Fock Potentials Obtained by the Depurated 
+Inversion Method,
+Adv. Quant. Chem. \textbf{76}, 117--132 (2018).
 
 \bibitem{montanari2017} 
+C. C. Montanari, J. E. Miraglia,
 Ionization probabilities of Ne, Ar, Kr, and Xe by
@@
 sections of antiprotons, H$^{+}$, He$^{+2},$ Be$^{+4},$ C$^{+6}$ and 
-O$^{+8}$ on H, C, N, O, P, and S atoms To be published Archive 2019.
+O$^{+8}$ on H, C, N, O, P, and S atoms (to be published).
+
+\bibitem{surdutovic2018} 
+Multiscale approach to the physics of radiation
+damage with ions. E. Surdutovich and A. V. Solov'yov, 
+arXiv:1312.0897v, (2013)
+
+\bibitem{abril2015} 
+P. de Vera1, I. Abril, R. Garcia-Molina and
+A.V.Solov'yov,\ Ionization of biomolecular targets by ion impact: input data
+for radiobiological applications. 
+Journal of Physics: Conference Series 438
+(2013) 012015
+
+\bibitem{Rudd1992} 
+M. E. Rudd, Y.-K. Kim,, D. H. Madison and T. J. Gay.
+Electron production in proton collisions with atoms and molecules: energy
+distributions. 
+Rev. Mod. Phys. \textbf{64}, 44-490 (1992).
 
@@
 M. Fuss, A. Muñoz, J. C. Oller, F. Blanco, D. Almeida, P. Limão-Vieira, 
-T. P. D. Do, M. J. Brunger, G. García,
+T. P. D. Do, M. J. Brunger, G. Garc\'{i}a,
 Electron-scattering cross sections for collisions with tetrahydrofuran 

### 2019-09-28 arxiv/stoi_ionization.tex
figs and text modified with 27/09 corrections

--- 2019-09-26 NewMonti25.tex
@@
 %\documentclass[pra,showpacs,twocolumn]{revtex4}
-\documentclass[preprint,showpacs]{revtex4}
+%\documentclass[pra,showpacs]{revtex4}
+%\documentclass[preprint,showpacs]{revtex4}
+\documentclass[10pt,showpacs,twocolumn]{revtex4}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\title{Ionization of biological molecules by multicharged ions by using 
+\title[Ionization of biological molecules by multicharged 
+ions]{Ionization of biological molecules by multicharged ions using 
 the stoichiometric model}
-
 \author{A. M. P. Mendez, C. C. Montanari, J. E. Miraglia}
-%\author{author}
-%\author{author}
 \address{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio 
@@
 
-\date{\today}% It is always \today, today,
-\pacs{34.50Gb, 34.80Gs, 34.80Dp}
+%\date{\today}% It is always \today, today,
 
@@
 intermediate to high energy range. We performed full non--perturbative
-distorted--wave calculations (CDW) for thirty--six collisional systems. 
-Six atomic targets compose these systems: H, C, N, O, F and S --which 
-are the constituents of most of the DNA and biological molecules-- and 
+distorted--wave calculations (CDW) for thirty--six collisional systems
+composed by six atomic targets: H, C, N, O, F and S --which
+are the constituents of most of the DNA and biological molecules--, and
 six charged projectiles (antiprotons, H, He, B, C, and O). On account
-of the radiation damage caused by secondary electrons, we also inspect 
-the energy and angular distributions of the emitted electrons from the 
-atomic targets. We examine seventeen molecules: DNA and RNA bases, 
+of the radiation damage caused by secondary electrons, we inspect
+the energy and angular distributions of the emitted electrons.
+We examine seventeen molecules: DNA and RNA bases,
 DNA backbone, pyrimidines, tetrahydrofuran (THF), and several
@@
 linear combination of the atomic ones, gives reasonably good results
-for complex molecules. We also inspect the extensively used Toburen 
+for complex molecules. We inspect the extensively used Toburen
 scaling of the total ionization cross sections of molecules with the
 number of weakly bound electrons. Based on the present atomic CDW
-results, we propose new active electron numbers. The CDW--based scaling 
-improves significantly the single curve behavior for all the targets 
-and ions studied here, from the intermediate to the high energy region. 
-Furthermore, the new scaling describes well the available experimental 
+results, we propose new active electron numbers, which
+improves significantly scaling for all the targets
+and ions studied here.
+The new scaling describes well the available experimental
 data for proton impact, including small molecules such as H$_2$, water,
-methane, and ammonia. For completeness, we perform full molecular 
+methane, and ammonia.
+We perform full molecular
 calculations for five nucleobases and test a modified stoichiometric
@@
 difference introduced by the new stoichiometric formula is less than
-$3\%$, which indicates the reliability and robustness of the SSM to 
+$3\%$, which indicates the reliability of the SSM to
 deal with this type of molecules. The results of the extensive
@@
 
-%\keywords{Suggested keywords}
+%\keywords{magnetic moment, solar neutrinos, astrophysics}
+\pacs{34.50Gb, 34.80Gs, 34.80Dp}
 
 \maketitle
-
-%\tableofcontents
-%\pacs{79.20.Rf, 68.49.Bc, 34.20.Cf,34.50.-s,34.35.+a}
+%\ioptwocol
 
@@
 tetrahydrofuran~(THF), pyrimidine, and DNA backbone, by the impact 
-of antiprotons, H$^{+}$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
+of antiprotons, H$^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$, and O$^{8+}$. 
 In Section~\ref{subsec:scaling}, we
@@
 In the present study, we consider six atoms, $\alpha=$ H, C, N, O, P, 
-and S, and six projectiles, antiprotons $\bar{p}$, H$^{+}$, He$^{+2}$, 
-Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
+and S, and six projectiles, antiprotons $\bar{p}$, H$^{+}$, He$^{2+}$, 
+Be$^{4+}$, C$^{6+}$, and O$^{8+}$. 
 Most of the organic molecules are composed of these atoms. Some 
@@
 \centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig1.eps}
-\includegraphics[width=0.8\textwidth]{figuras/atomicscaling.eps}
+\includegraphics[width=0.8\textwidth]{atomicscaling.eps}
 \caption{Reduced CDW total ionization cross section of six atomic 
@@
 all the figures of this work: dashed--red, solid--red, blue, magenta, 
-olive and orange for antiprotons, H$^{+}$, He$^{+2}$, Be$^{+4}$, 
-C$^{+6}$, and O$^{+8}$, respectively. Notably, there is no complete 
+olive and orange for antiprotons, H$^{+}$, He$^{2+}$, Be$^{4+}$, 
+C$^{6+}$, and O$^{8+}$, respectively. Notably, there is no complete 
 tabulation of ionization of atoms by the impact of multicharged ions. 
@@
 \centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig5.eps}
-\includegraphics[width=0.8\textwidth]{figuras/ener_mean.eps}
+\includegraphics[width=0.8\textwidth]{ener_mean.eps}
 \caption{Mean emitted energy distribution for ionization by the impact 
 of multicharged ions, given by Eq.~(\ref{40}). Dashed lines for $\bar{p}$,
-solid lines for ion charges $+1$, $+2$, $+4$, $+6$ and $+8$,
+solid lines for ion charges $+1$, $2+$, $4+$, $6+$ and $8+$,
 as indicated.}
@@
 In Fig.~\ref{fig:emittedener}, we estimate $\overline{E}_{\alpha}$ of
-the emitted electron in the 0.5--2.7 a.u. energy range, or equivalently 
-from 15 to 70 eV, for all the targets. Our results agree with the 
+the emitted electron in the 10--70 eV energy range,
+for all the targets. Our results agree with the 
 experimental findings~\cite{surdutovic2018}. As can be noted in the 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=0.8\textwidth]{ang_mean.eps}
+\caption{Mean emitted angle distribution for ionization by impact of
+multicharged ions.}
+\label{fig:emittedang}
+\end{figure*}
 
@@
 
-\begin{figure*}[t!]
-\centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig6.eps}
-\includegraphics[width=0.8\textwidth]{figuras/ang_mean.eps}
-\caption{Mean emitted angle distribution for ionization by impact of
-multicharged ions.}
-\label{fig:emittedang}
-\end{figure*}
-
 The mean emitted electron angles $\overline{\theta}_{\alpha}$ for the 
@@
 angular dispersion of emitted electrons is nearly isotropic. This 
-behavior is caused by the insignificant angular anisotropy of 
-sub--50--eV yield. 
+behavior is thought to be caused by the insignificant angular anisotropy 
+of sub--50--eV yield. 
 A typical value for the ejection angle considered in the literature is 
@@
 Fig.~\ref{fig:emittedang};
-for example, at 0.3 MeV/amu --where the Bragg peak for C$^{+6}$ impact 
+for example, at 0.3 MeV/amu --where the Bragg peak for C$^{6+}$ impact 
 occurs-- the CDW $\overline{\theta}_{\alpha}$ is half of the first Born 
@@
 
-\begin{table}[H]
+\begin{table}[t]
 \begin{center}
-\begin{tabular}{|p{0.06\textwidth}|p{0.6\textwidth}|}
+\begin{tabular}{|p{0.042\textwidth}|p{0.39\textwidth}|}
 \hline
 \multirow{2}{*}{CH} 
-      & CH$_4$ (methane), C$_2$H$_2$ (acetylene), C$_2$H$_4$ (ethene), \\
-      & C$_2$H$_6$ (ethane), C$_6$H$_6$ (benzene) \\
+      & CH$_4$ (methane), C$_2$H$_2$ (acetylene),  \\
+      & C$_2$H$_4$ (ethene), C$_2$H$_6$ (ethane), \\
+      & C$_6$H$_6$ (benzene) \\
 \hline
@@
       & C$_5$H$_5$N (pyridine), C$_4$H$_4$N$_2$ (pyrimidine), \\ 
-      & C$_2$H$_7$N (dimenthylamine), CH$_5$N (monomethylamine) \\
+      & C$_2$H$_7$N (dimenthylamine), \\
+      & CH$_5$N (monomethylamine) \\
 \hline
@@
       & C$_4$H$_4$N$_2$O$_2$ (uracil), C$_4$H$_8$O (THF), \\
-      & C$_5$H$_{10}$O$_5$P (DNA backbone), 
-        C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$ 
+      & C$_5$H$_{10}$O$_5$P (DNA backbone), \\
+      & C$_{20}$H$_{27}$N$_7$O$_{13}$P$_2$ 
 (dry DNA) \\
@@
 
-\begin{figure*}[t!]
-\centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
-\includegraphics[width=0.8\textwidth]{figuras/adn1.eps}
-\caption{Reduced CDW ionization cross section by the impact of 
-multicharged ions. Experiments: \mbox{\Large$\circ$}~\cite{iriki2011} 
-for proton impact and $\square$~\cite{rahman2016} for electron impact 
-with equivelocity conversion.}
-\label{fig:crossDNA_1}
-\end{figure*}
-
 Our results for uracil, DNA backbone, pyrimidine, and THF are displayed 
@@
 \centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig3.eps}
-\includegraphics[width=0.8\textwidth]{figuras/adn2.eps}
+\includegraphics[width=0.8\textwidth]{adn1.eps}
+\caption{Reduced CDW ionization cross section by the impact of 
+multicharged ions. Experiments: \mbox{\Large$\circ$}~\cite{iriki2011} 
+for proton impact and $\square$~\cite{rahman2016} for electron impact 
+with equivelocity conversion.}
+\label{fig:crossDNA_1}
+\end{figure*}
+
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=0.8\textwidth]{adn2.eps}
 \caption{Reduced CDW ionization cross section by the impact of 
@@
 $\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$
-THF~\cite{wang2016}. Impact of $\ominus$ C$^{+4}$, 
-$\boxminus$ C$^{+6}$, O$^{+6}$, F$^{+6}$, and
-$\triangle\mkern-14mu-$ O$^{+8}$, F$^{+8}$ on 
+THF~\cite{wang2016}. Impact of $\ominus$ C$^{4+}$, 
+$\oplus$ C$^{6+}$, O$^{6+}$, F$^{6+}$, and
+$\otimes$ O$^{8+}$, F$^{8+}$ on 
 uracil~\cite{agnihotri2012,agnihotri2013}. 
@@
 \centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig4.eps}
-\includegraphics[width=0.8\textwidth]{figuras/molscaling85.eps}
+\includegraphics[width=0.8\textwidth]{molscaling85.eps}
 \caption{Scaled ionization cross section per weakly bound electron using
@@
 \begin{equation}
-\sigma_{e}=\frac{\sigma_M}{n_e'},
+\sigma_{e}'=\frac{\sigma_M}{n_e'},
 \label{32} 
@@
 
-The new scaled cross sections $\sigma_{e}$ are plotted in 
-Fig.~\ref{fig:newscaling}b. 
-A much better sharp band is observed, especially for impact energies 
-$E=(0.5-8)$~MeV/amu for $Z=1$ and $Z=2$, and $E=(2.5-8)$~MeV/amu for 
-$Z>2$. The experimental data for ionization of 
+The new scaled cross sections $\sigma_{e}'$ are plotted in 
+Fig.~\ref{fig:newscaling}b. The experimental data for ionization of 
 adenine~\cite{iriki2011}, uracil~\cite{itoh2013}, 
@@
 
-\begin{table}[H]
+\begin{table}[t]
 \begin{center}
-\begin{tabular}{|ll|ll|ll|}
-\hline
- Molecule & $n_e$ &Molecule          & $n_e$ & Molecule             & $n_e$\\
+\begin{tabular}{|p{0.07\textwidth}p{0.02\textwidth}|
+p{0.095\textwidth}p{0.02\textwidth}|p{0.095\textwidth}p{0.035\textwidth}|}
+\hline
+ Molecule & $n_e'$ &Molecule          & $n_e'$ & Molecule             & $n_e'$\\
 \hline
@@
 \centering
-%\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig_recta.eps}
-\includegraphics[width=0.8\textwidth]{figuras/scale_ne.eps}
+\includegraphics[width=0.785\textwidth]{scale_ne.eps}
 \caption{Ionization cross sections by the impact of protons at 0.5, 1,
@@
 numbers $n_e'$ for some molecules of interest in Table~\ref{nn}. These 
-values are very different from the ones proposed by Toburen and used by 
+values are different from the ones proposed by Toburen and used by 
 other authors~\cite{itoh2013}. Moreover, an alternative way of showing 
@@
 dependence with the number of electrons from Table~\ref{nn}. We obtain 
-similar results even for $E=10$~MeV. The comparison with the 
+similar results, even for $E=10$~MeV. The comparison with the 
 experimental data available shows overall good agreement, for the 
@@
 ones, like adenine. For electron impact data, the experimental data was 
-interpolated between close neighboors.
-
-While finishing the present work, we noted an accepted manuscript by 
-Luedde~{\it et al.} \cite{luedde2019} on total ionization of biological
+interpolated between close neighbors.
+
+While finishing the present work, we became aware of an accepted manuscript by 
+Luedde~{\it et al.}~\cite{luedde2019} on total ionization of biological
 molecules by proton impact, using an independent--atom--model pixel counting
@@
 
-To test the range of validity of the SSM, we performed a full molecular 
-structure calculation of five nucleobases. We employed the {\sc gamess} 
-code and used the 6-31G(d,p) basis set, which includes polarization 
-functions for all the atoms. The calculations were carried out 
-implementing the B3LYP functional~\cite{Becke1993,Stephens1994} to 
-account for the correlation and exchange effects.
-
-The molecular binding energies of the valence electrons for adenine, 
-cytosine, guanine, thymine, and uracil are shown in Fig.~\ref{fig:bindener}. 
-We can compute the center of gravity of these molecular energy levels as 
-an average weighted by the electronic occupation number. The results 
-obtained from the full molecular calculation are given in the first row
-of Table~\ref{tab:gravener}. Similarly, we can compute the barycenter
-of the energy levels defined by the Toburen and the CDW--based rules, 
-which are also given in Table~\ref{tab:gravener}. The average energy 
-values obtained from the Toburen rule are around 20\% of the full 
-molecular ones. Surprisingly, the new scaling rule gives a significant 
-improvement in the average energy values, reducing the relative errors
-to about~7\%. This improvement would indicate that the new 
-scaling is appropriate.
-
-\begin{figure*}[t!]
+To test the range of validity of the SSM, we performed {\it ab initio}
+molecular calculation of five nucleobases by employing the {\sc gamess} 
+code. The geometry optimization and single point energy calculations 
+were performed implementing the restricted Hartree--Fock method and the 
+3-21G basis set.
+
+\begin{figure*}[t]
 \centering
-\includegraphics[width=0.8\textwidth]{figuras/levelsDNA.eps}
+\includegraphics[width=0.8\textwidth]{levelsDNA.eps}
 \caption{Theoretical molecular binding energies for adenine, cytosine, 
@@
 
-\begin{table}[H]
-\begin{center}
-\begin{tabular}{|c|ccccc|}
-\hline
- \multirow{2}{*}{$E_{\text{av}}$ (eV)} & A & C & G & T & U \\
- & C$_5$H$_5$N$_5$ & C$_4$H$_5$N$_3$O & 
-   C$_5$H$_5$N$_5$O & C$_5$H$_6$N$_2$O$_2$ & C$_4$H$_4$N$_2$O$_2$ \\
-\hline
- Theoretical calc. & $-7.1955$ & $-6.9058$ & $-7.4725$ & $-7.5304$ & $-7.6224$ \\
- Toburen rule  & $-8.4236$ & $-8.6743$ & $-8.7275$ & $-8.7947$ & $-9.0022$ \\
- Present work & $-7.9027$ & $-7.8639$ & $-7.9420$ & $-7.8066$ & $-7.8839$ \\
-%                 17%         25%         17%         17%         18%         
-%                 10%         13%         6%          4%          3%
-\hline
-\end{tabular}
-\caption{Center of gravity of the molecular energy levels of five 
-nucleobases.}
-\label{tab:gravener}
-\end{center}
-\end{table}
-
-Furthermore, on the left side of Fig.~\ref{fig:bindener}, we show 
+The molecular binding energies of the valence electrons for adenine, 
+cytosine, guanine, thymine, and uracil are shown in Fig.~\ref{fig:bindener}. 
+The binding energy of the highest molecular orbital (HOMO) agrees with 
+the experimental values~\cite{Hush,Verkin,Dougherty} within 
+2\% for all the DNA bases considered.
+On the left side of Fig.~\ref{fig:bindener}, we show 
 the atomic Hartree--Fock energies of the constituent elements, which 
-gives an insight into the distribution of the weakly bound electrons. 
-A dashed line around $-11$~eV is drawn to separate the band in two. 
+gives an insight into the distribution of the weakly bound electrons
+in the molecules. A dashed line around $-26$~eV is drawn to separate 
+the molecular band in two. 
 We can consider the atomic energy levels above this line as the ones
@@
 the separating line, which corresponds to the 4 electrons given by 
-Eq.~(\ref{eq:scalingCDW}). In the case of O, only the 4 electrons of 
+CDW--scaling. In the case of O, only the 4 electrons of 
 the $2p$ orbitals are located above the separating line, which 
@@
 The N case is not as straightforward; the $\nu_{N=4}^{\text{CDW}}$ 
-would suggest the $2s$ electrons partially contribute to the molecular 
-scheme.
-
+would suggest that one out of the two $2s$ electrons contribute to the 
+molecular scheme.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{A modified stoichiometric model}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 the other atoms~\cite{rappe1991}. 
-Following this idea, we can define a new number of atoms per molecule
+Following this idea, we can estimate a new number of atoms per molecule
 $n_{\alpha }^{\prime }$, given by
@@
 
-\begin{table}[H]
+\begin{table*}[t]
 \begin{center}
-\begin{tabular}{|p{0.12\textwidth}|p{0.07\textwidth}|p{0.07\textwidth}|p{
-0.07\textwidth}|p{0.07\textwidth}|p{0.25\textwidth}|}
+\begin{tabular}{|p{0.08\textwidth}|p{0.05\textwidth}|p{0.05\textwidth}|p{
+0.05\textwidth}|p{0.05\textwidth}|p{0.19\textwidth}|}
 \hline
@@
 \end{center}
-\end{table}
+\end{table*}
 
@@
 
-In this work, we have encouraged the calculation of ionization cross 
+In this work, we have dealt with the calculation of ionization cross 
 sections of seventeen biological molecules containing H, C, N, O, P, and 
@@
 
-% The main objective of this article was to provide the tools to estimate 
-% any inelastic parameter parameter --such as emission angle, emitted mean
-% energy and cross section-- by the impact of any multicharged projectiles 
-% on any molecule containing H, C, N, O, P and S, with the help of the
-% stoichimetrical model. Our goal was quite ambitious, considering the
-% simplicity of our proposal. However, the present results show the 
-% validity of the simple stoichiometric model to estimate the ionization 
-% magnitude with an acceptable level of uncertainty.
-
 \bigskip
-
-\begin{thebibliography}{99}
+%\section*{References}
+
+\begin{thebibliography}{}
 
@@
 M. Dupuis, J. A. Montgomery 
-J. Comput. Chem. \textbf{14}, 1347-1363 (1993)
+J. Comput. Chem. \textbf{14}, 1347-1363 (1993).
 
@@
 proton impact for different initial states and impact energies. 
-Nucl. Instr. Meth. Phys. Res. B 407 (2017) 236-243.
+Nucl. Instr. Meth. Phys. Res. B \textbf{407}, 236--243 (2017).
 
@@
 J. E. Miraglia. Shell-to-shell ionization cross
-sections of antiprotons, H$^{+}$, He$^{+2},$ Be$^{+4},$ C$^{+6}$ and 
-O$^{+8}$ on H, C, N, O, P, and S atoms (to be published).
+sections of antiprotons, H$^{+}$, He$^{2+},$ Be$^{4+},$ C$^{6+}$ and 
+O$^{8+}$ on H, C, N, O, P, and S atoms (to be published).
 
@@
 for radiobiological applications. 
-Journal of Physics: Conference Series 438
-(2013) 012015
+Journal of Physics: Conference Series \textbf{438}, 012015 (2013).
 
@@
 distributions. 
-Rev. Mod. Phys. \textbf{64}, 44-490 (1992).
+Rev. Mod. Phys. \textbf{64}, 44--490 (1992).
 
@@
 Y. Iriki, Y. Kikuchi, M. Imai, and A. Itoh
-Phys. Rev. A \textbf{84} 052719 (2011).
+Phys. Rev. A \textbf{84}, 052719 (2011).
 
@@
 biomolecules, 
-Phys. Rev. E \text{97}, 032403 (2018)
+Phys. Rev. E \textbf{97}, 032403 (2018)
 
@@
 Phys. Rev. A \textbf{88}, 052711 (2013).
-
-%\bibitem{} in energy and angles~,
 
@@
 ions of energy 100 keV to 78 MeV. 
-Phys. Rev. A \text{85}, 032711 (2012).
+Phys. Rev. A \textbf{85}, 032711 (2012).
 
@@
 Monte Carlo simulations,
-Rad. Phys. Chem. \textbf{130} 459--479 (2017).
+Rad. Phys. Chem. \textbf{130}, 459--479 (2017).
 
@@
 Water-molecule dissociation by proton and hydrogen impact,
-Phys. Rev. A \textbf{75} 042711 (2007).
+Phys. Rev. A \textbf{75}, 042711 (2007).
 
 \bibitem{luedde2019}
-H J Luedde et al 2019 
-J. Phys. B: At. Mol. Opt. Phys. in press https://doi.org/10.1088/1361-6455/ab3a63
-
-\bibitem{Becke1993}
-A. D. Becke, 
-J. Chem. Phys. 98, 5648-5652 (1993)
-
-\bibitem{Stephens1994}
-P. J. Stephens, F. J. Devlin, C. F. Chabalowski, M. J. Frisch,
-J. Phys. Chem. 98, 11623-11627 (1994)
+H J Luedde {\it et al.} 2019 
+J. Phys. B: At. Mol. Opt. Phys. in press 
+https://doi.org/10.1088/1361-6455/ab3a63
+
+\bibitem{Hush}
+Hush, N.S.; Cheung, A.S., 
+Ionization potentials and donor properties of nucleic acid bases and 
+related compounds, 
+Chem. Phys. Lett., \textbf{34}, 11 (1975).
+
+\bibitem{Verkin}
+Verkin, B.I.; Sukodub, L.F.; Yanson, I.K., 
+Ionization potentials of nitrogenous bases of of nucleic acids, 
+Dokl. Akad. Nauk SSSR, \textbf{228}, 1452 (1976).
+
+\bibitem{Dougherty}
+Dougherty, D.; Younathan, E.S.; Voll, R.; Abdulnur, S.; McGlynn, S.P., 
+Photoelectron spectroscopy of some biological molecules, 
+J. Electron Spectrosc. Relat. Phenom., \textbf{13}, 379 (1978).
 
@@
 Large Molecules Using Reassociation of Fragments. 
-Bull. Korean Chem. Soc.24 2003, 369 .
+Bull. Korean Chem. Soc. \textbf{24}, 369 (2003).
 
@@
 A. K. Rappe, A. K.and W. A. Goddard III,. 
-J. Phys. Chem. \textbf{95 (}1991) 3358.
-
-%\bibitem{pimblott2007} 
-%S.M. Pimblott and J. A. LaVerne, Radiation
-%Physics and Chemistry 76, 1244-1247 (2007)
-
-%\bibitem{clementi}
-%E. Clementi, C. Roetti,
-%At. Data Nucl. Data Tables 14, 177--478 (1974).
+J. Phys. Chem. \textbf{95}, 3358 (1991).
 

### 2019-10-07 arxiv/ionmol_stoi.tex
change file names

--- 2019-09-28 arxiv/stoi_ionization.tex
@@
 distorted--wave calculations (CDW) for thirty--six collisional systems 
-composed by six atomic targets: H, C, N, O, F and S --which
-are the constituents of most of the DNA and biological molecules--, and
-six charged projectiles (antiprotons, H, He, B, C, and O). On account
-of the radiation damage caused by secondary electrons, we inspect
-the energy and angular distributions of the emitted electrons.
-We examine seventeen molecules: DNA and RNA bases,
-DNA backbone, pyrimidines, tetrahydrofuran (THF), and several
-C$_n$H$_n$ compounds. We show that the simple stoichiometric model
-(SSM), which approximates the molecular ionization cross sections as a
-linear combination of the atomic ones, gives reasonably good results
-for complex molecules. We inspect the extensively used Toburen
-scaling of the total ionization cross sections of molecules with the
-number of weakly bound electrons. Based on the present atomic CDW
-results, we propose new active electron numbers, which
-improves significantly scaling for all the targets
-and ions studied here.
-The new scaling describes well the available experimental
-data for proton impact, including small molecules such as H$_2$, water,
-methane, and ammonia.
-We perform full molecular
-calculations for five nucleobases and test a modified stoichiometric
-formula based on the Mulliken charge of the composite atoms. The
-difference introduced by the new stoichiometric formula is less than
-$3\%$, which indicates the reliability of the SSM to
+composed by six atomic targets: H, C, N, O, F and S --which are the 
+constituents of most of the DNA and biological molecules-- and six 
+charged projectiles (antiprotons, H, He, B, C, and O). On account of 
+the radiation damage caused by secondary electrons, we inspect the 
+energy and angular distributions of the emitted electrons from the 
+atomic targets. We examine seventeen molecules: DNA and RNA bases, 
+DNA backbone, pyrimidines, tetrahydrofuran (THF), and C$_n$H$_n$ 
+compounds. We show that the simple stoichiometric model (SSM), which 
+approximates the molecular ionization cross sections as a linear 
+combination of the atomic ones, gives reasonably good results for 
+complex molecules. We also inspect the extensively used Toburen scaling 
+of the total ionization cross sections of molecules with the number of 
+weakly bound electrons. Based on the atomic CDW results, we 
+propose new active electron numbers, which improves significantly 
+scaling for all the targets and ions studied here in the intermediate 
+to the high energy region. The new scaling describes well the available 
+experimental data for proton impact, including small molecules. We 
+perform full molecular calculations for five nucleobases and test a 
+modified stoichiometric formula based on the Mulliken charge of the 
+composite atoms. The difference introduced by the new stoichiometric 
+formula is less than 3\%, which indicates the reliability of the SSM to 
 deal with this type of molecules. The results of the extensive 
-ion--target examination included in the present study allow us to
-assert that the SSM and the CDW--based scaling will be useful tools in
-this area.
+ion--target examination included in the present study allow us to assert 
+that the SSM and the CDW--based scaling will be useful tools in this area.
 \end{abstract}

### 2019-11-13 ionmol_stoi.tex
change file names
JPB reviewers' comments

--- 2019-10-07 arxiv/ionmol_stoi.tex
@@
 weakly bound electrons. Based on the atomic CDW results, we 
-propose new active electron numbers, which improves significantly 
+propose new active electron numbers, which leads to a more universal 
 scaling for all the targets and ions studied here in the intermediate 
@@
 Most of the organic molecules are composed of these atoms. Some 
-particular molecules also include halogen atoms such as fluor and 
+particular molecules also include halogen atoms such as fluorine and 
 bromine; ionization cross sections of these elements have been 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{atomicscaling.eps}
+\includegraphics[width=0.8\textwidth]{figuras/atomicscaling.eps}
 \caption{Reduced CDW total ionization cross section of six atomic 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{ener_mean.eps}
+\includegraphics[width=0.8\textwidth]{figuras/ener_mean.eps}
 \caption{Mean emitted energy distribution for ionization by the impact 
-of multicharged ions, given by Eq.~(\ref{40}). Dashed lines for $\bar{p}$,
-solid lines for ion charges $+1$, $2+$, $4+$, $6+$ and $8+$,
-as indicated.}
+of multicharged ions, given by Eq.~(\ref{40}). 
+Solid lines for ion charges $+1$, $2+$, $4+$, $6+$ and $8+$, as indicated.
+Dashed lines for $\bar{p}$ and dotted line for Born with $Z=1$.}
 \label{fig:emittedener}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{ang_mean.eps}
+\includegraphics[width=0.8\textwidth]{figuras/ang_mean.eps}
 \caption{Mean emitted angle distribution for ionization by impact of
-multicharged ions.}
+multicharged ions. Curves as in Fig.~\ref{fig:emittedener}.}
 \label{fig:emittedang}
@@
 and the mean angle $\overline{\theta}_{\alpha}$ can be defined as
-\begin{equation}
-\overline{\theta}_{\alpha}=\frac{\langle\theta_{\alpha}\rangle}
+\begin{eqnarray}
+\overline{\theta}_{\alpha}&=&\frac{\langle\theta_{\alpha}\rangle}
 {\langle 1\rangle}=\frac{1}{\sigma_{\alpha}}\sum\limits_{nl}
-\int d\Omega\,\theta\,\frac{d\sigma_{\alpha,nl}}{d\Omega}
-\end{equation}
+\int d\Omega\,\theta\,\frac{d\sigma_{\alpha,nl}}{d\Omega} \\
+\langle 1\rangle &=&\sigma_{\alpha}=\sum\limits_{nl}\int d\Omega\,
+\frac{d\sigma_{\alpha,nl}}{d\Omega}\,, 
+\end{eqnarray}
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{adn1.eps}
+\includegraphics[width=0.8\textwidth]{figuras/adn1.eps}
 \caption{Reduced CDW ionization cross section by the impact of 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{adn2.eps}
+\includegraphics[width=0.8\textwidth]{figuras/adn2.eps}
 \caption{Reduced CDW ionization cross section by the impact of 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{molscaling85.eps}
+\includegraphics[width=0.8\textwidth]{figuras/molscaling85.eps}
 \caption{Scaled ionization cross section per weakly bound electron using
 (a)~the Toburen numbers $\nu_{\alpha}^T$, and (b) our proposed numbers
-$\nu_{\alpha}^{\text{CDW}}$. Experiments: proton impact on 
+$\nu_{\alpha}^{\text{CDW}}$ for molecules listed in Table~\ref{tab:families}. 
+For each band, the molecules are ordered from the smallest (top curve) to the
+largest (bottom curve). Experiments: proton impact on 
 \mbox{\Large$\circ$} adenine~\cite{iriki2011}, 
@@
 \begin{center}
-\begin{tabular}{|p{0.07\textwidth}p{0.02\textwidth}|
-p{0.095\textwidth}p{0.02\textwidth}|p{0.095\textwidth}p{0.035\textwidth}|}
+\begin{tabular}{|p{0.07\textwidth}p{0.02\textwidth}p{0.02\textwidth}|
+p{0.095\textwidth}p{0.02\textwidth}p{0.02\textwidth}|
+p{0.095\textwidth}p{0.035\textwidth}p{0.02\textwidth}|}
 \hline
- Molecule & $n_e'$ &Molecule          & $n_e'$ & Molecule             & $n_e'$\\
+ Molecule & $n_e'$ & $n_e$ & Molecule          & $n_e'$ & $n_e$ & Molecule             & $n_e'$ & $n_e$ \\
 \hline
- H$_2$    & 2  & C$_2$H$_7$N         & 19    & C$_4$H$_5$N$_3$O     & 37   \\
- H$_2$O   & 6  & C$_4$H$_8$O         & 28    & C$_5$H$_6$N$_2$O$_2$ & 42   \\
- NH$_3$   & 7  & C$_4$H$_4$N$_2$     & 28    & C$_5$H$_5$N$_5$      & 45   \\
- CH$_4$   & 8  & C$_6$H$_6$          & 30    & C$_5$H$_5$N$_5$O     & 49   \\
- CH$_5$N  & 13 & C$_4$H$_4$N$_2$O$_2$& 36    & C$_5$H$_{10}$O$_5$P  & 54.5 \\
+ H$_2$    & 2 & 2   & C$_2$H$_7$N         & 19 & 20 & C$_4$H$_5$N$_3$O     & 37 & 42 \\
+ H$_2$O   & 6 & 8   & C$_4$H$_8$O         & 28 & 30 & C$_5$H$_6$N$_2$O$_2$ & 42 & 48 \\
+ NH$_3$   & 7 & 8   & C$_4$H$_4$N$_2$     & 28 & 30 & C$_5$H$_5$N$_5$      & 45 & 50 \\
+ CH$_4$   & 8 & 8   & C$_6$H$_6$          & 30 & 30 & C$_5$H$_5$N$_5$O     & 49 & 56 \\
+ CH$_5$N  & 13 & 14 & C$_4$H$_4$N$_2$O$_2$& 36 & 40 & C$_5$H$_{10}$O$_5$P  & 54.5 & 65 \\
  \hline
 \end{tabular}
-\caption{New scaling numbers for some molecular targets of biological 
-interest.}
+\caption{New scaling numbers, $n_e'$, and Toburen numbers, $n_e$,
+for some molecular targets of biological interest.}
 \label{nn}
@@
 \centering
-\includegraphics[width=0.785\textwidth]{scale_ne.eps}
+\includegraphics[width=0.785\textwidth]{figuras/scale_ne.eps}
 \caption{Ionization cross sections by the impact of protons at 0.5, 1,
@@
 $\bigtriangledown$ pyrimidine~\cite{wolff2014}, 
-$\blacktriangle$ C2H$_7$N, CH$_5$N, methane and ammonia~\cite{lynch1976},
+$\blacktriangle$ C$_2$H$_7$N, CH$_5$N, methane and ammonia~\cite{lynch1976},
 \mbox{\scriptsize$\bigstar$} ammonia and H$_2$~\cite{rudd1985}, and 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{levelsDNA.eps}
+\includegraphics[width=0.8\textwidth]{figuras/levelsDNA.eps}
 \caption{Theoretical molecular binding energies for adenine, cytosine, 
@@
 Cytosine & +0.28 & +0.21 & --0.56 & --0.53 & 
-C$_{3.93}$H$_{2.79}$N$_{5.14}$O$_{1.13}$ \\ 
+C$_{3.93}$H$_{4.79}$N$_{3.14}$O$_{1.13}$ \\ 
 \hline
@@
 Thymine & +0.20 & +0.19 & --0.54 & --0.52 & 
-C$_{4.95}$H$_{1.81}$N$_{6.13}$O$_{2.13}$ \\ 
+C$_{4.95}$H$_{5.81}$N$_{2.13}$O$_{2.13}$ \\ 
 \hline
 Uracil & +0.31 & +0.22 & --0.59 & --0.47 & 
-C$_{3.92}$H$_{1.78}$N$_{4.15}$O$_{2.12}$ \\ 
+C$_{3.92}$H$_{3.78}$N$_{2.15}$O$_{2.12}$ \\ 
 \hline

### 2019-11-13 kirchner.tex
JPB reviewers' comments

Dear Claudia,

thanks for your email and the preprint. Good to know that you have
started to work on this as well! In fact, we found your preprint on
arXiv (via researchgate) a few days ago and discussed it a bit already.
So, if you don't mind, here are a few comments/questions:

(i) It's gratifying to see that your scaling (Eq. (9)) agrees with our
findings for C,N,O, but this raises the questions why we disagree on P.
Would it be worthwhile to compare the atomic ionization cross sections
for proton impact? Perhaps we should begin with a sanity check. We are
using Talman's OPM (or OEP) which results in -18.9 and -10.5 eV for the
eigenvalues of P(3s) and P(3p). What do you have?

(ii) BTW, we have another paper on this topic in the pipeline (it's with
EPJD). I attach the revised version of it which we prepared in response
to the recommendations of the reviewers in the first round of
refereeing. The paper focuses a bit more on the nucleobases and compares
our IAM-PCM to the CNDO approach used by Roberto and his co-workers.

(iii) This brings me to the model that you propose in Sec III C of your
manuscript. Can you comment on its relation to the CNDO approach? It
seems to be similar in spirit (because it is based on a Mulliken
analysis), but simplified/modified. I say simplified because the CNDO
approach uses different Mulliken 'gross populations' for the
contributing AOs whereas your model is based on the charges obtained
from summing up the AO contributions. I say modified because of Eq.
(10). Do you agree with this?

(iv) About Eq. (10): I would have expected to find the big Q_alpha in
the numerator of the second term on the RHS, not the little one. Your
refer to Q_alpha as the 'total amount of electrons' found on the atoms
of a certain species. Dividing this number by your eta_alpha^CDW (the
denominator) - i.e., the effective number of electrons available for
ionization in one free atom of that kind - would give you the additional
fractional number of atoms of that species in the molecule ('additional'
refers to a negative charge Q_alpha). That's what I would add to
n_alpha. Or am I mistaken?

(v) If I use the big Q_alpha instead the little one and the Mulliken
charges provided in Table III of your manuscript I obtain for uracil the
stoichiometric coefficients 3.69, 3.12, 2.30, 2.24 instead of 3.92,
3.78, 2.15, 2.12 (there is clearly a typo in that column of your table -
you have 1.78 for H and 4.15 for N, but you should have 3.78 and 2.15).
Looks like a bigger effect, but when I sum everything up the overall
effect will be (even) smaller, because the positive and negative
corrections cancel almost completely. That's just an observation. I
haven't done this for the other molecules.

(vi) Regardless of (iii) to (v) it seems to me that the overall effect
of any Mulliken or CNDO variant is small compared to what you call
'simple SSM' (which is what we refer to as IAM-AR). That's consistent
with our own findings and, I believe, with Roberto's findings as well.
By contrast, our IAM-PCM can result in a substantial reduction of the
IAM-AR cross sections at low and intermediate energies. This effect is
most dramatic for electron capture at low energies (as shown in the
attached preprint).

(vii) We have also done calculations for multiply-charged ion impact and
are in the process of analyzing them. First results indicate that we
obtain good agreement with Lokesh's measurements for uracil at MeV
energies using our IAM-PCM. So we might disagree with your comment that
there might be a 'possible misstep of the experiments', but we still
have to complete our analysis.

Best regards,

Tom

### 2019-11-15 jorge_og/NewMonti24.tex

%\documentclass[pra,showpacs,twocolumn]{revtex4}

\documentclass[preprint,showpacs,pra]{revtex4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2953}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%TCIDATA{LastRevised=Thursday, March 07, 2019 14:11:39}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\input{tcilatex}
\begin{document}

\title{Ionization of molecules by multicharged bared ions by using the \
stoichiometric model }
\author{author}
\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
\author{author}
\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (CONICET-UBA).
Casilla de correo 67, sucursal 28 (C1428EGA) Buenos Aires, Argentina.}
\affiliation{Fac. de Ciencias Exactas y Naturales, Universidad de Buenos Aires}
\date{\today }

\begin{abstract}
\end{abstract}

\pacs{79.20.Rf, 68.49.Bc, 34.20.Cf,34.50.-s,34.35.+a}
\maketitle

\section{INTRODUCTION}

The damage caused by the impact of multicharged heavy projectile has become
a field of interest because of the use in ion-beam cancer therapy. The
effectiveness of the radiation depends on the choice of the ions.\ In
particular theoretical and experimental studies with different projectiles
arrived to the conclusion that charged Carbon ions could be the most
convenient ion to use. This opens a \ new challenge \ for the theoretical
point of view, since multicharged ions at not-so-high-velocities departs
from the first Born approximation which is the most popular theory used in
this field. The first Born approximation as any perturbative direct
calculation warrants the Z$^{2}$ laws where Z is the projectile charge.
However the concentrated damage in the vicinities of the Bragg peak
correspond to energies of hundreds of Kev/amu, that is in the intermediate
energy region. Precisely in this region \ the Born approximation starts to
fail. There is another serious problem from the theoretical point of view
and this is that we are dealing with complex molecules. This article deals
precisely with theses two items. First, we perform more appropriate
calculations on the main damage mechanism -i.e. atomic ionization by
multicharged ions which can replace the Born results. And secondly we use
and inspect the stoichiometric model which reduces a molecule to a sum of
atomic processes quantities weight by the \ numbers of a that atom in the
molecule.

As we have to deal with multicharged ions we resort to the Continuum
Distorted Wave-Eikonal Initial State (CDW for short) which includes higher
perturbative corrections. We start from the premise that ionization process
is the mechanism that deposit the largest primary energy. This process \
produces an electron-energy spectrum that we need to be integrated. In
addition these ejected electrons becomes a new source of local damage which
needs to be investigated because this quantities are used in MonteCarlo
simulations. With this end in mind we not only calculate ionization cross
section but also energy and angular mean values of the emitted electrons

To deal with the molecules we resort to the simplest stoichiometric model
(SSM): this is to consider that the molecule is composed of independent
isolated atoms . In all cases that the total cross section is simply the sum
of cross section of each individual atoms.

With this two tools in mind, i.e. CDW instead of Born approximation and the
SSM, we calculate ionization cross section of different molecules (see Table(%
\ref{20})) by the impact of antiprotons, H$^{+}$, He$^{2+}$, Be$^{4+}$, C$%
^{6+}$,\ and O$^{8+}.$\ In particular \ in section 3, we are interested in
ADN molecules such as Adenine, Timine, Cytosine, Guanine, Uracil, and DNA
backbone.

The results are processed to test the Toburen scaling rule which states that
the ratio of the ionization cross section divided by the number valence
electrons (outer electrons) plotted in terms of the projectile velocity can
be \textbf{grouped} in a narrow universal band. We have also applied this
rule to several hydrocarbons and \ pirimide molecules. We will prove that
the resulting universal band can be greatly sharped (\textbf{angostada}) if
we redefine \ effective valence electrons as developed in Section 3.2

It is well known the biological damage caused by the electron emerging after
the ionization process. To inspect this mechanism, in section 3.3 AND 3.4 we
have calculated the mean electron energy an angular values. To our surprise
we found a substantial dependence of the projectile charged, totally
unexpected in first Born approximation.

To deal with large projectile charge we resort to the CDW but the simplest
stoichiometric model~\ used \ seems to be very simplistic since consider
each atom as neutral, which is not correct. In section 3.5 we run the
chemistry code GAMES to calculate the excess or defect of electron density
one each atoms. With these knowledge we modify the simple stoichiometric
model to account for the departure of the neutrality. We find that, for the
ADN molecules this modification does not introduce a substantial change.

\section{THEORY: IONIZATION OF ATOMS}

For our interest we require just six\ atoms $\alpha =$H, C, N, O, P and S.
Most of the organic molecules are composed by these atoms. \ Some particular
molecules include also halogen atoms such as Fluor and Bromine; ionization
cross sections for these elements in its ion form were already published 
\cite{miraglia2008,miraglia2009}.

Total ionization cross sections of these atoms were calculated using the CDW
The initial bound and final continuum radial wave functions were obtained by
using the RADIALF code developed by Salvat and co-workers using a Hartree
Fock potential obtained the Depurated Inversion Model \cite%
{mendez2016,mendez2018} . The number of pivots used to solve the Schr\"{o}%
dinger equation rounds a few thousands of points, depending on the number of
oscillations of the continuum state. The radial integration was performed
using the cubic spline technique. The number of angular momenta considered
varied between 8, at very low ejected-electron energies, up to 30, at the
largest energies considered. The same number of azimuth angles were required
to obtain the four fold differential cross section \ The calculation so
performed does not display prior-post discrepancies at all. Each atomic
total cross section in Eq. (1) was calculated using 35 to 100 momentum
transfer values, 28 fixed electron angles and around 45 electron energies
depending on the projectile impact energy. Details of the calculation can be
seen in \cite{montanari2017} In parallel we will be reporting state to state
ionization cross sections for these cases in Ref.[\cite{miraglia2019}] which
will be very useful to estimate molecule fragmentation.

In Figure 1 we report our results of total ionization of the six basic
elements by impact of six different projectile, i.e.: antiprotons, H$^{+}$,
He$^{2+}$, Be$^{4+}$, C$^{6+}$,\ and O$^{8+}$ \ To bring all these 36
magnitudes to a consistent figure we exploit the property that in first Born
approximation, the ionization cross section scales with the projectile
charge to square , i.e. Z$^{2}$\ \ The values of impact energies considered
range between 0.1 to 10 MeV/amu, i.e where the CDW is supposed to hold. In
fact for the highest projectile charges the minimum impact energy where the
CDW is expected to be valid could be larger than 100 KeV. From some Mev/amu
on, the first the Born approximation provides quite reliable results and
using a much simpler formalism; we check it. We keep the same color to
indicate the projectile charge along the all figures of this work :
dashed-red, solid-red, blue, magenta, olive and orange for\ antiprotons, H$%
^{+}$, He$^{2+}$, Be$^{4+}$, C$^{6+}$,\ and O$^{8+},$ respectively . It is
notable that there is no complete tabulation of ionization of atoms by
impact of multiple charge ions. We hope that the ones presented in this
article will be very useful.

\section{IONIZATION OF MOLECULES}

\subsection{The stoichiometric model}

Lets us consider a molecule $M$\ composed by $n_{\alpha }$ atoms of the
element $\alpha $, the SSM describes the total ionization cross section of
the molecule $\sigma _{M}$\ as a simple sum of ionization cross sections of
the isolated atoms $\sigma _{\alpha }.$ i.e. 
\begin{equation}
\sigma _{M}=\dsum\limits_{\alpha }n_{\alpha }\sigma _{\alpha }  \label{10}
\end{equation}%
We divided sixteen molecular targets of our interest in 3 families, namely%
\begin{equation}
\begin{array}{|l|l|}
\hline
\text{CH} & \text{CH}_{4}\text{,\ C}_{2}\text{H}_{2}\text{, C}_{2}\text{H}%
_{4}\text{, C}_{2}\text{H}_{6}\text{, and C}_{6}\text{H}_{6}\text{.} \\ 
\hline
\text{CHN} & \text{C}_{5}\text{H}_{5}\text{N, C}_{4}\text{H}_{4}\text{N}_{2}%
\text{,\ C}_{2}\text{H}_{7}\text{N}_{1}\text{, and\ C}_{1}\text{H}_{5}\text{N%
}_{1} \\ \hline
\text{ADN} & 
\begin{array}{l}
\begin{array}{l}
\text{Adenine(C}_{5}\text{H}_{5}\text{N}_{5}\text{),Timine(C}_{5}\text{H}_{6}%
\text{N}_{2}\text{O}_{2}\text{),} \\ 
\text{Cytosine(C}_{4}\text{H}_{5}\text{N}_{3}\text{O),Guanine(C}_{5}\text{H}%
_{5}\text{N}_{5}\text{O),} \\ 
\text{Uracilo(C}_{4}\text{H}_{4}\text{N}_{2}\text{O}_{2}\text{)},%
\end{array}
\\ 
\begin{array}{l}
\text{DNA backbone (C}_{5}\text{H}_{10}\text{O}_{5}\text{P}_{1}\text{)} \\ 
\text{dry DNA(C}_{20}\text{H}_{27}\text{N}_{7}\text{O}_{13}\text{P}_{2}\text{%
)}%
\end{array}%
\end{array}
\\ \hline
\end{array}
\label{20}
\end{equation}

In Figure 2 we report total ionization cross sections by the impact of
multicharged ions for the four basic ADN component that is: \ Adenine,
Timine Cytosine, and Guanine, and in Figure 3 we report results on Uracil
and ADN Backbone containing P. For Adenine the agreement with the three
experiments available in our range of validity are quite good. For Uracil
there is a conflicting situation, we have a good agreement with the
experiments by proton impact \ of itoh et al \cite{itoh2013}, but for the
same target our theory fails by a factor of two for impact of C$^{4+}$ and O$%
^{6+}$ ions . Anyway should be said that our theoretical results coincide
with the ones of Champion Rivarola and collaborators \cite%
{champion2012,agnihotri2012}, indicating a possible\ misstep of the
experiments.

\subsection{Scaling rule}

The first attempt to develop a simple but comprehensive phenomenological
model for electron ejection from large molecules was posed by Toburen and
collaborators \cite{toburen1975,toburen1976} \ These authors found
convenient to scale the experimental ionization cross section in terms of
the number of outer or weakly bound valence electrons (total number of
electrons minus the inner-shell ones). We then introduce the cross section
per weakly bound electron $\sigma _{e}$, or simply\ ionization cross section
per valence electron \ as%
\begin{eqnarray}
\sigma _{e} &=&\frac{\sigma _{M}}{N_{M}}=\frac{\dsum\limits_{\alpha
}n_{\alpha }\sigma _{\alpha }}{\dsum\limits_{\alpha }n_{\alpha }v_{\alpha }}%
=\sigma _{e}(v),\text{ with}  \label{27} \\
v_{\alpha } &=&\left\{ 
\begin{array}{ll}
4,\ \ \  & \text{for C,} \\ 
5, & \text{for N and P} \\ 
6, & \text{for O and S}%
\end{array}%
\right.
\end{eqnarray}%
and \ $v_{H}=1$\ The Toburen rule can be stated by saying that $\sigma _{e}$
is an \textit{universal} parameter independent on the molecule and depending
only on the impact velocity$.$ In Ref. [\cite{toburen1976}] it was found
experimentally that for proton impact on some simple molecules $\sigma _{e}\ 
$result

\begin{equation}
\begin{array}{cccc}
E\text{(MeV)} & \ \ \ 0.25 & \ \ \ 1.00 & \ \ \ 2.00 \\ 
\sigma _{e}\ (\text{in}\ 10^{-16}cm^{2}) & \ \ \ 0.39 & \ \ \ 0.17 & \ \ \
0.11%
\end{array}
\label{30}
\end{equation}%
with an estimated error of about 20\%. A similar ratio was found in Ref.[%
\cite{itoh2013}] dealing with protons on uracil and adenine. Figure 5a shows 
$\sigma _{e}$ calculated with the CDW as a function of the impact velocity
for different projectile charges calculated with the SSM for the sixteen
molecular targets displayed in (\ref{20}). \ The universality with $Z$ is
the one provided by Born \ approximation, i.e. $\sigma _{e}(Z)=Z^{2}\sigma
_{e}(Z=1)$ and it holds for large impact velocities, as shown Figure5a .
Obviously, for lower impact velocities the distorted wave CDW breaks this
behavior discarding the rule\ $Z^{2}$. Although \ the Toburen rule holds for
high energies, its performance is still not satisfactory: the universal band
is quite wide. This departure of our theoretical results from the Toburen
rule can be explained by the simple fact that our atomic cross sections $%
\sigma _{\alpha }$ behaves differently for each atom in terms of the
projectile charges.\ By inspecting Figure 1 one can easily see that the rule 
$\sigma _{\alpha }/v_{\alpha }\sim \sigma _{e}$ is not well satisfied by the
CDW. A much better theoretical atomic rule is given by

\begin{eqnarray}
\sigma _{e}^{CDW} &=&\frac{\dsum\limits_{\alpha }n_{\alpha }\sigma _{\alpha
}^{CDW}}{\dsum\limits_{\alpha }n_{\alpha }v_{\alpha }^{CDW}},~\text{\ with}
\label{32} \\
v_{\alpha }^{CDW} &\sim &\left\{ 
\begin{array}{ll}
4,\ \ \  & \text{for C, N, and O,} \\ 
4.5,\ \  & \text{for P and S}%
\end{array}%
\right. \text{ }  \label{35}
\end{eqnarray}%
and obviously $v_{H}^{CDW}=1.\ \ \sigma _{e}^{CDW}$ is plotted in Figure 5b
where we can observe a much better sharp band, specially at high energy
where the theory is expected to work. Experiments will be interesting to
tune up this theoretical prediction

\subsection{Emitted electron energies}

In a given biological medium, ion direct ionization account for just a
fraction of the overall damage. Secondary electrons as well as recoil target
ions also contribute substantially to the total damage. We can consider the
magnitude $d\sigma _{\alpha nl}/dE$ \ -i.e. the single differential cross
section \ of the shell $nl$ of the atom $\alpha $ as a function of the
ejected electron energy $E$-\ as a simple distribution function \ref%
{surdutovic2018}. We can therefore define\ the mean value $\overline{E}%
_{\alpha }\ $simply as Ref.[\cite{Abril2015}]

\begin{eqnarray}
\overline{E}_{\alpha } &=&\frac{\langle E_{\alpha }\rangle }{\langle
1\rangle }=\frac{1}{\sigma _{\alpha }}\dsum\limits_{nl}\int dE\ E\frac{%
d\sigma _{\alpha ,nl}}{dE}  \label{40} \\
\langle 1\rangle  &=&\sigma _{\alpha }=\dsum\limits_{nl}\int dE\ \frac{%
d\sigma _{\alpha ,nl}}{dE}  \label{50}
\end{eqnarray}%
where $\Sigma _{nl\ }$takes into account the sum of the different sub-shells
contribution of the element $\alpha .$

Figure 5 shows $\overline{E}_{i}$ for our six elements of interest. Our
range of impact velocities in this figure was shorten up to $v=10$ and this
so because of \ a numerical limitation of our spherical harmonics expansion.
In our theoretical treatment we expand our final continuum wave function in
the usual form

\begin{equation}
\psi _{\overrightarrow{k}}^{-}(\overrightarrow{r})=\sum_{l=0}^{l_{\max
}}\sum_{m=-l}^{l}R_{kl}^{-}(r)Y_{l}^{m}(\widehat{r})Y_{l}^{m^{\ast }}(%
\widehat{k}),  \label{60}
\end{equation}%
We are confident with our calculations up to $l_{\max }\sim 30.$ As the
impact velocity $v$\ increases $\langle E_{\alpha }\rangle $\ also
increases, and therefore$\ \ l_{\max }$ should also increases, including in
this way very oscillatory functions in the integrand. Furthermore, as the
integrand of $\langle E_{\alpha }\rangle $ includes the kinetics-energy
variable $E\ ($ see Eq.(\ref{40})$),$ it\ cancels the small energy region
and reinforces the large one making the result more sensible lo large
angular momenta. Anyway for $v>10,$ the first Born approximation holds.

In Figure 5 we can \ estimate $\overline{E}_{\alpha }$ in the range \ 0.5-2
in a.u. or equivalently in between 15-50 eV for all the targets in
accordance with the experimental findings \ref{surdutovic2018} but what it
surprising is the sensible dependence with the projectile charge $Z$\ which
can duplicate the proton results. This effect can be attributed to the
depletion caused by the multicharged ions to the yields of low energy
electrons. In the high \ electron energy regime the CDW falls on the simple
first Born approximation surviving\ the simple $Z^{2}$ law which the ratio
in Eq.(\ref{40}) cancels out, becoming then $\overline{E}_{\alpha }$ an
universal value independent on $Z.$

Extending the simple stoichiometric model for the mean electron energy
calculation, it results%
\begin{equation}
\overline{E}_{M}=\frac{\dsum\limits_{\alpha }n_{\alpha }\overline{E_{\alpha }%
}}{\dsum\limits_{\alpha }n_{\alpha }\sigma _{\alpha }}.  \label{70}
\end{equation}%
For impact of H$^{+}$ and He$^{2+~}$ on water at 1 MeV/amu we obtain of \ $%
\overline{E}_{H_{2}O}=$43.7 \ and 45eV, while the experiments on liquid
water Pimblott and LaVerne [] found \ 51.5 and 52.2 eV, respectively. Just
to stress the importance of the projectile charge, for O$^{8+}$ on water at
the same impact energy 1 MeV/amu we, obtain $\overline{E}_{H_{2}O}=54.7$ eV,
i.e. 25\% larger than proton impact. We recall here that there should not be
any difference if the calculation is carried in first Born approximation. We
will came back on this issue

\subsection{Emitted electron angles}

As mentioned before, secondary electrons contribute to the total damage. It
is important not only the ejection energy but also the angle of emission. In
similar fashion, we can consider the magnitude $d\sigma _{\alpha
,nl}/d\Omega $ \ -i.e. the single differential cross section in terms of the
ejected electron solid angle $\Omega $ -\ as a distribution function, and
define the mean angle $\overline{\theta }_{\alpha }$ as

\begin{equation}
\overline{\theta }_{\alpha }=\frac{\langle \theta _{\alpha }\rangle }{%
\langle 1\rangle }=\frac{1}{\sigma _{\alpha }}\dsum\limits_{nl}\int d\Omega
\ \theta \ \frac{d\sigma _{\alpha ,nl}}{d\Omega }
\end{equation}%
Figure 6 shows $\overline{\theta }_{\alpha }$ for our six elements of
interest. Again here we observe an important dependence dependence of $%
\overline{\theta }_{\alpha }\ $with $Z.$ It is the common view \cite%
{Rudd1992} that the angular dispersion of emitted electrons are nearly
isotropic due to the fact that angular anisotropy of sub-50-eV yield is not
significant. A typical used value of ejection angle is about $\overline{%
\theta }_{\alpha }\sim $70 degrees \cite{surdutovic2018} and this quite
correct in the range of validity of the first Born approximation for any
target. But when a distorted wave approximation is used as observed in
Figure 6, $\overline{\theta }_{\alpha }$ decreases substantially with $Z$ in
the intermediate energy region. For example for C$^{6+}$ impact the Bragg
peak occurs at 0.3 MeV/amu where \ $\overline{\theta }_{\alpha }$ calculated
in CDW is about the half of the one calculated with the First Born
approximation. \ This correction should close the damage to the forward
direction.

The only responsible of this correction is the\ capture to the continuum
effect: the larger the charge $Z$ the smaller $\overline{\theta }$ will be,
of course at intermediate energies, not at high impact energies where the
Born approximation rules. One illustrative observation is the behavior of
antiprotons: the projectile in this case repels the electrons \ making the
distribution almost symmetric. Note the opposite effect of proton and
antiprotons, they run one oppose to the other one, as compared with the
first Born approximation.

\subsection{A modified stoichiometric model}

One can correctly argue that\ the SSM considers an assembly of isolated
neutral atoms which is definitively unrealistic. A first improvement is to
consider that the atoms are not neutral and within the molecule they have
more or less electrons given by a \ charge $q_{\alpha }$. One parameter that
measures $q_{\alpha }$ is the Mulliken charge. This is not the only one,
there is a large variety of charges such as the net or natural atomic charge 
\cite{lee2003}, the lowin charge, etc.

Consider\ that the total amount of electrons $Q_{\alpha }\ $on element $%
\alpha $ are equally distributed on all the atoms $\alpha ,$ therefore each
element $\alpha \ $\ will have a an additional charge: $q_{\alpha
}=Q_{\alpha }/n_{\alpha }$. positive or negative depending on the relative
electronegative value respect to the other ones\ \cite{rappe1991}$.$Instead
of the integer number of elements $n_{\alpha }$ of the atom $\alpha ,$ It
could be argued that we have now an continuous number of atoms\ \ given by 
\begin{equation}
n_{\alpha }^{\prime }=n_{\alpha }-\frac{q_{\alpha }}{v_{\alpha }^{CDW}}
\label{100}
\end{equation}%
In the case of neutral atoms $q_{\alpha }=0,$ we obviously recover $%
n_{\alpha }^{\prime }=n_{\alpha }$ as before$.$

To inspect the effect of the $q_{\alpha }$ we have run GAMES for.... In the
table ( \ref{110}) we display $q_{\alpha }$ of the different ADN basis and
in the last column we rewrite the new stoichiometric expression. 
\begin{equation}
\begin{array}{|l|l|l|l|l|l|}
\hline
\text{Element\ \ } & \text{H} & \text{C} & \text{N} & \text{O} & \text{New\
stoichiometry} \\ \hline
\text{Adenine} &  &  &  &  & \ \ \text{C}_{5}\text{H}_{5}\text{N}_{5} \\ 
\hline
\text{Timine} & +0.14 & +0.07 & -0.22 & -0.38 & \ \text{\ C}_{4.91}\text{H}%
_{5.16}\text{N}_{2.09}\text{O}_{2.13} \\ \hline
\text{Cytosine} &  &  &  &  & \ \text{\ C}_{3.81}\text{H}_{4.46}\text{N}%
_{3.12}\text{O}_{1.11} \\ \hline
\text{Guanine} &  &  &  &  & \ \ \text{C}_{5}\text{H}_{5}\text{N}_{5}\text{O}
\\ \hline
\end{array}
\label{110}
\end{equation}%
All the previous formula holds with the simple replacement of integer value $%
n_{\alpha }$ by the continuous values\ $n_{\alpha }^{\prime }$ to produce a
new ionization cross section $\sigma ^{\prime }$

In Figure 7, we displays the relative difference of ionization cross
sections 
\begin{equation}
e=\frac{\sigma ^{\prime }-\sigma }{\sigma }\times 100  \label{120}
\end{equation}%
for the four ADN basis. The difference is \ just very few percents.
Indicating that the SSM is a quite robust model to treat the type of
molecule we are dealing with, and of course within the range error that one
can expect from the SSM.

We now return to the calculation of the mean electron energy of H$^{+}$ and
He$^{2+~}$ in water\ \ $\overline{E}_{H_{2}O}$. If we consider that \ the
residual charge of \ each hydrogen in water is $q_{H}=$+0.35 \ \cite%
{rappe1991}\ which implies that on Oxygen we have \ a residual charge of $%
q_{O}=$-0.7, we could re-write the formula of water using (\ref{120}) as H$%
_{1.3}$O$_{1.17}$ considering $n_{O}^{CDW}\simeq 4$ and $n_{H}^{CDW}\simeq
1. $ Recalculating mean electron energy by impact of \ H$^{+}$ and He$^{2+~}$
on water at 1 MeV/amu we obtain: $\overline{E}_{H_{2}O}=$46.2 \ and 47.6 eV
which compared a little better with the experiments: 51.5 and 52.2 eV \cite%
{pimblott2007}, respectively. i.e. within 10\% of the experiments which is
not bad accounting for the simplicity of our method.

Another parameter that we can calculate in our model is the fraction of
energy carried by the electron $f$ defined as%
\begin{equation}
f=\frac{\dsum\limits_{\alpha }n_{\alpha }\sigma _{\alpha }\overline{%
E_{\alpha }}}{\dsum\limits_{\alpha }n_{\alpha }(\sigma _{\alpha }\overline{%
E_{\alpha }}+\dsum\limits_{nl}\sigma _{\alpha nl}E_{\alpha nl})}  \label{90}
\end{equation}%
Using our shell-to-shell ionization cross sections $\sigma _{\alpha nl}\ $%
\cite{miraglia2019}\ and atomic binding energies of the atom$\ \alpha ,$ $%
E_{\alpha nl}\ $\cite{clementi}, we obtain $f=$0$.70\ $and $\ 0.71$ for \ H$%
^{+}$ and He$^{2+~}$ on water at 1 MeV/amu,. which differ from the
experiments \ $f=0.81$ and $0.80$, \ respectively.

This difference with the experiment could be attributed to the difference of
binding energy between the molecular water 12.65 eV and the atomic component
H (13.6 eV) and O (17.19 eV), which is an issue beyond our independent atom
approximation and so our model cannot not accounted for. We could estimate
this contribution resorting, once more to the stoichiometric, model, we can
arriesgar a upper-limit difference per molecule of water\ as

\begin{equation}
\delta E=(13.6-12.65)1.17+(17.19-12.65)1.3=7\ \text{eV}  \label{80}
\end{equation}%
Most of this energy should be transfer to the kinetics energy of the emitted
electron. Thus we can \ add 7 eV to the previous values to give $\overline{E}%
_{H_{2}O}=$53.2 \ and 54.6 eV for \ H$^{+}$ and He$^{2+~}$ on water at 1
MeV/amu, respectively, much near to the experiments: 51.5 and 52.2 eV. If we
add $\delta E$ to the numerator of Eq.(\ref{90}) we obtain\ $f=0.81$ and $%
0.80$ in perfect agreement with the experiments (see Table 1 of Ref.(\cite%
{pimblott2007})

\section{CONCLUSIONS}

We have calculated ionization cross sections by impact of antiprotons, H$^{+}
$, He$^{2+}$, Be$^{4+}$, C$^{6+}$,\ and O$^{8+}$ with molecule involved in
biological basis containing H, C, N, O, P and S with the CDW method. \ The
importance of the influence of $Z\ $was observed in the mean energy $%
\overline{E}_{\alpha }\ $and angle $\overline{\theta }_{\alpha }.$ For a
given target $\alpha ,$ as $Z$ increases $\overline{E}_{\alpha }$ increases
but $\overline{\theta }_{\alpha }$ decreases \ At high impact energy, say
larger than 1 MeV/amu these values tend to the ones of the Born
approximation which embodies the simple Z$^{2}$ law. Sixteen molecules were
investigated using the simple stoichiometric model. Results for the six ADN
basis were presented and compared with the sparse available experiments \ We
explore the rule of Toburen which scales all the molecular ionization cross
section when divided by the number of weakly bound valence electrons $\nu
_{\alpha }$ given by Eq.(\ref{27})$.$ We have found the rule scales much
better when normalizing our theoretical ionization cross sections to the
number\ $\upsilon _{\alpha }^{\prime }$ given by Eq.(\ref{35}). And finally
we attempt to improve the stoichiometric model by the use of the Mulliken
charge to redefine a new stoichiometric model containing continuum rather
than integer proportions. NO substantial correction was found indicating
that the SSM works quite well.

Our aims is this article is to provide the tools to estimate any inelastic
parameter parameter -such as the emission angle, the emitted mean energy and
cross section- by the impact of any multicharged \ on any molecule
containing H, C, N, O, P and S, with the help of the stoichimetrical model.
Our goal was quite \textbf{pretencioso}, considering the simplicity of our
proposal. However we think our results could be used to estimate the
ionization magnitude with an acceptable level of uncertailties

\bigskip

\section{Basura}

\begin{thebibliography}{99}
\bibitem{itoh2013} A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D.
Rivarola,~Cross sections for ionization of uracil by MeV-energy-proton
impact,\ PHYSICAL REVIEW A 88, 052711 (2013)

\bibitem{miraglia2008} J. E. Miraglia and M. S. Gravielle. Ionization of the
He, Ne, Ar, Kr, and Xe isoelectronic series by proton impact. Phys Rev A 
\textbf{78}, 052705 (2008)

\bibitem{miraglia2009} J. E. Miraglia, Ionization of He, Ne, Ar, Kr, and Xe
by proton impact: Single differential distributions. Phys Rev A \textbf{79},
022708 (2009).

\bibitem{} in energy and angles~,

\bibitem{mendez2016} A.M.P. Mendez, D.M. Mitnik, and J.E. Miraglia.
Depurated inversion method for orbital-specific exchange potentials. Int. J.
Quantum Chem. 24 ,116 (2016).

\bibitem{mendez2018} A.M.P. Mendez, D.M. Mitnik, and J.E. Miraglia. Local E
ective HartreeFock Potentials Obtained by the Depurated Inversion Method,
????? 76. (2018).

\bibitem{champion2012} C Champion1, M E Galassi, O Foj\'{o}n, H Lekadir, J
Hanssen1, R D Rivarola,

P F Weck, A N Agnihotri, S Nandi, and L C Tribedi. Ionization of RNA-uracil
by highly charged carbon ions. J. Phys.: Conf. Ser. 373, 012004 (2012).

\bibitem{agnihotri2012} A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A.
Kumar, M. E. Galassi, R. D. Rivarola, O. Foj\'{o}n, C. Champion, J. Hanssen,
H. Lekadir, P. F. Weck, and L. C. Tribedi. Ionization of uracil in
collisions with highly charged carbon and oxygen ions of energy 100 keV to
78 MeV.\ \ Phys Rev A 85, 032711 (2012).

\bibitem{toburen1975} W. E. Wilson and L. H. Toburen. Electron emission from
proton ---hydrocarbon-molecule collisions at 0.3---2.0 MeV. PHYSICAL REVIEW
A\ 11 1303 (1975).

\bibitem{montanari2017} Ionization probabilities of Ne, Ar, Kr, and Xe by
proton impact for different initial states and impact energies. Nucl. Instr.
Meth. Phys. Res. B 407 (2017) 236-243.

\bibitem{miraglia2019} J. E. Miraglia. Shell-to-shell ionization cross
sections of antiprotons, H$^{+}$, \ He$^{2+},$ Be$^{4+},$ C$^{6+}$ and O$%
^{8+}$ on H, C, N, O, P, and S atoms To be published Archive 2019.

\bibitem{toburen1976} D. J. Lynch, L. H. Toburen, and W. E. Wilson. Electron
emission from methane, ammonia, monomethylamine, and dimethylamine by 0.25
to 2.0 MeV protons. J. Chem. Phys. 64, 2616 (1976).

\bibitem{surdutovic2018} Multiscale approach to the physics of radiation
damage with ions. E. Surdutovich and A. V. Solov'yov, arXiv:1312.0897v,
(2013)

\bibitem{abril2015} P. de Vera1, I. Abril, R. Garcia-Molina and
A.V.Solov'yov,\ Ionization of biomolecular targets by ion impact: input data
for radiobiological applications. Journal of Physics: Conference Series 438
(2013) 012015

\bibitem{lee2003} Jung-Goo Lee, Ho Young Jeong, and Hosull Lee, Charges of
Large Molecules Using Reassociation of Fragments. Bull. Korean Chem. Soc.24\
2003, 369 .

\bibitem{rappe1991} A. K. Rappe, A. K.and W. A. Goddard III,. J. Phys. Chem. 
\textbf{95 (}1991) 3358.

\bibitem{pimblott2007} S.M. Pimblott and J. A. LaVerne, ????Radiation
Physics and Chemistry 76, 1244-1247 (2007)

\bibitem{Rudd1992} M. E. Rudd, Y.-K. Kim,, D. H. Madison and T. J. Gay.
Electron production in proton collisions with atoms and molecules: energy
distributions. Rev. Mod. Phys. \textbf{64}, 44-490 (1992).
\end{thebibliography}

\end{document}

### 2019-11-20 ionmol_stoi.tex
response to reviewers and corrections

@@
 dealing with complex molecules, and the description of such targets 
-represents a hard task for {\it ab initio} calculations. The objective 
-of this article is to deal with these two aspects; first, we perform 
+represents a hard task for {\it ab initio} calculations.
+
+Different approaches have been proposed to deal with the ionization of 
+molecular targets within the independent atom model. For example, 
+Galassi \textit{et al.} \cite{galassi2000} obtains molecular cross 
+sections by combining CDW-EIS atomic ones based on the population of 
+the molecular orbitals. Much more recently, L\"udde \textit{et al.} 
+\cite{ludde2016,ludde2018} 
+propose a combination of atomic cross sections with geometrical screening
+corrections.
+
+The objective of this article is to deal with two aspects; first, we perform 
 more appropriate calculations on the primary damage mechanism, which can 
@@
 
-The total ionization cross sections of these atoms were calculated using 
-the CDW. The initial bound and final continuum radial wave 
-functions were obtained by using the {\sc radialf} code, developed by 
-Salvat and co--workers~\cite{salvat1995}, and a Hartree--Fock potential 
-obtained from the Depurated Inversion Method~\cite{mendez2016,mendez2018}. 
+The total ionization cross sections of these atoms $\sigma_{\alpha}$
+were calculated using the CDW. The initial bound and final continuum 
+radial wave functions were obtained by using the {\sc radialf} code, 
+developed by Salvat and co--workers~\cite{salvat1995}, and a Hartree--Fock 
+potential obtained from the Depurated Inversion Method~\cite{mendez2016,mendez2018}. 
 We used a few thousand pivot points to solve the Schr\"{o}dinger 
@@
 \includegraphics[width=0.8\textwidth]{figuras/atomicscaling.eps}
-\caption{Reduced CDW total ionization cross section of six atomic 
+\caption{Reduced CDW total ionization cross section $\sigma_{\alpha}/Z^2$ 
+of six atomic 
 targets. The curves are labeled with the charge state corresponding to 
@@
 Solid lines for ion charges $+1$, $2+$, $4+$, $6+$ and $8+$, as indicated.
-Dashed lines for $\bar{p}$ and dotted line for Born with $Z=1$.}
+Dashed lines for $\bar{p}$ and dotted line for the Born approximation with $Z=1$.}
 \label{fig:emittedener}
@@
 is used, $\overline{\theta}_{\alpha}$ decreases substantially with $Z$ 
-in the intermediate energy region. This effect is evident in 
-Fig.~\ref{fig:emittedang};
-for example, at 0.3 MeV/amu --where the Bragg peak for C$^{6+}$ impact 
-occurs-- the CDW $\overline{\theta}_{\alpha}$ is half of the first Born 
-value. This correction closes the damage to the forward direction.
+in the intermediate energy region, as shown in Fig.~\ref{fig:emittedang}.
+
+To illustrate these effects, consider the impact of C$^{6+}$ impact on oxygen.
+At an impact energy of 500~keV, the first Born approximation predicts
+emitted electrons with mean energies of 46.7 eV and mean angles of 78\degree, 
+while the CDW gives 62.5 eV and 60\degree. 
+These results imply depper penetration closer to the direction of the ion.
 We can attribute this forward direction correction to the capture to 
@@
 
-In Fig.~\ref{fig:crossDNA_1}, we report the total ionization cross 
-sections by the impact of multicharged ions for adenine, cytosine, 
+In Fig.~\ref{fig:crossDNA_1}, we report the reduced total ionization cross 
+sections $\sigma_M/Z^2$ by the impact of multicharged ions for adenine,
+cytosine, 
 guanine, and thymine, by combining the SSM and CDW results in 
@@
 
-Our results for uracil, DNA backbone, pyrimidine, and THF are displayed 
+At intermediate impact energies, the $Z^2$ rule no longer holds and other 
+scalings can be considered in this region. 
+In Fig.~\ref{fig:Zcaled_crossDNA_1}, we plotted the reduced ionization 
+cross section $\sigma_M/Z$ as a function of the reduced ion impact energy
+$E/Z$ as suggested by~\cite{janev1980,dubois2013}.
+This scaling may be a good alternative to deal with highly charged
+ions at intermediate energies in a coherent way.
+
+The reduced total ionization cross sections $\sigma_M/Z^2$ for uracil, 
+DNA backbone, pyrimidine, and THF are displayed 
 in Fig.~\ref{fig:crossDNA_2}. For uracil, the agreement with the 
@@
 \includegraphics[width=0.8\textwidth]{figuras/adn1.eps}
-\caption{Reduced CDW ionization cross section by the impact of 
-multicharged ions. Experiments: \mbox{\Large$\circ$}~\cite{iriki2011} 
+\caption{Reduced CDW ionization cross section $\sigma_{M}/Z^2$ as a function 
+of ion impact energy. Experiments: \mbox{\Large$\circ$}~\cite{iriki2011} 
 for proton impact and $\square$~\cite{rahman2016} for electron impact 
@@
 \centering
+\includegraphics[width=0.8\textwidth]{figuras/Zscaling_adn1.eps}
+\caption{Reduced CDW ionization cross section $\sigma_{M}/Z$ as a function 
+of reduced ion impact energy $E/Z$. 
+Experiments: \mbox{\Large$\circ$}~\cite{iriki2011} 
+for proton impact and $\square$~\cite{rahman2016} for electron impact 
+with equivelocity conversion.}
+\label{fig:Zcaled_crossDNA_1}
+\end{figure*}
+
+\begin{figure*}[t!]
+\centering
 \includegraphics[width=0.8\textwidth]{figuras/adn2.eps}
-\caption{Reduced CDW ionization cross section by the impact of 
-multicharged ions. Experiments: proton impact on 
+\caption{Reduced CDW ionization cross section $\sigma_{M}/Z^2$ as a function 
+of ion impact energy. Experiments: proton impact on 
 $\triangle$ uracil~\cite{itoh2013}, 
@@
 \end{tabular}
-\caption{New scaling numbers, $n_e'$, and Toburen numbers, $n_e$,
+\caption{New scaling numbers $n_e'$, and Toburen numbers $n_e$,
 for some molecular targets of biological interest.}
@@
 ionization cross sections for all the molecules show a linear 
-dependence with the number of electrons from Table~\ref{nn}. We obtain 
-similar results, even for $E=10$~MeV. The comparison with the 
+dependence with the number of electrons $n_e'$ from Table~\ref{nn}.
+We obtain similar results, even for $E=10$~MeV. An 
+equivalent plot using the Toburen numbers $n_e$ of Table~\ref{nn} does not 
+exhibit the straight lines obtained with the present scaling. The 
+comparison with the 
 experimental data available shows overall good agreement, for the 
@@
 
+\bibitem{galassi2000}
+M. E. Galasssi, R. D. Rivarola, M. Beuve, G. H. Olivera and P. D. Fainstein, 
+Phys. Rev. A \textbf{62}, 022701 (2000).
+
+\bibitem{ludde2016}
+H. J. L\"udde, A. Achenbach, T. Kalkbrenner, H.-C. Jankowiak and T. Kirchner,
+Eur. Phys. J. D \textbf{70}, 82 (2016).
+
+\bibitem{ludde2018}
+H. J. L\"udde, M. Horbatsch and T. Kirchner,
+Eur. Phys. J. B \textbf{91}, 99 (2018).
+
 \bibitem{fainstein1988}
@@
 Phys. Rev. E \textbf{97}, 032403 (2018)
+
+\bibitem{janev1980}
+R. K. Janev and L. P. Presnyakov 
+J. Phys. B \textbf{13}, 4233 (1980).
+
+\bibitem{dubois2013}
+R. D. DuBois, E. C. Montenegro and G. M. Sigaud,
+AIP Conference Proceeding \textbf{1525}, 679 (2013).
 

### 2019-11-22 submit_jpb/response.txt

Referee 1:

We thank the referee for the comments on our manuscript. Please find below our reply to his/her observations.

The present work considers fully stripped ions. Indeed, this may be considered as a weakness of our calculations. Nonetheless, we plan to extend our theoretical approach to partially stripped ions in the future.

Detailed reply:

1) We have changed the wording of our findings in the corresponding sections.

2) The grammatical error was corrected.

3a) The dependence of the mean energy with the projectile charge at intermediate energy reflects the non-linear dependence on E and ZP of the continuum state in the CDW approximation. Then, the dependence of the numerator and the denominator on ZP is not canceled out, which explains the maximum in Fig. 2. On the contrary, the behavior at high energy follows the Z^2 rule, and the mean energy distribution tends to a universal value for all ions, as noted on page 3.
3b) We included a few sentences discussing the usefulness of understanding the relationship between the mean energy and angle distribution of secondary electrons with the radiation damage.

4) The denominator in Eq. 4 is the same as in Eq. 3: the total cross-section. They are both integrated on different variables. We have included the expression of the normalization of the angular distribution.

5) We defined the dotted line accordingly.

6a) We included the reference to Table I in the caption.
6b) In general, the curves within each scaling band are ordered from the smallest to the largest. For the hydrocarbons, this behavior holds for both scalings since n_e for carbon does not change. However, this is not always the case (see, for example, adenine C5H5N5, uracil C4H4N2O2, and DNA backbone C5H10O5P in Fig. 1 attached). 
6c) Upon the suggestion of the referee, we included the Toburen numbers in Table II. The inclusion of the band by Toburen, together with the new scaling, was too confusing and finally decided not to modify the figure.

7) We included the Toburen scaling in Fig. 2, attached. The x-axis 
refers to the number of active electrons, whether they are from the 
Toburen or the CDW scaling. As seen, the scaling by Toburen is not as good as ours, which follows Fig. 6. To avoid having too many curves, 
we decided not to modify Fig. 7, but we comment on these differences 
in the manuscript: "An equivalent plot using the Toburen numbers n_e of Table II does not exhibit the straight lines obtained with
the present scaling."

8) We appreciate the suggestion of the scaling with Z at intermediate energies. We check it for the molecules in Figs. 4 and 5. We decided to include a new figure for DNA bases. We will continue to investigate the scope and limitation of this scaling for different biological molecules.

Referee 2:

We decided to include in the introduction a comment about different previous work combining atomic cross sections to obtain molecular ones by Galassi et al. and Ludde et al.
"Different approaches have been proposed to deal with the ionization of molecular targets within the independent atom model. For example, Galassi et al. [1] obtain molecular cross sections by combining CDW-EIS atomic ones based on the population of the molecular orbitals. Much more recently, Ludde et al. [2, 3] propose a combination of atomic cross sections with geometrical screening correction."

### 2019-11-22 ionmol_stoi.tex
include C6+ reference to manuscript

@@
 and experimental studies with different projectiles have concluded that 
-charged carbon ions could be the most suitable ions to be used. 
+charged carbon ions could be the most suitable ions to be used~\cite{Mohamad2017}. 
 Nonetheless, the study of such systems represents a challenge from the 
@@
 
+\bibitem{Mohamad2017}
+O. Mohamad, B. J. Sishc, J. Saha, A. Pompos, A. Rahimi, M. D. Story, A. J. Davis, D. N. Kim, 
+Carbon Ion Radiotherapy: A Review of Clinical Experiences and Preclinical Research, with an Emphasis on DNA Damage/Repair. 
+Cancers \textbf{9}, 66 (2017).
+
 \bibitem{galassi2000}
@@
 \bibitem{miraglia2008} 
-J. E. Miraglia and M. S. Gravielle. Ionization of the
-He, Ne, Ar, Kr, and Xe isoelectronic series by proton impact. 
+J. E. Miraglia and M. S. Gravielle. 
+Ionization of the He, Ne, Ar, Kr, and Xe isoelectronic series by proton impact. 
 Phys Rev A \textbf{78}, 052705 (2008)
@@
 \bibitem{toburen1975} 
-W. E. Wilson and L. H. Toburen. Electron emission from
-proton --hydrocarbon-molecule collisions at 0.3--2.0 MeV. 
+W. E. Wilson and L. H. Toburen. 
+Electron emission from proton --hydrocarbon-molecule collisions at 0.3--2.0 MeV. 
 Phys. Rev. A \textbf{11}, 1303 (1975).
@@
 \bibitem{toburen1976} 
-D. J. Lynch, L. H. Toburen, and W. E. Wilson. Electron
-emission from methane, ammonia, monomethylamine, and dimethylamine by 0.25
+D. J. Lynch, L. H. Toburen, and W. E. Wilson. 
+Electron emission from methane, ammonia, monomethylamine, and dimethylamine by 0.25
 to 2.0 MeV protons. 
@@
 A.M.P. Mendez, D.M. Mitnik, and J.E. Miraglia. 
-Local Effective Hartree--Fock Potentials Obtained by the Depurated 
-Inversion Method,
+Local Effective Hartree--Fock Potentials Obtained by the Depurated Inversion Method,
 Adv. Quant. Chem. \textbf{76}, 117--132 (2018).
@@
 C. C. Montanari, J. E. Miraglia,
-Ionization probabilities of Ne, Ar, Kr, and Xe by
-proton impact for different initial states and impact energies. 
+Ionization probabilities of Ne, Ar, Kr, and Xe by proton impact for different initial states and impact energies. 
 Nucl. Instr. Meth. Phys. Res. B \textbf{407}, 236--243 (2017).
@@
 \bibitem{miraglia2019} 
-J. E. Miraglia. Shell-to-shell ionization cross
-sections of antiprotons, H$^{+}$, He$^{2+},$ Be$^{4+},$ C$^{6+}$ and 
+J. E. Miraglia,
+Shell-to-shell ionization cross sections of antiprotons, H$^{+}$, He$^{2+},$ Be$^{4+},$ C$^{6+}$ and 
 O$^{8+}$ on H, C, N, O, P, and S atoms (to be published).
@@
 \bibitem{surdutovic2018} 
-Multiscale approach to the physics of radiation
-damage with ions. E. Surdutovich and A. V. Solov'yov, 
+E. Surdutovich and A. V. Solov'yov, 
+Multiscale approach to the physics of radiation damage with ions. 
 arXiv:1312.0897v, (2013)
@@
 P. de Vera1, I. Abril, R. Garcia-Molina and
-A.V.Solov'yov,\ Ionization of biomolecular targets by ion impact: input data
-for radiobiological applications. 
+A. V. Solov'yov,
+Ionization of biomolecular targets by ion impact: input data for radiobiological applications. 
 Journal of Physics: Conference Series \textbf{438}, 012015 (2013).
@@
 M. E. Rudd, Y.-K. Kim,, D. H. Madison and T. J. Gay.
-Electron production in proton collisions with atoms and molecules: energy
-distributions. 
+Electron production in proton collisions with atoms and molecules: energy distributions. 
 Rev. Mod. Phys. \textbf{64}, 44--490 (1992).
@@
 H. Q. Tan, Z. Mi, and A. A. Bettiol, 
-Simple and universal model for electron-impact ionization of complex 
-biomolecules, 
+Simple and universal model for electron-impact ionization of complex biomolecules, 
 Phys. Rev. E \textbf{97}, 032403 (2018)

### 2019-12-02 submit_jpb/reviewers/response.txt
include Z scaling work

--- 2019-11-22 submit_jpb/response.txt
@@
 
-We thank the referee for the comments on our manuscript. Please find below our reply to his/her observations.
-
+We thank the referee for the comments on our manuscript.
 The present work considers fully stripped ions.
@@
 Nonetheless, we plan to extend our theoretical approach to partially stripped ions in the future.
+Please find below our reply to his/her observations.
 
@@
 3b) We included a few sentences discussing the usefulness of understanding the relationship between the mean energy and angle distribution of secondary electrons with the radiation damage. 
+3) We included a reference on radiation damage in the introduction as well.
 
@@
 3: the total cross-section.
-They are both integrated on different variables.
-We have included the expression of the normalization of the angular distribution.
+However, they are both integrated on different variables.
+We have included the corresponding expression of the normalization of the angular distribution.
 
@@
 For the hydrocarbons, this behavior holds for both scalings since n_e for carbon does not change.
-However, this is not always the case (see, for example, adenine C5H5N5, uracil C4H4N2O2, and DNA backbone C5H10O5P in Fig.
-1 attached).
+However, this is not always the case (see, for example, adenine C5H5N5, uracil C4H4N2O2, and DNA backbone C5H10O5P in figure A attached).
 6c) Upon the suggestion of the referee, we included the Toburen numbers in Table II.
@@
 
-7) We included the Toburen scaling in Fig. 2, attached. The x-axis 
-refers to the number of active electrons, whether they are from the 
-Toburen or the CDW scaling. As seen, the scaling by Toburen is not as good as ours, which follows Fig. 6. To avoid having too many curves, 
-we decided not to modify Fig. 7, but we comment on these differences 
-in the manuscript: "An equivalent plot using the Toburen numbers n_e of Table II does not exhibit the straight lines obtained with
-the present scaling."
+7) We included the Toburen scaling in figure B, attached.
+The x-axis refers to the number of active electrons, whether they are from the Toburen or the CDW scaling.
+As seen, the scaling by Toburen is not as good as ours, which follows Fig.
+6.
+To avoid having too many curves, we decided not to modify Fig.
+7, but we comment on these differences in the manuscript:
+"An equivalent plot using the Toburen numbers n_e of Table II does not exhibit the straight lines obtained with the present scaling."
 
-8) We appreciate the suggestion of the scaling with Z at intermediate energies.
-We check it for the molecules in Figs.
-4 and 5.
-We decided to include a new figure for DNA bases.
-We will continue to investigate the scope and limitation of this scaling for different biological molecules.
+8) We appreciate the suggestion of the Z-scaling at intermediate energies. We are currently investigating its implementation. We refer to it in the manuscript by including the sentences:
+"At intermediate impact energies, the Z^2 rule no longer holds, and other scalings can be considered in this region.
+For example, the molecular cross section and ion impact energy can be reduced with the projectile charge Z, as suggested in [33, 34]."
 
@@
 For example, Galassi et al.
-[1] obtain molecular cross sections by combining CDW-EIS atomic ones based on the population of the molecular orbitals.
-Much more recently, Ludde et al.
-[2, 3] propose a combination of atomic cross sections with geometrical screening correction."
+[2] obtain molecular cross sections by combining CDW-EIS atomic ones based on the population of the molecular orbitals.
+More recently, Lüdde et al.
+[3, 4] propose a combination of atomic cross sections with geometrical screening corrections."

### 2019-12-02 ionmol_stoi.tex
include Z scaling work

@@
-%\documentclass[pra,showpacs,twocolumn]{revtex4}
-%\documentclass[pra,showpacs]{revtex4}
-%\documentclass[preprint,showpacs]{revtex4}
-\documentclass[10pt,showpacs,twocolumn]{revtex4}
+\documentclass[10pt,showpacs,showkeys,twocolumn]{revtex4}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \author{A. M. P. Mendez, C. C. Montanari, J. E. Miraglia}
-\address{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio 
+\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio 
 (CONICET--UBA), \\ Buenos Aires, Argentina.}
@@
 distorted--wave calculations (CDW) for thirty--six collisional systems 
-composed by six atomic targets: H, C, N, O, F and S --which are the 
+composed by six atomic targets: H, C, N, O, F, and S --which are the 
 constituents of most of the DNA and biological molecules-- and six 
@@
 weakly bound electrons. Based on the atomic CDW results, we 
-propose new active electron numbers, which leads to a more universal 
+propose new active electron numbers, which leads to a better universal 
 scaling for all the targets and ions studied here in the intermediate 
@@
 
-%\keywords{magnetic moment, solar neutrinos, astrophysics}
+\keywords{DNA bases, DNA ionization, stoichiometric model, 
+multicharged ions, biological molecules, ionization of molecules}
 \pacs{34.50Gb, 34.80Gs, 34.80Dp}
@@
 molecular targets within the independent atom model. For example, 
-Galassi \textit{et al.} \cite{galassi2000} obtains molecular cross 
+Galassi \textit{et al.} \cite{galassi2000} obtain molecular cross 
 sections by combining CDW-EIS atomic ones based on the population of 
-the molecular orbitals. Much more recently, L\"udde \textit{et al.} 
+the molecular orbitals. More recently, L\"udde \textit{et al.} 
 \cite{ludde2016,ludde2018} 
@@
 
-The objective of this article is to deal with two aspects; first, we perform 
+The objective of this article is to face with two aspects of the ionization
+of biological molecules; first, we perform 
 more appropriate calculations on the primary damage mechanism, which can 
@@
 
-To overcome the first perturbative approximation limitations, and since 
-the projectiles are multicharged ions, we resort to the Continuum 
-Distorted Wave--Eikonal Initial State 
-(CDW)~\cite{fainstein1988,miraglia2008,miraglia2009}, which includes higher 
-perturbative corrections. Details on the CDW calculation are given in 
-Section~\ref{sec:atoms}.
+To overcome the limitations of first order perturbative approximations, 
+and since the projectiles are multicharged ions, we resort to the 
+Continuum Distorted Wave--Eikonal Initial State 
+(CDW)~\cite{galassi2000,fainstein1988,miraglia2008,miraglia2009}, which 
+includes higher perturbative corrections. Details on the CDW calculation 
+are given in Section~\ref{sec:atoms}.
 We start from the premise that the ionization 
@@
 primary energy. Moreover, the residual electrons from the ionization 
-are known to be a source of significant local biological damage. 
+are known to be a source of significant local biological damage~\cite{Denifl2011}. 
 The secondary electrons are included in Monte Carlo simulations, 
@@
 for just a fraction of the overall damage. Secondary electrons, as well 
-as recoil target ions, also contribute substantially to the total damage. 
+as recoil target ions, also contribute substantially to the total damage~\cite{Denifl2011}. 
 We can consider the single differential cross section of the shell 
@@
 six atoms and six ions of interest are shown in Fig.~\ref{fig:emittedang}.
-An significant dependence of $\overline{\theta}_{\alpha}$ with $Z$ is 
+A significant dependence of $\overline{\theta}_{\alpha}$ with $Z$ is 
 noticed for all the cases. Once again, this effect could not be 
@@
 
-It is a general belief~\cite{Rudd1992} that the 
-angular dispersion of emitted electrons is nearly isotropic. This 
-behavior is thought to be caused by the insignificant angular anisotropy 
-of sub--50--eV yield. 
+For low energy electron emission, the angular dispersion is nearly 
+isotropic~\cite{Rudd1992}.
 A typical value for the ejection angle considered in the literature is 
@@
 in the intermediate energy region, as shown in Fig.~\ref{fig:emittedang}.
-
-To illustrate these effects, consider the impact of C$^{6+}$ impact on oxygen.
-At an impact energy of 500~keV, the first Born approximation predicts
-emitted electrons with mean energies of 46.7 eV and mean angles of 78\degree, 
-while the CDW gives 62.5 eV and 60\degree. 
-These results imply depper penetration closer to the direction of the ion.
-We can attribute this forward direction correction to the capture to 
-the continuum effect; the higher the charge $Z$, the smaller 
+The higher the charge $Z$, the smaller 
 $\overline{\theta}$ will be. Of course, this effect only holds at 
 intermediate energies and not at high impact energies.
+
+To illustrate this feature, consider the impact of 500~keV C$^{6+}$ on 
+oxygen. The first Born approximation predicts emitted electrons with 
+mean energies of 46.7 eV and mean angles of 78\degree, while the CDW 
+gives 62.5 eV and 60\degree. 
+These results imply deeper penetration of the secondary electrons with 
+an orientation closer to the direction of the ion. 
+We can attribute this forward direction correction to the capture to 
+the continuum effect.
 
@@
 In Fig.~\ref{fig:crossDNA_1}, we report the reduced total ionization cross 
-sections $\sigma_M/Z^2$ by the impact of multicharged ions for adenine,
-cytosine, 
-guanine, and thymine, by combining the SSM and CDW results in 
-Eq.~\ref{eq:sumion}. For adenine, the agreement with the experimental 
+sections $\sigma_M/Z^2$ for adenine, cytosine, guanine, and thymine 
+by the impact of multicharged ions obtained combining the SSM given by 
+Eq.~(\ref{eq:sumion}) and the CDW results. For adenine, the agreement 
+with the experimental 
 data available for proton impact~\cite{iriki2011} is excellent. To the 
@@
 predictions~\cite{mozejko2003,tan2018}.
-
-At intermediate impact energies, the $Z^2$ rule no longer holds and other 
-scalings can be considered in this region. 
-In Fig.~\ref{fig:Zcaled_crossDNA_1}, we plotted the reduced ionization 
-cross section $\sigma_M/Z$ as a function of the reduced ion impact energy
-$E/Z$ as suggested by~\cite{janev1980,dubois2013}.
-This scaling may be a good alternative to deal with highly charged
-ions at intermediate energies in a coherent way.
 
@@
 
+At intermediate impact energies, the $Z^2$ rule no longer holds, and 
+other scalings can be considered in this region. For example, the 
+molecular cross section and ion impact energy can be reduced with the
+projectile charge $Z$, as suggested in in~\cite{janev1980,dubois2013}.
+
 \begin{figure*}[t!]
@@
 \label{fig:crossDNA_1}
-\end{figure*}
-
-\begin{figure*}[t!]
-\centering
-\includegraphics[width=0.8\textwidth]{figuras/Zscaling_adn1.eps}
-\caption{Reduced CDW ionization cross section $\sigma_{M}/Z$ as a function 
-of reduced ion impact energy $E/Z$. 
-Experiments: \mbox{\Large$\circ$}~\cite{iriki2011} 
-for proton impact and $\square$~\cite{rahman2016} for electron impact 
-with equivelocity conversion.}
-\label{fig:Zcaled_crossDNA_1}
 \end{figure*}
@@
 By using Eq.~(\ref{eq:scalingCDW}), we define new active electron 
-numbers $n_e'$ for some molecules of interest in Table~\ref{nn}. These 
-values are different from the ones proposed by Toburen and used by 
-other authors~\cite{itoh2013}. Moreover, an alternative way of showing 
-the scaling can be attained by plotting the ionization cross sections 
-of molecules as a function of the number of active electrons from 
-Table~\ref{nn}. Our findings are displayed in Fig.~\ref{fig:recta} for 
+numbers $n_e'$ for molecules. In Table~\ref{nn}, we display the present 
+$n_e'$ values and $n_e$ ones by Toburen obtained from Eq.~(\ref{eq:nelec}).
+Our values are different from the ones proposed by Toburen and used by 
+other authors~\cite{itoh2013}, mainly due to the differences in the 
+active electron numbers of oxygen. An alternative way of testing 
+the present scaling can be attained by plotting the ionization cross sections 
+of molecules as a function of the $n_e'$ from Table~\ref{nn}. Our 
+findings are displayed in Fig.~\ref{fig:recta} for 
 impact energies 0.5, 1, and 2 MeV. As can be noted, the computed CDW 
@@
 dependence with the number of electrons $n_e'$ from Table~\ref{nn}.
-We obtain similar results, even for $E=10$~MeV. An 
-equivalent plot using the Toburen numbers $n_e$ of Table~\ref{nn} does not 
-exhibit the straight lines obtained with the present scaling. The 
-comparison with the 
+We obtain similar results, even for $E=10$~MeV. The comparison with the 
 experimental data available shows overall good agreement, for the 
@@
 interpolated between close neighbors.
+It is worth mentioning that an equivalent plot using the Toburen numbers 
+$n_e$ does not exhibit the straight lines obtained with the present scaling.
 
 While finishing the present work, we became aware of an accepted manuscript by 
-Luedde~{\it et al.}~\cite{luedde2019} on total ionization of biological
-molecules by proton impact, using an independent--atom--model pixel counting
-method. The authors also raised a scaling with $\nu_{\alpha}=4$ 
+L\"udde~{\it et al.}~\cite{ludde2019} on total ionization of biological
+molecules by proton impact, using the independent--atom--model pixel counting
+method~\cite{ludde2016,ludde2018}. The authors also raised a scaling 
+with $\nu_{\alpha}=4$ 
 for C, N, and O, but $\nu_{\alpha}=6$ for P. The agreement with this 
@@
 
-To test the range of validity of the SSM, we performed {\it ab initio}
+Finally, to test the range of validity of the SSM, we performed {\it ab initio}
 molecular calculation of five nucleobases by employing the {\sc gamess} 
@@
 
+\begin{table*}[t]
+\begin{center}
+\begin{tabular}{|p{0.08\textwidth}|p{0.05\textwidth}|p{0.05\textwidth}|p{
+0.05\textwidth}|p{0.05\textwidth}|p{0.19\textwidth}|}
+\hline
+Element & C & H & N & O & New stoichiometry \\
+\hline
+Adenine & +0.32 & +0.23 & --0.55 &       & 
+C$_{4.92}$H$_{4.77}$N$_{5.14}$ \\ 
+\hline
+Cytosine & +0.28 & +0.21 & --0.56 & --0.53 & 
+C$_{3.93}$H$_{4.79}$N$_{3.14}$O$_{1.13}$ \\ 
+\hline
+Guanine & +0.46 & +0.20 & --0.58 & --0.36 & 
+C$_{4.89}$H$_{4.80}$N$_{5.15}$O$_{1.09}$ \\ 
+\hline
+Thymine & +0.20 & +0.19 & --0.54 & --0.52 & 
+C$_{4.95}$H$_{5.81}$N$_{2.13}$O$_{2.13}$ \\ 
+\hline
+Uracil & +0.31 & +0.22 & --0.59 & --0.47 & 
+C$_{3.92}$H$_{3.78}$N$_{2.15}$O$_{2.12}$ \\ 
+\hline
+\end{tabular}
+\caption{Average effective Mulliken charge per atom $q_{\alpha}$, and 
+new stoichiometric formula defined by Eq.~(\ref{eq:newstoi}) for five 
+DNA molecules.}
+\label{tab:newstoi}
+\end{center}
+\end{table*}
+
 To take this effect into account, we can consider that the total amount 
@@
 
-\begin{table*}[t]
-\begin{center}
-\begin{tabular}{|p{0.08\textwidth}|p{0.05\textwidth}|p{0.05\textwidth}|p{
-0.05\textwidth}|p{0.05\textwidth}|p{0.19\textwidth}|}
-\hline
-Element & C & H & N & O & New stoichiometry \\
-\hline
-Adenine & +0.32 & +0.23 & --0.55 &       & 
-C$_{4.92}$H$_{4.77}$N$_{5.14}$ \\ 
-\hline
-Cytosine & +0.28 & +0.21 & --0.56 & --0.53 & 
-C$_{3.93}$H$_{4.79}$N$_{3.14}$O$_{1.13}$ \\ 
-\hline
-Guanine & +0.46 & +0.20 & --0.58 & --0.36 & 
-C$_{4.89}$H$_{4.80}$N$_{5.15}$O$_{1.09}$ \\ 
-\hline
-Thymine & +0.20 & +0.19 & --0.54 & --0.52 & 
-C$_{4.95}$H$_{5.81}$N$_{2.13}$O$_{2.13}$ \\ 
-\hline
-Uracil & +0.31 & +0.22 & --0.59 & --0.47 & 
-C$_{3.92}$H$_{3.78}$N$_{2.15}$O$_{2.12}$ \\ 
-\hline
-\end{tabular}
-\caption{Average effective Mulliken charge per atom $q_{\alpha}$, and 
-new stoichiometric formula defined by Eq.~(\ref{eq:newstoi}) for five 
-DNA molecules.}
-\label{tab:newstoi}
-\end{center}
-\end{table*}
-
 By implementing Eq.~(\ref{eq:newstoi}), it is possible to determine a 
@@
 computed for the DNA bases from Table~\ref{tab:newstoi}. The differences 
-obtained were less than 3\%, which indicates that the modified 
+obtained were less than 3\%, which indicates that the  
 SSM is a quite robust model to handle these type of molecules within 
@@
 The mean energy and angle of the emitted electrons, of importance in 
-post--collisional radiation damage,  has also been calculated, showing 
-a clear dependence with the ion charge $Z$. For a given target as $Z$ 
-increases, $\overline{E}_{\alpha}$
-increases, but $\overline{\theta}_{\alpha}$ decreases, showing a clear 
-tendency to the forward direction. At impact
-energies greater than 2 MeV/amu, these values converge to the Born
-approximation, which embodies the simple $Z^{2}$ law.
+post--collisional radiation damage,  has also been calculated. Our 
+findings show a clear dependence with the ion charge $Z$. For a given 
+target as $Z$ increases, $\overline{E}_{\alpha}$ also increases, but 
+$\overline{\theta}_{\alpha}$ decreases, showing a clear tendency to the 
+forward direction. At impact energies greater than 2 MeV/amu, these 
+values converge to the Born approximation, which embodies the simple 
+$Z^{2}$ law.
 
@@
 uracil, DNA backbone, pyrimidine, and THF are presented and compared 
-with the scarcely available experiments. We explore the rule of 
+with the scarcely available experiments. We explored the rule of 
 Toburen, which scales all the molecular ionization cross section 
@@
 projectiles and seventeen molecules studied here. The comparison with 
-the experimental data reinforce these results. Furthermore, we also tested
+the experimental data reinforce our findings. Furthermore, we tested
 the scaling by including experimental data of ionization of H$_2$, 
@@
 O. Mohamad, B. J. Sishc, J. Saha, A. Pompos, A. Rahimi, M. D. Story, A. J. Davis, D. N. Kim, 
-Carbon Ion Radiotherapy: A Review of Clinical Experiences and Preclinical Research, with an Emphasis on DNA Damage/Repair. 
+%Carbon Ion Radiotherapy: A Review of Clinical Experiences and Preclinical Research, with an Emphasis on DNA Damage/Repair. 
 Cancers \textbf{9}, 66 (2017).
@@
 J. E. Miraglia and M. S. Gravielle. 
-Ionization of the He, Ne, Ar, Kr, and Xe isoelectronic series by proton impact. 
+%Ionization of the He, Ne, Ar, Kr, and Xe isoelectronic series by proton impact. 
 Phys Rev A \textbf{78}, 052705 (2008)
@@
 \bibitem{miraglia2009} 
-J. E. Miraglia, Ionization of He, Ne, Ar, Kr, and Xe
-by proton impact: Single differential distributions. 
+J. E. Miraglia, 
+%Ionization of He, Ne, Ar, Kr, and Xe by proton impact: Single differential distributions. 
 Phys. Rev. A \textbf{79}, 022708 (2009).
+
+\bibitem{Denifl2011}
+Denifl S., Märk T.D., Scheier P. 
+The Role of Secondary Electrons in Radiation Damage. 
+In Radiation Damage in Biomolecular Systems. Biological and Medical Physics, Biomedical Engineering. 
+Eds: García Gómez-Tejedor G., Fuss M. 
+Springer, Dordrecht (2012)
 
@@
 W. E. Wilson and L. H. Toburen. 
-Electron emission from proton --hydrocarbon-molecule collisions at 0.3--2.0 MeV. 
+%Electron emission from proton --hydrocarbon-molecule collisions at 0.3--2.0 MeV. 
 Phys. Rev. A \textbf{11}, 1303 (1975).
@@
 D. J. Lynch, L. H. Toburen, and W. E. Wilson. 
-Electron emission from methane, ammonia, monomethylamine, and dimethylamine by 0.25
-to 2.0 MeV protons. 
+%Electron emission from methane, ammonia, monomethylamine, and dimethylamine by 0.25 to 2.0 MeV protons. 
 J. Chem. Phys. \textbf{64}, 2616 (1976).
@@
 A.M.P. Mendez, D.M. Mitnik, and J.E. Miraglia.
-Depurated inversion method for orbital-specific exchange potentials. 
+%Depurated inversion method for orbital-specific exchange potentials. 
 Int. J. Quantum Chem. \textbf{24} ,116 (2016).
@@
 A.M.P. Mendez, D.M. Mitnik, and J.E. Miraglia. 
-Local Effective Hartree--Fock Potentials Obtained by the Depurated Inversion Method,
+%Local Effective Hartree--Fock Potentials Obtained by the Depurated Inversion Method,
 Adv. Quant. Chem. \textbf{76}, 117--132 (2018).
@@
 C. C. Montanari, J. E. Miraglia,
-Ionization probabilities of Ne, Ar, Kr, and Xe by proton impact for different initial states and impact energies. 
+%Ionization probabilities of Ne, Ar, Kr, and Xe by proton impact for different initial states and impact energies. 
 Nucl. Instr. Meth. Phys. Res. B \textbf{407}, 236--243 (2017).
@@
 J. E. Miraglia,
-Shell-to-shell ionization cross sections of antiprotons, H$^{+}$, He$^{2+},$ Be$^{4+},$ C$^{6+}$ and 
+%Shell-to-shell ionization cross sections of antiprotons, H$^{+}$, He$^{2+},$ Be$^{4+},$ C$^{6+}$ and 
 O$^{8+}$ on H, C, N, O, P, and S atoms (to be published).
@@
 E. Surdutovich and A. V. Solov'yov, 
-Multiscale approach to the physics of radiation damage with ions. 
+%Multiscale approach to the physics of radiation damage with ions. 
 arXiv:1312.0897v, (2013)
@@
 \bibitem{abril2015} 
-P. de Vera1, I. Abril, R. Garcia-Molina and
-A. V. Solov'yov,
-Ionization of biomolecular targets by ion impact: input data for radiobiological applications. 
+P. de Vera, I. Abril, R. Garcia-Molina and A. V. Solov'yov,
+%Ionization of biomolecular targets by ion impact: input data for radiobiological applications. 
 Journal of Physics: Conference Series \textbf{438}, 012015 (2013).
@@
 M. E. Rudd, Y.-K. Kim,, D. H. Madison and T. J. Gay.
-Electron production in proton collisions with atoms and molecules: energy distributions. 
-Rev. Mod. Phys. \textbf{64}, 44--490 (1992).
+%Electron production in proton collisions with atoms and molecules: energy distributions. 
+Rev. Mod. Phys. \textbf{64}, 441--490 (1992).
 
@@
 P. Mozejko and L. Sanche, 
-Cross section calculations for electron scattering from DNA and RNA bases.
+%Cross section calculations for electron scattering from DNA and RNA bases.
 Radiat Environ. Biophys \textbf{42}, 201 (2003).
@@
 H. Q. Tan, Z. Mi, and A. A. Bettiol, 
-Simple and universal model for electron-impact ionization of complex biomolecules, 
+%Simple and universal model for electron-impact ionization of complex biomolecules, 
 Phys. Rev. E \textbf{97}, 032403 (2018)
-
-\bibitem{janev1980}
-R. K. Janev and L. P. Presnyakov 
-J. Phys. B \textbf{13}, 4233 (1980).
-
-\bibitem{dubois2013}
-R. D. DuBois, E. C. Montenegro and G. M. Sigaud,
-AIP Conference Proceeding \textbf{1525}, 679 (2013).
 
@@
 A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D. Rivarola, 
-Cross sections for ionization of uracil by MeV-energy-proton impact, 
+%Cross sections for ionization of uracil by MeV-energy-proton impact, 
 Phys. Rev. A \textbf{88}, 052711 (2013).
@@
 H. Lekadir, P. F. Weck, and L. C. Tribedi. 
-Ionization of uracil in collisions with highly charged carbon and oxygen 
-ions of energy 100 keV to 78 MeV. 
+%Ionization of uracil in collisions with highly charged carbon and oxygen ions of energy 100 keV to 78 MeV. 
 Phys. Rev. A \textbf{85}, 032711 (2012).
@@
 J Hanssen, P FWeck, M E Galassi, R D Rivarola, O Fojon and L C Tribedi, 
-Absolute total ionization cross sections of uracil (C$_4$H$_4$N$_2$O$_2$) in 
-collisions with MeV energy highly charged carbon, oxygen and fluorine ions
+%Absolute total ionization cross sections of uracil (C$_4$H$_4$N$_2$O$_2$) in collisions with MeV energy highly charged carbon, oxygen and fluorine ions
 J. Phys. B \textbf{46}, 185201 (2013).
@@
 P F Weck, A N Agnihotri, S Nandi, and L C Tribedi. 
-Ionization of RNA-uracil by highly charged carbon ions.
+%Ionization of RNA-uracil by highly charged carbon ions.
 J. Phys.: Conf. Ser. \textbf{373}, 012004 (2012).
@@
 W. Wolff, H. Luna, L. Sigaud, A. C. Tavares, and E. C. Montenegro
-Absolute total and partial dissociative cross sections of pyrimidine
-at electron and proton intermediate impact velocities
+%Absolute total and partial dissociative cross sections of pyrimidine at electron and proton intermediate impact velocities
 J. Chem. Phys. \textbf{140}, 064309 (2014).
@@
 M. U. Bug, W. Y. Baek, H. Rabus, C. Villagrasa, S. Meylan, A. B. Rosenfeld,
-An electron-impact cross section data set (10 eV--1 keV) of DNA
-constituents based on consistent experimental data: A requisite for 
-Monte Carlo simulations,
+%An electron-impact cross section data set (10 eV--1 keV) of DNA constituents based on consistent experimental data: A requisite for Monte Carlo simulations,
 Rad. Phys. Chem. \textbf{130}, 459--479 (2017).
@@
 G. Hilgers, H. Rabus, 
-Cross sections for ionization of tetrahydrofuran by protons at energies 
-between 300 and 3000 keV
+%Cross sections for ionization of tetrahydrofuran by protons at energies between 300 and 3000 keV
 Phys. Rev. A \textbf{93}, 052711 (2016).
@@
 M. G. P. Homem,
-Absolute ionization and dissociation cross sections of tetrahydrofuran:
-Fragmentation--ion production mechanisms
+%Absolute ionization and dissociation cross sections of tetrahydrofuran: Fragmentation--ion production mechanisms
 J. Chem. Phys. \textbf{151}, 064304 (2019).
@@
 T. P. D. Do, M. J. Brunger, G. Garc\'{i}a,
-Electron-scattering cross sections for collisions with tetrahydrofuran 
-from 50 to 5000 eV
+%Electron-scattering cross sections for collisions with tetrahydrofuran from 50 to 5000 eV
 Phys. Rev. A \textbf{80}, 052709 (2009).
+
+\bibitem{janev1980}
+R. K. Janev and L. P. Presnyakov 
+J. Phys. B \textbf{13}, 4233 (1980).
+
+\bibitem{dubois2013}
+R. D. DuBois, E. C. Montenegro and G. M. Sigaud,
+AIP Conference Proceeding \textbf{1525}, 679 (2013).
 
@@
 D. J. Lynch, L. H. Toburen, and W. E. Wilson,
-Electron emission from methane, ammonia, monomethylamine, and
-dimethylamine by 0.25 to 2.0 MeV protons
+%Electron emission from methane, ammonia, monomethylamine, and dimethylamine by 0.25 to 2.0 MeV protons
 J. Chem. Phys. \textbf{64}, 2616 (1976).
@@
 M.E. Rudd, Y.-K. Kim, D.H. Madison, J.W. Gallagher,
-Electron production in proton collisions: total cross sections,
+%Electron production in proton collisions: total cross sections,
 Review of Modern Physics, \textbf{57}, 965--994 (1985).
@@
 C. J. Latimer, and E. C. Montenegro,
-Water-molecule dissociation by proton and hydrogen impact,
+%Water-molecule dissociation by proton and hydrogen impact,
 Phys. Rev. A \textbf{75}, 042711 (2007).
 
-\bibitem{luedde2019}
-H J Luedde {\it et al.} 2019 
+\bibitem{ludde2019}
+H J L\"udde {\it et al.} 2019 
 J. Phys. B: At. Mol. Opt. Phys. in press 
@@
 Hush, N.S.; Cheung, A.S., 
-Ionization potentials and donor properties of nucleic acid bases and 
-related compounds, 
+%Ionization potentials and donor properties of nucleic acid bases and related compounds, 
 Chem. Phys. Lett., \textbf{34}, 11 (1975).
@@
 Verkin, B.I.; Sukodub, L.F.; Yanson, I.K., 
-Ionization potentials of nitrogenous bases of of nucleic acids, 
-Dokl. Akad. Nauk SSSR, \textbf{228}, 1452 (1976).
+%Ionization potentials of nitrogenous bases of of nucleic acids, Dokl. Akad. Nauk SSSR, \textbf{228}, 1452 (1976).
 
@@
 Dougherty, D.; Younathan, E.S.; Voll, R.; Abdulnur, S.; McGlynn, S.P., 
-Photoelectron spectroscopy of some biological molecules, 
+%Photoelectron spectroscopy of some biological molecules, 
 J. Electron Spectrosc. Relat. Phenom., \textbf{13}, 379 (1978).
@@
 Jung-Goo Lee, Ho Young Jeong, and Hosull Lee, Charges of
-Large Molecules Using Reassociation of Fragments. 
+%Large Molecules Using Reassociation of Fragments. 
 Bull. Korean Chem. Soc. \textbf{24}, 369 (2003).

### 2019-12-02 submit_jpb/revsubmission/ionmol_stoi.tex
include Z scaling work

--- 2019-12-02 ionmol_stoi.tex
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figuras/atomicscaling.eps}
+\includegraphics[width=0.8\textwidth]{atomicscaling.eps}
 \caption{Reduced CDW total ionization cross section $\sigma_{\alpha}/Z^2$ 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figuras/ener_mean.eps}
+\includegraphics[width=0.8\textwidth]{ener_mean.eps}
 \caption{Mean emitted energy distribution for ionization by the impact 
@@
 \label{fig:emittedener}
+\end{figure*}
+
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=0.8\textwidth]{ang_mean.eps}
+\caption{Mean emitted angle distribution for ionization by impact of
+multicharged ions. Curves as in Fig.~\ref{fig:emittedener}.}
+\label{fig:emittedang}
 \end{figure*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}[t!]
-\centering
-\includegraphics[width=0.8\textwidth]{figuras/ang_mean.eps}
-\caption{Mean emitted angle distribution for ionization by impact of
-multicharged ions. Curves as in Fig.~\ref{fig:emittedener}.}
-\label{fig:emittedang}
-\end{figure*}
 
@@
 
-For low energy electron emission, the angular dispersion is nearly 
-isotropic~\cite{Rudd1992}.
+It is a general belief~\cite{Rudd1992} that the 
+angular dispersion of emitted electrons is nearly isotropic. This 
+behavior is thought to be caused by the insignificant angular anisotropy 
+of sub--50--eV yield. 
 A typical value for the ejection angle considered in the literature is 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figuras/adn1.eps}
+\includegraphics[width=0.8\textwidth]{adn1.eps}
 \caption{Reduced CDW ionization cross section $\sigma_{M}/Z^2$ as a function 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figuras/adn2.eps}
+\includegraphics[width=0.8\textwidth]{adn2.eps}
 \caption{Reduced CDW ionization cross section $\sigma_{M}/Z^2$ as a function 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figuras/molscaling85.eps}
+\includegraphics[width=0.8\textwidth]{molscaling85.eps}
 \caption{Scaled ionization cross section per weakly bound electron using
@@
 \centering
-\includegraphics[width=0.785\textwidth]{figuras/scale_ne.eps}
+\includegraphics[width=0.785\textwidth]{scale_ne.eps}
 \caption{Ionization cross sections by the impact of protons at 0.5, 1,
@@
 \centering
-\includegraphics[width=0.8\textwidth]{figuras/levelsDNA.eps}
+\includegraphics[width=0.8\textwidth]{levelsDNA.eps}
 \caption{Theoretical molecular binding energies for adenine, cytosine, 
@@
 
-\begin{table*}[t]
+\begin{table*}[t!]
 \begin{center}
@@
 %Electron production in proton collisions with atoms and molecules: energy distributions. 
-Rev. Mod. Phys. \textbf{64}, 441--490 (1992).
+Rev. Mod. Phys. \textbf{64}, 44--490 (1992).
 

### 2019-12-02 submit_jpb/revsubmission_v2/ionmol_stoi.tex
include Z scaling work

--- 2019-12-02 submit_jpb/revsubmission/ionmol_stoi.tex
@@
 
-\begin{figure*}[t!]
-\centering
-\includegraphics[width=0.8\textwidth]{ang_mean.eps}
-\caption{Mean emitted angle distribution for ionization by impact of
-multicharged ions. Curves as in Fig.~\ref{fig:emittedener}.}
-\label{fig:emittedang}
-\end{figure*}
-
 The mean emitted electron energies $\overline{E}_{\alpha}$ for H, C, N, 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=0.8\textwidth]{ang_mean.eps}
+\caption{Mean emitted angle distribution for ionization by impact of
+multicharged ions. Curves as in Fig.~\ref{fig:emittedener}.}
+\label{fig:emittedang}
+\end{figure*}
 
@@
 
-\begin{table*}[t!]
+\begin{table*}[t]
 \begin{center}
@@
 %Electron production in proton collisions with atoms and molecules: energy distributions. 
-Rev. Mod. Phys. \textbf{64}, 44--490 (1992).
+Rev. Mod. Phys. \textbf{64}, 441--490 (1992).
 

### 2020-03-09 zscaling/main.tex
include zscaling paper

\documentclass[10pt,showpacs,showkeys,twocolumn]{revtex4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \usepackage[T1]{fontspec}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{gensymb}
\usepackage{float}
\usepackage{MnSymbol}
\usepackage{gensymb}
\usepackage{comment}
\usepackage{wasysym} 
\usepackage{stmaryrd}

\begin{document}

\title[Universal scaling for the ionization of biological molecules]{
Universal scaling for the ionization of biological molecules by highly charged ions}
\author{A. M. P. Mendez, C. C. Montanari, J. E. Miraglia}
\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio 
(CONICET--UBA), \\ Buenos Aires, Argentina.}

\date{\today}% It is always \today, today,

\begin{abstract}
In the present work, we investigate scaling rules for the ionization cross sections of multicharged ions on molecules of biological interest. The cross sections are obtained from distorted--wave calculations for atomic targets
combined with stoichiometric model for the molecules proposed in [Mendez \textit{et al.} J. Phys B (2020)]. We examine ions with charges $Z$ from $+1$ to $+8$ in the pyrimide bases: adenine, citosine, guanine, thymine, uracil, tetrahydrofuran, pyrimidine, and also in water. We propose a scaling with the ion charge valid in the intermediate to high energy range, i.e. 0.2-5 MeV/amu for oxigen impact. We extend it to a universal scaling for any ion and molecule, which merges the forty ion--molecule systems analyzed here in a single band, and proved to be valid for other molecules too.  
\end{abstract}

\keywords{ionization, scaling, molecules, charged-ions, DNA, 
multicharged ions}
\pacs{34.50Gb, 34.80Gs, 34.80Dp}

\maketitle
%\ioptwocol

%\section{Introduction}
The ionization of biological molecules by multicharged ions has increasing interest due to medical and environmental reasons \cite{PhysMed}, from medical treatments  \cite{Mohamad2017,Solov2009,Denifl2011} to recognition of contaminants in biological materials \cite{water,ferrazdias}. Many semiempirical \citep{vera_prl2013} and  theoretical efforts are currently being done \cite{MendezJPB20,Quinto20,ludde2019,ludde2018,ludde2016,Champion2012} to get reliable values for the ionization cross sections of these molecules.

Recently we combined the continue distorted--wave calculations  (CDW) for atoms and the simple stoichiometric model (SSM) to approximate the ionization cross sections of complex molecular targets by charged ions \cite{MendezJPB20}. This CDW-SSM  approximation showed reasonable results for six ions in seventeen molecules. As expected, in the high energy range (i.e. above 5 MeV/amu) the ionization cross sections  have the $Z^2$ dependence predicted by the first Born approximation. Instead, at intermediate energies the dependence with $Z$ is more complex, and non-perturvative models are mandatory.

The aim of this letter is to deep on our previous work in \cite{MendezJPB20} by proposing a scaling of the ionization cross sections of complex molecules with the ion charge $Z$ valid at intermediate energies.  The requirements of values for a multiplicity of systems make this kind of scalings very interesting as a first order test for new experimental measurements and as inputs in multipurpose codes. Based on the scaling of the ionization cross sections with the number of active electrons, we propose an universal scaling for any ion-target system, valid at least for the complex biological molecules studied here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Scaling with the ion charge}
%\label{sec:Z-scaling}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

At intermediate impact energies, the $Z^2$ rule no longer holds. Janev and Presnyakov ~\cite{janev1980} suggest $\sigma/Z$ versus $E/Z$  as the \textit{natural} reduced form of the ionization cross section $\sigma$. Much more recently, Montenegro and co-workers  ~\cite{dubois13,montenegro_pra13} proposed an alternative scaling  by taking into account that  $\sigma$ is a function of $Z^2/E$, so an scaling given by
\begin{equation}
    \sigma/Z^{\alpha}=f(E/Z^{2-\alpha}),
    \label{Montenegro}
\end{equation}
keeps the $Z^2/E$ relationship for any value of $\alpha$. 
%The scaling by Janev \cite{janev1980} displayed in figure {fig:zreduced}  is equivalent to using $\alpha=1$. 
In  \cite{dubois13} $\alpha=4/3$ is proposed for ionization of He and H$_2$ by different charged ions.

%\newpage
\begin{figure*}[!t]%[h]
\centering
\includegraphics[width=0.7\textwidth]{zscale_alpha.eps}
\caption{(Color online) Scaled ionization cross section $\sigma/Z^{\alpha}$ as a function 
of ion impact energy $E/Z^{2-\alpha}$ as explained in Eq. (\ref{Montenegro}). Colors are asociated with the impact charge as signed in the upper part of the figure. Curves: present CDW-SSM theoretical results.
Symbols: experimental impact of 
\mbox{\Large$\circ$} H$^+$~\cite{iriki2011} and 
$\lozenge$ C$^{+6}$ \cite{tribedi2019} on adenine;
H$^+$ on  $\triangle$ uracil~\cite{itoh2013}, 
$\ominus$ C$^{+4}$, 
$\oplus$ C$^{+6}$, O$^{+6}$, F$^{+6}$, and 
$\otimes$ O$^{+8}$, F$^{+8}$ on uracil~\cite{agnihotri2012,agnihotri2013};
H$^+$ on $\triangledown$ pyrimidine~\cite{wolff2014}, and
$\meddiamond$ THF~\cite{wang2016};
\mbox{\fontsize{10}{20} $\varhexagon$} H$^+$ \cite{Luna2007}, 
$\pentagon$ H$^+$ \cite{Rudd86}, 
$\odot$ He$^{+2}$ \cite{Rudd85},  
$\logof$ Li$^{+3}$ \cite{Luna_Li_water},  
$\ovee$ C$^{+6}$ \cite{DalCappello2009}, and 
$\varobslash$ O$^{+8}$ \cite{Tribedi_O_water} on water.
Markers~$\square$~\cite{rahman2016}, 
$\rhd$~\cite{bug2017}, 
$\lhd$~\cite{wolf2019}, and 
$\medstar$~\cite{fuss2009} correspond to electron impact ionization with equi-velocity conversion.}
\label{fig:zreduced}
\end{figure*}

% We consider our recent CDW-SSM results \cite{MendezJPB20} for eight targets (DNA and RNA nucleo-basis, tetrahydrofuran (THF) and pyrimidine) and five charged ions (H$^+$m He$^+2$, Be$^+4$, C$^+6$, and O$^+8$)eight targets (DNA and RNA nucleo-basis, tetrahydrofuran (THF) and pyrimidine) and five charged ions (H$^+$m He$^+2$, Be$^+4$, C$^+6$, and O$^+8$) as benchmark for the present scaling.

Combining Eq. (\ref{Montenegro}) and our recent CDW-SSM results \cite{MendezJPB20}, we propose here a $Z$-scaling and tested it %the best possible the cross sections of
for eight targets (the DNA and RNA nucleo-basis: adenine, cytosine, guanine, thymine, uracil, also tetrahydrofuran (THF), pyrimidine, and water) and five charged ions (H$^+$m He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$). We considered these forty collisional systems as benchmark for the present scaling.

%Based on these ion-target combinations, 
We found that $\sigma/Z^{\alpha}$ vs. $E^{2-\alpha}$, with $\alpha=1.2$ best fits the CDW-SSM scaled cross sections for all the ions. %$Z=+1$ to $+8$. , giving similar energy for the maximum of the cross sections. %, as displayed in  figure \ref{fig:zreduced}. 
The validity of the theoretical scaling with the ion charge is very clear in figure \ref{fig:zreduced}, where the CDW-SSM curves lays one over the other.  Out theoretical results are valid for impact energies around and above the maximum of the cross sections, which means above 50 keV for impact of H$^+$  to 250 keV/amu for impact of O$^{+8}$.

The scaling was tested with the experimental data available %for these eight molecules 
by impact of different charged ions \cite{itoh2013,iriki2011,wolff2014,wang2016,tribedi2019,agnihotri2012,agnihotri2013,Luna2007,Rudd86,Rudd85,Luna_Li_water,DalCappello2009,Tribedi_O_water},
and also by electron impact at sufficiently high velocity \cite{rahman2016,bug2017,wolf2019,fuss2009}. As can be noted, most of the data in figure \ref{fig:zreduced} verifies the scaling quite well. The data of uracil by swift C, O and F ions 
in \cite{agnihotri2012,agnihotri2013} are too low as compared with our CDW-SSM results, but also as compared with Itoh \textit{et al} data \cite{itoh2013}, and with the CTMC calculations by Sarkadi \cite{sarkadi2016}.
%as compared to proton impact measurements by Itoh \textit{et al} \cite{itoh2013} multiplied by $Z^2$. Independent CTMC calculations by Sarkadi \cite{sarkadi2016} also mention this. 
The data for Li$^{+3}$ in water in \cite{Luna_Li_water} also separate from the present theoretical curves for $E<600$ keV/amu.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Universal Scaling rule}
%\label{sec:U-scaling}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The good results obtained in the scaling with the ion charge challenged us to look for a more general scaling rule that could predict values for ionization cross sections of any ion in any molecule.  % that scales ions and molecules  
%Based on he good results shown in figure \ref{fig:zreduced}  and the scaling with the number of active electrons $n_e$ in each atom in  \cite{MendezJPB20}, we went further for an universal scaling that involves the different molecules biomolecules studied here, and 
To that end, we resorted to the %scaling with the 
number of active electrons in each atom $n_e$ proposed in \cite{MendezJPB20}, and combined it with the $Z$-scaling displayed in figure \ref{fig:zreduced}. %given by Eq. (\ref{Montenegro}) with $\alpha=1.2$.

The CDW ionization cross sections $\sigma^{CDW}$ of atomic H, C, N, O targets scale as $\sigma_e=\sigma^{CDW}/n_e$ with  $n_e$ being $1$ for H, $4$ for C, N, and O. %; and $4.5$ for P and S. 
The SSM leads to the molecular numbers of active electrons included in table \ref{nn}.

\begin{table}[H]
\begin{center}
\begin{tabular}{|ll|ll|ll|}
\hline
 Molecule & $n_e$ &Molecule          & $n_e$ & Molecule             & $n_e$\\
\hline
% --------------------------------------------------------------------------------
% H$_2$    & 2  & CH$_5$N             \ \ \ \ & 13    & C$_4$H$_5$N$_3$O     \ \ \ \ & 37   \\ %H2 -pyridine  -cytosine
% H$_2$O   & 6  & C$_4$H$_8$O         \ \ \ \ & 28    & C$_5$H$_6$N$_2$O$_2$ \ \ \ \ & 42   \\ %H2O-THF       -thymine
% O$_2$    & 8  & C$_4$H$_4$N$_2$    \ \ \ \  & 28    & C$_5$H$_5$N$_5$      \ \ \ \ & 45   \\ %O2- pyrimidine-adenine
% CH$_4$   & 8  & C$_6$H$_6$          \ \ \ \ & 30    & C$_5$H$_5$N$_5$O     \ \ \ \ & 49   \\ %methane-benzene-guanine
% CO$_2$   & 12 & C$_4$H$_4$N$_2$O$_2$\ \ \ \ & 36    & C$_5$H$_{10}$O$_5$P \ \ \ \ & 54.5 
% \\ %CO2- uracil-backbone
%--------------------------------------------------------------------------------
% Nueva tabla
% -------------------------------------------------------------------------------
 H$_2$O   & 6   &  CO$_2$  \ \ \ \ & 12  & C$_4$H$_5$N$_3$O     \ \ \ \ & 37   \\ %H2 -CO2  -cytosine
 N$_2$    & 8  & C$_4$H$_8$O         \ \ \ \ & 28    & C$_5$H$_6$N$_2$O$_2$ \ \ \ \ & 42   \\ %H2O-THF       -thymine
 O$_2$    & 8  & C$_4$H$_4$N$_2$    \ \ \ \  & 28    & C$_5$H$_5$N$_5$      \ \ \ \ & 45   \\ %O2- pyrimidine-adenine
 CH$_4$   & 8  & C$_4$H$_4$N$_2$O$_2$ \ \ \ \ &  36   & C$_5$H$_5$N$_5$O     \ \ \ \ & 49   \\ %methane-uracil-guanine
% --------------------------------------------------------------------------------
 \hline
\end{tabular}
\caption{Number of active electrons per target at intermediate to high energies obtained from the CDW calculations~\cite{MendezJPB20}.}
\label{nn}
\end{center}
\end{table}

\begin{figure*}[!t]%[h]
\centering
\includegraphics[width=0.7\textwidth]{zmol_alpha.eps}
\caption{(Color online) Universal scaling with the ions charge $Z$ and the number of active electrons in the molecule $n_e$ given by Eq. (\ref{u-scaling}). Curves: present CDW-SSM theoretical results. 
Symbols: experimental impact of H$^+$ on 
\mbox{\Large$\circ$} adenine~\cite{iriki2011}, 
$\triangle$ uracil~\cite{itoh2013}, 
$\triangledown$ pyrimidine~\cite{wolff2014} and 
$\meddiamond$ THF~\cite{wang2016};
$\lozenge$ C$^{+6}$ on adenine \cite{tribedi2019};
\mbox{\fontsize{10}{20} $\varhexagon$} H$^+$ \cite{Luna2007},
$\pentagon$ H$^+$ \cite{Rudd86}, 
$\odot$ He$^{+2}$ \cite{Rudd85},  
$\ovee$ C$^{+6}$ \cite{DalCappello2009}, and 
$\boxslash$ O$^{+8}$ \cite{Tribedi_O_water} on water;
H$^{+}$ and He$^{+2}$ impact on 
$\boxast$~N$_2$, 
$\boxbox$~O$_2$,
$\boxbar$~CO, 
$\boxbslash$~CO$_2$, and
$\boxdot$~CH$_4$ \cite{Rudd85,Rudd1983}, 
$\varowedge$~H$^{+}$ on CH$_4$~\cite{Luna2019}; 
and electron impact on $\rhd$~pyrimidine~\cite{bug2017}, and $\lhd$, $\medstar$~\cite{wolf2019,fuss2009} THF.}
\label{fig:zalpha}
\end{figure*}

The universal scaling we propose here is expressed as
 \begin{equation}
     \sigma_U=\frac{\sigma_e}{Z^{\alpha}}=\frac{\sigma/n_e}{Z^{\alpha}}\,,
     \label{u-scaling}
 \end{equation}
as a function of $E/Z^{2-\alpha}$, with $\sigma$ being the ionization cross section for the molecular target, $\alpha=1.2$ and  $n_e$ being the number of active electrons per molecule in table \ref{nn}. %It is important to point out that the scaling is based on CDW results atomic H, C, N, O, and P targets, so it is only  valid for ionization cross sections %by charged ions (at least up to +8) of molecules composed by these atoms.%, unless other values for ne were obtained for other atomic targets. 
In figure \ref{fig:zalpha} we test the universal scaling of Eq. (\ref{u-scaling}) %by showing in the same plot 
for all the theoretical and experimental values displayed in figure \ref{fig:zreduced}. 
As can be noted, the universal scaling works fine, all the curves and data lays in a narrow band valid for any charged ion (scaling with Z) in any molecule (scaling with the number of active electrons). We decided not including in this figure the data  for uracil in \cite{agnihotri2012,agnihotri2013}, and for Li on water in \cite{Luna_Li_water}. The discussion about these experimental values exceeds the present work. %is open for future work.

In principle, the \textit{universal} scaling should be valid for different ion-molecule combinations. 
We proved this by including in figure \ref{fig:zalpha} the measurements by Rudd et al \cite{Rudd85,Rudd1983} for H$^{+}$ and He$^{+2}$ in N$_2$, O$_2$, CH$_4$, CO and CO$_2$, and the recent values by Luna et al \cite{Luna2019} for H$^{+}$ in CH$_4$.

The good agreement shown in figure \ref{fig:zalpha} resumes the main result of this work, and holds the validity of present universal scaling. Although the theoretical CDW-SSM results  %Present scaling rule 
are valid for energies above the maximum of the cross sections, the scaling of the experimental data extends to lower impact energies%is more extensive
, as can be noted in figure \ref{fig:zalpha}.
The importance of scaling rules lay on the predictive capability. New measurements for other ions and molecules are expected to reinforce the present proposal.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
In this letter, we present an scaling for the ionization cross sections of highly charged ions in biological targets. The scaling rule states the cross sections divided by $Z^{\alpha}$ as a function of the reduced impact energy $E/Z^{2-\alpha}$, with $\alpha=1.2$. The scaling was obtained by means of the CDW-SSM calculations for five different charged ions in eight targets and tested with the available experimental data. An universal scaling rule  is also proposed, which reduced the cross sections with the number of active electrons of the molecule. The universal scaling proved to be valid for a large number of experimental data.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip
%\section*{References}

\begin{thebibliography}{}

% intro --------------------------------------------------------
\bibitem{PhysMed} T. Liamsuwan and H. Nikjoo, Phys. Med. Biol. \textbf{58}  641–672 (2013).

\bibitem{Mohamad2017}
O. Mohamad, B. J. Sishc, J. Saha, A. Pompos, A. Rahimi, M. D. Story, A. J. Davis, D. N. Kim, Cancers \textbf{9}, 66 (2017).

\bibitem{Solov2009} A. V. Solov'yov, E. Surdutovich, E. Scifoni, I. Mishustin, and W. Greiner, Phys. Rev. E \textbf{79}, 011909 (2009);
% https://link.aps.org/doi/10.1103/PhysRevE.79.011909

\bibitem{Denifl2011}
Denifl S., Märk T.D., Scheier P. 
% The Role of Secondary Electrons in Radiation Damage. 
% In Radiation Damage in Biomolecular Systems. Biological and Medical Physics, Biomedical Engineering. 
Eds: García Gómez-Tejedor G., Fuss M. 
Springer, Dordrecht (2012)

\bibitem{water} N. A. Gafur, M.  Sakakibara, S. Sano, K. A. Sera, 
% \textit{Case Study of Heavy Metal Pollution in Water of Bone River by Artisanal Small-Scale Gold Mine Activities in Eastern Part of Gorontalo, Indonesia}, 
Water \textbf{10}, 1507 (2018); doi:10.3390/w10111507.

\bibitem{ferrazdias} D. Benedetti, E. Nunes, M. Sarmento, C. Porto, C. E. Iochims dos Santos, J. Ferraz Dias, J. da Silva,
% \textit{Genetic damage in soybean workers exposed to pesticides: Evaluation with the comet and buccal micronucleus cytome assays},
Mutation Research/Genetic Toxicology and Environmental Mutagenesis,
Volume 752, 28-33 (2013);
% https://doi.org/10.1016/j.mrgentox.2013.01.001.

\bibitem{vera_prl2013} P. de Vera, R. Garcia-Molina,I. Abril, and A. V. Solov’yov, Phys. Rev. Lett.  110, 148104 (2013).

% our ---------------------------------------------------------
\bibitem{MendezJPB20}A. M. P. Mendez, C. C. Montanari, and J. E. Miraglia, J. Phys. B: At. Mol. Opt. Phys.  \textbf{53}, 055201 (2020).

% others -----------------------------------------------
\bibitem{Quinto20} M.A. Quinto, J.M. Monti, C.A. Tachino, P.F. Weck, O.A. Fojón, C. Champion, R.D. Rivarola, 
% \textit{The physics of irradiation of biological matter by ion beams}, 
Rad. Phys. Chem. \textbf{167}, 108337 (2020);
% https://doi.org/10.1016/j.radphyschem.2019.05.027.

\bibitem{ludde2019}
H. J. L\"udde,  M. Horbatsch and T. Kirchner, J. Phys. B: At. Mol. Opt. Phys.  \textbf{52}, 195203 (2019).

\bibitem{ludde2018}
H. J. L\"udde, M. Horbatsch and T. Kirchner, Eur. Phys. J. B \textbf{91}, 99 (2018).

\bibitem{ludde2016}
H. J. L\"udde, A. Achenbach, T. Kalkbrenner, H.-C. Jankowiak and T. Kirchner,
Eur. Phys. J. D \textbf{70}, 82 (2016).

\bibitem{Champion2012} 
C Champion, M E Galassi, O Foj\'{o}n, H Lekadir, J Hanssen, R D Rivarola, P F Weck, A N Agnihotri, S Nandi, and L C Tribedi. 
J. Phys.: Conf. Ser. \textbf{373}, 012004 (2012).

% Z-scaling------------------------------------------------------
\bibitem{janev1980}
R. K. Janev and L. P. Presnyakov 
J. Phys. B: At. Mol. Opt. Phys.  \textbf{13}, 4233 (1980).

\bibitem{dubois13}
R. D. DuBois, E. C. Montenegro and G. M. Sigaud,
AIP Conference Proceeding \textbf{1525}, 679 (2013).

\bibitem{montenegro_pra13} E. C. Montenegro, G. M. Sigaud,  and R. D. DuBois, Phys. Rev. A \textbf{87} 012706 (2013).

% Experimental data ----------------------------------------------

\bibitem{itoh2013} 
A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D. Rivarola, 
Phys. Rev. A \textbf{88}, 052711 (2013).

\bibitem{iriki2011}
Y. Iriki, Y. Kikuchi, M. Imai, and A. Itoh
Phys. Rev. A \textbf{84}, 052719 (2011).

%\bibitem{Tabet2010} J. Tabet, S. Eden, S. Feil, H. Abdoul-Carime, B. Farizon, M. Farizon, S. Ouaskit, and T. D. Mark, Phys. Rev. A \textbf{82}, 022703 (2010).

\bibitem{wolff2014}
W. Wolff, H. Luna, L. Sigaud, A. C. Tavares, and E. C. Montenegro
J. Chem. Phys. \textbf{140}, 064309 (2014).

\bibitem{wang2016}
M. Wang, B. Rudek, D. Bennett, P. de Vera, M. Bug, T. Buhr, W. Y. Baek, G. Hilgers, H. Rabus, 
Phys. Rev. A \textbf{93}, 052711 (2016).\bibitem{tribedi2019} S. Bhattacharjee, C. Bagdia, M. R. Chowdhury, A. Mandal, J. M. Monti, R. D. Rivarola, and L. C. Tribedi, 
Phys. Rev. A \textbf{100}, 012703(2019).

\bibitem{agnihotri2012}
A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A.
Kumar, M. E. Galassi, R. D. Rivarola, O. Foj\'{o}n, C. Champion, J. Hanssen, H. Lekadir, P. F. Weck, and L. C. Tribedi. 
Phys. Rev. A \textbf{85}, 032711 (2012).

\bibitem{agnihotri2013}
A N Agnihotri, S Kasthurirangan, S Nandi, A Kumar, C Champion,, H Lekadir, J Hanssen, P FWeck, M E Galassi, R D Rivarola, O Fojon and L C Tribedi, 
J. Phys. B: At. Mol. Opt. Phys.  \textbf{46}, 185201 (2013).

% H+ in water-------------------------------------
\bibitem{Luna2007}
H. Luna, A. L. F. de Barros, J. A. Wyer, S. W. J. Scully, J. Lecointre, P. M. Y. Garcia, G. M. Sigaud, A. C. F. Santos,
V. Senthil, M. B. Shah, C. J. Latimer, and E. C. Montenegro,
Phys. Rev. A \textbf{75}, 042711 (2007).

%\bibitem{Champion2007}C. Champion, O. Boudrioua, C. Dal Cappello, Y. Sato, D. Ohsawa, Phys. Rev. A 75 (2007) 032724.

\bibitem{Rudd86} M. A. Bolorizadeh and M. E. Rudd, Phys. Rev. A \textbf{33}, 888 (1986).

% He$^{+2}$ in water---------------------
%\bibitem{DalCappello2007} O. Boudrioua, C. Champion, C. Dal Cappello, Y.V. Popov, Phys. Rev. A 75 (2007) 012717.

\bibitem{Rudd85} M. E. Rudd, T. V. Goffe, and A. Itoh,  Phys. Rev. A \textbf{32}, 2128 (1985).

% Li$^{+3}$ in water---------------------------
\bibitem{Luna_Li_water} H. Luna, W. Wolff, and E. C. Montenegro, Andre C. Tavares, H. J. Ludde, G. Schenk, M. Horbatsch, and T. Kirchner, Phys. Rev. A \textbf{93}, 052705 (2016).

% C$^{+6}$ in water--------------------------
\bibitem{DalCappello2009}
C. Dal Cappello, C. Champion, O. Boudrioua, H. Lekadir, Y. Sato , D. Ohsawa, 
Nuclear Instruments and Methods in Physics Research B 267 (2009) 781–790.

%O$^{+8}$ in water -------------------------------
\bibitem{Tribedi_O_water} S. Bhattacharjee, S. Biswas, C. Bagdia, M. Roychowdhury, S. Nandi, D. Misra, J. M. Monti, C. A. Tachino, R. D. Rivarola, C. Champion and L. C. Tribedi, J. Phys. B: At. Mol. Opt. Phys. \textbf{49,}  065202 (2016).

% electron impact --------------------------
\bibitem{rahman2016}
M. A. Rahman and E. Krishnakumar,
Electron ionization of DNA bases,
J. Chem. Phys. \textbf{144}, 161102 (2016).

\bibitem{bug2017}
M. U. Bug, W. Y. Baek, H. Rabus, C. Villagrasa, S. Meylan, A. B. Rosenfeld,
Rad. Phys. Chem. \textbf{130}, 459--479 (2017).

\bibitem{wolf2019}
W. Wolff, B. Rudek, L. A. da Silva, G. Hilgers, E. C. Montenegro, 
M. G. P. Homem,
J. Chem. Phys. \textbf{151}, 064304 (2019).

\bibitem{fuss2009}
M. Fuss, A. Muñoz, J. C. Oller, F. Blanco, D. Almeida, P. Limão-Vieira, 
T. P. D. Do, M. J. Brunger, G. Garc\'{i}a,
Phys. Rev. A \textbf{80}, 052709 (2009).

\bibitem{sarkadi2016} L Sarkadi, J. Phys. B: At. Mol. Opt. Phys. \textbf{49} 185203 (2016)

% H+ in CH4 and CO2-----------------------------------------
\bibitem{Rudd1983} M. E. Rudd, R. D. DuBois, L. H. Toburen, and C. A. Ratcliffe, T. V. Goffe, Phys. Rev. A \textbf{28}, 3244 (1983).

\bibitem{Luna2019} H. Luna, W. Wolff, and E. C. Montenegro, L. Sigaud, Phys. Rev. A \textbf{99}, 012709 (2019).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%, %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{thebibliography}

\end{document}

### 2020-03-09 zscaling/zion_ale.tex
include zscaling paper

--- 2020-03-09 zscaling/main.tex
@@
 In the present work, we investigate scaling rules for the ionization cross sections of multicharged ions on molecules of biological interest.
-The cross sections are obtained from distorted--wave calculations for atomic targets
-combined with stoichiometric model for the molecules proposed in [Mendez \textit{et al.} J.
+The cross sections are obtained from distorted--wave calculations for atomic targets combined with a stoichiometric model for the molecules proposed in [Mendez \textit{et al.} J.
 Phys B (2020)].
-We examine ions with charges $Z$ from $+1$ to $+8$ in the pyrimide bases: adenine, citosine, guanine, thymine, uracil, tetrahydrofuran, pyrimidine, and also in water.
-We propose a scaling with the ion charge valid in the intermediate to high energy range, i.e.
-0.2-5 MeV/amu for oxigen impact.
-We extend it to a universal scaling for any ion and molecule, which merges the forty ion--molecule systems analyzed here in a single band, and proved to be valid for other molecules too.
+We examine ions with charges $Z$ from $+1$ to $+8$ in five nucleobases --adenine, cytosine, guanine, thymine, uracil--, tetrahydrofuran, pyrimidine, and also in water.
+We propose a scaling with the ion charge, which is valid in the intermediate to high energy range, i.e.
+0.2-5 MeV/amu for oxygen impact.
+We extend our work to a universal scaling for any ion and molecule, merging the forty ion--molecule systems analyzed here into a single band.
+Furthermore, our model proved to be valid for other molecules too.
 \end{abstract}
@@
 
-%\section{Introduction}
-The ionization of biological molecules by multicharged ions has increasing interest due to medical and environmental reasons \cite{PhysMed}, from medical treatments  \cite{Mohamad2017,Solov2009,Denifl2011} to recognition of contaminants in biological materials \cite{water,ferrazdias}.
-Many semiempirical \citep{vera_prl2013} and  theoretical efforts are currently being done \cite{MendezJPB20,Quinto20,ludde2019,ludde2018,ludde2016,Champion2012} to get reliable values for the ionization cross sections of these molecules.
+The ionization of biological molecules by multicharged ions has gained increasing interest due to medical and environmental reasons~\cite{PhysMed}, from medical treatments~\cite{Mohamad2017,Solov2009,Denifl2011} to contaminant recognition in biological materials~\cite{water,ferrazdias}.
+Many semiempirical \citep{vera_prl2013} and theoretical efforts are currently being undertaken~\cite{MendezJPB20,Quinto20,ludde2019,ludde2018,ludde2016,Champion2012} to get reliable values for the ionization cross sections of these molecules.
 
-Recently we combined the continue distorted--wave calculations  (CDW) for atoms and the simple stoichiometric model (SSM) to approximate the ionization cross sections of complex molecular targets by charged ions \cite{MendezJPB20}.
-This CDW-SSM  approximation showed reasonable results for six ions in seventeen molecules.
+Recently, we combined the continue distorted--wave calculations (CDW) for atoms and the simple stoichiometric model (SSM) to approximate the ionization cross sections of complex molecular targets by charged ions~\cite{MendezJPB20}.
+The CDW--SSM approximation showed reasonable results for over a hundred of ion--molecule systems.
 As expected, in the high energy range (i.e.
-above 5 MeV/amu) the ionization cross sections  have the $Z^2$ dependence predicted by the first Born approximation.
-Instead, at intermediate energies the dependence with $Z$ is more complex, and non-perturvative models are mandatory.
+above 5 MeV/amu) the ionization cross sections  present the $Z^2$ dependence predicted by the first Born approximation.
+However, at intermediate energies, the dependence with $Z$ is more complex, and non--perturvative models are mandatory.
 
-The aim of this letter is to deep on our previous work in \cite{MendezJPB20} by proposing a scaling of the ionization cross sections of complex molecules with the ion charge $Z$ valid at intermediate energies.
-The requirements of values for a multiplicity of systems make this kind of scalings very interesting as a first order test for new experimental measurements and as inputs in multipurpose codes.
-Based on the scaling of the ionization cross sections with the number of active electrons, we propose an universal scaling for any ion-target system, valid at least for the complex biological molecules studied here.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The intention of this letter is to give a follow up of our previous work~\cite{MendezJPB20} by proposing a scaling with the ion charge $Z$ of the ionization cross sections of complex molecules, valid at intermediate energies.
+In general, scaling rules are used as first--order tests in experimental measurements and multipurpose codes.
+Based on ~\cite{MendezJPB20}, we propose a universal scaling for any ion--target system.%, which is valid initially for the complex biological molecules studied here.
 
-%\section{Scaling with the ion charge}
-%\label{sec:Z-scaling}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-At intermediate impact energies, the $Z^2$ rule no longer holds.
-Janev and Presnyakov ~\cite{janev1980} suggest $\sigma/Z$ versus $E/Z$  as the \textit{natural} reduced form of the ionization cross section $\sigma$.
-Much more recently, Montenegro and co-workers  ~\cite{dubois13,montenegro_pra13} proposed an alternative scaling  by taking into account that  $\sigma$ is a function of $Z^2/E$, so an scaling given by
+At intermediate impact energies, %the $Z^2$ rule no longer holds. 
+Janev and Presnyakov~\cite{janev1980} suggest $\sigma/Z$ versus $E/Z$ as the \textit{natural} reduced form of the ionization cross section $\sigma$ and the incident ion energy $E$.
+Much more recently, Montenegro and co--workers~\cite{dubois13,montenegro_pra13} proposed an alternative scaling by taking into account that  $\sigma$ is a function of $Z^2/E$.
+Their scaling, given by
 \begin{equation}
@@
 keeps the $Z^2/E$ relationship for any value of $\alpha$. 
-%The scaling by Janev \cite{janev1980} displayed in figure {fig:zreduced}  is equivalent to using $\alpha=1$. 
-In  \cite{dubois13} $\alpha=4/3$ is proposed for ionization of He and H$_2$ by different charged ions.
+In Ref.~\cite{dubois13}, the authors propose $\alpha=4/3$ for ionization of He and H$_2$ by different charged ions.
 
-%\newpage
 \begin{figure*}[!t]%[h]
@@
 \caption{(Color online) Scaled ionization cross section $\sigma/Z^{\alpha}$ as a function 
-of ion impact energy $E/Z^{2-\alpha}$ as explained in Eq.
-(\ref{Montenegro}).
-Colors are asociated with the impact charge as signed in the upper part of the figure.
-Curves: present CDW-SSM theoretical results.
+of ion impact energy $E/Z^{2-\alpha}$.%, given by Eq. (\ref{Montenegro}). 
+%Colors are asociated with the impact charge as signed in the upper part of the figure. 
+Colors are associated with the incident ion labeled on top of the figure.
+Curves: present CDW--SSM theoretical results.
 Symbols: experimental impact of 
@@
 $\lhd$~\cite{wolf2019}, and 
-$\medstar$~\cite{fuss2009} correspond to electron impact ionization with equi-velocity conversion.}
+$\medstar$~\cite{fuss2009} correspond to electron impact ionization with the equi-velocity conversion.}
 \label{fig:zreduced}
@@
 
-Combining Eq. (\ref{Montenegro}) and our recent CDW-SSM results \cite{MendezJPB20}, we propose here a $Z$-scaling and tested it %the best possible the cross sections of
-for eight targets (the DNA and RNA nucleo-basis: adenine, cytosine, guanine, thymine, uracil, also tetrahydrofuran (THF), pyrimidine, and water) and five charged ions (H$^+$m He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$).
-We considered these forty collisional systems as benchmark for the present scaling.
+Combining our recent CDW--SSM results~\cite{MendezJPB20} and Eq.~(\ref{Montenegro}), we propose here a $Z$-scaling and implement it for forty collisional systems.
+The ion--molecule systems are composed of eight targets: the DNA and RNA nucleobases --adenine, citosine, guanine, thymine, uracil--, tetrahydrofuran (THF), pyrimidine, and water; and five charged ions: H$^+$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$.
+We considered these systems as a benchmark for the present scaling.
 
-%Based on these ion-target combinations, 
-We found that $\sigma/Z^{\alpha}$ vs.
+%We found that $\sigma/Z^{\alpha}$ vs.
 $E^{2-\alpha}$, with $\alpha=1.2$ best fits the CDW-SSM scaled cross sections for all the ions.
@@
 %, as displayed in  figure \ref{fig:zreduced}.
-The validity of the theoretical scaling with the ion charge is very clear in figure \ref{fig:zreduced}, where the CDW-SSM curves lays one over the other.
-Out theoretical results are valid for impact energies around and above the maximum of the cross sections, which means above 50 keV for impact of H$^+$  to 250 keV/amu for impact of O$^{+8}$.
+We found that the parameter $\alpha$ from Eq.~(\ref{Montenegro}) that fits the CDW--SSM scaled cross sections for all the ions is $\alpha=1.2$. 
+The validity of the theoretical scaling with the ion charge is very clear in Fig.~\ref{fig:zreduced}, where the CDW-SSM curves lays one over the other.
+Our theoretical results are valid for impact energies around and above the maximum of the cross sections, which means above 50 keV for impact of H$^+$  to 250 keV/amu for impact of O$^{+8}$.
 
@@
 and also by electron impact at sufficiently high velocity \cite{rahman2016,bug2017,wolf2019,fuss2009}.
-As can be noted, most of the data in figure \ref{fig:zreduced} verifies the scaling quite well.
-The data of uracil by swift C, O and F ions
-in \cite{agnihotri2012,agnihotri2013} are too low as compared with our CDW-SSM results, but also as compared with Itoh \textit{et al} data \cite{itoh2013}, and with the CTMC calculations by Sarkadi \cite{sarkadi2016}.
+As can be noted, most of the data in Fig.~\ref{fig:zreduced} confirms the present scaling, even for O$^{+8}$ in water~\cite{Tribedi_O_water}.
+However, the data of uracil by swift C, O and F ions in \cite{agnihotri2012,agnihotri2013} are too low compared with our CDW--SSM results, but also as compared with Itoh \textit{et al.} data \cite{itoh2013}, and with the CTMC calculations by Sarkadi \cite{sarkadi2016}.
 %as compared to proton impact measurements by Itoh \textit{et al} \cite{itoh2013} multiplied by $Z^2$. Independent CTMC calculations by Sarkadi \cite{sarkadi2016} also mention this. 
-The data for Li$^{+3}$ in water in \cite{Luna_Li_water} also separate from the present theoretical curves for $E<600$ keV/amu.
+The data for Li$^{+3}$ in water from Ref.~\cite{Luna_Li_water} also spreads out from the present theoretical curves for $E<600$ keV/amu.
 
@@
 To that end, we resorted to the %scaling with the 
-number of active electrons in each atom $n_e$ proposed in \cite{MendezJPB20}, and combined it with the $Z$-scaling displayed in figure \ref{fig:zreduced}.
+number of active electrons in each atom $n_e$ proposed in \cite{MendezJPB20}, and combined it with the $Z$-scaling displayed in Fig.~\ref{fig:zreduced}.
 %given by Eq.
@@
 
-The CDW ionization cross sections $\sigma^{CDW}$ of atomic H, C, N, O targets scale as $\sigma_e=\sigma^{CDW}/n_e$ with  $n_e$ being $1$ for H, $4$ for C, N, and O. %; and $4.5$ for P and S. 
-The SSM leads to the molecular numbers of active electrons included in table \ref{nn}.
+The CDW ionization cross sections $\sigma^{\mathrm{CDW}}$ of atomic H, C, N, O targets scale as $\sigma_e=\sigma^{\mathrm{CDW}}/n_e$ with $n_e$ being $1$ for H, $4$ for C, N, and O.
+%; and $4.5$ for P and S.
+The SSM leads to the molecular numbers of active electrons included in Table \ref{nn}.
 
@@
 
-The universal scaling we propose here is expressed as
+The universal scaling we propose here is expressed as $\sigma_U$ as a function of $E/Z^{2-\alpha}$, with
  \begin{equation}
@@
  \end{equation}
-as a function of $E/Z^{2-\alpha}$, with $\sigma$ being the ionization cross section for the molecular target, $\alpha=1.2$ and  $n_e$ being the number of active electrons per molecule in table \ref{nn}.
+$\sigma$ is the ionization cross section for the molecular target, $\alpha=1.2$ and $n_e$ is the number of active electrons per molecule given in Table \ref{nn}.
 %It is important to point out that the scaling is based on CDW results atomic H, C, N, O, and P targets, so it is only  valid for ionization cross sections %by charged ions (at least up to +8) of molecules composed by these atoms.%, unless other values for ne were obtained for other atomic targets.
-In figure \ref{fig:zalpha} we test the universal scaling of Eq. (\ref{u-scaling}) %by showing in the same plot 
-for all the theoretical and experimental values displayed in figure \ref{fig:zreduced}. 
-As can be noted, the universal scaling works fine, all the curves and data lays in a narrow band valid for any charged ion (scaling with Z) in any molecule (scaling with the number of active electrons).
-We decided not including in this figure the data  for uracil in \cite{agnihotri2012,agnihotri2013}, and for Li on water in \cite{Luna_Li_water}.
+In Fig.~\ref{fig:zalpha}, we test the universal scaling of Eq. (\ref{u-scaling}) %by showing in the same plot 
+for all the theoretical and experimental values displayed in Fig. \ref{fig:zreduced}. 
+As can be noted, the universal scaling works well, all the curves and data lays in a narrow band valid for any charged ion (scaling with Z) in any molecule (scaling with the number of active electrons).
+We decided not including in this figure the data for uracil from Ref.~\cite{agnihotri2012,agnihotri2013}, and for Li$^{+3}$ on water Ref.~\cite{Luna_Li_water}.
 The discussion about these experimental values exceeds the present work.
@@
 
-In principle, the \textit{universal} scaling should be valid for different ion-molecule combinations. 
-We proved this by including in figure \ref{fig:zalpha} the measurements by Rudd et al \cite{Rudd85,Rudd1983} for H$^{+}$ and He$^{+2}$ in N$_2$, O$_2$, CH$_4$, CO and CO$_2$, and the recent values by Luna et al \cite{Luna2019} for H$^{+}$ in CH$_4$.
+In principle, the \textit{universal} scaling should be valid for different ion--molecule combinations. 
+We proved this statement by including in Fig.~\ref{fig:zalpha} the measurements by Rudd \textit{et al.} \cite{Rudd85,Rudd1983} for H$^{+}$ and He$^{+2}$ in N$_2$, O$_2$, CH$_4$, CO and CO$_2$, and the recent values by Luna \textit{et al.} \cite{Luna2019} for H$^{+}$ in CH$_4$.
 
-The good agreement shown in figure \ref{fig:zalpha} resumes the main result of this work, and holds the validity of present universal scaling.
-Although the theoretical CDW-SSM results  %Present scaling rule
+The good agreement shown in Fig.~\ref{fig:zalpha} summaries the main result of this work, and holds the validity of our universal scaling.
+Although the theoretical CDW--SSM results  %Present scaling rule
 are valid for energies above the maximum of the cross sections, the scaling of the experimental data extends to lower impact energies%is more extensive
-, as can be noted in figure \ref{fig:zalpha}.
-The importance of scaling rules lay on the predictive capability. New measurements for other ions and molecules are expected to reinforce the present proposal.
+, as can be noted in Fig. \ref{fig:zalpha}.
+The importance of scaling rules lay on their predictive capability. New measurements for other ions and molecules are expected to reinforce the present proposal.
 
@@
 \section{Conclusions}
-In this letter, we present an scaling for the ionization cross sections of highly charged ions in biological targets.
+In this letter, we present a scaling for the ionization cross sections of highly charged ions in biological targets.
 The scaling rule states the cross sections divided by $Z^{\alpha}$ as a function of the reduced impact energy $E/Z^{2-\alpha}$, with $\alpha=1.2$.
 The scaling was obtained by means of the CDW-SSM calculations for five different charged ions in eight targets and tested with the available experimental data.
-An universal scaling rule  is also proposed, which reduced the cross sections with the number of active electrons of the molecule.
+A universal scaling rule  is also proposed, which reduced the cross sections with the number of active electrons of the molecule.
 The universal scaling proved to be valid for a large number of experimental data.
@@
 % intro --------------------------------------------------------
-\bibitem{PhysMed} T. Liamsuwan and H. Nikjoo, Phys. Med. Biol. \textbf{58}  641–672 (2013).
+\bibitem{PhysMed} T. Liamsuwan and H. Nikjoo, Phys. Med. Biol. \textbf{58}  641--672 (2013).
 
@@
 % In Radiation Damage in Biomolecular Systems. Biological and Medical Physics, Biomedical Engineering. 
-Eds: García Gómez-Tejedor G., Fuss M. 
+Eds: Garc\'ia G\'omez-Tejedor G., Fuss M. 
 Springer, Dordrecht (2012)
@@
 % others -----------------------------------------------
-\bibitem{Quinto20} M.A. Quinto, J.M. Monti, C.A. Tachino, P.F. Weck, O.A. Fojón, C. Champion, R.D. Rivarola, 
+\bibitem{Quinto20} M.A. Quinto, J.M. Monti, C.A. Tachino, P.F. Weck, O.A. Foj\'on, C. Champion, R.D. Rivarola, 
 % \textit{The physics of irradiation of biological matter by ion beams}, 
@@
 C. Dal Cappello, C. Champion, O. Boudrioua, H. Lekadir, Y. Sato , D. Ohsawa, 
-Nuclear Instruments and Methods in Physics Research B 267 (2009) 781–790.
+Nuclear Instruments and Methods in Physics Research B 267 (2009) 781--790.
 

### 2020-03-09 zscaling/zscaling.tex
include zscaling paper

--- 2020-03-09 zscaling/zion_ale.tex
@@
 Combining our recent CDW--SSM results~\cite{MendezJPB20} and Eq.~(\ref{Montenegro}), we propose here a $Z$-scaling and implement it for forty collisional systems.
-The ion--molecule systems are composed of eight targets: the DNA and RNA nucleobases --adenine, citosine, guanine, thymine, uracil--, tetrahydrofuran (THF), pyrimidine, and water; and five charged ions: H$^+$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$.
+The ion--molecule systems are composed of eight targets: the DNA and RNA nucleobases --adenine, cytosine, guanine, thymine, uracil--, tetrahydrofuran (THF), pyrimidine, and water; and five charged ions: H$^+$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$.
 We considered these systems as a benchmark for the present scaling.
@@
 , as can be noted in Fig. \ref{fig:zalpha}.
-The importance of scaling rules lay on their predictive capability. New measurements for other ions and molecules are expected to reinforce the present proposal.
+The importance of scaling rules lays in their predictive capability. New measurements for other ions and molecules are expected to reinforce the present proposal.
 

### 2020-04-28 figuras/graphs/zscale.py
submission changes

@@ -1,0 +1,1629 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mticker
+from scipy import interpolate
+from matplotlib.legend_handler import HandlerLine2D
+plt.rc("text", usetex=True)
+plt.rc('font', family='serif')
+plt.rc('text.latex', preamble=r'\usepackage{wasysym} \usepackage{stmaryrd}')
+
+convMb=0.28002*100
+convcm2=0.28002
+co_p='tab:red'
+co_ap='tab:red'
+co_he='tab:green'
+co_be='tab:blue'
+co_c='tab:purple'
+co_o='tab:orange'
+
+def convkeV(x):
+    return 25.0*(x**2)
+
+def convMeV(x):
+    return 25.0*(x**2)/1000.
+
+def interp_XS(XY,ix,iy,kind):
+    x=XY[ix].values
+    y=XY[iy].values
+    n=len(x)
+    spline = interpolate.interp1d(x, y, kind=kind)
+    xnew = np.arange(x[0], x[n-1], 0.01)
+    ynew = spline(xnew)
+    XYnew = pd.DataFrame({ix:xnew, iy:ynew})
+    return XYnew
+
+class HandlerXoffset(HandlerLine2D):
+    def __init__(self, marker_pad=0.3, numpoints=1, x_offset=0,  **kw):
+        HandlerLine2D.__init__(self, marker_pad=marker_pad, numpoints=numpoints, **kw)
+        self._xoffset = x_offset
+    def get_xdata(self, legend, xdescent, ydescent, width, height, fontsize):
+        numpoints = self.get_numpoints(legend)
+
+        if numpoints > 1:
+            # we put some pad here to compensate the size of the
+            # marker
+            xdata = np.linspace(-xdescent + self._marker_pad * fontsize,
[…]

### 2020-05-11 zscaling/submitted/zscaling.tex
reviewers comments

--- 2020-03-09 zscaling/zscaling.tex
@@
 % \usepackage[T1]{fontspec}
+\usepackage{bm}
 \usepackage{amssymb}
@@
 \usepackage{multirow}
-\usepackage{gensymb}
 \usepackage{float}
 \usepackage{MnSymbol}
-\usepackage{gensymb}
 \usepackage{comment}
@@
 \usepackage{stmaryrd}
+\usepackage[outline]{contour}
+\usepackage[dvipsnames]{xcolor}
+
+\definecolor{olive}{RGB}{182,187,37}
 
@@
 
-Recently, we combined the continue distorted--wave calculations (CDW) for atoms and the simple stoichiometric model (SSM) to approximate the ionization cross sections of complex molecular targets by charged ions~\cite{MendezJPB20}.
+Recently, we combined the continue distorted--wave calculations (CDW) for atoms and the simple stoichiometric model (SSM), also known as the Bragg sum rule, to approximate the ionization cross sections of complex molecular targets by charged ions~\cite{MendezJPB20}.
 The CDW--SSM approximation showed reasonable results for over a hundred of ion--molecule systems.
@@
 In general, scaling rules are used as first--order tests in experimental measurements and multipurpose codes.
-Based on ~\cite{MendezJPB20}, we propose a universal scaling for any ion--target system.%, which is valid initially for the complex biological molecules studied here.
+Based on ~\cite{MendezJPB20}, we propose a universal scaling for any ion--target system.
 
-At intermediate impact energies, %the $Z^2$ rule no longer holds. 
+At intermediate impact energies, 
 Janev and Presnyakov~\cite{janev1980} suggest $\sigma/Z$ versus $E/Z$ as the \textit{natural} reduced form of the ionization cross section $\sigma$ and the incident ion energy $E$.
@@
 \includegraphics[width=0.7\textwidth]{zscale_alpha.eps}
-\caption{(Color online) Scaled ionization cross section $\sigma/Z^{\alpha}$ as a function 
-of ion impact energy $E/Z^{2-\alpha}$.%, given by Eq. (\ref{Montenegro}). 
-%Colors are asociated with the impact charge as signed in the upper part of the figure. 
+\caption{(Color online) Scaled ionization cross section $\sigma/Z^{\alpha}$ as a function of ion impact energy $E/Z^{2-\alpha}$ with $\alpha=1.2$.
 Colors are associated with the incident ion labeled on top of the figure.
@@
 Symbols: experimental impact of
-\mbox{\Large$\circ$} H$^+$~\cite{iriki2011} and 
-$\lozenge$ C$^{+6}$ \cite{tribedi2019} on adenine;
-H$^+$ on  $\triangle$ uracil~\cite{itoh2013}, 
-$\ominus$ C$^{+4}$, 
-$\oplus$ C$^{+6}$, O$^{+6}$, F$^{+6}$, and 
-$\otimes$ O$^{+8}$, F$^{+8}$ on uracil~\cite{agnihotri2012,agnihotri2013};
-H$^+$ on $\triangledown$ pyrimidine~\cite{wolff2014}, and
-$\meddiamond$ THF~\cite{wang2016};
-\mbox{\fontsize{10}{20} $\varhexagon$} H$^+$ \cite{Luna2007}, 
-$\pentagon$ H$^+$ \cite{Rudd86}, 
-$\odot$ He$^{+2}$ \cite{Rudd85},  
-$\logof$ Li$^{+3}$ \cite{Luna_Li_water},  
-$\ovee$ C$^{+6}$ \cite{DalCappello2009}, and 
-$\varobslash$ O$^{+8}$ \cite{Tribedi_O_water} on water.
+\mbox{\LARGE$\color{red}\circ$} H$^+$~\cite{iriki2011} and
+{\fontsize{11}{20}$\color{Purple}\pmb{\lozenge}$} C$^{+6}$ \cite{tribedi2019} on adenine;
+H$^+$ on {\fontsize{11}{20}$\color{red}\pmb{\triangle}$} uracil~\cite{itoh2013}, 
+{\fontsize{11}{20}$\color{NavyBlue}\pmb{\ominus}$} C$^{+4}$, 
+{\fontsize{11}{20}$\color{Purple}\pmb{\oplus}$} C$^{+6}$, O$^{+6}$, F$^{+6}$, and 
+{\fontsize{11}{20}$\color{BurntOrange}\pmb{\otimes}$} O$^{+8}$, F$^{+8}$ on uracil~\cite{agnihotri2012,agnihotri2013};
+H$^+$ on {\fontsize{11}{20}$\color{red}\pmb{\triangledown}$} pyrimidine~\cite{wolff2014}, and
+{\fontsize{10}{20}$\color{red}\pmb{\meddiamond}$} THF~\cite{wang2016};
+% water
+\mbox{\fontsize{11}{20}$\color{red}\pmb{\odot}$}~\cite{Luna2007}, 
+{\fontsize{11}{20}\color{red}$\pmb{\logof}$}~\cite{Rudd86}, 
+{\fontsize{11}{20}\color{red}$\pmb{\varowedge}$}~\cite{pRudd85}, 
+{\fontsize{11}{20}\color{red}$\pmb{\varoslash}$}~\cite{toburen80} H$^+$,
+{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varolessthan}$}~\cite{Ohsawa05},
+{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varogreaterthan}$}~\cite{Rudd85},
+{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varoslash}$}~\cite{toburen80} He$^{+2}$,
+{\fontsize{11}{20}\color{Purple}$\pmb{\ovee}$}~C$^{+6}$ \cite{DalCappello2009,Bhattacharjee17}, and 
+{\fontsize{11}{20}\color{BurntOrange}$\pmb{\obslash}$}
+O$^{+8}$ \cite{Tribedi_O_water} on water.
 Markers~$\square$~\cite{rahman2016}, 
@@
 
-% We consider our recent CDW-SSM results \cite{MendezJPB20} for eight targets (DNA and RNA nucleo-basis, tetrahydrofuran (THF) and pyrimidine) and five charged ions (H$^+$m He$^+2$, Be$^+4$, C$^+6$, and O$^+8$)eight targets (DNA and RNA nucleo-basis, tetrahydrofuran (THF) and pyrimidine) and five charged ions (H$^+$m He$^+2$, Be$^+4$, C$^+6$, and O$^+8$) as benchmark for the present scaling.
-
 Combining our recent CDW--SSM results~\cite{MendezJPB20} and Eq.~(\ref{Montenegro}), we propose here a $Z$-scaling and implement it for forty collisional systems.
@@
 
-%We found that $\sigma/Z^{\alpha}$ vs.
-$E^{2-\alpha}$, with $\alpha=1.2$ best fits the CDW-SSM scaled cross sections for all the ions.
-%$Z=+1$ to $+8$.
-, giving similar energy for the maximum of the cross sections.
-%, as displayed in  figure \ref{fig:zreduced}.
 We found that the parameter $\alpha$ from Eq.~(\ref{Montenegro}) that fits the CDW--SSM scaled cross sections for all the ions is $\alpha=1.2$. 
@@
 
-The scaling was tested with the experimental data available %for these eight molecules 
-by impact of different charged ions \cite{itoh2013,iriki2011,wolff2014,wang2016,tribedi2019,agnihotri2012,agnihotri2013,Luna2007,Rudd86,Rudd85,Luna_Li_water,DalCappello2009,Tribedi_O_water},
+The scaling was tested with the experimental data available by impact of different charged ions \cite{itoh2013,iriki2011,wolff2014,wang2016,tribedi2019,agnihotri2012,agnihotri2013,Luna2007,Rudd86,Rudd85,Luna_Li_water,DalCappello2009,Tribedi_O_water},
 and also by electron impact at sufficiently high velocity \cite{rahman2016,bug2017,wolf2019,fuss2009}.
@@
 However, the data of uracil by swift C, O and F ions in \cite{agnihotri2012,agnihotri2013} are too low compared with our CDW--SSM results, but also as compared with Itoh \textit{et al.} data \cite{itoh2013}, and with the CTMC calculations by Sarkadi \cite{sarkadi2016}.
-%as compared to proton impact measurements by Itoh \textit{et al} \cite{itoh2013} multiplied by $Z^2$. Independent CTMC calculations by Sarkadi \cite{sarkadi2016} also mention this. 
 The data for Li$^{+3}$ in water from Ref.~\cite{Luna_Li_water} also spreads out from the present theoretical curves for $E<600$ keV/amu.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The good results obtained in the scaling with the ion charge challenged us to look for a more general scaling rule that could predict values for ionization cross sections of any ion in any molecule. 
+To that end, we resorted to the number of active electrons in each atom $n_e$ proposed in \cite{MendezJPB20}, and combined it with the $Z$-scaling displayed in Fig.~\ref{fig:zreduced}.
 
-%\section{Universal Scaling rule}
-%\label{sec:U-scaling}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The good results obtained in the scaling with the ion charge challenged us to look for a more general scaling rule that could predict values for ionization cross sections of any ion in any molecule.
-% that scales ions and molecules
-%Based on he good results shown in figure \ref{fig:zreduced}  and the scaling with the number of active electrons $n_e$ in each atom in  \cite{MendezJPB20}, we went further for an universal scaling that involves the different molecules biomolecules studied here, and
-To that end, we resorted to the %scaling with the 
-number of active electrons in each atom $n_e$ proposed in \cite{MendezJPB20}, and combined it with the $Z$-scaling displayed in Fig.~\ref{fig:zreduced}.
-%given by Eq.
-(\ref{Montenegro}) with $\alpha=1.2$.
+The CDW ionization cross sections $\sigma^{\mathrm{CDW}}$ of atomic H, C, N, O targets scale as $\sigma_e=\sigma^{\mathrm{CDW}}/n_e$ with $n_e$ being $1$ for H, $4$ for C, N, and O, i.e.
+\begin{equation}
+ \frac{\sigma_{\mathrm{H}}^{\mathrm{CDW}}}{1}\sim
+ \frac{\sigma_{\mathrm{C}}^{\mathrm{CDW}}}{4}\sim
+ \frac{\sigma_{\mathrm{N}}^{\mathrm{CDW}}}{4}\sim
+ \frac{\sigma_{\mathrm{O}}^{\mathrm{CDW}}}{4}
+\end{equation}
+The SSM leads to the molecular numbers of active electrons included in Table \ref{nn}.
 
-The CDW ionization cross sections $\sigma^{\mathrm{CDW}}$ of atomic H, C, N, O targets scale as $\sigma_e=\sigma^{\mathrm{CDW}}/n_e$ with $n_e$ being $1$ for H, $4$ for C, N, and O.
-%; and $4.5$ for P and S.
-The SSM leads to the molecular numbers of active electrons included in Table \ref{nn}.
+\contourlength{0.03em}
+\contournumber{30}
 
@@
 \hline
-% --------------------------------------------------------------------------------
-% H$_2$    & 2  & CH$_5$N             \ \ \ \ & 13    & C$_4$H$_5$N$_3$O     \ \ \ \ & 37   \\ %H2 -pyridine  -cytosine
-% H$_2$O   & 6  & C$_4$H$_8$O         \ \ \ \ & 28    & C$_5$H$_6$N$_2$O$_2$ \ \ \ \ & 42   \\ %H2O-THF       -thymine
-% O$_2$    & 8  & C$_4$H$_4$N$_2$    \ \ \ \  & 28    & C$_5$H$_5$N$_5$      \ \ \ \ & 45   \\ %O2- pyrimidine-adenine
-% CH$_4$   & 8  & C$_6$H$_6$          \ \ \ \ & 30    & C$_5$H$_5$N$_5$O     \ \ \ \ & 49   \\ %methane-benzene-guanine
-% CO$_2$   & 12 & C$_4$H$_4$N$_2$O$_2$\ \ \ \ & 36    & C$_5$H$_{10}$O$_5$P \ \ \ \ & 54.5 
-% \\ %CO2- uracil-backbone
-%--------------------------------------------------------------------------------
-% Nueva tabla
-% -------------------------------------------------------------------------------
- H$_2$O   & 6   &  CO$_2$  \ \ \ \ & 12  & C$_4$H$_5$N$_3$O     \ \ \ \ & 37   \\ %H2 -CO2  -cytosine
- N$_2$    & 8  & C$_4$H$_8$O         \ \ \ \ & 28    & C$_5$H$_6$N$_2$O$_2$ \ \ \ \ & 42   \\ %H2O-THF       -thymine
- O$_2$    & 8  & C$_4$H$_4$N$_2$    \ \ \ \  & 28    & C$_5$H$_5$N$_5$      \ \ \ \ & 45   \\ %O2- pyrimidine-adenine
- CH$_4$   & 8  & C$_4$H$_4$N$_2$O$_2$ \ \ \ \ &  36   & C$_5$H$_5$N$_5$O     \ \ \ \ & 49   \\ %methane-uracil-guanine
-% --------------------------------------------------------------------------------
+ H$_2$O   & 6   &  CO$_2$  \ \ \ \ & 12  & C$_4$H$_5$N$_3$O     \ \ \ \ & 37   \\ 
+ N$_2$    & 8  & C$_4$H$_8$O         \ \ \ \ & 28    & C$_5$H$_6$N$_2$O$_2$ \ \ \ \ & 42   \\ 
+ O$_2$    & 8  & C$_4$H$_4$N$_2$    \ \ \ \  & 28    & C$_5$H$_5$N$_5$      \ \ \ \ & 45   \\ 
+ CH$_4$   & 8  & C$_4$H$_4$N$_2$O$_2$ \ \ \ \ &  36   & C$_5$H$_5$N$_5$O     \ \ \ \ & 49   \\ 
  \hline
@@
 \centering
-\includegraphics[width=0.7\textwidth]{zmol_alpha.eps}
+\includegraphics[width=0.7\textwidth]{zmol_werror.eps}
 \caption{(Color online) Universal scaling with the ions charge $Z$ and the number of active electrons in the molecule $n_e$ given by Eq.
@@
 Symbols: experimental impact of H$^+$ on 
-\mbox{\Large$\circ$} adenine~\cite{iriki2011}, 
-$\triangle$ uracil~\cite{itoh2013}, 
-$\triangledown$ pyrimidine~\cite{wolff2014} and 
-$\meddiamond$ THF~\cite{wang2016};
-$\lozenge$ C$^{+6}$ on adenine \cite{tribedi2019};
-\mbox{\fontsize{10}{20} $\varhexagon$} H$^+$ \cite{Luna2007},
-$\pentagon$ H$^+$ \cite{Rudd86}, 
-$\odot$ He$^{+2}$ \cite{Rudd85},  
-$\ovee$ C$^{+6}$ \cite{DalCappello2009}, and 
-$\boxslash$ O$^{+8}$ \cite{Tribedi_O_water} on water;
-H$^{+}$ and He$^{+2}$ impact on 
-$\boxast$~N$_2$, 
-$\boxbox$~O$_2$,
-$\boxbar$~CO, 
-$\boxbslash$~CO$_2$, and
-$\boxdot$~CH$_4$ \cite{Rudd85,Rudd1983}, 
-$\varowedge$~H$^{+}$ on CH$_4$~\cite{Luna2019}; 
+\mbox{\LARGE$\color{red}\circ$} adenine~\cite{iriki2011}, 
+{\fontsize{11}{20}$\color{red}\pmb{\triangle}$} uracil~\cite{itoh2013}, 
+{\fontsize{11}{20}$\color{red}\pmb{\triangledown}$} pyrimidine~\cite{wolff2014} and 
+{\fontsize{10}{20}$\color{red}\pmb{\meddiamond}$} THF~\cite{wang2016};
+{\fontsize{11}{20}$\color{Purple}\pmb{\lozenge}$} C$^{+6}$ on adenine \cite{tribedi2019};
+\mbox{\fontsize{11}{20}$\color{red}\pmb{\odot}$}~\cite{Luna2007}, 
+{\fontsize{11}{20}\color{red}$\pmb{\logof}$}~\cite{Rudd86}, 
+{\fontsize{11}{20}\color{red}$\pmb{\varowedge}$}~\cite{pRudd85}, 
+{\fontsize{11}{20}\color{red}$\pmb{\varoslash}$}~\cite{toburen80} H$^+$,
+{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varolessthan}$}~\cite{Ohsawa05},
+{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varogreaterthan}$}~\cite{Rudd85},
+{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varoslash}$}~\cite{toburen80} He$^{+2}$,
+{\fontsize{11}{20}\color{Purple}$\pmb{\ovee}$}~C$^{+6}$ \cite{DalCappello2009,Bhattacharjee17}, and 
+{\fontsize{11}{20}\color{BurntOrange}$\pmb{\obslash}$}
+O$^{+8}$ \cite{Tribedi_O_water} on water.
+H$^{+}$ impact on 
+{\fontsize{11}{20}${\color{red}\pmb{\boxast}}$}~N$_2$, 
+{\fontsize{11}{20}${\color{red}\pmb{\boxbox}}$}~O$_2$, 
+{\fontsize{11}{20}${\color{red}\pmb{\boxbar}}$}~CO, 
+{\fontsize{11}{20}${\color{red}\pmb{\boxbslash}}$}~CO$_2$, and
+{\fontsize{11}{20}${\color{red}\pmb{\boxdot}}$}~CH$_4$; 
+and He$^{+2}$ impact on 
+{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxast}}$}~N$_2$,
+{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxbox}}$}~O$_2$, 
+{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxbar}}$}~CO, 
+{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxbslash}}$}~CO$_2$, and
+{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxdot}}$}~CH$_4$~\cite{Rudd85,Rudd1983}, 
+{\fontsize{11}{20}${\color{red}\pmb{\varowedge}}$}~H$^{+}$ on CH$_4$~\cite{Luna2019}; 
 and electron impact on $\rhd$~pyrimidine~\cite{bug2017}, and $\lhd$, $\medstar$~\cite{wolf2019,fuss2009} THF.}
@@
 $\sigma$ is the ionization cross section for the molecular target, $\alpha=1.2$ and $n_e$ is the number of active electrons per molecule given in Table \ref{nn}.
-%It is important to point out that the scaling is based on CDW results atomic H, C, N, O, and P targets, so it is only  valid for ionization cross sections %by charged ions (at least up to +8) of molecules composed by these atoms.%, unless other values for ne were obtained for other atomic targets.
-In Fig.~\ref{fig:zalpha}, we test the universal scaling of Eq. (\ref{u-scaling}) %by showing in the same plot 
-for all the theoretical and experimental values displayed in Fig. \ref{fig:zreduced}. 
-As can be noted, the universal scaling works well, all the curves and data lays in a narrow band valid for any charged ion (scaling with Z) in any molecule (scaling with the number of active electrons).
-We decided not including in this figure the data for uracil from Ref.~\cite{agnihotri2012,agnihotri2013}, and for Li$^{+3}$ on water Ref.~\cite{Luna_Li_water}.
+In Fig.~\ref{fig:zalpha}, we test the universal scaling of Eq.
+(\ref{u-scaling}) for all the theoretical and experimental values displayed in Fig.
+\ref{fig:zreduced}.
+We also included a gray area representing the 30\% deviation of our theoretical curves.
+As can be noted, the universal scaling works very well.
+All the curves and data lays in a narrow band valid for any charged ion (scaled with Z) in any molecule (scaled with the number of active electrons).
+We decided not to include in this figure the data for uracil from Refs.~\cite{agnihotri2012,agnihotri2013}, and for Li$^{+3}$ on water~\cite{Luna_Li_water}.
 The discussion about these experimental values exceeds the present work.
@@
 
-\bibitem{montenegro_pra13} E. C. Montenegro, G. M. Sigaud,  and R. D. DuBois, Phys. Rev. A \textbf{87} 012706 (2013).
+\bibitem{montenegro_pra13} 
+E. C. Montenegro, G. M. Sigaud, and R. D. DuBois, 
+Phys. Rev. A \textbf{87} 012706 (2013).
 
@@
 \bibitem{wang2016}
-M. Wang, B. Rudek, D. Bennett, P. de Vera, M. Bug, T. Buhr, W. Y. Baek, G. Hilgers, H. Rabus, 
-Phys. Rev. A \textbf{93}, 052711 (2016).\bibitem{tribedi2019} S. Bhattacharjee, C. Bagdia, M. R. Chowdhury, A. Mandal, J. M. Monti, R. D. Rivarola, and L. C. Tribedi, 
+M. Wang, B. Rudek, D. Bennett, P. de Vera, M. Bug, T. Buhr, W. Y. Baek,
+G. Hilgers, H. Rabus, 
+Phys. Rev. A \textbf{93}, 052711 (2016).
+
+\bibitem{tribedi2019} 
+S. Bhattacharjee, C. Bagdia, M. R. Chowdhury, A. Mandal, J. M. Monti, 
+R. D. Rivarola, and L. C. Tribedi, 
 Phys. Rev. A \textbf{100}, 012703(2019).
@@
 \bibitem{agnihotri2012}
-A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A.
-Kumar, M. E. Galassi, R. D. Rivarola, O. Foj\'{o}n, C. Champion, J. Hanssen, H. Lekadir, P. F. Weck, and L. C. Tribedi. 
+A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A. Kumar, M. E. Galassi, 
+R. D. Rivarola, O. Foj\'on, C. Champion, J. Hanssen, H. Lekadir, 
+P. F. Weck, and L. C. Tribedi. 
 Phys. Rev. A \textbf{85}, 032711 (2012).
@@
 \bibitem{agnihotri2013}
-A N Agnihotri, S Kasthurirangan, S Nandi, A Kumar, C Champion,, H Lekadir, J Hanssen, P FWeck, M E Galassi, R D Rivarola, O Fojon and L C Tribedi, 
+A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A. Kumar, C. Champion, 
+H. Lekadir, J. Hanssen, P. F. Weck, M. E. Galassi, R. D. Rivarola, O. Foj\'on and 
+L. C. Tribedi, 
 J. Phys. B: At. Mol. Opt. Phys. \textbf{46}, 185201 (2013).
@@
 \bibitem{Luna2007}
-H. Luna, A. L. F. de Barros, J. A. Wyer, S. W. J. Scully, J. Lecointre, P. M. Y. Garcia, G. M. Sigaud, A. C. F. Santos,
-V. Senthil, M. B. Shah, C. J. Latimer, and E. C. Montenegro,
+H. Luna, A. L. F. de Barros, J. A. Wyer, S. W. J. Scully, J. Lecointre, 
+P. M. Y. Garcia, G. M. Sigaud, A. C. F. Santos, V. Senthil, M. B. Shah, 
+C. J. Latimer, and E. C. Montenegro,
 Phys. Rev. A \textbf{75}, 042711 (2007).
 
-%\bibitem{Champion2007}C. Champion, O. Boudrioua, C. Dal Cappello, Y. Sato, D. Ohsawa, Phys. Rev. A 75 (2007) 032724.
+\bibitem{Rudd86} 
+M. A. Bolorizadeh and M. E. Rudd, 
+Phys. Rev. A \textbf{33}, 888 (1986).
 
-\bibitem{Rudd86} M. A. Bolorizadeh and M. E. Rudd, Phys. Rev. A \textbf{33}, 888 (1986).
+\bibitem{pRudd85} 
+M. E. Rudd, T. V. Goffe, R. D. DuBois, L. H. Toburen, 
+Phys. Rev. A \textbf{31}, 492 (1985).
+
+\bibitem{toburen80} 
+L. H. Toburen, W. E. Wilson and R. J. Popowich,
+Radiat. Res. \textbf{82}, 27--44 (1980).
 
 % He$^{+2}$ in water---------------------
-%\bibitem{DalCappello2007} O. Boudrioua, C. Champion, C. Dal Cappello, Y.V. Popov, Phys. Rev. A 75 (2007) 012717.
+\bibitem{Ohsawa05}
+D. Ohsawa, Y. Sato, Y. Okada, V. P. Shevelko, and F. Soga
+Phys. Rev. A \textbf{72}, 062710 (2005).
 
-\bibitem{Rudd85} M. E. Rudd, T. V. Goffe, and A. Itoh,  Phys. Rev. A \textbf{32}, 2128 (1985).
+\bibitem{Rudd85} 
+M. E. Rudd, T. V. Goffe, and A. Itoh, 
+Phys. Rev. A \textbf{32}, 2128 (1985).
 
 % Li$^{+3}$ in water---------------------------
-\bibitem{Luna_Li_water} H. Luna, W. Wolff, and E. C. Montenegro, Andre C. Tavares, H. J. Ludde, G. Schenk, M. Horbatsch, and T. Kirchner, Phys. Rev. A \textbf{93}, 052705 (2016).
+\bibitem{Luna_Li_water} 
+H. Luna, W. Wolff, E. C. Montenegro, Andre C. Tavares, H. J. Ludde, 
+G. Schenk, M. Horbatsch, and T. Kirchner, 
+Phys. Rev. A \textbf{93}, 052705 (2016).
 
@@
 \bibitem{DalCappello2009}
-C. Dal Cappello, C. Champion, O. Boudrioua, H. Lekadir, Y. Sato , D. Ohsawa, 
+C. Dal Cappello, C. Champion, O. Boudrioua, H. Lekadir, Y. Sato, D. Ohsawa, 
 Nuclear Instruments and Methods in Physics Research B 267 (2009) 781--790.
 
+\bibitem{Bhattacharjee17}
+Shamik Bhattacharjee, S. Biswas, J. M. Monti, R. D. Rivarola, and L. C. Tribedi,
+Phys. Rev A \textbf{96}, 052707 (2017).
+
 %O$^{+8}$ in water -------------------------------
-\bibitem{Tribedi_O_water} S.
-Bhattacharjee, S.
-Biswas, C.
-Bagdia, M.
-Roychowdhury, S.
-Nandi, D.
-Misra, J.
-M.
-Monti, C.
-A.
-Tachino, R.
-D.
-Rivarola, C.
-Champion and L.
-C.
-Tribedi, J.
-Phys.
-B: At.
-Mol.
-Opt.
-Phys.
-\textbf{49,}  065202 (2016).
+\bibitem{Tribedi_O_water} 
+S. Bhattacharjee, S. Biswas, C. Bagdia, M. Roychowdhury, S. Nandi, 
+D. Misra, J. M. Monti, C. A. Tachino, R. D. Rivarola, C. Champion and 
+L. C. Tribedi, J. 
+Phys. B: At. Mol. Opt. Phys. \textbf{49,}  065202 (2016).
 
@@
 
-\bibitem{sarkadi2016} L Sarkadi, J. Phys. B: At. Mol. Opt. Phys. \textbf{49} 185203 (2016)
+\bibitem{sarkadi2016}
+L. Sarkadi, 
+J. Phys. B: At. Mol. Opt. Phys. \textbf{49} 185203 (2016)
 
 % H+ in CH4 and CO2-----------------------------------------
-\bibitem{Rudd1983} M. E. Rudd, R. D. DuBois, L. H. Toburen, and C. A. Ratcliffe, T. V. Goffe, Phys. Rev. A \textbf{28}, 3244 (1983).
+\bibitem{Rudd1983} 
+M. E. Rudd, R. D. DuBois, L. H. Toburen, and C. A. Ratcliffe, T. V. Goffe, 
+Phys. Rev. A \textbf{28}, 3244 (1983).
 
-\bibitem{Luna2019} H. Luna, W. Wolff, and E. C. Montenegro, L. Sigaud, Phys. Rev. A \textbf{99}, 012709 (2019).
+\bibitem{Luna2019} 
+H. Luna, W. Wolff, and E. C. Montenegro, L. Sigaud, 
+Phys. Rev. A \textbf{99}, 012709 (2019).
 

### 2020-05-11 zscaling/zscaling.tex
reviewers comments

@@
-\documentclass[10pt,showpacs,showkeys,twocolumn]{revtex4}
+\documentclass[10pt,showpacs,showkeys,twocolumn]{revtex4-1}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % \usepackage[T1]{fontspec}
+\usepackage{bm}
 \usepackage{amssymb}
@@
 \usepackage{multirow}
-\usepackage{gensymb}
-\usepackage{float}
 \usepackage{MnSymbol}
-\usepackage{gensymb}
-\usepackage{comment}
 \usepackage{wasysym} 
 \usepackage{stmaryrd}
+\usepackage[outline]{contour}
+\usepackage[dvipsnames]{xcolor}
+\usepackage{float}
+
+\definecolor{olive}{RGB}{182,187,37}
+\usepackage[mathlines]{lineno}% Enable numbering of text and display math
+%\linenumbers\relax % Commence numbering lines
 
@@
 
-\title[Universal scaling for the ionization of biological molecules]{
-Universal scaling for the ionization of biological molecules by highly charged ions}
+\title[General scaling rule for the ionization of biological molecules]{
+General scaling rule for the ionization of biological molecules \\ by 
+highly charged ions}
 \author{A. M. P. Mendez, C. C. Montanari, J. E. Miraglia}
 \affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio 
-(CONICET--UBA), \\ Buenos Aires, Argentina.}
+(CONICET-UBA), \\ Buenos Aires, Argentina.}
 
-\date{\today}% It is always \today, today,
+\date{}% It is always \today, today,
 
 \begin{abstract}
-In the present work, we investigate scaling rules for the ionization cross sections of multicharged ions on molecules of biological interest.
-The cross sections are obtained from distorted--wave calculations for atomic targets combined with a stoichiometric model for the molecules proposed in [Mendez \textit{et al.} J.
-Phys B (2020)].
-We examine ions with charges $Z$ from $+1$ to $+8$ in five nucleobases --adenine, cytosine, guanine, thymine, uracil--, tetrahydrofuran, pyrimidine, and also in water.
-We propose a scaling with the ion charge, which is valid in the intermediate to high energy range, i.e.
-0.2-5 MeV/amu for oxygen impact.
-We extend our work to a universal scaling for any ion and molecule, merging the forty ion--molecule systems analyzed here into a single band.
-Furthermore, our model proved to be valid for other molecules too.
+In the present work, we investigate scaling rules for the ionization 
+cross sections of multicharged ions on molecules of biological interest. 
+The cross sections are obtained using a methodology presented in 
+[Mendez \textit{et al.} J. Phys B (2020)], which considers distorted-wave 
+calculations for atomic targets combined with a molecular stoichiometric 
+model. We examine ions with nuclear charges $Z$ from $+1$ to $+8$ 
+impacting on five nucleobases --adenine, cytosine, guanine, thymine, 
+uracil--, tetrahydrofuran, pyrimidine, and water. We propose a scaling 
+with the ion charge, which is valid in the intermediate to high energy 
+range, i.e., 0.2-5 MeV/amu for oxygen impact. We extend our work to a 
+universal scaling for any ion and molecule, merging the forty 
+ion-molecule systems analyzed here into a single band. Furthermore, our 
+model proved to be valid for other molecules too.  
 \end{abstract}
@@
 %\ioptwocol
+\linenumbers
 
-The ionization of biological molecules by multicharged ions has gained increasing interest due to medical and environmental reasons~\cite{PhysMed}, from medical treatments~\cite{Mohamad2017,Solov2009,Denifl2011} to contaminant recognition in biological materials~\cite{water,ferrazdias}.
-Many semiempirical \citep{vera_prl2013} and theoretical efforts are currently being undertaken~\cite{MendezJPB20,Quinto20,ludde2019,ludde2018,ludde2016,Champion2012} to get reliable values for the ionization cross sections of these molecules.
+The ionization of biological molecules by multicharged ions has gained 
+increasing interest due to medical and environmental 
+implementations~\cite{PhysMed}, which includes medical 
+treatments~\cite{Mohamad2017,Solov2009,Denifl2011} and contaminant 
+recognition in biological materials~\cite{water,ferrazdias}. 
+Many semiempirical \citep{vera_prl2013} and theoretical efforts are 
+currently being undertaken~\cite{MendezJPB20,Quinto20,ludde2019,ludde2018,
+ludde2016,Champion2012} to get reliable values for the ionization cross 
+sections of these molecular systems.
 
-Recently, we combined the continue distorted--wave calculations (CDW) for atoms and the simple stoichiometric model (SSM) to approximate the ionization cross sections of complex molecular targets by charged ions~\cite{MendezJPB20}.
-The CDW--SSM approximation showed reasonable results for over a hundred of ion--molecule systems.
-As expected, in the high energy range (i.e.
-above 5 MeV/amu) the ionization cross sections  present the $Z^2$ dependence predicted by the first Born approximation.
-However, at intermediate energies, the dependence with $Z$ is more complex, and non--perturvative models are mandatory.
+In recent work~\cite{MendezJPB20}, we combined the continuum 
+distorted-wave calculations (CDW) for atoms and the simple 
+stoichiometric model (SSM), also known as the Bragg sum rule, to 
+approximate the ionization cross sections of complex molecular targets 
+by charged ions. The CDW-SSM approximation showed consistent results 
+for over a hundred of ion-molecule systems. As expected, in the high 
+energy range (i.e., above 5 MeV/amu), the ionization cross sections of
+the molecular systems follow the $Z^2$ dependence predicted by the 
+first Born approximation. However, at intermediate energies, the 
+dependence with $Z$ is not straightforward since non-perturbative 
+models are mandatory.
 
-The intention of this letter is to give a follow up of our previous work~\cite{MendezJPB20} by proposing a scaling with the ion charge $Z$ of the ionization cross sections of complex molecules, valid at intermediate energies.
-In general, scaling rules are used as first--order tests in experimental measurements and multipurpose codes.
-Based on ~\cite{MendezJPB20}, we propose a universal scaling for any ion--target system.%, which is valid initially for the complex biological molecules studied here.
+This letter intends to give a follow up of our previous work by 
+proposing a scaling rule for the ionization cross sections of complex 
+molecules with the ion charge $Z$, which is valid at intermediate 
+energies. In general, scaling rules are used as first-order 
+approximations in experimental measurements and multipurpose codes. 
+Furthermore, we explore the generality of our scaling rule by inspecting 
+various other ion-target systems.
 
-At intermediate impact energies, %the $Z^2$ rule no longer holds. 
-Janev and Presnyakov~\cite{janev1980} suggest $\sigma/Z$ versus $E/Z$ as the \textit{natural} reduced form of the ionization cross section $\sigma$ and the incident ion energy $E$.
-Much more recently, Montenegro and co--workers~\cite{dubois13,montenegro_pra13} proposed an alternative scaling by taking into account that  $\sigma$ is a function of $Z^2/E$.
-Their scaling, given by
+We have found in the literature two scaling rules applicable at 
+intermediate impact energy range. The scaling rule suggested by Janev 
+and Presnyakov~\cite{janev1980} depends linearly with ion charge $Z$,
+considering $\sigma/Z$ versus $E/Z$ to be the \textit{natural} reduced 
+form of the ionization cross section $\sigma$ and the incident ion 
+energy $E$. More recently, Montenegro and co-workers~\cite{dubois13,
+montenegro_pra13} proposed an alternative scaling by taking into account 
+that the cross section is a function of $Z^2/E$. Their scaling, given by 
 \begin{equation}
@@
 \end{equation}
-keeps the $Z^2/E$ relationship for any value of $\alpha$. 
-In Ref.~\cite{dubois13}, the authors propose $\alpha=4/3$ for ionization of He and H$_2$ by different charged ions.
+keeps the $Z^2/E$ relationship for any value of the parameter $\alpha$. 
+In Ref.~\cite{dubois13}, the authors propose $\alpha=4/3$ for ionization 
+of He and H$_2$ by differently charged ions.
 
-\begin{figure*}[!t]%[h]
+Combining our recent CDW-SSM results~\cite{MendezJPB20} and 
+Eq.~(\ref{Montenegro}), we propose here a $Z$-scaling and implement it 
+for forty collisional systems. The ion-molecule systems are composed of 
+eight targets: the DNA and RNA nucleobases --adenine, cytosine, guanine, 
+thymine, uracil--, tetrahydrofuran (THF), pyrimidine, and water; and 
+five ion species: H$^+$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
+We considered these systems as a benchmark for the present scaling.
+
+We found that the parameter $\alpha$ from Eq.~(\ref{Montenegro}) that 
+fits the CDW-SSM scaled cross sections for all the ions is $\alpha=1.2$. 
+The validity of the theoretical scaling with the ion charge is evident
+in Fig.~\ref{fig:zreduced}, where the CDW-SSM curves lay one over the 
+other. Our theoretical results are valid for impact energies around and 
+above the maximum of the cross sections, which corresponds to an impact
+energy range from 50 keV for H$^+$ to 250 keV/amu for O$^{+8}$.
+
+The scaling was tested with the experimental data available for 
+ionization by the impact of differently charged ions \cite{itoh2013,
+iriki2011,wolff2014,wang2016,tribedi2019,agnihotri2012,agnihotri2013,
+Luna2007,Rudd86,Rudd85,Luna_Li_water,DalCappello2009,Tribedi_O_water}, 
+and also by electron impact at sufficiently high velocity 
+\cite{rahman2016,bug2017,wolf2019,fuss2009}. As can be noted, most of 
+the data in Fig.~\ref{fig:zreduced} confirm the present scaling, even 
+for O$^{+8}$ in water~\cite{Tribedi_O_water}. However, the data of 
+uracil by swift C, O, and F ions in \cite{agnihotri2012,agnihotri2013} 
+are too low compared with our CDW-SSM results, but also as compared 
+with Itoh \textit{et al.} data \cite{itoh2013}, and with the CTMC 
+calculations by Sarkadi~\cite{sarkadi2016}. The data for Li$^{+3}$ in 
+water from Ref.~\cite{Luna_Li_water} also spreads out from the present 
+theoretical curves for $E<600$ keV/amu.
+
+The good results obtained in the scaling with the ion charge challenged 
+us to look for a more general scaling rule that could predict values 
+for ionization cross sections of any ion in any molecule. To that end, 
+we resorted to the number of active electrons in each atom $n_e$ 
+proposed in \cite{MendezJPB20}, and combined it with the $Z$-scaling 
+displayed in Fig.~\ref{fig:zreduced}.
+
+\begin{figure*}[!htb]
 \centering
-\includegraphics[width=0.7\textwidth]{zscale_alpha.eps}
-\caption{(Color online) Scaled ionization cross section $\sigma/Z^{\alpha}$ as a function 
-of ion impact energy $E/Z^{2-\alpha}$.%, given by Eq. (\ref{Montenegro}). 
-%Colors are asociated with the impact charge as signed in the upper part of the figure. 
+\includegraphics[width=0.9\textwidth]{zscale_alpha.eps}
+\caption{(Color online) Scaled ionization cross section $\sigma/Z^{\alpha}$ 
+as a function of ion impact energy $E/Z^{2-\alpha}$ with $\alpha=1.2$. 
 Colors are associated with the incident ion labeled on top of the figure. 
-Curves: present CDW--SSM theoretical results.
-Symbols: experimental impact of 
-\mbox{\Large$\circ$} H$^+$~\cite{iriki2011} and 
-$\lozenge$ C$^{+6}$ \cite{tribedi2019} on adenine;
-H$^+$ on  $\triangle$ uracil~\cite{itoh2013}, 
-$\ominus$ C$^{+4}$, 
-$\oplus$ C$^{+6}$, O$^{+6}$, F$^{+6}$, and 
-$\otimes$ O$^{+8}$, F$^{+8}$ on uracil~\cite{agnihotri2012,agnihotri2013};
-H$^+$ on $\triangledown$ pyrimidine~\cite{wolff2014}, and
-$\meddiamond$ THF~\cite{wang2016};
-\mbox{\fontsize{10}{20} $\varhexagon$} H$^+$ \cite{Luna2007}, 
-$\pentagon$ H$^+$ \cite{Rudd86}, 
-$\odot$ He$^{+2}$ \cite{Rudd85},  
-$\logof$ Li$^{+3}$ \cite{Luna_Li_water},  
-$\ovee$ C$^{+6}$ \cite{DalCappello2009}, and 
-$\varobslash$ O$^{+8}$ \cite{Tribedi_O_water} on water.
+Curves: present CDW-SSM theoretical results. Symbols: experimental 
+impact of \mbox{\LARGE$\color{red}\circ$} H$^+$~\cite{iriki2011} and
+{\fontsize{11}{20}$\color{Purple}\pmb{\lozenge}$} C$^{+6}$ 
+\cite{tribedi2019} on adenine;
+H$^+$ on {\fontsize{11}{20}$\color{red}\pmb{\triangle}$} uracil~\cite{itoh2013}, 
+{\fontsize{11}{20}$\color{NavyBlue}\pmb{\ominus}$} C$^{+4}$, 
+{\fontsize{11}{20}$\color{Purple}\pmb{\oplus}$} C$^{+6}$, O$^{+6}$, F$^{+6}$, and 
+{\fontsize{11}{20}$\color{BurntOrange}\pmb{\otimes}$} O$^{+8}$, 
+F$^{+8}$ on uracil~\cite{agnihotri2012,agnihotri2013};
+H$^+$ on {\fontsize{11}{20}$\color{red}\pmb{\triangledown}$} 
+pyrimidine~\cite{wolff2014}, and 
+{\fontsize{10}{20}$\color{red}\pmb{\meddiamond}$} THF~\cite{wang2016};
+% water
+\mbox{\fontsize{11}{20}$\color{red}\pmb{\odot}$}~\cite{Luna2007}, 
+{\fontsize{11}{20}\color{red}$\pmb{\logof}$}~\cite{Rudd86}, 
+{\fontsize{11}{20}\color{red}$\pmb{\varowedge}$}~\cite{pRudd85}, 
+{\fontsize{11}{20}\color{red}$\pmb{\varoslash}$}~\cite{toburen80} H$^+$,
+{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varolessthan}$}~\cite{Ohsawa05},
+{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varogreaterthan}$}~\cite{Rudd85},
+{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varoslash}$}~\cite{toburen80} He$^{+2}$,
+{\fontsize{11}{20}\color{Purple}$\pmb{\ovee}$}~C$^{+6}$ \cite{DalCappello2009,Bhattacharjee17}, and 
+{\fontsize{11}{20}\color{BurntOrange}$\pmb{\obslash}$}
+O$^{+8}$ \cite{Tribedi_O_water} on water.
 Markers~$\square$~\cite{rahman2016}, 
@@
 $\lhd$~\cite{wolf2019}, and 
-$\medstar$~\cite{fuss2009} correspond to electron impact ionization with the equi-velocity conversion.}
+$\medstar$~\cite{fuss2009} correspond to electron impact ionization with 
+the equi-velocity conversion.}
 \label{fig:zreduced}
@@
 
-% We consider our recent CDW-SSM results \cite{MendezJPB20} for eight targets (DNA and RNA nucleo-basis, tetrahydrofuran (THF) and pyrimidine) and five charged ions (H$^+$m He$^+2$, Be$^+4$, C$^+6$, and O$^+8$)eight targets (DNA and RNA nucleo-basis, tetrahydrofuran (THF) and pyrimidine) and five charged ions (H$^+$m He$^+2$, Be$^+4$, C$^+6$, and O$^+8$) as benchmark for the present scaling.
+The CDW ionization cross sections $\sigma^{\mathrm{CDW}}$ of atomic H, 
+C, N, O targets scale as $\sigma_e=\sigma^{\mathrm{CDW}}/n_e$ with $n_e$ 
+being $1$ for H, $4$ for C, N, and O, i.e.,
+\begin{equation}
+ \frac{\sigma_{\mathrm{H}}^{\mathrm{CDW}}}{1}\sim
+ \frac{\sigma_{\mathrm{C}}^{\mathrm{CDW}}}{4}\sim
+ \frac{\sigma_{\mathrm{N}}^{\mathrm{CDW}}}{4}\sim
+ \frac{\sigma_{\mathrm{O}}^{\mathrm{CDW}}}{4}
+\end{equation}
+The SSM leads to the molecular numbers of active electrons included in 
+Table \ref{nn}.
 
-Combining our recent CDW--SSM results~\cite{MendezJPB20} and Eq.~(\ref{Montenegro}), we propose here a $Z$-scaling and implement it for forty collisional systems.
-The ion--molecule systems are composed of eight targets: the DNA and RNA nucleobases --adenine, cytosine, guanine, thymine, uracil--, tetrahydrofuran (THF), pyrimidine, and water; and five charged ions: H$^+$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$.
-We considered these systems as a benchmark for the present scaling.
+\contourlength{0.03em}
+\contournumber{30}
 
-%We found that $\sigma/Z^{\alpha}$ vs.
-$E^{2-\alpha}$, with $\alpha=1.2$ best fits the CDW-SSM scaled cross sections for all the ions.
-%$Z=+1$ to $+8$.
-, giving similar energy for the maximum of the cross sections.
-%, as displayed in  figure \ref{fig:zreduced}.
-We found that the parameter $\alpha$ from Eq.~(\ref{Montenegro}) that fits the CDW--SSM scaled cross sections for all the ions is $\alpha=1.2$. 
-The validity of the theoretical scaling with the ion charge is very clear in Fig.~\ref{fig:zreduced}, where the CDW-SSM curves lays one over the other.
-Our theoretical results are valid for impact energies around and above the maximum of the cross sections, which means above 50 keV for impact of H$^+$  to 250 keV/amu for impact of O$^{+8}$.
-
-The scaling was tested with the experimental data available %for these eight molecules 
-by impact of different charged ions \cite{itoh2013,iriki2011,wolff2014,wang2016,tribedi2019,agnihotri2012,agnihotri2013,Luna2007,Rudd86,Rudd85,Luna_Li_water,DalCappello2009,Tribedi_O_water},
-and also by electron impact at sufficiently high velocity \cite{rahman2016,bug2017,wolf2019,fuss2009}.
-As can be noted, most of the data in Fig.~\ref{fig:zreduced} confirms the present scaling, even for O$^{+8}$ in water~\cite{Tribedi_O_water}.
-However, the data of uracil by swift C, O and F ions in \cite{agnihotri2012,agnihotri2013} are too low compared with our CDW--SSM results, but also as compared with Itoh \textit{et al.} data \cite{itoh2013}, and with the CTMC calculations by Sarkadi \cite{sarkadi2016}.
-%as compared to proton impact measurements by Itoh \textit{et al} \cite{itoh2013} multiplied by $Z^2$. Independent CTMC calculations by Sarkadi \cite{sarkadi2016} also mention this. 
-The data for Li$^{+3}$ in water from Ref.~\cite{Luna_Li_water} also spreads out from the present theoretical curves for $E<600$ keV/amu.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\section{Universal Scaling rule}
-%\label{sec:U-scaling}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The good results obtained in the scaling with the ion charge challenged us to look for a more general scaling rule that could predict values for ionization cross sections of any ion in any molecule.
-% that scales ions and molecules
-%Based on he good results shown in figure \ref{fig:zreduced}  and the scaling with the number of active electrons $n_e$ in each atom in  \cite{MendezJPB20}, we went further for an universal scaling that involves the different molecules biomolecules studied here, and
-To that end, we resorted to the %scaling with the 
-number of active electrons in each atom $n_e$ proposed in \cite{MendezJPB20}, and combined it with the $Z$-scaling displayed in Fig.~\ref{fig:zreduced}.
-%given by Eq.
-(\ref{Montenegro}) with $\alpha=1.2$.
-
-The CDW ionization cross sections $\sigma^{\mathrm{CDW}}$ of atomic H, C, N, O targets scale as $\sigma_e=\sigma^{\mathrm{CDW}}/n_e$ with $n_e$ being $1$ for H, $4$ for C, N, and O.
-%; and $4.5$ for P and S.
-The SSM leads to the molecular numbers of active electrons included in Table \ref{nn}.
-
-\begin{table}[H]
+\begin{table}[t]
 \begin{center}
@@
 \hline
- Molecule & $n_e$ &Molecule          & $n_e$ & Molecule             & $n_e$\\
+ Molecule & $n_e$ & Molecule          & $n_e$ & Molecule          & $n_e$ \\
 \hline
-% --------------------------------------------------------------------------------
-% H$_2$    & 2  & CH$_5$N             \ \ \ \ & 13    & C$_4$H$_5$N$_3$O     \ \ \ \ & 37   \\ %H2 -pyridine  -cytosine
-% H$_2$O   & 6  & C$_4$H$_8$O         \ \ \ \ & 28    & C$_5$H$_6$N$_2$O$_2$ \ \ \ \ & 42   \\ %H2O-THF       -thymine
-% O$_2$    & 8  & C$_4$H$_4$N$_2$    \ \ \ \  & 28    & C$_5$H$_5$N$_5$      \ \ \ \ & 45   \\ %O2- pyrimidine-adenine
-% CH$_4$   & 8  & C$_6$H$_6$          \ \ \ \ & 30    & C$_5$H$_5$N$_5$O     \ \ \ \ & 49   \\ %methane-benzene-guanine
-% CO$_2$   & 12 & C$_4$H$_4$N$_2$O$_2$\ \ \ \ & 36    & C$_5$H$_{10}$O$_5$P \ \ \ \ & 54.5 
-% \\ %CO2- uracil-backbone
-%--------------------------------------------------------------------------------
-% Nueva tabla
-% -------------------------------------------------------------------------------
- H$_2$O   & 6   &  CO$_2$  \ \ \ \ & 12  & C$_4$H$_5$N$_3$O     \ \ \ \ & 37   \\ %H2 -CO2  -cytosine
- N$_2$    & 8  & C$_4$H$_8$O         \ \ \ \ & 28    & C$_5$H$_6$N$_2$O$_2$ \ \ \ \ & 42   \\ %H2O-THF       -thymine
- O$_2$    & 8  & C$_4$H$_4$N$_2$    \ \ \ \  & 28    & C$_5$H$_5$N$_5$      \ \ \ \ & 45   \\ %O2- pyrimidine-adenine
- CH$_4$   & 8  & C$_4$H$_4$N$_2$O$_2$ \ \ \ \ &  36   & C$_5$H$_5$N$_5$O     \ \ \ \ & 49   \\ %methane-uracil-guanine
-% --------------------------------------------------------------------------------
+ H$_2$O   & 6  & CO$_2$               & 12 & C$_4$H$_5$N$_3$O     & 37   \\ 
+ N$_2$    & 8  & C$_4$H$_8$O          & 28 & C$_5$H$_6$N$_2$O$_2$ & 42   \\ 
+ O$_2$    & 8  & C$_4$H$_4$N$_2$      & 28 & C$_5$H$_5$N$_5$      & 45   \\ 
+ CH$_4$   & 8  & C$_4$H$_4$N$_2$O$_2$ & 36 & C$_5$H$_5$N$_5$O     & 49   \\ 
  \hline
 \end{tabular}
-\caption{Number of active electrons per target at intermediate to high energies obtained from the CDW calculations~\cite{MendezJPB20}.}
+\caption{Number of active electrons per target at intermediate to high 
+energies obtained from the CDW calculations~\cite{MendezJPB20}.}
 \label{nn}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{zmol_alpha.eps}
-\caption{(Color online) Universal scaling with the ions charge $Z$ and the number of active electrons in the molecule $n_e$ given by Eq.
-(\ref{u-scaling}).
-Curves: present CDW-SSM theoretical results.
-Symbols: experimental impact of H$^+$ on 
-\mbox{\Large$\circ$} adenine~\cite{iriki2011}, 
-$\triangle$ uracil~\cite{itoh2013}, 
-$\triangledown$ pyrimidine~\cite{wolff2014} and 
-$\meddiamond$ THF~\cite{wang2016};
-$\lozenge$ C$^{+6}$ on adenine \cite{tribedi2019};
-\mbox{\fontsize{10}{20} $\varhexagon$} H$^+$ \cite{Luna2007},
-$\pentagon$ H$^+$ \cite{Rudd86}, 
-$\odot$ He$^{+2}$ \cite{Rudd85},  
-$\ovee$ C$^{+6}$ \cite{DalCappello2009}, and 
-$\boxslash$ O$^{+8}$ \cite{Tribedi_O_water} on water;
-H$^{+}$ and He$^{+2}$ impact on 
-$\boxast$~N$_2$, 
-$\boxbox$~O$_2$,
-$\boxbar$~CO, 
-$\boxbslash$~CO$_2$, and
-$\boxdot$~CH$_4$ \cite{Rudd85,Rudd1983}, 
-$\varowedge$~H$^{+}$ on CH$_4$~\cite{Luna2019}; 
-and electron impact on $\rhd$~pyrimidine~\cite{bug2017}, and $\lhd$, $\medstar$~\cite{wolf2019,fuss2009} THF.}
+\includegraphics[width=0.7\textwidth]{zmol_werror.eps}
+\caption{(Color online) Universal scaling with the ions charge $Z$ and 
+the number of active electrons in the molecule $n_e$ given by Eq. 
+(\ref{u-scaling}) with $\alpha=1.2$. Curves: present CDW-SSM theoretical 
+results. Symbols: experimental impact of H$^+$ on 
+\mbox{\LARGE$\color{red}\circ$} adenine~\cite{iriki2011}, 
+{\fontsize{11}{20}$\color{red}\pmb{\triangle}$} uracil~\cite{itoh2013}, 
+{\fontsize{11}{20}$\color{red}\pmb{\triangledown}$} pyrimidine~\cite{wolff2014} and 
+{\fontsize{10}{20}$\color{red}\pmb{\meddiamond}$} THF~\cite{wang2016};
+{\fontsize{11}{20}$\color{Purple}\pmb{\lozenge}$} C$^{+6}$ on adenine \cite{tribedi2019};
+\mbox{\fontsize{11}{20}$\color{red}\pmb{\odot}$}~\cite{Luna2007}, 
+{\fontsize{11}{20}\color{red}$\pmb{\logof}$}~\cite{Rudd86}, 
+{\fontsize{11}{20}\color{red}$\pmb{\varowedge}$}~\cite{pRudd85}, 
+{\fontsize{11}{20}\color{red}$\pmb{\varoslash}$}~\cite{toburen80} H$^+$,
+{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varolessthan}$}~\cite{Ohsawa05},
+{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varogreaterthan}$}~\cite{Rudd85},
+{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varoslash}$}~\cite{toburen80} He$^{+2}$,
+{\fontsize{11}{20}\color{Purple}$\pmb{\ovee}$}~C$^{+6}$ \cite{DalCappello2009,Bhattacharjee17}, and 
+{\fontsize{11}{20}\color{BurntOrange}$\pmb{\obslash}$}
+O$^{+8}$ \cite{Tribedi_O_water} on water.
+H$^{+}$ impact on 
+{\fontsize{11}{20}${\color{red}\pmb{\boxast}}$}~N$_2$, 
+{\fontsize{11}{20}${\color{red}\pmb{\boxbox}}$}~O$_2$, 
+{\fontsize{11}{20}${\color{red}\pmb{\boxbar}}$}~CO, 
+{\fontsize{11}{20}${\color{red}\pmb{\boxbslash}}$}~CO$_2$, and
+{\fontsize{11}{20}${\color{red}\pmb{\boxdot}}$}~CH$_4$; 
+and He$^{+2}$ impact on 
+{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxast}}$}~N$_2$,
+{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxbox}}$}~O$_2$, 
+{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxbar}}$}~CO, 
+{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxbslash}}$}~CO$_2$, and
+{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxdot}}$} 
+CH$_4$~\cite{Rudd85,Rudd1983}, 
+{\fontsize{11}{20}${\color{red}\pmb{\varowedge}}$}~H$^{+}$ on 
+CH$_4$~\cite{Luna2019}; 
+and electron impact on $\rhd$~pyrimidine~\cite{bug2017}, and $\lhd$, 
+$\medstar$~\cite{wolf2019,fuss2009} THF.}
 \label{fig:zalpha}
@@
 
-The universal scaling we propose here is expressed as $\sigma_U$ as a function of $E/Z^{2-\alpha}$, with
+The universal scaling we propose here is expressed as $\sigma_U$ as a 
+function of $E/Z^{2-\alpha}$, with
  \begin{equation}
@@
  \end{equation}
-$\sigma$ is the ionization cross section for the molecular target, $\alpha=1.2$ and $n_e$ is the number of active electrons per molecule given in Table \ref{nn}.
-%It is important to point out that the scaling is based on CDW results atomic H, C, N, O, and P targets, so it is only  valid for ionization cross sections %by charged ions (at least up to +8) of molecules composed by these atoms.%, unless other values for ne were obtained for other atomic targets.
-In Fig.~\ref{fig:zalpha}, we test the universal scaling of Eq. (\ref{u-scaling}) %by showing in the same plot 
-for all the theoretical and experimental values displayed in Fig. \ref{fig:zreduced}. 
-As can be noted, the universal scaling works well, all the curves and data lays in a narrow band valid for any charged ion (scaling with Z) in any molecule (scaling with the number of active electrons).
-We decided not including in this figure the data for uracil from Ref.~\cite{agnihotri2012,agnihotri2013}, and for Li$^{+3}$ on water Ref.~\cite{Luna_Li_water}.
-The discussion about these experimental values exceeds the present work.
-%is open for future work.
+$\sigma$ is the ionization cross section for the molecular target, 
+$\alpha=1.2$ and $n_e$ is the number of active electrons per molecule 
+given in Table \ref{nn}. In Fig.~\ref{fig:zalpha}, we test the universal 
+scaling of Eq.~(\ref{u-scaling}) for all the theoretical and 
+experimental values displayed in Fig. \ref{fig:zreduced}. We also 
+included a gray area representing the 30\% deviation of our theoretical 
+curves. As can be noted, the universal scaling works very well. All the 
+curves and data lays in a narrow band valid for any charged ion (scaled 
+with Z) in any molecule (scaled with the number of active electrons). 
+We decided not to include in this figure the data for uracil from 
+Refs.~\cite{agnihotri2012,agnihotri2013}, and for Li$^{+3}$ on 
+water~\cite{Luna_Li_water}. The discussion about these experimental 
+values exceeds the present work. %is open for future work.
 
-In principle, the \textit{universal} scaling should be valid for different ion--molecule combinations. 
-We proved this statement by including in Fig.~\ref{fig:zalpha} the measurements by Rudd \textit{et al.} \cite{Rudd85,Rudd1983} for H$^{+}$ and He$^{+2}$ in N$_2$, O$_2$, CH$_4$, CO and CO$_2$, and the recent values by Luna \textit{et al.} \cite{Luna2019} for H$^{+}$ in CH$_4$.
+In principle, the \textit{universal} scaling should be valid for 
+different ion--molecule combinations. We proved this statement by 
+including in Fig.~\ref{fig:zalpha} the measurements by 
+Rudd~\textit{et al.} \cite{Rudd85,Rudd1983} for H$^{+}$ and He$^{+2}$ 
+in N$_2$, O$_2$, CH$_4$, CO and CO$_2$, and the recent values by 
+Luna~\textit{et al.} \cite{Luna2019} for H$^{+}$ in CH$_4$.
 
-The good agreement shown in Fig.~\ref{fig:zalpha} summaries the main result of this work, and holds the validity of our universal scaling.
-Although the theoretical CDW--SSM results  %Present scaling rule
-are valid for energies above the maximum of the cross sections, the scaling of the experimental data extends to lower impact energies%is more extensive
-, as can be noted in Fig. \ref{fig:zalpha}.
-The importance of scaling rules lays in their predictive capability. New measurements for other ions and molecules are expected to reinforce the present proposal.
+The good agreement shown in Fig.~\ref{fig:zalpha} summaries the main 
+result of this work, and holds the validity of our universal scaling. 
+Although the theoretical CDW-SSM results are valid for energies above 
+the maximum of the cross sections, the scaling of the experimental data 
+extends to lower impact energies, as can be noted in 
+Fig.~\ref{fig:zalpha}. The importance of scaling rules lays in their 
+predictive capability. New measurements for other ions and molecules 
+are expected to reinforce the present proposal.
 
@@
 \section{Conclusions}
-In this letter, we present a scaling for the ionization cross sections of highly charged ions in biological targets.
-The scaling rule states the cross sections divided by $Z^{\alpha}$ as a function of the reduced impact energy $E/Z^{2-\alpha}$, with $\alpha=1.2$.
-The scaling was obtained by means of the CDW-SSM calculations for five different charged ions in eight targets and tested with the available experimental data.
-A universal scaling rule  is also proposed, which reduced the cross sections with the number of active electrons of the molecule.
-The universal scaling proved to be valid for a large number of experimental data.
+In this letter, we present a scaling for the ionization cross sections 
+of highly charged ions in biological targets. The scaling rule states 
+the cross sections divided by $Z^{\alpha}$ as a function of the reduced 
+impact energy $E/Z^{2-\alpha}$, with $\alpha=1.2$. The scaling was 
+obtained by means of the CDW-SSM calculations for five different charged 
+ions in eight targets and tested with the available experimental data. 
+A universal scaling rule  is also proposed, which reduced the cross 
+sections with the number of active electrons of the molecule. The 
+universal scaling proved to be valid for a large number of experimental 
+data.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bigskip
-%\section*{References}
 
@@
 % intro --------------------------------------------------------
-\bibitem{PhysMed} T. Liamsuwan and H. Nikjoo, Phys. Med. Biol. \textbf{58}  641--672 (2013).
+\bibitem{PhysMed} 
+T. Liamsuwan and H. Nikjoo, 
+Phys. Med. Biol. \textbf{58}  641--672 (2013).
 
 \bibitem{Mohamad2017}
-O. Mohamad, B. J. Sishc, J. Saha, A. Pompos, A. Rahimi, M. D. Story, A. J. Davis, D. N. Kim, Cancers \textbf{9}, 66 (2017).
+O. Mohamad, B. J. Sishc, J. Saha, A. Pompos, A. Rahimi, M. D. Story, 
+A. J. Davis, D. N. Kim, 
+Cancers \textbf{9}, 66 (2017).
 
-\bibitem{Solov2009} A. V. Solov'yov, E. Surdutovich, E. Scifoni, I. Mishustin, and W. Greiner, Phys. Rev. E \textbf{79}, 011909 (2009);
+\bibitem{Solov2009}
+A. V. Solov'yov, E. Surdutovich, E. Scifoni, I. Mishustin, and 
+W. Greiner, 
+Phys. Rev. E \textbf{79}, 011909 (2009);
 % https://link.aps.org/doi/10.1103/PhysRevE.79.011909
@@
 
-\bibitem{water} N. A. Gafur, M.  Sakakibara, S. Sano, K. A. Sera, 
+\bibitem{water} 
+N. A. Gafur, M.  Sakakibara, S. Sano, K. A. Sera, 
 % \textit{Case Study of Heavy Metal Pollution in Water of Bone River by Artisanal Small-Scale Gold Mine Activities in Eastern Part of Gorontalo, Indonesia}, 
@@
 
-\bibitem{ferrazdias} D. Benedetti, E. Nunes, M. Sarmento, C. Porto, C. E. Iochims dos Santos, J. Ferraz Dias, J. da Silva,
+\bibitem{ferrazdias} 
+D. Benedetti, E. Nunes, M. Sarmento, C. Porto, C. E. Iochims dos Santos, 
+J. Ferraz Dias, J. da Silva,
 % \textit{Genetic damage in soybean workers exposed to pesticides: Evaluation with the comet and buccal micronucleus cytome assays},
@@
 
-\bibitem{vera_prl2013} P. de Vera, R. Garcia-Molina,I. Abril, and A. V. Solov’yov, Phys. Rev. Lett.  110, 148104 (2013).
+\bibitem{vera_prl2013} 
+P. de Vera, R. Garcia-Molina,I. Abril, and A. V. Solov’yov, 
+Phys. Rev. Lett.  110, 148104 (2013).
 
 % our ---------------------------------------------------------
-\bibitem{MendezJPB20}A. M. P. Mendez, C. C. Montanari, and J. E. Miraglia, J. Phys. B: At. Mol. Opt. Phys.  \textbf{53}, 055201 (2020).
+\bibitem{MendezJPB20}
+A. M. P. Mendez, C. C. Montanari, and J. E. Miraglia, 
+J. Phys. B: At. Mol. Opt. Phys.  \textbf{53}, 055201 (2020).
 
 % others -----------------------------------------------
-\bibitem{Quinto20} M.A. Quinto, J.M. Monti, C.A. Tachino, P.F. Weck, O.A. Foj\'on, C. Champion, R.D. Rivarola, 
+\bibitem{Quinto20} 
+M. A. Quinto, J. M. Monti, C. A. Tachino, P. F. Weck, O. A. Foj\'on, 
+C. Champion, R. D. Rivarola, 
 % \textit{The physics of irradiation of biological matter by ion beams}, 
@@
 \bibitem{ludde2019}
-H. J. L\"udde,  M. Horbatsch and T. Kirchner, J. Phys. B: At. Mol. Opt. Phys.  \textbf{52}, 195203 (2019).
+H. J. L\"udde,  M. Horbatsch and T. Kirchner, 
+J. Phys. B: At. Mol. Opt. Phys. \textbf{52}, 195203 (2019).
 
 \bibitem{ludde2018}
-H. J. L\"udde, M. Horbatsch and T. Kirchner, Eur. Phys. J. B \textbf{91}, 99 (2018).
+H. J. L\"udde, M. Horbatsch and T. Kirchner, 
+Eur. Phys. J. B \textbf{91}, 99 (2018).
 
@@
 \bibitem{Champion2012} 
-C Champion, M E Galassi, O Foj\'{o}n, H Lekadir, J Hanssen, R D Rivarola, P F Weck, A N Agnihotri, S Nandi, and L C Tribedi. 
+C. Champion, M. E. Galassi, O. Foj\'{o}n, H. Lekadir, J. Hanssen, 
+R. D. Rivarola, P. F. Weck, A. N. Agnihotri, S. Nandi, and L. C. Tribedi. 
 J. Phys.: Conf. Ser. \textbf{373}, 012004 (2012).
@@
 \bibitem{agnihotri2013}
-A N Agnihotri, S Kasthurirangan, S Nandi, A Kumar, C Champion,, H Lekadir, J Hanssen, P FWeck, M E Galassi, R D Rivarola, O Fojon and L C Tribedi, 
+A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A. Kumar, C. Champion, 
+H. Lekadir, J. Hanssen, P. F. Weck, M. E. Galassi, R. D. Rivarola, 
+O. Foj\'on and L. C. Tribedi, 
 J. Phys. B: At. Mol. Opt. Phys. \textbf{46}, 185201 (2013).
@@
 \bibitem{DalCappello2009}
-C. Dal Cappello, C. Champion, O. Boudrioua, H. Lekadir, Y. Sato , D. Ohsawa, 
+C. Dal Cappello, C. Champion, O. Boudrioua, H. Lekadir, Y. Sato, 
+D. Ohsawa, 
 Nuclear Instruments and Methods in Physics Research B 267 (2009) 781--790.
 
+\bibitem{Bhattacharjee17}
+Shamik Bhattacharjee, S. Biswas, J. M. Monti, R. D. Rivarola, and 
+L. C. Tribedi,
+Phys. Rev A \textbf{96}, 052707 (2017).
+
 %O$^{+8}$ in water -------------------------------
-\bibitem{Tribedi_O_water} S.
-Bhattacharjee, S.
-Biswas, C.
-Bagdia, M.
-Roychowdhury, S.
-Nandi, D.
-Misra, J.
-M.
-Monti, C.
-A.
-Tachino, R.
-D.
-Rivarola, C.
-Champion and L.
-C.
-Tribedi, J.
-Phys.
-B: At.
-Mol.
-Opt.
-Phys.
-\textbf{49,}  065202 (2016).
+\bibitem{Tribedi_O_water} 
+S. Bhattacharjee, S. Biswas, C. Bagdia, M. Roychowdhury, S. Nandi, 
+D. Misra, J. M. Monti, C. A. Tachino, R. D. Rivarola, C. Champion and 
+L. C. Tribedi, J. 
+Phys. B: At. Mol. Opt. Phys. \textbf{49,}  065202 (2016).
 
@@
 \bibitem{bug2017}
-M. U. Bug, W. Y. Baek, H. Rabus, C. Villagrasa, S. Meylan, A. B. Rosenfeld,
+M. U. Bug, W. Y. Baek, H. Rabus, C. Villagrasa, S. Meylan, 
+A. B. Rosenfeld,
 Rad. Phys. Chem. \textbf{130}, 459--479 (2017).
@@
 
-\bibitem{sarkadi2016} L Sarkadi, J. Phys. B: At. Mol. Opt. Phys. \textbf{49} 185203 (2016)
+\bibitem{sarkadi2016}
+L. Sarkadi, 
+J. Phys. B: At. Mol. Opt. Phys. \textbf{49} 185203 (2016)
 
 % H+ in CH4 and CO2-----------------------------------------
-\bibitem{Rudd1983} M. E. Rudd, R. D. DuBois, L. H. Toburen, and C. A. Ratcliffe, T. V. Goffe, Phys. Rev. A \textbf{28}, 3244 (1983).
+\bibitem{Rudd1983} 
+M. E. Rudd, R. D. DuBois, L. H. Toburen, and C. A. Ratcliffe, 
+T. V. Goffe, 
+Phys. Rev. A \textbf{28}, 3244 (1983).
 
-\bibitem{Luna2019} H. Luna, W. Wolff, and E. C. Montenegro, L. Sigaud, Phys. Rev. A \textbf{99}, 012709 (2019).
+\bibitem{Luna2019} 
+H. Luna, W. Wolff, and E. C. Montenegro, L. Sigaud, 
+Phys. Rev. A \textbf{99}, 012709 (2019).
 

### 2020-05-11 figuras/graphs/zscale.py

@@ -1,1629 +1,0 @@
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-import matplotlib.ticker as mticker
-from scipy import interpolate
-from matplotlib.legend_handler import HandlerLine2D
-plt.rc("text", usetex=True)
-plt.rc('font', family='serif')
-plt.rc('text.latex', preamble=r'\usepackage{wasysym} \usepackage{stmaryrd}')
-
-convMb=0.28002*100
-convcm2=0.28002
-co_p='tab:red'
-co_ap='tab:red'
-co_he='tab:green'
-co_be='tab:blue'
-co_c='tab:purple'
-co_o='tab:orange'
-
-def convkeV(x):
-    return 25.0*(x**2)
-
-def convMeV(x):
-    return 25.0*(x**2)/1000.
-
-def interp_XS(XY,ix,iy,kind):
-    x=XY[ix].values
-    y=XY[iy].values
-    n=len(x)
-    spline = interpolate.interp1d(x, y, kind=kind)
-    xnew = np.arange(x[0], x[n-1], 0.01)
-    ynew = spline(xnew)
-    XYnew = pd.DataFrame({ix:xnew, iy:ynew})
-    return XYnew
-
-class HandlerXoffset(HandlerLine2D):
-    def __init__(self, marker_pad=0.3, numpoints=1, x_offset=0,  **kw):
-        HandlerLine2D.__init__(self, marker_pad=marker_pad, numpoints=numpoints, **kw)
-        self._xoffset = x_offset
-    def get_xdata(self, legend, xdescent, ydescent, width, height, fontsize):
-        numpoints = self.get_numpoints(legend)
-
-        if numpoints > 1:
-            # we put some pad here to compensate the size of the
-            # marker
-            xdata = np.linspace(-xdescent + self._marker_pad * fontsize,
[…]

### 2020-05-27 zscaling/overleaf/zscaling_overleaf.tex
scaling manuscript with major revisions

--- 2020-05-11 zscaling/zscaling.tex
@@
 
-\title[General scaling rule for the ionization of biological molecules]{
-General scaling rule for the ionization of biological molecules \\ by 
-highly charged ions}
+\title[Scaling rules for the ionization of biological
+molecules]{Scaling rules for the ionization of biological
+molecules by highly charged ions}
 \author{A. M. P. Mendez, C. C. Montanari, J. E. Miraglia}
@@
 
-\date{}% It is always \today, today,
+\date{\today}% It is always \today, today,
 
 \begin{abstract}
-In the present work, we investigate scaling rules for the ionization 
-cross sections of multicharged ions on molecules of biological interest. 
-The cross sections are obtained using a methodology presented in 
-[Mendez \textit{et al.} J. Phys B (2020)], which considers distorted-wave 
-calculations for atomic targets combined with a molecular stoichiometric 
-model. We examine ions with nuclear charges $Z$ from $+1$ to $+8$ 
-impacting on five nucleobases --adenine, cytosine, guanine, thymine, 
-uracil--, tetrahydrofuran, pyrimidine, and water. We propose a scaling 
-with the ion charge, which is valid in the intermediate to high energy 
-range, i.e., 0.2-5 MeV/amu for oxygen impact. We extend our work to a 
-universal scaling for any ion and molecule, merging the forty 
-ion-molecule systems analyzed here into a single band. Furthermore, our 
-model proved to be valid for other molecules too.  
+We investigate scaling rules for the ionization cross sections of
+multicharged ions on molecules of biological interest. The cross 
+sections are obtained using a methodology presented in [Mendez 
+\textit{et al.} J. Phys B (2020)], which considers distorted-wave 
+calculations for atomic targets combined with a molecular 
+stoichiometric model. We examine ions with nuclear charges $Z$ from 
+$+1$ to $+8$ impacting on five nucleobases --adenine, cytosine, 
+guanine, thymine, uracil--, tetrahydrofuran, pyrimidine, and water. 
+We investigate %the scaling 
+scaling rules of the ionization cross section with 
+the ion charge and the number of active electrons per molecule. 
+%valid in the intermediate to 
+%high energy range, i.e., 0.2-5 MeV/amu for oxygen impact. 
+% Furthermore, 
+% we introduce a modified scaling rule, which takes into account the 
+% number of active electrons per molecule. 
+Combining these two features, we define a scaling law  for any ion and molecular target %independent of  the ion charge and the complexity of the molecular target
+, which is 
+valid in the intermediate to high energy range, i.e., 0.2-5 MeV/amu for oxygen impact. %Then, 
+Thus, the forty 
+ion-molecule systems analyzed here can be merged into a single band. 
+We confirm the generality of our independent scaling law with several
+collisional systems. 
 \end{abstract}
@@
 
-The ionization of biological molecules by multicharged ions has gained 
-increasing interest due to medical and environmental 
-implementations~\cite{PhysMed}, which includes medical 
+\section{Introduction}
+
+The interest in the ionization of biological molecules by 
+multicharged ions has increased due to medical and environmental
+implementations~\cite{PhysMed}, including medical 
 treatments~\cite{Mohamad2017,Solov2009,Denifl2011} and contaminant 
@@
 Many semiempirical \citep{vera_prl2013} and theoretical efforts are 
-currently being undertaken~\cite{MendezJPB20,Quinto20,ludde2019,ludde2018,
-ludde2016,Champion2012} to get reliable values for the ionization cross 
-sections of these molecular systems.
+currently being undertaken~\cite{MendezJPB20,Quinto20,ludde2019,
+ludde2018,ludde2016,Champion2012} to get reliable values for the 
+ionization cross sections of these molecular systems.
 
@@
 distorted-wave calculations (CDW) for atoms and the simple 
-stoichiometric model (SSM), also known as the Bragg sum rule, to 
-approximate the ionization cross sections of complex molecular targets 
-by charged ions. The CDW-SSM approximation showed consistent results 
-for over a hundred of ion-molecule systems. As expected, in the high 
-energy range (i.e., above 5 MeV/amu), the ionization cross sections of
+stoichiometric model (SSM) to approximate the ionization cross 
+sections of complex molecular targets by the impact of charged ions. 
+The molecular ionization cross section~$\sigma_M$ was expressed as 
+a linear combination of atomic CDW calculations $\sigma_A$, 
+weighted with the number of atoms for each specie $n_A$, i.e, 
+$\sigma_M=\sum_A n_A \sigma_A$. The CDW-SSM approximation showed 
+consistent results for over a hundred of biologically relevant 
+ion-molecule systems. As expected, in the high energy range (i.e., 
+above 5 MeV/amu), the ionization cross sections of 
 the molecular systems follow the $Z^2$ dependence predicted by the 
-first Born approximation. However, at intermediate energies, the 
-dependence with $Z$ is not straightforward since non-perturbative 
-models are mandatory.
+first Born approximation. However, at intermediate 
+energies, the dependence with $Z$ is not straightforward since 
+non-perturbative models are mandatory.
 
-This letter intends to give a follow up of our previous work by 
-proposing a scaling rule for the ionization cross sections of complex 
-molecules with the ion charge $Z$, which is valid at intermediate 
-energies. In general, scaling rules are used as first-order 
+This contribution constitutes a follow-up of our previous work~\cite{MendezJPB20}. We 
+introduce here a two-folded scaling rule for the ionization cross 
+sections of complex molecules by charged ions. Our approach considers 
+the dependence of the cross section with the ion charge $Z$ 
+and incorporates the scaling of the ionization with the number of 
+active electron $n_e$ of the molecular targets. Scaling rules are 
+generally very useful since they can be used as first-order 
 approximations in experimental measurements and multipurpose codes.
-Furthermore, we explore the generality of our scaling rule by inspecting 
-various other ion-target systems.
 
-We have found in the literature two scaling rules applicable at 
-intermediate impact energy range. The scaling rule suggested by Janev 
-and Presnyakov~\cite{janev1980} depends linearly with ion charge $Z$,
-considering $\sigma/Z$ versus $E/Z$ to be the \textit{natural} reduced 
-form of the ionization cross section $\sigma$ and the incident ion 
-energy $E$. More recently, Montenegro and co-workers~\cite{dubois13,
-montenegro_pra13} proposed an alternative scaling by taking into account 
-that the cross section is a function of $Z^2/E$. Their scaling, given by 
-\begin{equation}
-    \sigma/Z^{\alpha}=f(E/Z^{2-\alpha}),
-    \label{Montenegro}
-\end{equation}
-keeps the $Z^2/E$ relationship for any value of the parameter $\alpha$. 
-In Ref.~\cite{dubois13}, the authors propose $\alpha=4/3$ for ionization 
-of He and H$_2$ by differently charged ions.
+\section{Scaling rules}
 
-Combining our recent CDW-SSM results~\cite{MendezJPB20} and 
-Eq.~(\ref{Montenegro}), we propose here a $Z$-scaling and implement it 
-for forty collisional systems. The ion-molecule systems are composed of 
-eight targets: the DNA and RNA nucleobases --adenine, cytosine, guanine, 
-thymine, uracil--, tetrahydrofuran (THF), pyrimidine, and water; and 
-five ion species: H$^+$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
-We considered these systems as a benchmark for the present scaling.
+\subsection{Scale with the ion charge}
+\label{sec:zscaling}
 
-We found that the parameter $\alpha$ from Eq.~(\ref{Montenegro}) that 
-fits the CDW-SSM scaled cross sections for all the ions is $\alpha=1.2$. 
-The validity of the theoretical scaling with the ion charge is evident
-in Fig.~\ref{fig:zreduced}, where the CDW-SSM curves lay one over the 
-other. Our theoretical results are valid for impact energies around and 
-above the maximum of the cross sections, which corresponds to an impact
-energy range from 50 keV for H$^+$ to 250 keV/amu for O$^{+8}$.
-
-The scaling was tested with the experimental data available for 
-ionization by the impact of differently charged ions \cite{itoh2013,
-iriki2011,wolff2014,wang2016,tribedi2019,agnihotri2012,agnihotri2013,
-Luna2007,Rudd86,Rudd85,Luna_Li_water,DalCappello2009,Tribedi_O_water}, 
-and also by electron impact at sufficiently high velocity 
-\cite{rahman2016,bug2017,wolf2019,fuss2009}. As can be noted, most of 
-the data in Fig.~\ref{fig:zreduced} confirm the present scaling, even 
-for O$^{+8}$ in water~\cite{Tribedi_O_water}. However, the data of 
-uracil by swift C, O, and F ions in \cite{agnihotri2012,agnihotri2013} 
-are too low compared with our CDW-SSM results, but also as compared 
-with Itoh \textit{et al.} data \cite{itoh2013}, and with the CTMC 
-calculations by Sarkadi~\cite{sarkadi2016}. The data for Li$^{+3}$ in 
-water from Ref.~\cite{Luna_Li_water} also spreads out from the present 
-theoretical curves for $E<600$ keV/amu.
-
-The good results obtained in the scaling with the ion charge challenged 
-us to look for a more general scaling rule that could predict values 
-for ionization cross sections of any ion in any molecule. To that end, 
-we resorted to the number of active electrons in each atom $n_e$ 
-proposed in \cite{MendezJPB20}, and combined it with the $Z$-scaling 
-displayed in Fig.~\ref{fig:zreduced}.
+In the development of our scaling rule, we examine forty collisional 
+systems. The target-ion systems are composed of eight targets: 
+the DNA and RNA nucleobases --adenine, cytosine, guanine, thymine, 
+uracil--, tetrahydrofuran (THF), pyrimidine, and water; and five ion 
+species: H$^+$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$. 
+We consider these systems as a benchmark for the present rule.
 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{zscale_alpha.eps}
+\includegraphics[width=0.87\textwidth]{zscale_alpha.eps}
 \caption{(Color online) Scaled ionization cross section $\sigma/Z^{\alpha}$ 
@@
 
-The CDW ionization cross sections $\sigma^{\mathrm{CDW}}$ of atomic H, 
-C, N, O targets scale as $\sigma_e=\sigma^{\mathrm{CDW}}/n_e$ with $n_e$ 
-being $1$ for H, $4$ for C, N, and O, i.e.,
+We found two types of $Z$-scaling laws in the literature applicable 
+to the intermediate impact energy range. The rule suggested by Janev 
+and Presnyakov~\cite{janev1980} 
+%depends linearly with ion charge $Z$, considering 
+considers $\sigma/Z$ versus $E/Z$ to be the \textit{natural} reduced  
+form of the ionization cross section $\sigma$ and the incident ion energy $E$. More recently, Montenegro and co-workers~\cite{dubois13,
+montenegro_pra13} suggested an alternative scaling by taking into 
+account that the cross section is a function of $Z^2/E$ at high 
+energies. Their scaling, given by 
 \begin{equation}
- \frac{\sigma_{\mathrm{H}}^{\mathrm{CDW}}}{1}\sim
- \frac{\sigma_{\mathrm{C}}^{\mathrm{CDW}}}{4}\sim
- \frac{\sigma_{\mathrm{N}}^{\mathrm{CDW}}}{4}\sim
- \frac{\sigma_{\mathrm{O}}^{\mathrm{CDW}}}{4}
+ \sigma/Z^{\alpha}=f(E/Z^{2-\alpha}),
+\label{eq:Montenegro}
 \end{equation}
-The SSM leads to the molecular numbers of active electrons included in 
-Table \ref{nn}.
+keeps the $Z^2/E$ relationship for any value of the parameter 
+$\alpha$. The authors proposed $\alpha=4/3$ for the ionization of He and 
+H$_2$ by differently charged ions~\cite{dubois13}.
 
-\contourlength{0.03em}
-\contournumber{30}
+Following the work of Montenegro and collaborators, we found that the 
+parameter that best converges the CDW-SSM cross sections of the forty 
+collisional systems over the broadest energy range is $\alpha=1.2$. 
+The validity of this particular scaling is evident in 
+Fig.~\ref{fig:zreduced}, where --for each target-- the CDW-SSM curves
+corresponding to different ions lay one over the other. 
+It is worth noting that our theoretical results are valid for impact
+energies above the maximum of the cross sections, which corresponds to 
+an impact energy range from 50 keV for H$^+$ to 250 keV/amu for 
+O$^{+8}$.
 
-\begin{table}[t]
-\begin{center}
-\begin{tabular}{|ll|ll|ll|}
-\hline
- Molecule & $n_e$ & Molecule          & $n_e$ & Molecule          & $n_e$ \\
-\hline
- H$_2$O   & 6  & CO$_2$               & 12 & C$_4$H$_5$N$_3$O     & 37   \\ 
- N$_2$    & 8  & C$_4$H$_8$O          & 28 & C$_5$H$_6$N$_2$O$_2$ & 42   \\ 
- O$_2$    & 8  & C$_4$H$_4$N$_2$      & 28 & C$_5$H$_5$N$_5$      & 45   \\ 
- CH$_4$   & 8  & C$_4$H$_4$N$_2$O$_2$ & 36 & C$_5$H$_5$N$_5$O     & 49   \\ 
- \hline
-\end{tabular}
-\caption{Number of active electrons per target at intermediate to high 
-energies obtained from the CDW calculations~\cite{MendezJPB20}.}
-\label{nn}
-\end{center}
-\end{table}
+We also examined the experimental data available for the forty 
+ion-target systems~\cite{itoh2013,iriki2011,wolff2014,wang2016,
+tribedi2019,agnihotri2012,agnihotri2013,Luna2007,Rudd86,Rudd85,pRudd85,
+toburen80,Ohsawa05,Bhattacharjee17,Luna_Li_water,DalCappello2009,
+Tribedi_O_water} with the $Z^\alpha$-scaling rule. For targets with none or little experimental data, we included
+electron impact ionization results~\cite{rahman2016,bug2017,wolf2019,
+fuss2009} at high velocity with the corresponding equivelocity 
+conversion.
+As can be noted, 
+most of the data in Fig.~\ref{fig:zreduced} confirm the present 
+scaling, even for O$^{+8}$ in water~\cite{Tribedi_O_water}. 
+Only two data sets are off our predictions: the ionization cross sections of 
+uracil by swift C, O, and F ions from 
+Refs~\cite{agnihotri2012,agnihotri2013}% are too low  compared with our CDW-SSM results
+; and the values 
+for Li$^{+3}$ in water from Ref.~\cite{Luna_Li_water} %spread out from the present theoretical curves
+for $E<600$~keV/amu. 
+In the case of uracil, recent CTMC calculations by Sarkadi~\cite{sarkadi2016} are also above the experimental values by Tribedi group~\cite{agnihotri2012,agnihotri2013}.
 
-\begin{figure*}[!t]%[h]
+\subsection{Scale with the molecular target}
+
+The good results obtained in the scaling with the ion charge 
+encouraged us to further investigate a scaling law that could 
+predict values for ionization cross sections of any ion in any 
+molecule. To this end, we considered the number of active electrons 
+in each molecule $n_e$ proposed in Ref.~\cite{MendezJPB20} and combined 
+it with the $Z^\alpha$-scaling from Section~\ref{sec:zscaling}.
+
+In our previous work, we noticed that the CDW ionization cross 
+sections, $\sigma_A$, of atomic targets H, C, N, and O  scale with the number of
+active electrons per atom $\nu_A$, as \mbox{$\sigma_e=\sigma_A/\nu_A$,} 
+where $\nu_A$ is $1$ for H and $4$ for C, N, O, i.e.,
+\begin{equation}
+ \frac{\sigma_{\mathrm{H}}}{1}\sim
+ \frac{\sigma_{\mathrm{C}}}{4}\sim
+ \frac{\sigma_{\mathrm{N}}}{4}\sim
+ \frac{\sigma_{\mathrm{O}}}{4}\,.
+\end{equation}
+By %considering
+means of the SSM, we define the number of active electrons per
+molecule as $n_e=\sum_A n_A \nu_A$. The $n_e$ values for the 
+molecular targets considered throughtout this work are displayed in 
+Table~\ref{nn}. The scaling with the molecular number of active
+electrons proved to give excellent results, as shown in Fig.~6 of 
+Ref.~\cite{MendezJPB20}.
+
+\subsection{Scale with the ion charge and \\ the molecular target}
+
+By incorporating the $Z^\alpha$ reduction and the scaling with the %molecular 
+number  of active electrons% scaling
+, we introduce the scaled and reduced
+ionization cross section of molecules $\tilde{\sigma}$, which is 
+expressed as a function of $E/Z^{2-\alpha}$, and it is given by
+\begin{equation}
+ \tilde{\sigma}=\frac{\sigma_e}{Z^{\alpha}}=\frac{\sigma_M/n_e}{Z^{\alpha}}\,,
+\label{eq:u-scaling}
+\end{equation}
+where $\sigma_M$ is the ionization cross section for the molecular target, 
+$n_e$ is the number of active electrons per molecule displayed in 
+Table~\ref{nn} and the parameter is $\alpha=1.2$.
+Fig.~\ref{fig:zalpha} shows the %reduced-scaled 
+theoretical and 
+experimental values of $ \tilde{\sigma}$ (given by Eq.~(\ref{eq:u-scaling})) %data 
+for all the systems displayed in Fig.~\ref{fig:zreduced}% obtained using Eq.~(\ref{eq:u-scaling})
+. As can be noted, the scaling works very well
+and is independent of the ion charge or the complexity of the molecular
+target. 
+Our theoretical curves lay in a narrow band valid for any charged ion 
+(reduced with $Z^\alpha$) in any molecule (scaled with the number of 
+active electrons) with a dispersion of about 20\%. If we consider
+the experimental data, the uncertainty of our scaling grows to 30\%, 
+which is coverd by %shown with 
+the gray area in Fig.~\ref{fig:zalpha}.
+It is worth noting that we did not include in this figure %Fig.~\ref{fig:zalpha}
+the data for uracil from Refs.~\cite{agnihotri2012,agnihotri2013}, 
+and for Li$^{+3}$ on water~\cite{Luna_Li_water}. The discussion 
+about these experimental values exceeds the present work.
+
+\begin{figure*}[!htb]%[h]
 \centering
-\includegraphics[width=0.7\textwidth]{zmol_werror.eps}
-\caption{(Color online) Universal scaling with the ions charge $Z$ and 
-the number of active electrons in the molecule $n_e$ given by Eq. 
-(\ref{u-scaling}) with $\alpha=1.2$. Curves: present CDW-SSM theoretical 
-results. Symbols: experimental impact of H$^+$ on 
+\includegraphics[width=0.75\textwidth]{zmol_werror.eps}
+\caption{(Color online) Ionization cross section reduced with the ion
+charge $Z$ and scaled with number of active electrons per molecule $n_e$,
+given by Eq.~(\ref{eq:u-scaling}) with $\alpha=1.2$. 
+Curves: present CDW-SSM theoretical results. 
+Symbols: experimental impact of H$^+$ on 
 \mbox{\LARGE$\color{red}\circ$} adenine~\cite{iriki2011}, 
@@
 
-The universal scaling we propose here is expressed as $\sigma_U$ as a 
-function of $E/Z^{2-\alpha}$, with
- \begin{equation}
-     \sigma_U=\frac{\sigma_e}{Z^{\alpha}}=\frac{\sigma/n_e}{Z^{\alpha}}\,,
-     \label{u-scaling}
- \end{equation}
-$\sigma$ is the ionization cross section for the molecular target, 
-$\alpha=1.2$ and $n_e$ is the number of active electrons per molecule 
-given in Table \ref{nn}. In Fig.~\ref{fig:zalpha}, we test the universal 
-scaling of Eq.~(\ref{u-scaling}) for all the theoretical and 
-experimental values displayed in Fig. \ref{fig:zreduced}. We also 
-included a gray area representing the 30\% deviation of our theoretical 
-curves. As can be noted, the universal scaling works very well. All the 
-curves and data lays in a narrow band valid for any charged ion (scaled 
-with Z) in any molecule (scaled with the number of active electrons). 
-We decided not to include in this figure the data for uracil from 
-Refs.~\cite{agnihotri2012,agnihotri2013}, and for Li$^{+3}$ on 
-water~\cite{Luna_Li_water}. The discussion about these experimental 
-values exceeds the present work. %is open for future work.
-
-In principle, the \textit{universal} scaling should be valid for 
-different ion--molecule combinations. We proved this statement by 
-including in Fig.~\ref{fig:zalpha} the measurements by 
-Rudd~\textit{et al.} \cite{Rudd85,Rudd1983} for H$^{+}$ and He$^{+2}$ 
+We consider this scaling robust enough to be valid for different 
+ion--molecule combinations. We tested the generality of our model 
+by including in Fig.~\ref{fig:zalpha} several data sets of 
+molecular targets not considered previously, such as the measurements 
+by Rudd~\textit{et al.}~\cite{Rudd85,Rudd1983} for H$^{+}$ and He$^{+2}$ 
 in N$_2$, O$_2$, CH$_4$, CO and CO$_2$, and the recent values by 
@@
 The good agreement shown in Fig.~\ref{fig:zalpha} summaries the main 
-result of this work, and holds the validity of our universal scaling. 
+result of this work, and holds the validity of the present scaling for different ions and targets.
+%with the ion charge and the number of active electrons in the target. 
 Although the theoretical CDW-SSM results are valid for energies above 
-the maximum of the cross sections, the scaling of the experimental data 
-extends to lower impact energies, as can be noted in 
-Fig.~\ref{fig:zalpha}. The importance of scaling rules lays in their 
-predictive capability. New measurements for other ions and molecules 
-are expected to reinforce the present proposal.
+the maximum of the cross sections, %it is worth noting from Fig.~\ref{fig:zalpha} that 
+the scaling of the experimental data extends 
+even to lower impact energies, as can be noted in Fig.~\ref{fig:zalpha}. 
+New measurements for other ions and molecules are expected to 
+reinforce the present proposal.
+
+\begin{table}[t]
+\begin{center}
+\begin{tabular}{|ll|ll|ll|}
+\hline
+ Molecule & $n_e$ & Molecule          & $n_e$ & Molecule          & $n_e$ \\
+\hline
+ H$_2$O   & 6  & CO$_2$               & 12 & C$_4$H$_5$N$_3$O     & 37   \\ 
+ N$_2$    & 8  & C$_4$H$_8$O          & 28 & C$_5$H$_6$N$_2$O$_2$ & 42   \\ 
+ O$_2$    & 8  & C$_4$H$_4$N$_2$      & 28 & C$_5$H$_5$N$_5$      & 45   \\ 
+ CH$_4$   & 8  & C$_4$H$_4$N$_2$O$_2$ & 36 & C$_5$H$_5$N$_5$O     & 49   \\ 
+ \hline
+\end{tabular}
+\caption{Number of active electrons per target at intermediate to high 
+energies obtained from the CDW calculations~\cite{MendezJPB20}.}
+\label{nn}
+\end{center}
+\vspace{-0.75cm}
+\end{table}
 
@@
 \section{Conclusions}
-In this letter, we present a scaling for the ionization cross sections 
-of highly charged ions in biological targets. The scaling rule states 
-the cross sections divided by $Z^{\alpha}$ as a function of the reduced 
-impact energy $E/Z^{2-\alpha}$, with $\alpha=1.2$. The scaling was 
-obtained by means of the CDW-SSM calculations for five different charged 
-ions in eight targets and tested with the available experimental data. 
-A universal scaling rule  is also proposed, which reduced the cross 
-sections with the number of active electrons of the molecule. The 
-universal scaling proved to be valid for a large number of experimental 
-data.
+
+We present scaling rules for the ionization
+cross sections of highly charged ions in biological targets. The first
+scaling reduces the nature of the projectile by scaling the cross 
+section with the ion charge, $Z^{\alpha}$, as a function of the 
+reduced impact energy $E/Z^{2-\alpha}$, with $\alpha=1.2$. The second
+scaling considers the molecular characteristic of the target by taking 
+into account the number of active electrons per molecule, $n_e$. 
+The last scaling law combines the $Z^{\alpha}$-reduction with the
+$n_e$-scaling 
+of cross section, and it becomes independent of the ion charge and 
+the molecular target. The scalings are obtained by means of 
+CDW-SSM calculations for five different charged ions in eight targets 
+and tested with the available experimental data. The generality of our
+independent scaling is proved to be valid in a wide energy range 
+by considering a significant number of experimental data sets for 
+other collisional systems.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Acknowlegments}
+
+This work was finantially supported by Consejo Nacional de
+Investigaciones Cient\'ificas y T\'ecnicas (CONICET), Agencia 
+Nacional de Promoci\'on Cient\'ifica y Tecnol\'ogica (ANPCyT), 
+and Universidad de Buenos Aires (UBA).
 
@@
 \bibitem{Bhattacharjee17}
-Shamik Bhattacharjee, S. Biswas, J. M. Monti, R. D. Rivarola, and 
+S. Bhattacharjee, S. Biswas, J. M. Monti, R. D. Rivarola, and 
 L. C. Tribedi,
@@
 
-\bibitem{sarkadi2016}
-L. Sarkadi, 
-J. Phys. B: At. Mol. Opt. Phys. \textbf{49} 185203 (2016)
+\bibitem{sarkadi2016} L. Sarkadi, J. Phys. B: At. Mol. Opt. Phys. \textbf{49} 185203 (2016).
 

### 2020-05-27 zscaling/submitted/zscaling.tex
scaling manuscript with major revisions

@@
 
-The ionization of biological molecules by multicharged ions has gained increasing interest due to medical and environmental reasons~\cite{PhysMed}, from medical treatments~\cite{Mohamad2017,Solov2009,Denifl2011} to contaminant recognition in biological materials~\cite{water,ferrazdias}.
-Many semiempirical \citep{vera_prl2013} and theoretical efforts are currently being undertaken~\cite{MendezJPB20,Quinto20,ludde2019,ludde2018,ludde2016,Champion2012} to get reliable values for the ionization cross sections of these molecules.
+The ionization of biological molecules by multicharged ions has gained 
+increasing interest due to medical and environmental 
+reasons~\cite{PhysMed}, from medical treatments~\cite{Mohamad2017,
+Solov2009,Denifl2011} to contaminant recognition in biological 
+materials~\cite{water,ferrazdias}. Many semiempirical 
+\citep{vera_prl2013} and theoretical efforts are currently being 
+undertaken~\cite{MendezJPB20,Quinto20,ludde2019,ludde2018,ludde2016,
+Champion2012} to get reliable values for the ionization cross sections 
+of these molecules.
 
-Recently, we combined the continue distorted--wave calculations (CDW) for atoms and the simple stoichiometric model (SSM), also known as the Bragg sum rule, to approximate the ionization cross sections of complex molecular targets by charged ions~\cite{MendezJPB20}.
-The CDW--SSM approximation showed reasonable results for over a hundred of ion--molecule systems.
-As expected, in the high energy range (i.e.
-above 5 MeV/amu) the ionization cross sections  present the $Z^2$ dependence predicted by the first Born approximation.
-However, at intermediate energies, the dependence with $Z$ is more complex, and non--perturvative models are mandatory.
+Recently, we combined the continue distorted--wave calculations (CDW) 
+for atoms and the simple stoichiometric model (SSM), also known as the 
+Bragg sum rule, to approximate the ionization cross sections of complex 
+molecular targets by charged ions~\cite{MendezJPB20}. The CDW--SSM 
+approximation showed reasonable results for over a hundred of 
+ion--molecule systems. As expected, in the high energy range (i.e. 
+above 5 MeV/amu) the ionization cross sections  present the $Z^2$ 
+dependence predicted by the first Born approximation. However, at 
+intermediate energies, the dependence with $Z$ is more complex, and 
+non--perturvative models are mandatory.
 
-The intention of this letter is to give a follow up of our previous work~\cite{MendezJPB20} by proposing a scaling with the ion charge $Z$ of the ionization cross sections of complex molecules, valid at intermediate energies.
-In general, scaling rules are used as first--order tests in experimental measurements and multipurpose codes.
-Based on ~\cite{MendezJPB20}, we propose a universal scaling for any ion--target system.
+The intention of this letter is to give a follow up of our previous 
+work~\cite{MendezJPB20} by proposing a scaling with the ion charge $Z$ 
+of the ionization cross sections of complex molecules, valid at 
+intermediate energies. In general, scaling rules are used as 
+first--order tests in experimental measurements and multipurpose codes. 
+Based on ~\cite{MendezJPB20}, we propose a universal scaling for any 
+ion--target system.
 
-At intermediate impact energies, 
-Janev and Presnyakov~\cite{janev1980} suggest $\sigma/Z$ versus $E/Z$ as the \textit{natural} reduced form of the ionization cross section $\sigma$ and the incident ion energy $E$.
-Much more recently, Montenegro and co--workers~\cite{dubois13,montenegro_pra13} proposed an alternative scaling by taking into account that  $\sigma$ is a function of $Z^2/E$.
-Their scaling, given by
+At intermediate impact energies, Janev and Presnyakov~\cite{janev1980} 
+suggest $\sigma/Z$ versus $E/Z$ as the \textit{natural} reduced form of 
+the ionization cross section $\sigma$ and the incident ion energy $E$. 
+Much more recently, Montenegro and co--workers~\cite{dubois13,
+montenegro_pra13} proposed an alternative scaling by taking into 
+account that  $\sigma$ is a function of $Z^2/E$. Their scaling, given 
+by
 \begin{equation}
@@
 keeps the $Z^2/E$ relationship for any value of $\alpha$. 
-In Ref.~\cite{dubois13}, the authors propose $\alpha=4/3$ for ionization of He and H$_2$ by different charged ions.
+In Ref.~\cite{dubois13}, the authors propose $\alpha=4/3$ for 
+ionization of He and H$_2$ by different charged ions.
 
@@
 
-Combining our recent CDW--SSM results~\cite{MendezJPB20} and Eq.~(\ref{Montenegro}), we propose here a $Z$-scaling and implement it for forty collisional systems.
-The ion--molecule systems are composed of eight targets: the DNA and RNA nucleobases --adenine, cytosine, guanine, thymine, uracil--, tetrahydrofuran (THF), pyrimidine, and water; and five charged ions: H$^+$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, and O$^{+8}$.
-We considered these systems as a benchmark for the present scaling.
+Combining our recent CDW--SSM results~\cite{MendezJPB20} and 
+Eq.~(\ref{Montenegro}), we propose here a $Z$-scaling and implement it 
+for forty collisional systems. The ion--molecule systems are composed 
+of eight targets: the DNA and RNA nucleobases --adenine, cytosine, 
+guanine, thymine, uracil--, tetrahydrofuran (THF), pyrimidine, and 
+water; and five charged ions: H$^+$, He$^{+2}$, Be$^{+4}$, C$^{+6}$, 
+and O$^{+8}$. We considered these systems as a benchmark for the 
+present scaling.
 
-We found that the parameter $\alpha$ from Eq.~(\ref{Montenegro}) that fits the CDW--SSM scaled cross sections for all the ions is $\alpha=1.2$. 
-The validity of the theoretical scaling with the ion charge is very clear in Fig.~\ref{fig:zreduced}, where the CDW-SSM curves lays one over the other.
-Our theoretical results are valid for impact energies around and above the maximum of the cross sections, which means above 50 keV for impact of H$^+$  to 250 keV/amu for impact of O$^{+8}$.
+We found that the parameter $\alpha$ from Eq.~(\ref{Montenegro}) that 
+fits the CDW--SSM scaled cross sections for all the ions is $\alpha=1.2$. 
+The validity of the theoretical scaling with the ion charge is very 
+clear in Fig.~\ref{fig:zreduced}, where the CDW-SSM curves lays one 
+over the other.  Our theoretical results are valid for impact energies 
+around and above the maximum of the cross sections, which means above 
+50 keV for impact of H$^+$  to 250 keV/amu for impact of O$^{+8}$.
 
-The scaling was tested with the experimental data available by impact of different charged ions \cite{itoh2013,iriki2011,wolff2014,wang2016,tribedi2019,agnihotri2012,agnihotri2013,Luna2007,Rudd86,Rudd85,Luna_Li_water,DalCappello2009,Tribedi_O_water},
-and also by electron impact at sufficiently high velocity \cite{rahman2016,bug2017,wolf2019,fuss2009}.
-As can be noted, most of the data in Fig.~\ref{fig:zreduced} confirms the present scaling, even for O$^{+8}$ in water~\cite{Tribedi_O_water}.
-However, the data of uracil by swift C, O and F ions in \cite{agnihotri2012,agnihotri2013} are too low compared with our CDW--SSM results, but also as compared with Itoh \textit{et al.} data \cite{itoh2013}, and with the CTMC calculations by Sarkadi \cite{sarkadi2016}.
-The data for Li$^{+3}$ in water from Ref.~\cite{Luna_Li_water} also spreads out from the present theoretical curves for $E<600$ keV/amu.
+The scaling was tested with the experimental data available by impact 
+of different charged ions \cite{itoh2013,iriki2011,wolff2014,wang2016,
+tribedi2019,agnihotri2012,agnihotri2013,Luna2007,Rudd86,Rudd85,
+Luna_Li_water,DalCappello2009,Tribedi_O_water}, and also by electron 
+impact at sufficiently high velocity \cite{rahman2016,bug2017,wolf2019,
+fuss2009}. As can be noted, most of the data in Fig.~\ref{fig:zreduced} 
+confirms the present scaling, even for O$^{+8}$ in 
+water~\cite{Tribedi_O_water}. However, the data of uracil by swift C, 
+O and F ions in \cite{agnihotri2012,agnihotri2013} are too low compared 
+with our CDW--SSM results, but also as compared with Itoh 
+\textit{et al.} data \cite{itoh2013}, and with the CTMC calculations by 
+Sarkadi \cite{sarkadi2016}. The data for Li$^{+3}$ in water from 
+Ref.~\cite{Luna_Li_water} also spreads out from the present theoretical 
+curves for $E<600$ keV/amu.
 
-The good results obtained in the scaling with the ion charge challenged us to look for a more general scaling rule that could predict values for ionization cross sections of any ion in any molecule. 
-To that end, we resorted to the number of active electrons in each atom $n_e$ proposed in \cite{MendezJPB20}, and combined it with the $Z$-scaling displayed in Fig.~\ref{fig:zreduced}.
+The good results obtained in the scaling with the ion charge challenged 
+us to look for a more general scaling rule that could predict values 
+for ionization cross sections of any ion in any molecule. To that end, 
+we resorted to the number of active electrons in each atom $n_e$ 
+proposed in \cite{MendezJPB20}, and combined it with the $Z$-scaling 
+displayed in Fig.~\ref{fig:zreduced}.
 
-The CDW ionization cross sections $\sigma^{\mathrm{CDW}}$ of atomic H, C, N, O targets scale as $\sigma_e=\sigma^{\mathrm{CDW}}/n_e$ with $n_e$ being $1$ for H, $4$ for C, N, and O, i.e.
+The CDW ionization cross sections $\sigma^{\mathrm{CDW}}$ of atomic H, 
+C, N, O targets scale as $\sigma_e=\sigma^{\mathrm{CDW}}/n_e$ with 
+$n_e$ being $1$ for H, $4$ for C, N, and O, i.e.
 \begin{equation}
@@
 \end{equation}
-The SSM leads to the molecular numbers of active electrons included in Table \ref{nn}.
+The SSM leads to the molecular numbers of active electrons included in 
+Table \ref{nn}.
 
@@
 \end{tabular}
-\caption{Number of active electrons per target at intermediate to high energies obtained from the CDW calculations~\cite{MendezJPB20}.}
+\caption{Number of active electrons per target at intermediate to high 
+energies obtained from the CDW calculations~\cite{MendezJPB20}.}
 \label{nn}
@@
 \includegraphics[width=0.7\textwidth]{zmol_werror.eps}
-\caption{(Color online) Universal scaling with the ions charge $Z$ and the number of active electrons in the molecule $n_e$ given by Eq.
-(\ref{u-scaling}).
-Curves: present CDW-SSM theoretical results.
+\caption{(Color online) Universal scaling with the ions charge $Z$ and 
+the number of active electrons in the molecule $n_e$ given by 
+Eq. (\ref{u-scaling}). Curves: present CDW-SSM theoretical results. 
 Symbols: experimental impact of H$^+$ on 
@@
  \end{equation}
-$\sigma$ is the ionization cross section for the molecular target, $\alpha=1.2$ and $n_e$ is the number of active electrons per molecule given in Table \ref{nn}.
-In Fig.~\ref{fig:zalpha}, we test the universal scaling of Eq.
-(\ref{u-scaling}) for all the theoretical and experimental values displayed in Fig.
-\ref{fig:zreduced}.
-We also included a gray area representing the 30\% deviation of our theoretical curves.
-As can be noted, the universal scaling works very well.
-All the curves and data lays in a narrow band valid for any charged ion (scaled with Z) in any molecule (scaled with the number of active electrons).
-We decided not to include in this figure the data for uracil from Refs.~\cite{agnihotri2012,agnihotri2013}, and for Li$^{+3}$ on water~\cite{Luna_Li_water}.
-The discussion about these experimental values exceeds the present work.
-%is open for future work.
+$\sigma$ is the ionization cross section for the molecular target, 
+$\alpha=1.2$ and $n_e$ is the number of active electrons per molecule 
+given in Table \ref{nn}. In Fig.~\ref{fig:zalpha}, we test the 
+universal scaling of Eq. (\ref{u-scaling}) for all the theoretical and 
+experimental values displayed in Fig. \ref{fig:zreduced}. We also 
+included a gray area representing the 30\% deviation of our theoretical 
+curves. As can be noted, the universal scaling works very well. All the 
+curves and data lays in a narrow band valid for any charged ion (scaled 
+with Z) in any molecule (scaled with the number of active electrons). 
+We decided not to include in this figure the data for uracil from 
+Refs.~\cite{agnihotri2012,agnihotri2013}, and for Li$^{+3}$ on 
+water~\cite{Luna_Li_water}. The discussion about these experimental 
+values exceeds the present work. %is open for future work.
 

### 2020-06-02 scalings/review/response.tex
cleaned folder

\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\setlength{\parindent}{0pt}
\usepackage{soul}
\usepackage{xcolor}
\usepackage[margin=0.8in]{geometry}
\usepackage{graphicx}

\setstcolor{blue}
\def\reviewer#1{\vspace{0.35cm}\textsl{#1}}
\def\reply#1{\vspace{0.1cm}\textcolor{blue}{#1}}

\title{Response to referee reports \\ JPHYSB-106014}

\begin{document}
\maketitle

\reply{We appreciate the comments and questions of the three referees. 
They were taken into account, as explained in the replies to each 
referee. In what follows, the referee reports are in black letters and 
our answers and comments in blue. }

\reply{\textbf{Summary of the modifications:} The manuscript was 
changed from letter to regular manuscript by the editorial board. 
Attending to this fact and the comments by the three referees 
requesting further explanations, we decided to modify the manuscript by
dividing the text into three sections: Introduction, Scaling rules (with
subsections), and Conclusions. Additional specifications of the scaling 
models are given in Section II-A, B, and C. Figure 2 was improved by 
including a gray area of $\pm 30\%$ that covers most of the available 
data. Also, experiments for H$^+$ and He$^{+2}$ in water (missing in 
the previous version) were added to the figures (Refs. 25, 26, and 27), 
extending the energy range where the present scaling agrees with the 
experimental data. 
% the agreement of the present scaling for H$^+$ in water above 40 keV 
% and He$^{+2}$ in water up to 10 MeV/amu. 
Following the suggestion by one of the referees, we changed the title 
from ``Universal scaling for the ionization...'' to ``Scaling 
rules for the ionization...''}.

% ----------------------------------------------------------------------
\section{Reply to report of the First Referee}
% ----------------------------------------------------------------------

\reviewer{The authors propose the universal scaling law of the 
ionization cross sections by the impact of multiply charged atomic ions 
on the basis of the experimental data reported in their very recent 
publication [J. Phys. B, 53, 055201 (2020)]. Their conclusion of this 
newly submitted paper is that they found the scaling law of Eq. (1) 
with the alpha value of 1.2. However, as the authors mention in the 
introduction part, the same scaling law with the alpha value of 
4/3 = 1.333 was reported in 2013 by DuBois et al. [Ref. 15]. The 
authors should explain if the scaling with alpha = 4/3, which is very 
close to their value of 1.2, could not explain the experimental data 
they recorded. If the value of 1.2 is much better than 1.333, the 
author should explain possible reason why alpha should be 1.2 on the 
basis of the physical meaning of the parameter alpha.}

\vspace{0.2cm}

\reply{The value of $\alpha=1.2$ was found numerically as the best
convergence of the CDW-SSM cross sections of the forty collisional 
systems over the broadest energy range. Our methodology does not rely 
on the fitting of experimental data. The work considers the scaling of 
our theoretical results, which is tested afterward with the 
experimental data. We also noticed that all the maxima of the 
theoretical cross sections scaled with $\alpha=1.2$ lay at the same 
value of $E/Z^{2-\alpha}=E/Z^{0.8}$. In the present version of our 
manuscript, we modified lines 59-61 to clarify our choice of $\alpha$.}

\reply{About the  physical meaning of this parameter, the scaling by
Janev et~al.~[14] uses $E/Z^1$ as abscissa based on the long-distance
approximation for the ionization cross sections. Similarly, DuBois 
et~al.~[15] propose $E/Z^{2/3}$. The 2/3 in Ref.~[15] was found by 
trial and error. However, the dependence with $Z^{2/3}$ recalls the 
Thomas Fermi model for a constant density of electrons around the ion. 
% Also in [15], it is mentioned that $E/Z^{0.88}$ joins  the maximum of 
% the cross sections of He and H$_2$. 
In either case, both models are approximations, and our numerical 
proposal of $\alpha$ is located between them.}

\vspace{0.2 cm}
% ----------------------------------------------------------------------
\section{Reply to report of the Second Referee}

The authors propose a scaling formula for cross sections for ionization
of complex molecules by multiply charged ions. Such cross sections are
required, e.g., for estimating radiation damage in biomolecules. A
routine ab-initio calculation of such cross sections by quantum methods
is beyond reach of the state-of-the-arts methods. In this situation, 
it is helpful to have semi-empirical scaling formulas for modeling
purposes. Thus, the paper is timely and serves a need. It is concise.
However, there are some language issues. The paper should eventually be
published as a JPB letter after the authors having adequately responded
to my detailed points below.

% ----------------------------------------------------------------------

\vspace{0.2cm}

\reply{The points 1)-4), 6) and 7) raised by the referee are language
corrections. They were all considered and modified in the manuscript
where appropriate.}

%\reviewer{1) page1, line 11: `` ... from +1 to +8 colliding with five ...''}
%\reviewer{2) page 1, line 14: `` ... fourty ...''}
%\reviewer{3) page 1, line 26: `` ... continuum distorted-wave ...''}
%\reviewer{4) page 1, line 42: ``... first order approximation in experimental ...''}
%\reviewer{6) page 1, line 20, column 2: ``... fourty ...''}
%\reviewer{7) page 1, line 24,, column 2: `` ... and five ion species: ...''}

\reviewer{5) page 1, line 53: I do not see how any value for alpha keeps
the $Z^2/E$ relationship? $\alpha = 1.2$ results in $Z^{0.8}/E$.}

\reply{In first order approaches, the ionization cross section $\sigma$
depends linearly with $Z^2/E$. This dependence is valid in the first Born 
approximation, and at high impact energies, $\sigma/Z^{2}$ scales with
$E$ for any charged ion. Within this approximation, $\sigma/Z^{\alpha}$
will be a function of $Z^{2-\alpha}/E$ for any value of $\alpha$. At
intermediate energy, the linear dependence with $Z^2/E$ no longer holds,
so we numerically sought for the value of $\alpha$ that best merges
the cross sections for different impinging charges.}

\reviewer{8) Figure captions. Both caption should mention that all 
plots are for alpha=1.2.}

\reply{Done.}

\reviewer{9) page 2, line 40, column 2: How broad is the ``narrow 
band''? The authors should supply some estimate for the uncertainty of 
the scaling formula. I consider this very important.}

\reply{We estimated the uncertainty of the scaling formula to 20\% for 
the theoretical curves of the different targets, and 30\% to incorporate 
most of the available data. The gray area drawn in Fig.~2 accounts for 
this uncertainty. We also included a sentence to refer to this subject 
in lines 119-122.}

\vspace{0.2 cm}
% ----------------------------------------------------------------------
\section{Reply to report of the Third Referee}
% ----------------------------------------------------------------------

This paper tries to obtain a scaling law for ionization of some 
biological molecules by highly charged ions. As is well known, such
processes are quite relevant and important in medical physics. Since 
the molecules considered are complex, formal theories of ionization are
difficult to apply and scaling laws, if found applicable, greatly 
simplify the process of obtaining reliable cross sections. In this
respect the present paper is quite significant. The authors have
proposed a scaling law and have applied it to several bio molecules 
and have tried to extend and justify the validity of the scaling law 
by including results for N2, O2, CO, CO2 and CH4 to show they have the
same scaling behaviour. However, there are several aspects of the paper
which I either do not understand clearly, or have reservations.

\reviewer{1. The authors mention $\sigma$ to be a function of $E/Z$. 
But the functional form is nowhere mentioned in the paper. What is the
functional dependence on $E/Z$ the authors consider in the work?}

\reply{In different energy regions, the ionization cross section 
follows different $Z/E$ laws. At high energies, it is a function of 
$Z^2/E$, as predicted by the first Born approximation. The CDW 
approximation has a more complex dependence with $Z/E$ but tends to the
Born approximation at high energies, as shown in our previous work [8]. 
The objective of this manuscript is precisely to deepen into the study 
of the dependence of the ionization cross sections with $Z$ and $E$ in 
the intermediate energy region. Janev and Presnyakov [14], in their 
paper from 1980, suggest that $\sigma/Z$ is a linear function of $E/Z$ 
at intermediate energies (around the maximum of the cross sections).}

\reply{In this version, we further explained the models and cross 
section dependence with $E/Z$ (line 24 and the second paragraph of 
Section II A).}

\reviewer{2. I have reservations in calling the scaling law developed 
a universal scaling law. Not only have the authors considered only 8
molecular targets and five incident ions, the results, as the authors
claim, are applicable only around the maximum of the cross sections. 
Though this may be reasonable for practical purposes, in my opinion, 
the results are in too narrow range for calling it a universal scaling
law. I would recommend dropping the word universal everywhere in the
paper.}

\reply{We called our scaling ``universal'' in the sense that it can be
implemented for any ion-target combination within the intermediate 
energy range, i.e., $E/Z^{0.8} \simeq (0.04-5)$ MeV/amu. Nevertheless, 
we followed the referee's recommendation and dropped the word 
``universal'' from the title and the rest of the manuscript. Instead, 
we emphasized the independent nature of the reduced scaling law for 
different ions and molecular targets. We also remaked that even 
the experimental data (in the energy range where our theoretical method
starts to fail) follows the scaling proposed. In that sense, we changed
the last sentence of the abstract, Section II C (lines 127-130, 136),
and the Conclusions (lines 140-154, 157-160).}

\reviewer{3. Figure 1 somehow needs to be improved or made larger,
because it is very difficult to gauge the deviation of the experimental
points from the curves. Is it possible to separate the figure in to two
figures (eg. top four Figure 1, bottom four Figure 2)?}

\reply{Separating Fig.~1 would complicate the ratio of the figure; 
instead, we considered convenient to make the figure larger to utilize 
the space better. We have also reduced the scale of the y-axis of the 
subplots to improve the visualization of the data.}

\reviewer{4. Figure captions need to be significantly improved as it is
difficult to read and correlate the legend descriptions with those in
the figure. For the caption in Figure 2, it is not clear what the
CDW-SSM theoretical results represent ? What is the target molecule
considered?}

\reply{We believe the confusion about Fig.~2 is originated from 
inconsistencies in the text. Figure~2 shows a scaling that is 
independent of the ion charge of the projectile and the molecular 
target. All the figures have the same CDW-SSM results as inputs. We 
improved the explanation about our calculations by adding the last 
paragraph of Section II B (and Eq. (2)), and the first sentence of 
Section II. C. The notation of Eq. (3) was slightly changed to underline 
that the starting point is the CDW-SSM cross sections for molecules.}

%\reviewer{5. The language should be considerably improved as there are many unusual statements.}

%\reviewer{6. There are many typographical errors.}

\vspace{0.5cm}
\reply{Regarding points 5) and 6), we revised our manuscript and we 
believe it has been considerably improved.}

\end{document}

### 2020-06-02 scalings/justification.tex
cleaned folder

\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}

\begin{document}
% If you want headings on subsequent pages,
% remove the ``%'' on the next line:
\pagestyle{headings}
\date{}% It is always \today, today,

\begin{letter}{}

\opening{}

\begin{center}
\it Justification for Accelerated Publication in Environmental Research Letters
\end{center}

We are submitting electronically a paper entitled:
``Universal scaling for the ionization of biological molecules by 
highly charged ions'' by A.M.P. Mendez, C.C. Montanari and J.E. Miraglia.
The present manuscript is a follow up of previous work [Mendez {\it et al.}
J. Phys B (2020)]. In this letter, we present a scaling for the 
ionization cross sections of highly charged ions in biological targets.
The scaling 
was obtained by means of the CDW--SSM calculations for forty ions--molecule
systems and tested with the available experimental 
data. 
A universal scaling rule is also proposed, which reduced the 
cross sections with the number of active electrons of the molecule. 
The universal scaling proved to be valid for a large number of 
experimental data.

The importance of our scaling rule lays in its predictive capability, 
which is useful in experimental measurements and multipurpose codes.
We believe that our model will appeal to a wide audience, particularly 
for those interested in biological and complex molecules.

\signature{A.M.P. Mendez}

%enclosure listing
%\encl{}

\end{letter}
\end{document}

### 2020-06-02 scalings/scalings.tex
cleaned folder

--- 2020-05-27 zscaling/overleaf/zscaling_overleaf.tex
@@
 \definecolor{olive}{RGB}{182,187,37}
-\usepackage[mathlines]{lineno}% Enable numbering of text and display math
-%\linenumbers\relax % Commence numbering lines
+\usepackage[mathlines]{lineno}
 
@@
 \author{A. M. P. Mendez, C. C. Montanari, J. E. Miraglia}
-\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio 
-(CONICET-UBA), \\ Buenos Aires, Argentina.}
-
-\date{\today}% It is always \today, today,
+\affiliation{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio, 
+Consejo Nacional de Investigaciones Cient\'ificas y T\'ecnicas - 
+Universidad de Buenos Aires, Pabll\'on IAFE, 1428 Buenos Aires, 
+Argentina}
 
@@
 guanine, thymine, uracil--, tetrahydrofuran, pyrimidine, and water. 
-We investigate %the scaling 
-scaling rules of the ionization cross section with 
+We investigate scaling rules of the ionization cross section with 
 the ion charge and the number of active electrons per molecule. 
-%valid in the intermediate to 
-%high energy range, i.e., 0.2-5 MeV/amu for oxygen impact. 
-% Furthermore, 
-% we introduce a modified scaling rule, which takes into account the 
-% number of active electrons per molecule. 
-Combining these two features, we define a scaling law  for any ion and molecular target %independent of  the ion charge and the complexity of the molecular target
-, which is 
-valid in the intermediate to high energy range, i.e., 0.2-5 MeV/amu for oxygen impact. %Then, 
-Thus, the forty 
+Combining these two features, we define a scaling law for any ion and 
+molecular target, which is valid in the intermediate to high energy 
+range, i.e., 0.2-5 MeV/amu for oxygen impact. Thus, the forty 
 ion-molecule systems analyzed here can be merged into a single band. 
@@
 \maketitle
-%\ioptwocol
-\linenumbers
 
@@
 
-This contribution constitutes a follow-up of our previous work~\cite{MendezJPB20}. We 
-introduce here a two-folded scaling rule for the ionization cross 
-sections of complex molecules by charged ions. Our approach considers 
-the dependence of the cross section with the ion charge $Z$ 
-and incorporates the scaling of the ionization with the number of 
-active electron $n_e$ of the molecular targets. Scaling rules are 
-generally very useful since they can be used as first-order 
+This contribution constitutes a follow-up to our previous 
+work~\cite{MendezJPB20}. We introduce here a two-folded scaling rule 
+for the ionization cross sections of complex molecules by charged ions. 
+Our approach considers the dependence of the cross section with the ion 
+charge $Z$ and incorporates the scaling of the ionization with the 
+number of active electron $n_e$ of the molecular targets. Scaling rules 
+are generally very useful since they can be used as first-order 
 approximations in experimental measurements and multipurpose codes.
@@
 \centering
-\includegraphics[width=0.87\textwidth]{zscale_alpha.eps}
+\includegraphics[width=0.9\textwidth]{zscale_alpha-wref.eps}
 \caption{(Color online) Scaled ionization cross section $\sigma/Z^{\alpha}$ 
-as a function of ion impact energy $E/Z^{2-\alpha}$ with $\alpha=1.2$. 
+as a function of the ion impact energy $E/Z^{2-\alpha}$ with $\alpha=1.2$. 
 Colors are associated with the incident ion labeled on top of the figure. 
-Curves: present CDW-SSM theoretical results. Symbols: experimental 
-impact of \mbox{\LARGE$\color{red}\circ$} H$^+$~\cite{iriki2011} and
-{\fontsize{11}{20}$\color{Purple}\pmb{\lozenge}$} C$^{+6}$ 
-\cite{tribedi2019} on adenine;
-H$^+$ on {\fontsize{11}{20}$\color{red}\pmb{\triangle}$} uracil~\cite{itoh2013}, 
-{\fontsize{11}{20}$\color{NavyBlue}\pmb{\ominus}$} C$^{+4}$, 
-{\fontsize{11}{20}$\color{Purple}\pmb{\oplus}$} C$^{+6}$, O$^{+6}$, F$^{+6}$, and 
-{\fontsize{11}{20}$\color{BurntOrange}\pmb{\otimes}$} O$^{+8}$, 
-F$^{+8}$ on uracil~\cite{agnihotri2012,agnihotri2013};
-H$^+$ on {\fontsize{11}{20}$\color{red}\pmb{\triangledown}$} 
-pyrimidine~\cite{wolff2014}, and 
-{\fontsize{10}{20}$\color{red}\pmb{\meddiamond}$} THF~\cite{wang2016};
-% water
-\mbox{\fontsize{11}{20}$\color{red}\pmb{\odot}$}~\cite{Luna2007}, 
-{\fontsize{11}{20}\color{red}$\pmb{\logof}$}~\cite{Rudd86}, 
-{\fontsize{11}{20}\color{red}$\pmb{\varowedge}$}~\cite{pRudd85}, 
-{\fontsize{11}{20}\color{red}$\pmb{\varoslash}$}~\cite{toburen80} H$^+$,
-{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varolessthan}$}~\cite{Ohsawa05},
-{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varogreaterthan}$}~\cite{Rudd85},
-{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varoslash}$}~\cite{toburen80} He$^{+2}$,
-{\fontsize{11}{20}\color{Purple}$\pmb{\ovee}$}~C$^{+6}$ \cite{DalCappello2009,Bhattacharjee17}, and 
-{\fontsize{11}{20}\color{BurntOrange}$\pmb{\obslash}$}
-O$^{+8}$ \cite{Tribedi_O_water} on water.
-Markers~$\square$~\cite{rahman2016}, 
-$\rhd$~\cite{bug2017}, 
-$\lhd$~\cite{wolf2019}, and 
-$\medstar$~\cite{fuss2009} correspond to electron impact ionization with 
-the equi-velocity conversion.}
+Curves: present CDW-SSM theoretical results. 
+Symbols: experimental data~\cite{itoh2013,iriki2011,wolff2014,wang2016,
+tribedi2019,agnihotri2012,agnihotri2013,Luna2007,Rudd86,pRudd85,
+toburen80,Ohsawa05,Bhattacharjee17,Luna_Li_water,DalCappello2009,
+Tribedi_O_water}. Electron impact ionization values~\cite{rahman2016,
+bug2017,wolf2019,fuss2009} are included with the corresponding 
+equi-velocity conversion.}
 \label{fig:zreduced}
@@
 to the intermediate impact energy range. The rule suggested by Janev 
-and Presnyakov~\cite{janev1980} 
-%depends linearly with ion charge $Z$, considering 
-considers $\sigma/Z$ versus $E/Z$ to be the \textit{natural} reduced  
-form of the ionization cross section $\sigma$ and the incident ion energy $E$. More recently, Montenegro and co-workers~\cite{dubois13,
-montenegro_pra13} suggested an alternative scaling by taking into 
-account that the cross section is a function of $Z^2/E$ at high 
-energies. Their scaling, given by 
+and Presnyakov~\cite{janev1980} considers $\sigma/Z$ versus $E/Z$ to be 
+the \textit{natural} reduced form of the ionization cross section 
+$\sigma$ and the incident ion energy $E$. More recently, Montenegro and 
+co-workers~\cite{dubois13,montenegro_pra13} suggested an alternative 
+scaling by taking into account that the cross section is a function of 
+$Z^2/E$ at high energies. Their scaling, given by 
 \begin{equation}
@@
 ion-target systems~\cite{itoh2013,iriki2011,wolff2014,wang2016,
-tribedi2019,agnihotri2012,agnihotri2013,Luna2007,Rudd86,Rudd85,pRudd85,
+tribedi2019,agnihotri2012,agnihotri2013,Luna2007,Rudd86,pRudd85,
 toburen80,Ohsawa05,Bhattacharjee17,Luna_Li_water,DalCappello2009,
-Tribedi_O_water} with the $Z^\alpha$-scaling rule. For targets with none or little experimental data, we included
-electron impact ionization results~\cite{rahman2016,bug2017,wolf2019,
-fuss2009} at high velocity with the corresponding equivelocity 
-conversion.
-As can be noted, 
-most of the data in Fig.~\ref{fig:zreduced} confirm the present 
-scaling, even for O$^{+8}$ in water~\cite{Tribedi_O_water}. 
-Only two data sets are off our predictions: the ionization cross sections of 
-uracil by swift C, O, and F ions from 
-Refs~\cite{agnihotri2012,agnihotri2013}% are too low  compared with our CDW-SSM results
-; and the values 
-for Li$^{+3}$ in water from Ref.~\cite{Luna_Li_water} %spread out from the present theoretical curves
-for $E<600$~keV/amu. 
-In the case of uracil, recent CTMC calculations by Sarkadi~\cite{sarkadi2016} are also above the experimental values by Tribedi group~\cite{agnihotri2012,agnihotri2013}.
+Tribedi_O_water} with the $Z^\alpha$-scaling rule. For targets with 
+none or little experimental data, we included electron impact 
+ionization results~\cite{rahman2016,bug2017,wolf2019,fuss2009} at high 
+velocity with the corresponding equivelocity conversion. As can be 
+noted, most of the data in Fig.~\ref{fig:zreduced} confirm the present 
+scaling, even for O$^{+8}$ in water~\cite{Tribedi_O_water}. Only two 
+data sets are off our predictions: the ionization cross section of 
+uracil by swift C, O, and F ions from Refs.~\cite{agnihotri2012,
+agnihotri2013}, and the values for Li$^{+3}$ in water from 
+Ref.~\cite{Luna_Li_water} for $E<600$~keV/amu. In the case of uracil, 
+recent CTMC calculations by Sarkadi~\cite{sarkadi2016} are also above 
+the experimental values by Tribedi and collaborators~\cite{agnihotri2012,
+agnihotri2013}.
 
@@
 
-In our previous work, we noticed that the CDW ionization cross 
-sections, $\sigma_A$, of atomic targets H, C, N, and O  scale with the number of
+In our previous work, we noticed that the CDW ionization cross sections 
+$\sigma_A$ of atomic targets H, C, N, and O scale with the number of 
 active electrons per atom $\nu_A$, as \mbox{$\sigma_e=\sigma_A/\nu_A$,} 
@@
 \end{equation}
-By %considering
-means of the SSM, we define the number of active electrons per
+By means of the SSM, we define the number of active electrons per 
 molecule as $n_e=\sum_A n_A \nu_A$. The $n_e$ values for the 
-molecular targets considered throughtout this work are displayed in 
+molecular targets considered throughout this work are displayed in 
 Table~\ref{nn}. The scaling with the molecular number of active
@@
 
-By incorporating the $Z^\alpha$ reduction and the scaling with the %molecular 
-number  of active electrons% scaling
-, we introduce the scaled and reduced
+By incorporating the $Z^\alpha$ reduction and the scaling with the 
+number of active electrons, we introduce the scaled and reduced 
 ionization cross section of molecules $\tilde{\sigma}$, which is 
@@
 \end{equation}
-where $\sigma_M$ is the ionization cross section for the molecular target, 
-$n_e$ is the number of active electrons per molecule displayed in 
-Table~\ref{nn} and the parameter is $\alpha=1.2$.
-Fig.~\ref{fig:zalpha} shows the %reduced-scaled 
-theoretical and 
-experimental values of $ \tilde{\sigma}$ (given by Eq.~(\ref{eq:u-scaling})) %data 
-for all the systems displayed in Fig.~\ref{fig:zreduced}% obtained using Eq.~(\ref{eq:u-scaling})
-. As can be noted, the scaling works very well
-and is independent of the ion charge or the complexity of the molecular
-target. 
-Our theoretical curves lay in a narrow band valid for any charged ion 
-(reduced with $Z^\alpha$) in any molecule (scaled with the number of 
-active electrons) with a dispersion of about 20\%. If we consider
-the experimental data, the uncertainty of our scaling grows to 30\%, 
-which is coverd by %shown with 
-the gray area in Fig.~\ref{fig:zalpha}.
-It is worth noting that we did not include in this figure %Fig.~\ref{fig:zalpha}
-the data for uracil from Refs.~\cite{agnihotri2012,agnihotri2013}, 
-and for Li$^{+3}$ on water~\cite{Luna_Li_water}. The discussion 
-about these experimental values exceeds the present work.
+where $\sigma_M$ is the ionization cross section for the molecular 
+target, $n_e$ is the number of active electrons per molecule displayed 
+in Table~\ref{nn}, and the parameter is $\alpha=1.2$. 
+Fig.~\ref{fig:zalpha} shows the theoretical and experimental values of 
+$\tilde{\sigma}$ (given by Eq.~\ref{eq:u-scaling}) for all the systems 
+displayed in Fig.~\ref{fig:zreduced}. As can be noted, the scaling 
+works very well and is independent of the ion charge or the complexity 
+of the molecular target. Our theoretical curves lay in a narrow band 
+valid for any charged ion (reduced with $Z^\alpha$) in any molecule 
+(scaled with the number of active electrons) with a dispersion of about 
+$\pm 20\%$. If we consider the experimental data, the uncertainty of 
+our scaling grows to $\pm 30\%$, which is schematized in 
+Fig.~\ref{fig:zreduced} with a gray area. It is worth noting that we 
+did not include in this figure the data for uracil from 
+Refs.~\cite{agnihotri2012,agnihotri2013}, and Li$^{+3}$ on 
+water~\cite{Luna_Li_water}. The discussion about these experimental 
+values exceeds the present work.
 
-\begin{figure*}[!htb]%[h]
+\begin{figure*}[!htb]
 \centering
-\includegraphics[width=0.75\textwidth]{zmol_werror.eps}
+\includegraphics[width=0.8\textwidth]{zmol_werror-wref.eps}
 \caption{(Color online) Ionization cross section reduced with the ion
@@
 Curves: present CDW-SSM theoretical results. 
-Symbols: experimental impact of H$^+$ on 
-\mbox{\LARGE$\color{red}\circ$} adenine~\cite{iriki2011}, 
-{\fontsize{11}{20}$\color{red}\pmb{\triangle}$} uracil~\cite{itoh2013}, 
-{\fontsize{11}{20}$\color{red}\pmb{\triangledown}$} pyrimidine~\cite{wolff2014} and 
-{\fontsize{10}{20}$\color{red}\pmb{\meddiamond}$} THF~\cite{wang2016};
-{\fontsize{11}{20}$\color{Purple}\pmb{\lozenge}$} C$^{+6}$ on adenine \cite{tribedi2019};
-\mbox{\fontsize{11}{20}$\color{red}\pmb{\odot}$}~\cite{Luna2007}, 
-{\fontsize{11}{20}\color{red}$\pmb{\logof}$}~\cite{Rudd86}, 
-{\fontsize{11}{20}\color{red}$\pmb{\varowedge}$}~\cite{pRudd85}, 
-{\fontsize{11}{20}\color{red}$\pmb{\varoslash}$}~\cite{toburen80} H$^+$,
-{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varolessthan}$}~\cite{Ohsawa05},
-{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varogreaterthan}$}~\cite{Rudd85},
-{\fontsize{11}{20}\color{ForestGreen}$\pmb{\varoslash}$}~\cite{toburen80} He$^{+2}$,
-{\fontsize{11}{20}\color{Purple}$\pmb{\ovee}$}~C$^{+6}$ \cite{DalCappello2009,Bhattacharjee17}, and 
-{\fontsize{11}{20}\color{BurntOrange}$\pmb{\obslash}$}
-O$^{+8}$ \cite{Tribedi_O_water} on water.
-H$^{+}$ impact on 
-{\fontsize{11}{20}${\color{red}\pmb{\boxast}}$}~N$_2$, 
-{\fontsize{11}{20}${\color{red}\pmb{\boxbox}}$}~O$_2$, 
-{\fontsize{11}{20}${\color{red}\pmb{\boxbar}}$}~CO, 
-{\fontsize{11}{20}${\color{red}\pmb{\boxbslash}}$}~CO$_2$, and
-{\fontsize{11}{20}${\color{red}\pmb{\boxdot}}$}~CH$_4$; 
-and He$^{+2}$ impact on 
-{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxast}}$}~N$_2$,
-{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxbox}}$}~O$_2$, 
-{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxbar}}$}~CO, 
-{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxbslash}}$}~CO$_2$, and
-{\fontsize{11}{20}${\color{ForestGreen}\pmb{\boxdot}}$} 
-CH$_4$~\cite{Rudd85,Rudd1983}, 
-{\fontsize{11}{20}${\color{red}\pmb{\varowedge}}$}~H$^{+}$ on 
-CH$_4$~\cite{Luna2019}; 
-and electron impact on $\rhd$~pyrimidine~\cite{bug2017}, and $\lhd$, 
-$\medstar$~\cite{wolf2019,fuss2009} THF.}
+Symbols: experimental data~\cite{itoh2013,iriki2011,wolff2014,wang2016,
+tribedi2019,Luna2007,Rudd86,pRudd85,toburen80,Ohsawa05,Bhattacharjee17,
+DalCappello2009,Tribedi_O_water,Rudd85,Luna2019,Rudd1983}. Electron 
+impact ionization values~\cite{rahman2016,bug2017,wolf2019,fuss2009} 
+are included with the corresponding equi-velocity conversion.}
 \label{fig:zalpha}
@@
 
-We consider this scaling robust enough to be valid for different 
-ion--molecule combinations. We tested the generality of our model 
-by including in Fig.~\ref{fig:zalpha} several data sets of 
+We consider the present scaling robust enough to be valid for different 
+ion-molecule combinations. We tested the generality of our model 
+by including in Fig.~\ref{fig:zreduced} several data sets of 
 molecular targets not considered previously, such as the measurements 
 by Rudd~\textit{et al.}~\cite{Rudd85,Rudd1983} for H$^{+}$ and He$^{+2}$ 
-in N$_2$, O$_2$, CH$_4$, CO and CO$_2$, and the recent values by 
-Luna~\textit{et al.} \cite{Luna2019} for H$^{+}$ in CH$_4$.
+in N$_2$, O$_2$, CH$_4$, CO and CO$_2$, and recent values by 
+Luna~\textit{et al.} \cite{Luna2019} for H$^{+}$ in CH$_4$ .
 
-The good agreement shown in Fig.~\ref{fig:zalpha} summaries the main 
-result of this work, and holds the validity of the present scaling for different ions and targets.
-%with the ion charge and the number of active electrons in the target. 
-Although the theoretical CDW-SSM results are valid for energies above 
-the maximum of the cross sections, %it is worth noting from Fig.~\ref{fig:zalpha} that 
-the scaling of the experimental data extends 
-even to lower impact energies, as can be noted in Fig.~\ref{fig:zalpha}. 
-New measurements for other ions and molecules are expected to 
-reinforce the present proposal.
+The good agreement shown in Fig.~\ref{fig:zalpha} summarizes the main 
+result of this work and holds the validity of the present scaling for 
+different ions and targets. Although the theoretical CDW-SSM results 
+are valid for energies above the maximum of the cross sections, the 
+scaling of the experimental data extends even to lower impact energies, 
+as can be noted in Fig.~\ref{fig:zalpha}. New measurements for other 
+ions and molecules are expected to reinforce the present proposal.
 
@@
 scaling reduces the nature of the projectile by scaling the cross 
-section with the ion charge, $Z^{\alpha}$, as a function of the 
-reduced impact energy $E/Z^{2-\alpha}$, with $\alpha=1.2$. The second
-scaling considers the molecular characteristic of the target by taking 
-into account the number of active electrons per molecule, $n_e$. 
-The last scaling law combines the $Z^{\alpha}$-reduction with the
-$n_e$-scaling 
-of cross section, and it becomes independent of the ion charge and 
-the molecular target. The scalings are obtained by means of 
-CDW-SSM calculations for five different charged ions in eight targets 
-and tested with the available experimental data. The generality of our
-independent scaling is proved to be valid in a wide energy range 
-by considering a significant number of experimental data sets for 
-other collisional systems.
+section with the ion charge, $Z^{\alpha}$, as a function of the reduced 
+impact energy $E/Z^{2-\alpha}$, with $\alpha=1.2$. The second scaling 
+considers the molecular description of the target by taking into 
+account the number of active electrons per molecule, $n_e$. The last 
+scaling law combines the $Z^{\alpha}$-reduction with the $n_e$-scaling 
+of the cross section, and it becomes independent of the ion charge and the 
+molecular target. The scalings are obtained by means of CDW-SSM 
+calculations for five different charged ions in eight targets and 
+tested with the available experimental data. The generality of our 
+independent scaling is proved to be valid in a wide energy range by 
+considering a significant number of experimental data sets for other 
+collisional systems.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Acknowlegments}
+\section{Acknowledgments}
 
 This work was finantially supported by Consejo Nacional de
-Investigaciones Cient\'ificas y T\'ecnicas (CONICET), Agencia 
-Nacional de Promoci\'on Cient\'ifica y Tecnol\'ogica (ANPCyT), 
-and Universidad de Buenos Aires (UBA).
+Investigaciones Cient\'ificas y T\'ecnicas (PIP 2014), Agencia 
+Nacional de Promoci\'on Cient\'ifica y Tecnol\'ogica (PICT 2017-2945), 
+and Universidad de Buenos Aires (UBACyT 20020170100727).
 
@@
 
-% our ---------------------------------------------------------
+% ours ---------------------------------------------------------
 \bibitem{MendezJPB20}
@@
 % Experimental data ----------------------------------------------
-
-\bibitem{itoh2013} 
-A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D. Rivarola, 
-Phys. Rev. A \textbf{88}, 052711 (2013).
-
+%17
 \bibitem{iriki2011}
@@
 Phys. Rev. A \textbf{84}, 052719 (2011). 
-
-%\bibitem{Tabet2010} J. Tabet, S. Eden, S. Feil, H. Abdoul-Carime, B. Farizon, M. Farizon, S. Ouaskit, and T. D. Mark, Phys. Rev. A \textbf{82}, 022703 (2010).
-
-\bibitem{wolff2014}
-W. Wolff, H. Luna, L. Sigaud, A. C. Tavares, and E. C. Montenegro
-J. Chem. Phys. \textbf{140}, 064309 (2014).
-
-\bibitem{wang2016}
-M. Wang, B. Rudek, D. Bennett, P. de Vera, M. Bug, T. Buhr, W. Y. Baek,
-G. Hilgers, H. Rabus, 
-Phys. Rev. A \textbf{93}, 052711 (2016).
-
+%18
 \bibitem{tribedi2019} 
@@
 Phys. Rev. A \textbf{100}, 012703(2019).
-
+%19
+\bibitem{itoh2013} 
+A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D. Rivarola, 
+Phys. Rev. A \textbf{88}, 052711 (2013).
+%20
 \bibitem{agnihotri2012}
@@
 Phys. Rev. A \textbf{85}, 032711 (2012).
-
+%21
 \bibitem{agnihotri2013}
@@
 J. Phys. B: At. Mol. Opt. Phys. \textbf{46}, 185201 (2013).
-
+%22
+\bibitem{wolff2014}
+W. Wolff, H. Luna, L. Sigaud, A. C. Tavares, and E. C. Montenegro
+J. Chem. Phys. \textbf{140}, 064309 (2014).
+%23
+\bibitem{wang2016}
+M. Wang, B. Rudek, D. Bennett, P. de Vera, M. Bug, T. Buhr, W. Y. Baek,
+G. Hilgers, H. Rabus, 
+Phys. Rev. A \textbf{93}, 052711 (2016).
+%24
 % H+ in water-------------------------------------
@@
 Phys. Rev. A \textbf{75}, 042711 (2007).
-
+%25
 \bibitem{Rudd86} 
@@
 Phys. Rev. A \textbf{33}, 888 (1986). 
-
+%26
 \bibitem{pRudd85} 
@@
 Phys. Rev. A \textbf{31}, 492 (1985). 
-
+%27
 \bibitem{toburen80} 
@@
 Radiat. Res. \textbf{82}, 27--44 (1980).
-
+%28
 % He$^{+2}$ in water---------------------
@@
 Phys. Rev. A \textbf{72}, 062710 (2005).
-
+%29
+% He+2 in H2 N2 O2 CO CO2 CH4 N2O
 \bibitem{Rudd85} 
@@
 Phys. Rev. A \textbf{32}, 2128 (1985).
-
+%30
 % Li$^{+3}$ in water---------------------------
@@
 Phys. Rev. A \textbf{93}, 052705 (2016).  
-
+%31
 % C$^{+6}$ in water--------------------------
@@
 Nuclear Instruments and Methods in Physics Research B 267 (2009) 781--790.
-
+%32
 \bibitem{Bhattacharjee17}
@@
 Phys. Rev A \textbf{96}, 052707 (2017).
-
+%33
 %O$^{+8}$ in water -------------------------------
@@
 Phys. B: At. Mol. Opt. Phys. \textbf{49,}  065202 (2016).
-
+%34
 % electron impact --------------------------
@@
 J. Chem. Phys. \textbf{144}, 161102 (2016).
-
+%35
 \bibitem{bug2017}
@@
 Rad. Phys. Chem. \textbf{130}, 459--479 (2017).
-
+%36
 \bibitem{wolf2019}
@@
 J. Chem. Phys. \textbf{151}, 064304 (2019).
-
+%37
 \bibitem{fuss2009}
@@
 Phys. Rev. A \textbf{80}, 052709 (2009).
-
-\bibitem{sarkadi2016} L. Sarkadi, J. Phys. B: At. Mol. Opt. Phys. \textbf{49} 185203 (2016).
-
-% H+ in CH4 and CO2-----------------------------------------
+%38
+\bibitem{sarkadi2016}
+L. Sarkadi, 
+J. Phys. B: At. Mol. Opt. Phys. \textbf{49} 185203 (2016)
+%39
+% H+ in H2 N2 O2 CO CO2 CH4 N2O
 \bibitem{Rudd1983} 
@@
 Phys. Rev. A \textbf{28}, 3244 (1983).
-
+%40
+% H+ in CH4
 \bibitem{Luna2019} 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%, %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{thebibliography}
